### 2020-03-05 asymp_report_disease.abs.tex
Compiling

{\footnotesize We analyze a mechanistic model of a coronavirus-like pathogen
to assess the impact of asymptomatic cases on epidemic potential
-- as measured both by the basic reproduction
number and the fraction of new secondary cases attributable to asymptomatic
individuals. As we show, the impact of asymptomatic
cases depends on the interval over which asymptomatic cases
are infectious.  If the infectious duration of asymptomatic cases differs than that 
of symptomatic cases, then estimates of the basic reproductive ratio which do not explicitly account for asymptomatic cases may be systematically biased. Specifically, if asymptomatic cases have a shorter duration, 
${\cal{R}}_0$ will be over-estimated, and if they have a longer duration, ${\cal{R}}_0$ will be under-estimated.
%If infectiousness of asymptomatic cases is relatively short/long in duration compared
%to symptomatic cases, then
%estimates of the basic reproduction number may be over/under-estimates
%compared to estimates only attributing secondary cases to symptomatic cases.
The analysis provides a rationale for assessing the duration of asymptomatic cases 
of COVID-19 in addition to their prevalence in the population.
}

### 2020-03-05 short.body.tex
Rejiggering

Epidemic outbreaks include a spectrum of illness, including
asymptomatic cases that can be mild and/or subclinical.
As such, symptomatic cases are the predominant focus of treatment and usually represent
the bulk of reported cases. However, infected individuals who are asymptomatic
yet infectious can be a critical, albeit poorly characterized
factor in the spread of pathogens, as well as 
present challenges for control.
Asymptomatic individuals
are hard to trace, unlikely to self-isolate,
may move outside of quarantine,  
retain normal social and travel patterns, and potentially spark new
outbreaks.
The COVID-19 outbreak has raised significant
questions regarding the role of asymptomatic cases~\citep{fauci_nejm2020}.
%For example, the incidence of asymptomatic
%infection was estimated to be
%approximately 33\% (or higher) 
%from an outbreak of COVID-19 on the Princess Cruises ship~\citep{mizumoto_2020}.
A key focus has been on estimating asymptomatic prevalence (see~\citep{mizumoto_2020}), e.g., what fraction of individuals have asymptomatic infections relative to those with symptomatic infections?
%.(i) What fraction of newly infected individuals
%have mild and/or subclinical infections rather than severe and/or
%clinical infections? (ii) What is the time-scale over which 
%individuals who have mild and/or subclinical cases remain
%infectious? (iii) How infectious are individuals
%with mild and/or subclinical infections relative to those
%with severe symptoms?  
Here, we attempt to address the impact of asymptomatic cases differently, by relating 
individual-level features of asymptomatic cases (e.g., the probability
of initiating an asymptomatic case, asymptomatic case duration, and
the tranmission rates from asymptomatic individuals) to dynamics at the
population scale. That is, rather than focusing on the prevalence
of asymptomatic cases, we are interested in understanding the
relevance of asymptomatic infections to secondary case production -- including
to the production of symptomatic cases.
%Our purpose is to characterize key drivers of contribution to
%secondary cases during an outbreak by `asymptomatic' individuals --
%and help characterize the relevance of asymptomatic transmission to
%outbreak dynamics and control.

To begin, consider a SEIR model variant in which there are two infectious categories --
$I_a$ and $I_s$ -- corresponding to asymptomatic and symptomatic cases,
respectively. Both types of individuals can infect others, but,
only symptomatic cases can lead to fatalities, denoted
by the $D$ category. In total, the dynamics of susceptibles, exposed,
infectious, recovered, and dead are:
\begin{eqnarray}
\dot{S}&=&-\beta_a S I_a -\beta_s S I_s \\
\dot{E}&=&\beta_a S I_a +\beta_s S I_s -\gamma_e E\\
\dot{I}_a&=&p\gamma_e E-\gamma_a I_a\\
\dot{I}_s&=&(1-p)\gamma_e E-\gamma_s I_s\\
\dot{R}&=&\gamma_a I_a + (1-f)\gamma_s I_s \\
\dot{D}&=&f\gamma_s I_s.
\end{eqnarray}
Here, $\beta_a$ and $\beta_s$ denote transmission rates,
$\gamma_e$ denotes the transition from exposed to infectious,
$p$ is the fraction of asymptomatic cases that
are generated for each exposed individual,
$1-p$ is the fraction of symptomatic cases that
are generated for each exposed individual,
$\gamma_a$ and $\gamma_s$ denote recovery rates,
and $f$ denotes the case fatality ratio for symptomatic cases.

%The basic reproduction number, ${\cal{R}}_0$,
%characterize the strength of an epidemic outbreak in an other
%wise susceptible population:
%\begin{equation}
%{\cal{R}}_{0}= p\left(\frac{\beta_a}{\gamma_a}\right)+ (1-p)\left(\frac{\beta_s}{\gamma_s}\right)
%\end{equation}
%Pooling estimates via a Bayesian approach applied to the early stages of Wuhan case data,
%suggests ${\cal{R}}_0\approx 3.0$ 
%with a 95\% confidence interval from 2-4.5.  Yet, that information
%is not sufficient to disentangle the role of asymptomatic cases, i.e.,
%what fraction of secondary cases can be ascribed to transmission
%from asymptomatic cases vs.~symptomatic cases?  A step towards such
%a link is enabled given the relationship between strength and speed, $r$,
%i.e., the rate at which cases grow in number and which we assume
%should be the same for both classes of cases.  Strength and size
%can be related via a Gamma approximation as:
%\begin{equation}
%{\cal{R}}^{gamma}=(1+\kappa r \bar{G})^{1/\kappa}
%\end{equation}
%where $\bar{G}$ is the mean generation interval and
%$\kappa$  is the squared coefficient of variation of
%the generation interval.  This approximation (explored in Champredon
%et al.) reveals why for a given observed speed,
%increases in the mean generation interval imply
%larger reproduction number. Reports of individuals
%with mild cases that remain infectious for (relatively)
%long periods suggest that the mean generation interval
%could be longer than estimated from symptomatic cases alone - both
%increasing ${\cal{R}}_0$ and driving more secondary cases
%than expected. Yet the relevance of asymptomatic cases
%depends on their realized proportion at a population level.

The number of infected cases is expected
to increase exponentially at rate $r$ at the outset of an outbreak.  We note
that, in practice,
counted cases may largely be of the symptomatic type. 
Hence, we ask: is the expected ratio of $I_a/I_s$ 
during the outbreak phase the same or different
than $p/(1-p)$?  In other words, is the ratio of asymptomatic to symptomatic cases population-wide approximately equal to the ratio of asymptomatic to symptomatic cases generated by newly exposed individuals?
To answer this question, note that the equations
for the infectious cases can be rewritten given the ansatz
$E(t)=c_e e^{rt}$,
$I_a(t)=c_a e^{rt}$,
$I_s(t)=c_s e^{rt}$,
given the prefactors $c_e$, $c_a$, and $c_s$
such that
\begin{eqnarray}
r c_a&=&p\gamma_e c_e-\gamma_a c_a,\\
r c_s&=&(1-p)\gamma_e c_e-\gamma_s c_s,
\end{eqnarray} 
which implies that
%\begin{eqnarray}
%c_a(r+\gamma_a)&=&p\gamma_e c_e,\\
%c_s(r+\gamma_s)&=&(1-p)\gamma_e c_e.
%\end{eqnarray} 
%Taking the ratio of these two equations yieldds
\begin{equation}
\frac{c_a}{c_s}=\frac{p}{1-p}\left[\frac{r+\gamma_s}{r+\gamma_a}\right].
\label{eq.relevance}
\end{equation}
%Alternatively, this same equation can be written as:
%\begin{equation}
%\frac{c_a}{c_s}=\frac{p}{1-p}\left[\frac{1+\tau/T_s}{1+\tau/T_a}\right]
%\end{equation}
%where $\tau$ is the characteristic time of exponential case increase,
%$T_s$ is the average period of symptomatic infectious periods,
%and $T_a$ is the average period of asymptomatic infectious periods. 
Hence, we conclude that, during the exponential
growth phase, the intrinsic
ratio of asymptomatic to symptomatic cases ($p/(1-p)$) may differ from
the realized ratio at the population level ($c_a/c_s$).  
%This difference
%suggests that additional steps are required to link asymptomatic features
%at the individual to the population scale, i.e., by including
%the unknown transmission rates, $\beta_a$ and $\beta_s$.
Indeed, the ratio of secondary case production caused by asymptomatic vs.~symptomatic
individuals during the exponential phase should be
\begin{equation}
\frac{q}{1-q} = \left(\frac{\beta_a}{\beta_s}\right)\frac{p}{1-p}\left[\frac{r+\gamma_s}{r+\gamma_a}\right],
\label{eq.qratio}
\end{equation}
where $q$ is the fraction of new secondary cases caused by
asymptomatic individuals or `relevance' of asymptomatic cases.
The value of $q$ is an unknown feature of
outbreaks at the population scale, distinct from $p$ the probability of becoming
asymptomatic upon infection. 
As is apparent from Eq.~\req{eq.qratio}, relevance increases
with both $p$ and $\beta_a/\beta_s$. However, the consequences
for outbreak potential depends on the relative duration of infectiousness.

Here, given $1/r=7$ days, $1/\gamma_e=4$ days, and
$1/\gamma_s=10$ days, we evaluate the impacts of $p$ and $\beta_a/\beta_s$ on the
relevance of asymptomatic infections, given variation in 
$p$, $\beta_a/\beta_s$, and $\gamma_a$.  We consider two
scenarios, one in which asymptomatic infectiousness is short, i.e., with
average duration of $1/\gamma_a=5$ days,
and one in which asymptomatic infectiousness is long,i.e., $1/\gamma_a=20$ days.
We use the renewal equation formalism to explicitly link duration of infectiousness to the 
basic reproductive number (for technical details and example 
applications see~\citep{wallinga2007generation,weitz_scirep2015,champredon_2018}).
In brief, we
infer ${\cal{R}}_0$ compatible with an estimated value of $r$ from case
data given the generation interval distribution 
(set by $q$ and the duration in the exposed and infectious states).
By solving for $q$, we can then relate the basic
reproduction number to the relative transmission rates ($\beta_a/\beta_s$)
and the probability, $p$, of asymptomatic cases at the individual scale.
Figure~\ref{fig.relevance}C shows that
when $\gamma_a<\gamma_s$, then the strength ${\cal{R}}_0$ increases
with $q$. 
This increase arises because asymptomatic infections that resolve
slower increase the duration of
overall generation intervals (see~\citep{park_2019practical}). In contrast,
Figure~\ref{fig.relevance}D show that
when $\gamma_a>\gamma_s$ then
the strength ${\cal{R}}_0$ decreases with $q$.  
This decrease arises because asymptomatic infections that resolve
faster decrease the duration of
overall generation intervals (again, see~\citep{park_2019practical}). In both 
cases, the dependence of ${\cal{R}}_0$ on $q$ is
compared to a baseline of 
${\cal{R}}_0\approx 3.1$ in a model with no secondary
case production from asymptomatic infections (see filled
circle at bottom left of Figure~\ref{fig.relevance}C-D.
In other words, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread, it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.

The present findings highlight the need to characterize
the duration of asymptomatic cases and their consequences
not only for contact tracing but for constraining
uncertainty in the strength of the ongoing COVID-19 outbreak~\citep{park_preprint}.
The present findings are also consistent with
a recent generalization linking speed, strength, and
generation intervals, such that
for a given observed speed
increases in the mean generation interval imply
larger reproduction number~\citep{park_2019practical}. Hence, reports of individuals
with mild, persistent cases 
suggest the possibility that the mean generation interval for COVID-19
could be longer than estimated from symptomatic cases alone - possibly
increasing ${\cal{R}}_0$ and driving a larger fraction of secondary cases
(see Figure~\ref{fig.relevance} top row).
However, if asymptomatic cases tend to be shorter, then
current estimates of ${\cal{R}}_0$ may be over-estimates of the
underlying strength (see Figure~\ref{fig.relevance} bottom row).
Finally, it is important to note we focused here on the exponential
phase, but that the asymptomatic relevance $q$ is time-dependent, and will
vary given the population state structure of infected individuals.  Such
variation in the ratio of asymptomatic to symptomatic cases
will also impact estimates of case fatality rates insofar
as many asymptomatic cases are not counted, particularly early in an outbreak.
Future work might also consider the ways in which asymptomatic individuals
modulate resurgent epidemics in a networked metapopulation~\citep{watts_pnas2005}.

\begin{figure*}[b!]
\begin{center}
\includegraphics[width=0.4\textwidth]{figures/figheatmap_seird_noname.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.44\textwidth]{figures/figheatmap_seirdR0_noname.pdf}\\
\mbox{}\\
\includegraphics[width=0.4\textwidth]{figures/figheatmap_seird_2_noname.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.44\textwidth]{figures/figheatmap_seird_R02_noname.pdf}
\caption{Relevance of asymptomatic transmission given variation in
relative transmission and probability that a given, newly infected individual is asymptomatic.  (Top) Long duration asymptomatic cases increase ${\cal{R}}_0$ with increasing relevance.
(Bottom) Short duration asymptomatic cases decrease ${\cal{R}}_0$ with increasing relevance.
Technically, renewal equations provide a route to connect
observed increases in case counts, i.e., ${\cal{R}}_0 = \frac{1}{M(-r)}$
where $M(-r)=\int_0^{\infty}\mathrm{d} a e^{-ra}g(a)$.
For the present model,
$M(r)=qM_E(-r)M_{I_a}(-r)+(1-q)M_E(-r)M_{I_s}(-r)$
where each of the component functions are $M_E(-r)=\frac{\gamma_e}{\gamma_e+r}$,
$M_{I_a}(-r)=\frac{\gamma_a}{\gamma_a+r}$, 
$M_{I_s}(-r)=\frac{\gamma_s}{\gamma_s+r}$,
and $q$ is the fraction of realized new secondary cases caused by
asymptomatic individuals.  In all of these heatmaps, $\gamma_e=1/4$,
$\gamma_s=1/10$, and $r=1/7$. Here, the average duration
in symptomatic and asymptomatic states are $T_s=1/\gamma_s$ and 
$T_a=1/\gamma_a$, respectively. Here the filled circle denotes ${\cal{R}}_0\approx 3.12$
in the event of $p=0$ and $\beta_a=0$, and the open symbols are for $\beta_a/\beta_s=0.5$ and 
$p=0.5$ and $p=0.9$ for reference.
%Renewal equations provide a route to connect
%observed increases in case counts, i.e.,
%\begin{equation}
%{\cal{R}}_0 = \frac{1}{M(-r)}
%\end{equation}
%where $r$ is the speed of the disease spread and 
%$M(r)$ is related to 
%$g(a)$ (the normalized age of transmission) such that 
%\begin{equation}
%M(r)=\int_0^{\infty}\mathrm{d} a e^{ra}g(a).
%\end{equation}
%For the present model, the moment generating function is
%\begin{equation}
%M(r)=qM_E(r)M_{I_a}(r)+(1-q)M_E(r)M_{I_s}(r)
%\end{equation}
%where each of the component functions are $M_E(-r)=\frac{\gamma_e}{\gamma_e+r}$,
%$M_{I_a}(-r)=\frac{\gamma_a}{\gamma_a+r}$, 
%$M_{I_s}(-r)=\frac{\gamma_s}{\gamma_s+r}$,
%and $q$ is the fraction of realized new secondary cases caused by
%asymptomatic individuals. 
%The relevance $q$ is an unknown feature of
\label{fig.relevance}}
\end{center}
\end{figure*}

%We also note that efforts to characterize asymptomatic tranissmion
%should consider its effect on
%the basic reproduction number, which for this SEIR coronavirus-like model is ${\cal{R}}_0=p\left(\frac{\beta_a}{\gamma_a}\right)+ (1-p)\left(\frac{\beta_s}{\gamma_s}\right).$
%%Pooling estimates via a Bayesian approach applied to the early stages of Wuhan case data,
%%suggests ${\cal{R}}_0\approx 3.0$ 
%%with a 95\% confidence interval from 2-4.5.  Yet, that information
%%is not sufficient to disentangle the role of asymptomatic cases, i.e.,
%%what fraction of secondary cases can be ascribed to transmission
%%from asymptomatic cases vs.~symptomatic cases?  
%Strength, ${\cal{R}}_0$ and size $r$
%can be related via a Gamma approximation to the generation
%interval distribution as follows:
%\begin{equation}
%{\cal{R}}^{gamma}=(1+\kappa r \bar{G})^{1/\kappa}
%\end{equation}
%where $\bar{G}$ is the mean generation interval and
%$\kappa$  is the squared coefficient of variation of
%the generation interval.  
%This approximation (explored in Champredon
%et al.) reveals why for a given observed speed,
%increases in the mean generation interval imply
%larger reproduction number. Hence, reports of individuals
%with mild cases that remain infectious for (relatively)
%long periods suggest that the mean generation interval
%could be longer than estimated from symptomatic cases alone - both
%increasing ${\cal{R}}_0$ and driving a larger fraction of secondary cases.
%This inference also reinforces 
%the need to characterize the epidemiological characteristics of asymptomatic transmission.

%than expected. Yet the relevance of asymptomatic cases
%depends on their realized proportion at a population level.

%Renewal equations provide a route to connect
%observed increases in case counts, i.e.,
%\begin{equation}
%{\cal{R}}_0 = \frac{1}{M(-r)}
%\end{equation}
%where $r$ is the speed of the disease spread and $M(r)$ is the
%moment generating function of the generation interval distribution
%$g(a)$ (normalized age of transmission) such that 
%\begin{equation}
%M(r)=\int_0^{\infty}\mathrm{d} a e^{ra}g(a).
%\end{equation}
%For the present model, the moment generating function is
%\begin{equation}
%M(r)=qM_E(r)M_{I_a}(r)+(1-q)M_E(r)M_{I_s}(r)
%\end{equation}
%where each of the component functions are $M_E(-r)=\frac{\gamma_e}{\gamma_e+r}$,
%$M_{I_a}(-r)=\frac{\gamma_a}{\gamma_a+r}$, 
%$M_{I_s}(-r)=\frac{\gamma_s}{\gamma_s+r}$,
%and $q$ is the fraction of realized new secondary cases caused by
%asymptomatic individuals. The relevance $q$ is an unknown feature of
%outbreaks at the population scale, distinct from $p$ the probability of having
%an asymptomatic cases, conditional upon being infected
%but not yet infectious. Hence,
%if one were to observe $r$ (which can vary from country to 
%country and from region to region) then it should be possible
%to link the values $p$ and the relative transmission rates,
%$\beta_a/\beta_s$ to the relevance of asymptomatic transmission
%at the population scale.

%Renewal equations provide a route to connect
%observed increases in case counts, i.e.,
%\begin{equation}
%{\cal{R}}_0 = \frac{1}{M(-r)}
%\end{equation}
%where $r$ is the speed of the disease spread and $M(r)$ is the
%moment generating function of the generation interval distribution
%$g(a)$ (normalized age of transmission) such that 
%\begin{equation}
%M(r)=\int_0^{\infty}\mathrm{d} a e^{ra}g(a).
%\end{equation}
%For the present model, the moment generating function is
%\begin{equation}
%M(r)=qM_E(r)M_{I_a}(r)+(1-q)M_E(r)M_{I_s}(r)
%\end{equation}
%where each of the component functions are $M_E(-r)=\frac{\gamma_e}{\gamma_e+r}$,
%$M_{I_a}(-r)=\frac{\gamma_a}{\gamma_a+r}$, 
%$M_{I_s}(-r)=\frac{\gamma_s}{\gamma_s+r}$,
%and $q$ is the fraction of realized new secondary cases caused by
%asymptomatic individuals. The relevance $q$ is an unknown feature of
%outbreaks at the population scale, distinct from $p$ the probability of having
%an asymptomatic cases, conditional upon being infected
%but not yet infectious. Hence,
%if one were to observe $r$ (which can vary from country to 
%country and from region to region) then it should be possible
%to link the values $p$ and the relative transmission rates,
%$\beta_a/\beta_s$ to the relevance of asymptomatic transmission
%at the population scale.
%
%
%
%
%Hence, recalling the equation for the basic reproduction number
%\begin{equation}
%{\cal{R}}_{0,E}= p\left(\frac{\beta_a}{\gamma_a}\right)+ (1-p)\left(\frac{\beta_s}{\gamma_s}\right)
%\end{equation}
%suggests that 
%This gap between intrinsic and realized transmission routes
%lies at the base of our exploration.
%
%\section{Dynamics}
%We simulate the SEIaIsRD model assuming $N=10^6$ with
%the following initial conditions: $S_0=10^6-1$, $E_0=1$
%and all other elements 0.  The following model vary $p$ from
%0.1 to 0.5 to 0.9.  For various reasons, the parameters are:
%$\gamma_e=1/4$, $\gamma_a=1/42$, $\gamma_s=1/14$,
%$\beta_a=1/14$, $\beta_s=3/14$, $f=0.02$.  The resultant
%value of ${\cal{R}}_0=3$ for all values of $p$, however
%the realized CFR, fraction of asymptomatic cases, and even
%the speed of the disease varies significantly. Hence, we 
%need to adopt a different approach, given that we
%observe a speed, $r$, and yet are uncertain with
%respect to the underlying contribution of asymptomatic
%vs.~symptomatic cases.
%
%\begin{figure*}[h!]
%\begin{center}
%\includegraphics[width=0.9\textwidth]{figseird_base_noname.pdf}\\
%\includegraphics[width=0.9\textwidth]{figseird_base2_noname.pdf}\\
%\includegraphics[width=0.9\textwidth]{figseird_base3_noname.pdf}\\
%\end{center}
%\end{figure*}
%
%\section{Constrained Dynamics}
%Here, we simulate the SEIR model developed
%for coronavirus assuming $N=10^6$ with
%the following initial conditions: $S_0=10^6-1$, $E_0=1$
%and all other elements set to 0.  We assume that the speed of
%the outbreak is $r=1/6$ days$^{-1}$. We further assume that $\gamma_e=1/4$
%(4 days to onset), $\gamma_a=1/42$, $\gamma_s=1/14$, and $p=0.9$.
%How do we solve for the unknown transmission rates, $\beta_a$
%and $\beta_s$?  Alone, it would seem we have a under-determined
%problem, such that
%\begin{equation}
%p\left(\frac{\beta_a}{\gamma_a}\right)+ (1-p)\left(\frac{\beta_s}{\gamma_s}\right)=\frac{1}{M(-r)}.
%\end{equation}
%However, if one assumes that a fraction $q$ of secondary infections are caused by
%asymptomatic individuals, then there is an additional constraint:
%\begin{equation}
%p\frac{\beta_a}{\gamma_a}=\frac{q}{M(-r)}
%\end{equation}
%such that 
%\begin{equation}
%\beta_a = \frac{q\gamma_a}{pM(-r)}.
%\end{equation}
%As a result, then 
%\begin{equation}
%\beta_s = \frac{(1-q)\gamma_s}{(1-p)M(-r)}
%\end{equation}
%In essence, as $q$ varies, then both tranmission rates will have 
%to covary (indeed in a negative fashion) to reconciled the realized
%speed of the outbreak. We now put this into practice for three scenarios,
%all for the case of $p=0.9$ (in which intrinsically most cases
%are asymptomatic):
%\begin{description}
%\item[Short asymptomatic cases] Here we assume
%$\gamma_s=1/14$ (2 week for severe cases) and $\gamma_a=1/2$ 
%(2 day resolution, i.e., a 7-fold change). 
%\item[Long asymptomatic cases] Here we assume
%$\gamma_s=1/14$ (2 week for severe cases) and $\gamma_a=1/42$ 
%(6 week for mild cases)
%\end{description}
%We also assume as before that $f=0.02$ for severe cases. The following 
%results show that we can in fact calculate the correct values of
%$\beta_a$ and $\beta_s$ given variation in $q$.
%It is also important to point out that
%${\cal{R}}_0$ can be extended or decreased with $q$ depending
%on whether $\gamma_a$ is faster or slower relative to $\gamma_s$.
%The key idea there is the same as that for the impact of post-death
%transmission of Ebola virus disease.
%
%For the short duration asymptomatic cases (see Figure~\ref{constrain}), we find the following trade-offs:
%\begin{verbatim}
%         q: [0.0100 0.1000 0.5000 0.9000 0.9900]
%    beta_a: [0.0258 0.2311 0.7857 1.0714 1.1176]
%    beta_s: [3.2898 2.6741 1.0102 0.1531 0.0145]
%        R0: [4.6523 4.1597 2.8286 2.1429 2.0320]
%\end{verbatim}
%whereas for the longer duration asymptomatic cases we find
%\begin{verbatim}
%         q: [0.0100 0.1000 0.5000 0.9000 0.9900]
%    beta_a: [0.0013 0.0132 0.0873 0.2311 0.2843]
%    beta_s: [3.3528 3.2143 2.3571 0.6933 0.0775]
%        R0: [4.7414 5 6.6000 9.7059 10.8553]
%\end{verbatim}
%In the first case, when most illnesses
%are caused by asymptomatic cases, then shorter generation intervals
%for the same growth rate means a lower ${\cal{R}}_0$. Whereas,
%in the second case, when most illnesses are caused by asymptomatic
%cases, then longer generation intervals for the same growth rate
%means a higher ${\cal{R}}_0$.
%\begin{figure*}[b!]
%\begin{center}
%\includegraphics[width=0.9\textwidth]{figconstrain_short_noname.pdf}\\
%\includegraphics[width=0.9\textwidth]{figconstrain_long_noname.pdf}\\
%\caption{Short, mild asymptomatic cases (top) vs. longer, mild asymptomatic
%cases (bottom). For both, common parameters are $\gamma_e=0.25$,
%$\gamma_s=1/14$, $f=0.02$, $p=0.9$, and $r=1/7$.  For the short
%asymptomatic case scenario, $\gamma_a=1/2$ whereas for the long asymptomatic
%case scenario $\gamma_a=1/42$.
%\label{constrain}}
%\end{center}
%\end{figure*}
%
%Finally, in an effort to try and reconcile this, we point out the following
%synthetic figure of outbreaks all with a growth rate of $r=1/7$ by construction, yet differ in vastly different ways based on 3 facets, the value of $p$ (the instrinsic fraction of asymptomatic cases),
%the value of $1/\gamma_a$ (that sets the average duration of asymptomatic cases), and
%the realized value of $q$ (the fraction of secondary cases caused by asymptomatic cases).  As is
%apparent, all disease take off at the same speed, but have very different peak strengths,
%and also, different decomposition of the relative importance of the asymptomatic component.
%What is notable is that the peak size is more driven by $p$ and $\gamma_a$ than by $q$
%(see Figure~\ref{constrain2}).
%\begin{figure*}[bh!]
%\begin{center}
%\includegraphics[width=0.9\textwidth]{package_overlay_p_T.pdf}
%\caption{Synthesis of dynamical results given variation in 
%the intrinsic generation interval of asymptomatic cases (set by $1/\gamma_a$), frequency ($p$), 
%and importance ($q$).
%For all, common parameters are $\gamma_e=0.25$,
%$\gamma_s=1/14$, $f=0.02$, and $r=1/7$.  For the short
%asymptomatic case scenario, $\gamma_a=1/2$ whereas for the long asymptomatic
%case scenario $\gamma_a=1/42$.
%\label{constrain2}}
%\end{center}
%\end{figure*}
%
%%
%%\section{Simulations}
%%Consider an outbreak whose
%%symptomatic cases is ${\cal{R}}_0\approx 3$, such that
%%$\beta_s/\gamma_s=3$.  We further assume that transition from
%%exposed to either $I_a$ or $I_s$ takes 4 days on average,
%%such that $\eta=1/4$.  The following is an example
%%outbreak, in which $\beta_s=\beta_a=3/7$, $\gamma_a=1/45$,
%%and $f=0.02$ (corresponding to a 2\% case fatality rate
%%for symptomatic cases). As is apparent, there is an exponential
%%increase in cases, such that $r\approx 0.30$ days$^{-1}$.
%%In this case, we expect that in the exponential phase,
%%then $I_a/I_s\approx 13.8$.  This prediction is borne out
%%by simulation as in Figure~\ref{fig.ratio}.
%%\begin{figure*}[h!]
%%\begin{center}
%%\includegraphics[width=0.4\textwidth]{figexample1_noname.pdf}
%%\mbox{\hspace{0.05\textwidth}}
%%\includegraphics[width=0.4\textwidth]{figexample1_ratio_noname.pdf}
%%\caption{Asymptomatic to symptomatic case ratio at 
%%the population scale can exceed the ratio of relative case
%%production at the individual scale, when $\gamma_a\ll \gamma_s$.\label{fig.ratio}}
%%\end{center}
%%\end{figure*}
%%Similalry, in the case that asymmptomatic cases rapidly
%%recover, then we expect the population rate to be less then
%%$z$. In the event that $\gamma_a=1$ (7-fold faster than
%%the the symptomatic removal rate) then $r\approx 0.17$ and
%%the ratio is expected to converge to $\approx 2.7$, as shown in Figure~\ref{fig.ratio2}.
%%\begin{figure*}[h!]
%%\begin{center}
%%\includegraphics[width=0.4\textwidth]{figexample2_noname.pdf}
%%\mbox{\hspace{0.05\textwidth}}
%%\includegraphics[width=0.4\textwidth]{figexample2_ratio_noname.pdf}
%%\caption{Asymptomatic to symptomatic case ratio at 
%%the population scale can exceed the ratio of relative case
%%production at the individual scale, when $\gamma_a\gg \gamma_s$.
%%\label{fig.ratio2}
%%}
%%\end{center}
%%\end{figure*}
%%Finally, in the case that asymptomatic cases and symptomatic
%%cases have the same exepcted rudation
%%then we expect the population ratio to be less then
%%$z$. In the event that $\gamma_a=1$ (7-fold faster than
%%the the symptomatic removal rate) then $r\approx 0.26$ and
%%the ratio is expected to converge to $\approx 10$, as shown in Figure~\ref{fig.ratio3}.
%%\begin{figure*}[h!]
%%\begin{center}
%%\includegraphics[width=0.4\textwidth]{figexample3_noname.pdf}
%%\mbox{\hspace{0.05\textwidth}}
%%\includegraphics[width=0.4\textwidth]{figexample3_ratio_noname.pdf}
%%\caption{Asymptomatic to symptomatic case ratio at 
%%the population scale can exceed the ratio of relative case
%%production at the individual scale, when $\gamma_s=\gamma_a$.
%%\label{fig.ratio3}
%%}
%%\end{center}
%%\end{figure*}
%%
%%\section{Stability of the infection-free equilibrium}
%%Consider the following infection subystem, assume $S\approx 1$
%%\begin{eqnarray}
%%\dot{E}&=&\beta_a I_a +\beta_s I_s -\eta E\\
%%\dot{I}_a&=&\frac{z}{z+1}\eta E-\gamma_a I_a\\
%%\dot{I}_s&=&\frac{1}{z+1}\eta E-\gamma_s I_s
%%\end{eqnarray}
%%such that the Jacobian is:
%%\begin{equation}
%%J = \left[
%%\begin{array}{ccc}
%%-\eta & \beta_a & \beta_s \\
%%\frac{z}{z+1}E & -\gamma_a & 0 \\
%%\frac{1}{z+1}E & -\gamma_s & 0 
%%\end{array}
%%\right]
%%\end{equation}

### 2020-03-05 short.body.tex
Fiddling

@@
 \begin{center}
-\includegraphics[width=0.4\textwidth]{figures/figheatmap_seird_noname.pdf}
+\includegraphics[width=0.4\textwidth]{group/figheatmap_seird_noname.pdf}
 \mbox{\hspace{0.05\textwidth}}
-\includegraphics[width=0.44\textwidth]{figures/figheatmap_seirdR0_noname.pdf}\\
+\includegraphics[width=0.44\textwidth]{group/figheatmap_seirdR0_noname.pdf}\\
 \mbox{}\\
-\includegraphics[width=0.4\textwidth]{figures/figheatmap_seird_2_noname.pdf}
+\includegraphics[width=0.4\textwidth]{group/figheatmap_seird_2_noname.pdf}
 \mbox{\hspace{0.05\textwidth}}
-\includegraphics[width=0.44\textwidth]{figures/figheatmap_seird_R02_noname.pdf}
+\includegraphics[width=0.44\textwidth]{group/figheatmap_seird_R02_noname.pdf}
 \caption{Relevance of asymptomatic transmission given variation in

### 2020-03-05 acknowledge.tex
Update acknowledge.tex

\mbox{}\\
\noindent
\textbf{Acknowledgments:} The authors thank John Glasser for comments
and discussion on the manuscript, particularly on short notice. 
This work was supported, in part,
by support from the Army Research Office (W911NF1910384).

\noindent
\textbf{Data Availabililty:} All code is available at weitzgroup.github.io.

### 2020-03-05 short.body.tex
time for dinner

@@
 
-To begin, consider a SEIR model variant in which there are two infectious categories --
-$I_a$ and $I_s$ -- corresponding to asymptomatic and symptomatic cases,
-respectively. Both types of individuals can infect others, but,
-only symptomatic cases can lead to fatalities, denoted
-by the $D$ category. In total, the dynamics of susceptibles, exposed,
-infectious, recovered, and dead are:
+To begin, consider a renewal equation variant in which incidence $i$ is divided into two categories -- $i_a$ and $i_s$ -- corresponding to incidence of asymptomatic and symptomatic cases, respectively.
+Both types of individuals can infect others, but, they differ in their intrinsic reproduction numbers, ${\cal{R}}_a$ and ${\cal{R}}_s$, as well as intrinsic generation-interval distributions, $g_a(\tau)$ and $g_s(\tau)$, reflecting their differences in the abilities to transmit and the courses of infection.
+Generation intervals, which are defined as the time between when an individual is infected and when that individual infects another person, depend on the natural history of infection:
+an individual with subclinical, and fast-clearing, symptoms is likely to have short generation intervals, whereas an individual with mild, but long-lasting, symptoms is likely to have long generation intervals.
+In total, the dynamics of susceptibles and incidence are:
 \begin{eqnarray}
-\dot{S}&=&-\beta_a S I_a -\beta_s S I_s \\
-\dot{E}&=&\beta_a S I_a +\beta_s S I_s -\gamma_e E\\
-\dot{I}_a&=&p\gamma_e E-\gamma_a I_a\\
-\dot{I}_s&=&(1-p)\gamma_e E-\gamma_s I_s\\
-\dot{R}&=&\gamma_a I_a + (1-f)\gamma_s I_s \\
-\dot{D}&=&f\gamma_s I_s.
+\dot{S}&=&-i(t) \\
+i(t)&=&\mathcal R_a S \int_0^\infty i_a(t-\tau) g_a(\tau) \mathrm{d}\tau + \mathcal R_s S \int_0^\infty i_s(t-\tau) g_s(\tau) \mathrm{d}\tau.
 \end{eqnarray}
-Here, $\beta_a$ and $\beta_s$ denote transmission rates,
-$\gamma_e$ denotes the transition from exposed to infectious,
-$p$ is the fraction of asymptomatic cases that
-are generated for each exposed individual,
-$1-p$ is the fraction of symptomatic cases that
-are generated for each exposed individual,
-$\gamma_a$ and $\gamma_s$ denote recovery rates,
-and $f$ denotes the case fatality ratio for symptomatic cases.
+Here, $p$ is the fraction of asymptomatic cases that are generated for each infected individual ($i_a(t)= p i(t)$), and $1-p$ is the fraction of symptomatic cases that are generated for each infected individual ($i_s(t)= (1-p) i(t)$).
+
+%To begin, consider a SEIR model variant in which there are two infectious categories --
+%$I_a$ and $I_s$ -- corresponding to asymptomatic and symptomatic cases,
+%respectively. Both types of individuals can infect others, but,
+%only symptomatic cases can lead to fatalities, denoted
+%by the $D$ category. In total, the dynamics of susceptibles, exposed,
+%infectious, recovered, and dead are:
+%\begin{eqnarray}
+%\dot{S}&=&-\beta_a S I_a -\beta_s S I_s \\
+%\dot{E}&=&\beta_a S I_a +\beta_s S I_s -\gamma_e E\\
+%\dot{I}_a&=&p\gamma_e E-\gamma_a I_a\\
+%\dot{I}_s&=&(1-p)\gamma_e E-\gamma_s I_s\\
+%\dot{R}&=&\gamma_a I_a + (1-f)\gamma_s I_s \\
+%\dot{D}&=&f\gamma_s I_s.
+%\end{eqnarray}
+%Here, $\beta_a$ and $\beta_s$ denote transmission rates,
+%$\gamma_e$ denotes the transition from exposed to infectious,
+%$p$ is the fraction of asymptomatic cases that
+%are generated for each exposed individual,
+%$1-p$ is the fraction of symptomatic cases that
+%are generated for each exposed individual,
+%$\gamma_a$ and $\gamma_s$ denote recovery rates,
+%and $f$ denotes the case fatality ratio for symptomatic cases.
+
+The basic reproduction number, ${\cal{R}}_0$, characterize the strength of an epidemic in an otherwise susceptible population:
+\begin{equation}
+{\cal{R}}_{0}= p {\cal{R}}_a + (1-p) {\cal{R}}_s.
+\end{equation}
+Then, the \emph{intrinsic} proportion of asymptomatic $z$ and symptomatic $1-z$ transmission is equal to their relative contribution toward the basic reproduction number, 
+\begin{eqnarray}
+z &=& p {\cal{R}}_a/{\cal{R}}_{0},\\
+1-z &=& (1-p) {\cal{R}}_s/{\cal{R}}_{0}.
+\end{eqnarray}
+Then, the \emph{intrinsic} generation-interval distribution depends on the intrinsic proportion of asymptomatic vs.~symptomatic transmission and their corresponding \emph{intrinsic} generation-interval distributions:
+\begin{equation}
+g(\tau) = z g_a(\tau) + (1-z) g_s(\tau),
+\end{equation}
+which allows us to express incidence of infection as a renewal process that depends on previous incidence:
+\begin{equation}
+i(t) = {\cal{R}}_{0} \int_0^\infty i(t-\tau) g(\tau) \mathrm{d} \tau.
+\end{equation}
+Yet, this information is not sufficient to disentangle the role of asymptomatic cases, i.e., what fraction of secondary cases can be ascribed to \emph{realized} transmission from asymptomatic cases vs.~symptomatic cases?
+
+The number of infected cases is expected to increase exponentially at rate $r$ at the outset of an outbreak. We note that, in practice, counted cases may largely be of the symptomatic type. 
+Hence, we ask: is the expected ratio of incidence caused by asymptomatic cases vs.~symptomatic cases during the outbreak phase the same or different than $z/(1-z)$?
+The ratio of secondary case production caused by asymptomatic vs.~symptomatic individuals during the exponential phase should be
+\begin{equation}
+\frac{q}{1-q}=\left(\frac{z}{1-z}\right)\left[\frac{\int_0^\infty \exp(-r\tau) g_a(\tau) \mathrm{d}\tau}{\int_0^\infty \exp(-r\tau) g_s(\tau) \mathrm{d}\tau}\right],
+\label{eq.qratio}
+\end{equation}
+where $q$ is the fraction of new secondary cases caused by asymptomatic individuals or `relevance' of asymptomatic cases. 
+The value of $q$ is an unknown feature of outbreaks at the population scale, distinct from $p$ the probability of becoming asymptomatic upon infection or $z$ the intrinsic proportion of asymptomatic transmission.
+
+Assuming that the intrinsic generation-interval distributions for asymptomatic and symptomatic cases follow gamma distributions with different means, $\bar G_a$ and  $\bar G_s$, and dispersions (represented by squared coefficients of variations), $\kappa_a$ and $\kappa_s$.
+Then, we have
+\begin{equation}
+\frac{q}{1-q}=\left(\frac{z}{1-z}\right)\left[\frac{(1 + \kappa_s r \bar G_s)^{1/\kappa_s}}{(1 + \kappa_a r \bar G_a)^{1/\kappa_a}}\right].
+\label{eq.gammaratio}
+\end{equation}
+As is apparent from Eq.~\req{eq.qratio}, relevance $q$ increases with $z$, i.e., with both $p$ and $\mathcal R_a/\mathcal R_s$.
+The consequences for outbreak potential further depends on the relative lengths of generation intervals as well as the relative amount of dispersions in them.
 
@@
 
-The number of infected cases is expected
-to increase exponentially at rate $r$ at the outset of an outbreak.  We note
-that, in practice,
-counted cases may largely be of the symptomatic type. 
-Hence, we ask: is the expected ratio of $I_a/I_s$ 
-during the outbreak phase the same or different
-than $p/(1-p)$?
+%The number of infected cases is expected
+%to increase exponentially at rate $r$ at the outset of an outbreak.  We note
+%that, in practice,
+%counted cases may largely be of the symptomatic type. 
+%Hence, we ask: is the expected ratio of $I_a/I_s$ 
+%during the outbreak phase the same or different
+%than $p/(1-p)$?
 In other words, is the ratio of asymptomatic to symptomatic cases population-wide approximately equal to the ratio of asymptomatic to symptomatic cases generated by newly exposed individuals?
-To answer this question, note that the equations
-for the infectious cases can be rewritten given the ansatz
-$E(t)=c_e e^{rt}$,
-$I_a(t)=c_a e^{rt}$,
-$I_s(t)=c_s e^{rt}$,
-given the prefactors $c_e$, $c_a$, and $c_s$
-such that
-\begin{eqnarray}
-r c_a&=&p\gamma_e c_e-\gamma_a c_a,\\
-r c_s&=&(1-p)\gamma_e c_e-\gamma_s c_s,
-\end{eqnarray} 
-which implies that
+%To answer this question, note that the equations
+%for the infectious cases can be rewritten given the ansatz
+%$E(t)=c_e e^{rt}$,
+%$I_a(t)=c_a e^{rt}$,
+%$I_s(t)=c_s e^{rt}$,
+%given the prefactors $c_e$, $c_a$, and $c_s$
+%such that
+%\begin{eqnarray}
+%r c_a&=&p\gamma_e c_e-\gamma_a c_a,\\
+%r c_s&=&(1-p)\gamma_e c_e-\gamma_s c_s,
+%\end{eqnarray} 
+%which implies that
 %\begin{eqnarray}
@@
 %Taking the ratio of these two equations yieldds
-\begin{equation}
-\frac{c_a}{c_s}=\frac{p}{1-p}\left[\frac{r+\gamma_s}{r+\gamma_a}\right].
-\label{eq.relevance}
-\end{equation}
+%\begin{equation}
+%\frac{c_a}{c_s}=\frac{p}{1-p}\left[\frac{r+\gamma_s}{r+\gamma_a}\right].
+%\label{eq.relevance}
+%\end{equation}
 %Alternatively, this same equation can be written as:
@@
 %and $T_a$ is the average period of asymptomatic infectious periods. 
-Hence, we conclude that, during the exponential
-growth phase, the intrinsic
-ratio of asymptomatic to symptomatic cases ($p/(1-p)$) may differ from
-the realized ratio at the population level ($c_a/c_s$).  
-%This difference
+%Hence, we conclude that, during the exponential
+%growth phase, the intrinsic
+%ratio of asymptomatic to symptomatic cases ($p/(1-p)$) may differ from
+%the realized ratio at the population level ($c_a/c_s$).  
+%%This difference
 %suggests that additional steps are required to link asymptomatic features
@@
 %the unknown transmission rates, $\beta_a$ and $\beta_s$.
-Indeed, the ratio of secondary case production caused by asymptomatic vs.~symptomatic
-individuals during the exponential phase should be
-\begin{equation}
-\frac{q}{1-q} = \left(\frac{\beta_a}{\beta_s}\right)\frac{p}{1-p}\left[\frac{r+\gamma_s}{r+\gamma_a}\right],
-\label{eq.qratio}
-\end{equation}
-where $q$ is the fraction of new secondary cases caused by
-asymptomatic individuals or `relevance' of asymptomatic cases.
-The value of $q$ is an unknown feature of
-outbreaks at the population scale, distinct from $p$ the probability of becoming
-asymptomatic upon infection. 
-As is apparent from Eq.~\req{eq.qratio}, relevance increases
-with both $p$ and $\beta_a/\beta_s$. However, the consequences
-for outbreak potential depends on the relative duration of infectiousness.
+%Indeed, the ratio of secondary case production caused by asymptomatic vs.~symptomatic
+%individuals during the exponential phase should be
+%\begin{equation}
+%\frac{q}{1-q} = \left(\frac{\beta_a}{\beta_s}\right)\frac{p}{1-p}\left[\frac{r+\gamma_s}{r+\gamma_a}\right],
+%\label{eq.qratio}
+%\end{equation}
+%where $q$ is the fraction of new secondary cases caused by
+%asymptomatic individuals or `relevance' of asymptomatic cases.
+%The value of $q$ is an unknown feature of
+%outbreaks at the population scale, distinct from $p$ the probability of becoming
+%asymptomatic upon infection. 
+%As is apparent from Eq.~\req{eq.qratio}, relevance increases
+%with both $p$ and $\beta_a/\beta_s$. However, the consequences
+%for outbreak potential depends on the relative duration of infectiousness.
 
-Here, given $1/r=7$ days, $1/\gamma_e=4$ days, and
-$1/\gamma_s=10$ days, we evaluate the impacts of $p$ and $\beta_a/\beta_s$ on the
-relevance of asymptomatic infections, given variation in 
-$p$, $\beta_a/\beta_s$, and $\gamma_a$.  We consider two
-scenarios, one in which asymptomatic infectiousness is short, i.e., with
-average duration of $1/\gamma_a=5$ days,
-and one in which asymptomatic infectiousness is long,i.e., $1/\gamma_a=20$ days.
-We use the renewal equation formalism to explicitly link duration of infectiousness to the 
-basic reproductive number (for technical details and example 
-applications see~\citep{wallinga2007generation,weitz_scirep2015,champredon_2018}).
-In brief, we
-infer ${\cal{R}}_0$ compatible with an estimated value of $r$ from case
-data given the generation interval distribution 
-(set by $q$ and the duration in the exposed and infectious states).
-By solving for $q$, we can then relate the basic
-reproduction number to the relative transmission rates ($\beta_a/\beta_s$)
-and the probability, $p$, of asymptomatic cases at the individual scale.
+Here, given $1/r=7$ days, $\bar G_s=6$ days, and $\kappa_s=0.5$, we evaluate the impacts of intrinsic proportion of asymptomatic transmission $z$ on the realized relevance of asymptomatic infection, given variation in relative mean generation interval $\bar G_a/\bar G_s$ and relative generation-interval dispersion $\kappa_a/\kappa_s$ of asymptomatic cases.
+We vary $\bar G_a/\bar G_s$ and $\kappa_a/\kappa_s$ from 0.5 to 1.5, one at a time, and infer $q$ as well as ${\cal{R}}_0$ compatible with an estimated value of $r$ from case data given the generation interval distributions of asymptomatic and asymptomatic cases.
+Across the ranges of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.relevance}A,C).
+When the mean asymptomatic generation interval is longer than the mean symptomatic generation interval, $q$ decreases because short generation intervals (thus, faster infection) drive transmission events during the growth phase.
+On the other hand, assuming a wider asymptomatic generation interval (higher $\kappa_a$) increases $q$ because
+
 Figure~\ref{fig.relevance}C shows that
@@
 In other words, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread, it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
+
+%Here, given $1/r=7$ days, $1/\gamma_e=4$ days, and
+%$1/\gamma_s=10$ days, we evaluate the impacts of $p$ and $\beta_a/\beta_s$ on the
+%relevance of asymptomatic infections, given variation in 
+%$p$, $\beta_a/\beta_s$, and $\gamma_a$.  We consider two
+%scenarios, one in which asymptomatic infectiousness is short, i.e., with
+%average duration of $1/\gamma_a=5$ days,
+%and one in which asymptomatic infectiousness is long,i.e., $1/\gamma_a=20$ days.
+%We use the renewal equation formalism to explicitly link duration of infectiousness to the 
+%basic reproductive number (for technical details and example 
+%applications see~\citep{wallinga2007generation,weitz_scirep2015,champredon_2018}).
+%In brief, we
+%infer ${\cal{R}}_0$ compatible with an estimated value of $r$ from case
+%data given the generation interval distribution 
+%(set by $q$ and the duration in the exposed and infectious states).
+%By solving for $q$, we can then relate the basic
+%reproduction number to the relative transmission rates ($\beta_a/\beta_s$)
+%and the probability, $p$, of asymptomatic cases at the individual scale.
+%Figure~\ref{fig.relevance}C shows that
+%when $\gamma_a<\gamma_s$, then the strength ${\cal{R}}_0$ increases
+%with $q$. 
+%This increase arises because asymptomatic infections that resolve
+%slower increase the duration of
+%overall generation intervals (see~\citep{park_2019practical}). In contrast,
+%Figure~\ref{fig.relevance}D show that
+%when $\gamma_a>\gamma_s$ then
+%the strength ${\cal{R}}_0$ decreases with $q$.  
+%This decrease arises because asymptomatic infections that resolve
+%faster decrease the duration of
+%overall generation intervals (again, see~\citep{park_2019practical}). In both 
+%cases, the dependence of ${\cal{R}}_0$ on $q$ is
+%compared to a baseline of 
+%${\cal{R}}_0\approx 3.1$ in a model with no secondary
+%case production from asymptomatic infections (see filled
+%circle at bottom left of Figure~\ref{fig.relevance}C-D.
+%In other words, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread, it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
 
@@
 \begin{center}
-\includegraphics[width=0.4\textwidth]{group/figheatmap_seird_noname.pdf}
+\includegraphics[width=0.4\textwidth]{figheatmap.pdf}
 \mbox{\hspace{0.05\textwidth}}
-\includegraphics[width=0.44\textwidth]{group/figheatmap_seirdR0_noname.pdf}\\
+\includegraphics[width=0.4\textwidth]{figheatmap_R0.pdf}\\
 \mbox{}\\
-\includegraphics[width=0.4\textwidth]{group/figheatmap_seird_2_noname.pdf}
+\includegraphics[width=0.4\textwidth]{figheatmap_kappa.pdf}
 \mbox{\hspace{0.05\textwidth}}
-\includegraphics[width=0.44\textwidth]{group/figheatmap_seird_R02_noname.pdf}
+\includegraphics[width=0.4\textwidth]{figheatmap_kappa_R0.pdf}
 \caption{Relevance of asymptomatic transmission given variation in

### 2020-03-05 figheatmap.R

@@ -1,0 +1,43 @@
+library(emdbook)
+library(ggplot2); theme_set(theme_bw())
+
+r <- 1/7
+G_s <- 6
+kappa_s <- 0.5
+kappa_a <- 0.5
+
+z <- seq(0.01, 0.99, by=0.005)
+relG <- seq(0.5, 1.5, by=0.005)
+
+qodds <- apply2d(
+  "*", 
+  z/(1-z),
+  (1 + kappa_s * r * G_s)^(1/kappa_s)/(1 + kappa_a * r * relG * G_s)^(1/kappa_a)
+)
+
+qvals <- qodds/(1+qodds)
+
+figdata <- data.frame(
+  q=c(qvals),
+  z=rep(z, length(relG)),
+  relG=rep(relG, each=length(z))
+)
+
+g0 <- ggplot(figdata) +
+  geom_raster(aes(relG, z, fill=q)) +
+  geom_contour(aes(relG, z, z=q), col="white") +
+  scale_x_continuous("Relative mean asymptomatic generation interval", expand=c(0, 0),
+                     breaks=3:7*2/10) +
+  scale_y_continuous("Intrinsic proportion of asymptomatic transmission", expand=c(0, 0),
+                     limits=c(0, 1),
+                     breaks=0:10/10) +
+  scale_fill_gradientn(colors=c("#2B4162", "#40E0D0", "#FF8C00", "#FF0080"),
+                       limits=c(0, 1),
+                       breaks=0:5*2/10) +
+  ggtitle("A. Relevance of asymptomatic cases") +
+  theme(
+    legend.title = element_blank(),
+    legend.key.height = unit(1.6, "cm")
+  )
+
+ggsave("figheatmap.pdf", g0, width=5, height=4)

### 2020-03-05 figheatmap_R0.R

@@ -1,0 +1,43 @@
+library(emdbook)
+library(ggplot2); theme_set(theme_bw())
+
+r <- 1/7
+G_s <- 6
+kappa_s <- 0.5
+kappa_a <- 0.5
+
+z <- seq(0.01, 0.99, by=0.005)
+relG <- seq(0.5, 1.5, by=0.005)
+
+R0 <- apply2d(
+  function(x, y) {
+    1/((1-x) * (1 + kappa_s * r * G_s)^(-1/kappa_s) + x * (1 + kappa_a * r * y * G_s)^(-1/kappa_a))
+  }, 
+  z,
+  relG
+)
+
+figdata <- data.frame(
+  R0=c(R0),
+  z=rep(z, length(relG)),
+  relG=rep(relG, each=length(z))
+)
+
+g0 <- ggplot(figdata) +
+  geom_raster(aes(relG, z, fill=R0)) +
+  geom_contour(aes(relG, z, z=R0), col="white") +
+  scale_x_continuous("Relative mean asymptomatic generation interval", expand=c(0, 0),
+                     breaks=3:7*2/10) +
+  scale_y_continuous("Intrinsic proportion of asymptomatic transmission", expand=c(0, 0),
+                     limits=c(0, 1),
+                     breaks=0:10/10) +
+  scale_fill_gradientn(colors=c("#2B4162", "#40E0D0", "#FF8C00", "#FF0080"),
+                       limits=c(1.4, 2.8),
+                       breaks=c(1.4, 1.6, 1.8, 2.0, 2.2, 2.4, 2.6, 2.8)) +
+  ggtitle("B. Basic reproduction number") +
+  theme(
+    legend.title = element_blank(),
+    legend.key.height = unit(1.6, "cm")
+  )
+
+ggsave("figheatmap_R0.pdf", g0, width=5, height=4)

### 2020-03-05 figheatmap_kappa.R

@@ -1,0 +1,43 @@
+library(emdbook)
+library(ggplot2); theme_set(theme_bw())
+
+r <- 1/7
+G_s <- 6
+G_a <- 6
+kappa_s <- 0.5
+
+z <- seq(0.01, 0.99, by=0.005)
+relkappa <- seq(0.5, 1.5, by=0.005)
+
+qodds <- apply2d(
+  "*", 
+  z/(1-z),
+  (1 + kappa_s * r * G_s)^(1/kappa_s)/(1 + kappa_s * relkappa * r * G_a)^(1/(kappa_s * relkappa))
+)
+
+qvals <- qodds/(1+qodds)
+
+figdata <- data.frame(
+  q=c(qvals),
+  z=rep(z, length(relkappa)),
+  relkappa=rep(relkappa, each=length(z))
+)
+
+g0 <- ggplot(figdata) +
+  geom_raster(aes(relkappa, z, fill=q)) +
+  geom_contour(aes(relkappa, z, z=q), col="white") +
+  scale_x_continuous("Relative asymptomatic generation-interval dispersion", expand=c(0, 0),
+                     breaks=3:7*2/10) +
+  scale_y_continuous("Intrinsic proportion of asymptomatic transmission", expand=c(0, 0),
+                     limits=c(0, 1),
+                     breaks=0:10/10) +
+  scale_fill_gradientn(colors=c("#2B4162", "#40E0D0", "#FF8C00", "#FF0080"),
+                       limits=c(0, 1),
+                       breaks=0:5*2/10) +
+  ggtitle("C. Relevance of asymptomatic cases") +
+  theme(
+    legend.title = element_blank(),
+    legend.key.height = unit(1.6, "cm")
+  )
+
+ggsave("figheatmap_kappa.pdf", g0, width=5, height=4)

### 2020-03-05 figheatmap_kappa_R0.R

@@ -1,0 +1,43 @@
+library(emdbook)
+library(ggplot2); theme_set(theme_bw())
+
+r <- 1/7
+G_s <- 6
+G_a <- 6
+kappa_s <- 0.5
+
+z <- seq(0.01, 0.99, by=0.005)
+relkappa <- seq(0.5, 1.5, by=0.005)
+
+R0 <- apply2d(
+  function(x, y) {
+    1/((1-x) * (1 + kappa_s * r * G_s)^(-1/kappa_s) + x * (1 + kappa_s * y * r * G_a)^(-1/(kappa_s * y)))
+  }, 
+  z,
+  relkappa
+)
+
+figdata <- data.frame(
+  R0=c(R0),
+  z=rep(z, length(relkappa)),
+  relkappa=rep(relkappa, each=length(z))
+)
+
+g0 <- ggplot(figdata) +
+  geom_raster(aes(relkappa, z, fill=R0)) +
+  geom_contour(aes(relkappa, z, z=R0), col="white") +
+  scale_x_continuous("Relative asymptomatic generation-interval dispersion", expand=c(0, 0),
+                     breaks=3:7*2/10) +
+  scale_y_continuous("Intrinsic proportion of asymptomatic transmission", expand=c(0, 0),
+                     limits=c(0, 1),
+                     breaks=0:10/10) +
+  scale_fill_gradientn(colors=c("#2B4162", "#40E0D0", "#FF8C00", "#FF0080"),
+                       limits=c(1.4, 2.8),
+                       breaks=c(1.4, 1.6, 1.8, 2.0, 2.2, 2.4, 2.6, 2.8)) +
+  ggtitle("D. Basic reproduction number") +
+  theme(
+    legend.title = element_blank(),
+    legend.key.height = unit(1.6, "cm")
+  )
+
+ggsave("figheatmap_kappa_R0.pdf", g0, width=5, height=4)

### 2020-03-05 short.body.tex
i like this explanation

@@
 Across the ranges of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.relevance}A,C).
-When the mean asymptomatic generation interval is longer than the mean symptomatic generation interval, $q$ decreases because short generation intervals (thus, faster infection) drive transmission events during the growth phase.
-On the other hand, assuming a wider asymptomatic generation interval (higher $\kappa_a$) increases $q$ because
+When the mean asymptomatic generation interval is longer than the mean symptomatic generation interval, $q$ decreases because short generation intervals (i.e., fast transmission) drive transmission events during the growth phase.
+On the other hand, assuming a wider asymptomatic generation interval (higher $\kappa_a$) increases $q$ because the amount of short generation intervals (i.e., the proportion of faster transmission) increases.
 
-Figure~\ref{fig.relevance}C shows that
-when $\gamma_a<\gamma_s$, then the strength ${\cal{R}}_0$ increases
-with $q$. 
-This increase arises because asymptomatic infections that resolve
-slower increase the duration of
-overall generation intervals (see~\citep{park_2019practical}). In contrast,
-Figure~\ref{fig.relevance}D show that
-when $\gamma_a>\gamma_s$ then
-the strength ${\cal{R}}_0$ decreases with $q$.  
-This decrease arises because asymptomatic infections that resolve
-faster decrease the duration of
-overall generation intervals (again, see~\citep{park_2019practical}). In both 
-cases, the dependence of ${\cal{R}}_0$ on $q$ is
-compared to a baseline of 
-${\cal{R}}_0\approx 3.1$ in a model with no secondary
-case production from asymptomatic infections (see filled
-circle at bottom left of Figure~\ref{fig.relevance}C-D.
-In other words, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread, it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
+%Figure~\ref{fig.relevance}C shows that
+%when $\gamma_a<\gamma_s$, then the strength ${\cal{R}}_0$ increases
+%with $q$. 
+%This increase arises because asymptomatic infections that resolve
+%slower increase the duration of
+%overall generation intervals (see~\citep{park_2019practical}). In contrast,
+%Figure~\ref{fig.relevance}D show that
+%when $\gamma_a>\gamma_s$ then
+%the strength ${\cal{R}}_0$ decreases with $q$.  
+%This decrease arises because asymptomatic infections that resolve
+%faster decrease the duration of
+%overall generation intervals (again, see~\citep{park_2019practical}). In both 
+%cases, the dependence of ${\cal{R}}_0$ on $q$ is
+%compared to a baseline of 
+%${\cal{R}}_0\approx 3.1$ in a model with no secondary
+%case production from asymptomatic infections (see filled
+%circle at bottom left of Figure~\ref{fig.relevance}C-D.
+%In other words, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread, it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
 

### 2020-03-06 abs.tex
almost there?

--- 2020-03-05 asymp_report_disease.abs.tex
@@
 individuals. As we show, the impact of asymptomatic
-cases depends on the interval over which asymptomatic cases
-are infectious.  If the infectious duration of asymptomatic cases differs than that 
+cases depends on the generation intervals of asymptomatic cases.  
+If the generation intervals of asymptomatic cases differs than that 
 of symptomatic cases, then estimates of the basic reproductive ratio which do not explicitly account for asymptomatic cases may be systematically biased.
-Specifically, if asymptomatic cases have a shorter duration,
-${\cal{R}}_0$ will be over-estimated, and if they have a longer duration, ${\cal{R}}_0$ will be under-estimated.
+Specifically, if asymptomatic cases have a shorter generation interval,
+${\cal{R}}_0$ will be over-estimated, and if they have a longer generation interval, ${\cal{R}}_0$ will be under-estimated.
 %If infectiousness of asymptomatic cases is relatively short/long in duration compared

### 2020-03-06 short.body.tex
almost there?

@@
 Across the ranges of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.relevance}A,C).
-When the mean asymptomatic generation interval is longer than the mean symptomatic generation interval, $q$ decreases because short generation intervals (i.e., fast transmission) drive transmission events during the growth phase.
-On the other hand, assuming a wider asymptomatic generation interval (higher $\kappa_a$) increases $q$ because the amount of short generation intervals (i.e., the proportion of faster transmission) increases.
+When the mean asymptomatic generation interval is longer than the mean symptomatic generation interval, $q$ decreases because short generation intervals (i.e., fast transmission) caused by symptomatic individuals drive the transmission during the growth phase.
+On the other hand, assuming a wide generation-interval distribution (higher $\kappa_a$) for asymptomatic individuals increases $q$ because the amount of short generation intervals (i.e., the proportion of faster transmission by asymptomatic individuals) increases.
 
-%Figure~\ref{fig.relevance}C shows that
-%when $\gamma_a<\gamma_s$, then the strength ${\cal{R}}_0$ increases
-%with $q$. 
-%This increase arises because asymptomatic infections that resolve
-%slower increase the duration of
-%overall generation intervals (see~\citep{park_2019practical}). In contrast,
-%Figure~\ref{fig.relevance}D show that
-%when $\gamma_a>\gamma_s$ then
-%the strength ${\cal{R}}_0$ decreases with $q$.  
-%This decrease arises because asymptomatic infections that resolve
-%faster decrease the duration of
-%overall generation intervals (again, see~\citep{park_2019practical}). In both 
-%cases, the dependence of ${\cal{R}}_0$ on $q$ is
-%compared to a baseline of 
-%${\cal{R}}_0\approx 3.1$ in a model with no secondary
-%case production from asymptomatic infections (see filled
-%circle at bottom left of Figure~\ref{fig.relevance}C-D.
-%In other words, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread, it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
+Figure~\ref{fig.relevance}C shows that when $\bar G_s<\bar G_a$, then the strength ${\cal{R}}_0$ increases with $z$.
+This increase arises because asymptomatic infections that have long generation intervals increase the duration of overall generation intervals (see~\citep{park_2019practical})
+Conversely, when $\bar G_a > \bar G_s$ then the strength ${\cal{R}}_0$ decreases with $z$ because short generation intervals of asymptomatic cases reduce the overall mean generation interval.
+Likewise, the amount of dispersion in the generation intervals of asymptomatic cases $\kappa_a$ affect the amount of dispersion in the overall generation intervals; 
+therefore, depending on whether $\kappa_a$ is larger or smaller than $\kappa_s$, increase in the proportion of asymptomatic transmission $z$ can either decrease or increase the strength ${\cal{R}}_0$.
+In other words, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread, it can be over- or under- estimated depending on the relative mean and dispersion in generation intervals of asymptomatic and symptomatic individuals.
 
@@
 The present findings highlight the need to characterize
-the duration of asymptomatic cases and their consequences
+the course of infection of asymptomatic cases and their consequences
 not only for contact tracing but for constraining
@@
 (see Figure~\ref{fig.relevance} top row).
-However, if asymptomatic cases tend to be shorter, then
+However, if asymptomatic cases tend to have shorter infection, then
 current estimates of ${\cal{R}}_0$ may be over-estimates of the
@@
 \caption{Relevance of asymptomatic transmission given variation in
-relative transmission and probability that a given, newly infected individual is asymptomatic.  (Top) Long duration asymptomatic cases increase ${\cal{R}}_0$ with increasing relevance.
-(Bottom) Short duration asymptomatic cases decrease ${\cal{R}}_0$ with increasing relevance.
-Technically, renewal equations provide a route to connect
-observed increases in case counts, i.e., ${\cal{R}}_0 = \frac{1}{M(-r)}$
-where $M(-r)=\int_0^{\infty}\mathrm{d} a e^{-ra}g(a)$.
-For the present model,
-$M(r)=qM_E(-r)M_{I_a}(-r)+(1-q)M_E(-r)M_{I_s}(-r)$
-where each of the component functions are $M_E(-r)=\frac{\gamma_e}{\gamma_e+r}$,
-$M_{I_a}(-r)=\frac{\gamma_a}{\gamma_a+r}$, 
-$M_{I_s}(-r)=\frac{\gamma_s}{\gamma_s+r}$,
-and $q$ is the fraction of realized new secondary cases caused by
-asymptomatic individuals.  In all of these heatmaps, $\gamma_e=1/4$,
-$\gamma_s=1/10$, and $r=1/7$. Here, the average duration
-in symptomatic and asymptomatic states are $T_s=1/\gamma_s$ and 
-$T_a=1/\gamma_a$, respectively. Here the filled circle denotes ${\cal{R}}_0\approx 3.12$
-in the event of $p=0$ and $\beta_a=0$, and the open symbols are for $\beta_a/\beta_s=0.5$ and 
-$p=0.5$ and $p=0.9$ for reference.
+probability that a given, newly infected individual is asymptomatic. (Top) Long/short generation intervals of asymptomatic cases increase/decrease ${\cal{R}}_0$ with decreasing/increasing relevance.
+(Bottom) Wide/narrow generation intervals of asymptomatic cases decrease/increase ${\cal{R}}_0$ with increasing/decreasing relevance.
+% Technically, renewal equations provide a route to connect
+% observed increases in case counts, i.e., ${\cal{R}}_0 = \frac{1}{M(-r)}$
+% where $M(-r)=\int_0^{\infty}\mathrm{d} a e^{-ra}g(a)$.
+% For the present model,
+% $M(r)=qM_E(-r)M_{I_a}(-r)+(1-q)M_E(-r)M_{I_s}(-r)$
+% where each of the component functions are $M_E(-r)=\frac{\gamma_e}{\gamma_e+r}$,
+% $M_{I_a}(-r)=\frac{\gamma_a}{\gamma_a+r}$, 
+% $M_{I_s}(-r)=\frac{\gamma_s}{\gamma_s+r}$,
+% and $q$ is the fraction of realized new secondary cases caused by
+% asymptomatic individuals.  In all of these heatmaps, $\gamma_e=1/4$,
+% $\gamma_s=1/10$, and $r=1/7$. Here, the average duration
+% in symptomatic and asymptomatic states are $T_s=1/\gamma_s$ and 
+% $T_a=1/\gamma_a$, respectively. Here the filled circle denotes ${\cal{R}}_0\approx 3.12$
+% in the event of $p=0$ and $\beta_a=0$, and the open symbols are for $\beta_a/\beta_s=0.5$ and 
+% $p=0.5$ and $p=0.9$ for reference.
 %Renewal equations provide a route to connect

### 2020-03-06 short.body.tex
push

@@
 Both types of individuals can infect others, but, they differ in their intrinsic reproduction numbers, ${\cal{R}}_a$ and ${\cal{R}}_s$, as well as intrinsic generation-interval distributions, $g_a(\tau)$ and $g_s(\tau)$, reflecting their differences in the abilities to transmit and the courses of infection.
-Generation intervals, which are defined as the time between when an individual is infected and when that individual infects another person, depend on the natural history of infection:
+Generation intervals, which are defined as the time between when an individual is infected and when that individual infects another person \citep{svensson2007note}, depend on the natural history of infection:
 an individual with subclinical, and fast-clearing, symptoms is likely to have short generation intervals, whereas an individual with mild, but long-lasting, symptoms is likely to have long generation intervals.
@@
 
-The basic reproduction number, ${\cal{R}}_0$, characterize the strength of an epidemic in an otherwise susceptible population:
+The basic reproduction number, ${\cal{R}}_0$, characterize the strength of an epidemic in an otherwise susceptible population \citep{anderson1992infectious}:
 \begin{equation}
@@
 Here, given $1/r=7$ days, $\bar G_s=6$ days, and $\kappa_s=0.5$, we evaluate the impacts of intrinsic proportion of asymptomatic transmission $z$ on the realized relevance of asymptomatic infection, given variation in relative mean generation interval $\bar G_a/\bar G_s$ and relative generation-interval dispersion $\kappa_a/\kappa_s$ of asymptomatic cases.
-We vary $\bar G_a/\bar G_s$ and $\kappa_a/\kappa_s$ from 0.5 to 1.5, one at a time, and infer $q$ as well as ${\cal{R}}_0$ compatible with an estimated value of $r$ from case data given the generation interval distributions of asymptomatic and asymptomatic cases.
+We vary $\bar G_a/\bar G_s$ and $\kappa_a/\kappa_s$ between 0.5 and 1.5 one at a time, and infer $q$ and ${\cal{R}}_0$ compatible with an estimated value of $r$ from case data given the generation interval distributions of asymptomatic and asymptomatic cases.
 Across the ranges of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.relevance}A,C).
-When the mean asymptomatic generation interval is longer than the mean symptomatic generation interval, $q$ decreases because short generation intervals (i.e., fast transmission) caused by symptomatic individuals drive the transmission during the growth phase.
-On the other hand, assuming a wide generation-interval distribution (higher $\kappa_a$) for asymptomatic individuals increases $q$ because the amount of short generation intervals (i.e., the proportion of faster transmission by asymptomatic individuals) increases.
+When the mean asymptomatic generation interval is longer than the mean symptomatic generation interval, $q$ decreases because short generation intervals (i.e., fast transmission) caused by symptomatic individuals drive the transmission during the growth phase (Figure~\ref{fig.relevance}A).
+On the other hand, assuming a wide generation-interval distribution (higher $\kappa_a$) for asymptomatic individuals increases $q$ because the amount of short generation intervals (i.e., the proportion of faster transmission by asymptomatic individuals) increases (Figure~\ref{fig.relevance}C).
 
@@
 Likewise, the amount of dispersion in the generation intervals of asymptomatic cases $\kappa_a$ affect the amount of dispersion in the overall generation intervals; 
-therefore, depending on whether $\kappa_a$ is larger or smaller than $\kappa_s$, increase in the proportion of asymptomatic transmission $z$ can either decrease or increase the strength ${\cal{R}}_0$.
+therefore, depending on whether $\kappa_a$ is larger or smaller than $\kappa_s$, increase in the proportion of asymptomatic transmission $z$ can either decrease or increase the strength ${\cal{R}}_0$ (Figure~\ref{fig.relevance}D).
 In other words, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread, it can be over- or under- estimated depending on the relative mean and dispersion in generation intervals of asymptomatic and symptomatic individuals.

### 2020-03-06 short.body.tex
typo

@@
 of initiating an asymptomatic case, asymptomatic case duration, and
-the tranmission rates from asymptomatic individuals) to dynamics at the
+the transmission rates from asymptomatic individuals) to dynamics at the
 population scale. That is, rather than focusing on the prevalence

### 2020-03-06 short.body.tex
tweak

@@
 \end{equation}
-Then, the \emph{intrinsic} proportion of asymptomatic $z$ and symptomatic $1-z$ transmission is equal to their relative contribution toward the basic reproduction number, 
+We define the intrinsic proportions of asymptomatic and symptomatic transmission as their relative contribution toward the basic reproduction number:
 \begin{eqnarray}
@@
 \end{eqnarray}
-Then, the \emph{intrinsic} generation-interval distribution depends on the intrinsic proportion of asymptomatic vs.~symptomatic transmission and their corresponding \emph{intrinsic} generation-interval distributions:
+Then, the intrinsic generation-interval distribution depends on the intrinsic proportion of asymptomatic vs.~symptomatic transmission and their corresponding intrinsic generation-interval distributions:
 \begin{equation}

### 2020-03-06 short.body.tex
new figs

@@
 Here, given $1/r=7$ days, $\bar G_s=6$ days, and $\kappa_s=0.5$, we evaluate the impacts of intrinsic proportion of asymptomatic transmission $z$ on the realized relevance of asymptomatic infection, given variation in relative mean generation interval $\bar G_a/\bar G_s$ and relative generation-interval dispersion $\kappa_a/\kappa_s$ of asymptomatic cases.
-We vary $\bar G_a/\bar G_s$ and $\kappa_a/\kappa_s$ between 0.5 and 1.5 one at a time, and infer $q$ and ${\cal{R}}_0$ compatible with an estimated value of $r$ from case data given the generation interval distributions of asymptomatic and asymptomatic cases.
+We vary $\bar G_a/\bar G_s$ and $\kappa_a/\kappa_s$ between 0.5 and 2 one at a time, and infer $q$ and ${\cal{R}}_0$ compatible with an estimated value of $r$ from case data given the generation interval distributions of asymptomatic and asymptomatic cases.
 Across the ranges of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.relevance}A,C).

### 2020-03-06 figheatmap.R

@@ -2,12 +2,12 @@ library(emdbook)
 library(ggplot2); theme_set(theme_bw())
 
 r <- 1/7
-G_s <- 6
+G_s <- 7
 kappa_s <- 0.5
 kappa_a <- 0.5
 
 z <- seq(0.01, 0.99, by=0.005)
-relG <- seq(0.5, 1.5, by=0.005)
+relG <- exp(seq(log(0.5), log(2), by=0.005))
 
 qodds <- apply2d(
   "*", 
@@ -26,8 +26,8 @@ figdata <- data.frame(
 g0 <- ggplot(figdata) +
   geom_raster(aes(relG, z, fill=q)) +
   geom_contour(aes(relG, z, z=q), col="white") +
-  scale_x_continuous("Relative mean asymptomatic generation interval", expand=c(0, 0),
-                     breaks=3:7*2/10) +
+  scale_x_log10("Relative mean asymptomatic generation interval", expand=c(0, 0),
+                     breaks=c(0.5, 1, 2)) +
   scale_y_continuous("Intrinsic proportion of asymptomatic transmission", expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +

### 2020-03-06 figheatmap_R0.R

@@ -2,12 +2,12 @@ library(emdbook)
 library(ggplot2); theme_set(theme_bw())
 
 r <- 1/7
-G_s <- 6
+G_s <- 7
 kappa_s <- 0.5
 kappa_a <- 0.5
 
 z <- seq(0.01, 0.99, by=0.005)
-relG <- seq(0.5, 1.5, by=0.005)
+relG <- exp(seq(log(0.5), log(2), by=0.01))
 
 R0 <- apply2d(
   function(x, y) {
@@ -26,14 +26,14 @@ figdata <- data.frame(
 g0 <- ggplot(figdata) +
   geom_raster(aes(relG, z, fill=R0)) +
   geom_contour(aes(relG, z, z=R0), col="white") +
-  scale_x_continuous("Relative mean asymptomatic generation interval", expand=c(0, 0),
-                     breaks=3:7*2/10) +
+  scale_x_log10("Relative mean asymptomatic generation interval", expand=c(0, 0),
+                     breaks=c(0.5, 1, 2)) +
   scale_y_continuous("Intrinsic proportion of asymptomatic transmission", expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +
   scale_fill_gradientn(colors=c("#2B4162", "#40E0D0", "#FF8C00", "#FF0080"),
-                       limits=c(1.4, 2.8),
-                       breaks=c(1.4, 1.6, 1.8, 2.0, 2.2, 2.4, 2.6, 2.8)) +
+                       limits=c(1.5, 4),
+                       breaks=c(1.5, 2, 2.5, 3.0, 3.5, 4)) +
   ggtitle("B. Basic reproduction number") +
   theme(
     legend.title = element_blank(),

### 2020-03-06 figheatmap_kappa.R

@@ -2,12 +2,12 @@ library(emdbook)
 library(ggplot2); theme_set(theme_bw())
 
 r <- 1/7
-G_s <- 6
-G_a <- 6
+G_s <- 7
+G_a <- 7
 kappa_s <- 0.5
 
 z <- seq(0.01, 0.99, by=0.005)
-relkappa <- seq(0.5, 1.5, by=0.005)
+relkappa <- exp(seq(log(0.5), log(2), by=0.005))
 
 qodds <- apply2d(
   "*", 
@@ -26,8 +26,8 @@ figdata <- data.frame(
 g0 <- ggplot(figdata) +
   geom_raster(aes(relkappa, z, fill=q)) +
   geom_contour(aes(relkappa, z, z=q), col="white") +
-  scale_x_continuous("Relative asymptomatic generation-interval dispersion", expand=c(0, 0),
-                     breaks=3:7*2/10) +
+  scale_x_log10("Relative asymptomatic generation-interval dispersion", expand=c(0, 0),
+                     breaks=c(0.5, 1, 2)) +
   scale_y_continuous("Intrinsic proportion of asymptomatic transmission", expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +

### 2020-03-06 figheatmap_kappa_R0.R

@@ -2,12 +2,12 @@ library(emdbook)
 library(ggplot2); theme_set(theme_bw())
 
 r <- 1/7
-G_s <- 6
-G_a <- 6
+G_s <- 7
+G_a <- 7
 kappa_s <- 0.5
 
 z <- seq(0.01, 0.99, by=0.005)
-relkappa <- seq(0.5, 1.5, by=0.005)
+relkappa <- exp(seq(log(0.5), log(2), by=0.01))
 
 R0 <- apply2d(
   function(x, y) {
@@ -26,14 +26,14 @@ figdata <- data.frame(
 g0 <- ggplot(figdata) +
   geom_raster(aes(relkappa, z, fill=R0)) +
   geom_contour(aes(relkappa, z, z=R0), col="white") +
-  scale_x_continuous("Relative asymptomatic generation-interval dispersion", expand=c(0, 0),
-                     breaks=3:7*2/10) +
+  scale_x_log10("Relative asymptomatic generation-interval dispersion", expand=c(0, 0),
+                     breaks=c(0.5, 1, 2)) +
   scale_y_continuous("Intrinsic proportion of asymptomatic transmission", expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +
   scale_fill_gradientn(colors=c("#2B4162", "#40E0D0", "#FF8C00", "#FF0080"),
-                       limits=c(1.4, 2.8),
-                       breaks=c(1.4, 1.6, 1.8, 2.0, 2.2, 2.4, 2.6, 2.8)) +
+                       limits=c(1.5, 4),
+                       breaks=c(1.5, 2, 2.5, 3.0, 3.5, 4)) +
   ggtitle("D. Basic reproduction number") +
   theme(
     legend.title = element_blank(),

### 2020-03-06 short.body.tex
tweak

@@
 
-Here, given $1/r=7$ days, $\bar G_s=6$ days, and $\kappa_s=0.5$, we evaluate the impacts of intrinsic proportion of asymptomatic transmission $z$ on the realized relevance of asymptomatic infection, given variation in relative mean generation interval $\bar G_a/\bar G_s$ and relative generation-interval dispersion $\kappa_a/\kappa_s$ of asymptomatic cases.
+Here, given $1/r=7$ days, $\bar G_s=7$ days, and $\kappa_s=0.5$, we evaluate the impacts of intrinsic proportion of asymptomatic transmission $z$ on the realized relevance of asymptomatic infection, given variation in relative mean generation interval $\bar G_a/\bar G_s$ and relative generation-interval dispersion $\kappa_a/\kappa_s$ of asymptomatic cases.
 We vary $\bar G_a/\bar G_s$ and $\kappa_a/\kappa_s$ between 0.5 and 2 one at a time, and infer $q$ and ${\cal{R}}_0$ compatible with an estimated value of $r$ from case data given the generation interval distributions of asymptomatic and asymptomatic cases.

### 2020-03-06 figheatmap_kappa.R
axis label missing

@@ -27,7 +27,8 @@ g0 <- ggplot(figdata) +
   geom_raster(aes(relkappa, z, fill=q)) +
   geom_contour(aes(relkappa, z, z=q), col="white") +
   scale_x_log10("Relative asymptomatic generation-interval dispersion", expand=c(0, 0),
-                     breaks=c(0.5, 1, 2)) +
+                breaks=c(0.5, 1, 2),
+                limits=c(0.5, 2)) +
   scale_y_continuous("Intrinsic proportion of asymptomatic transmission", expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +

### 2020-03-06 figheatmap_kappa_R0.R

@@ -27,7 +27,8 @@ g0 <- ggplot(figdata) +
   geom_raster(aes(relkappa, z, fill=R0)) +
   geom_contour(aes(relkappa, z, z=R0), col="white") +
   scale_x_log10("Relative asymptomatic generation-interval dispersion", expand=c(0, 0),
-                     breaks=c(0.5, 1, 2)) +
+                breaks=c(0.5, 1, 2),
+                limits=c(0.5, 2)) +
   scale_y_continuous("Intrinsic proportion of asymptomatic transmission", expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +

### 2020-03-06 short.body.tex
Working.

--- 2020-03-06 short.body.tex
@@
 %with severe symptoms?  
-Here, we attempt to address the impact of asymptomatic cases differently, by relating 
-individual-level features of asymptomatic cases (e.g., the probability
-of initiating an asymptomatic case, asymptomatic case duration, and
-the transmission rates from asymptomatic individuals) to dynamics at the
-population scale. That is, rather than focusing on the prevalence
+There is currently a lot of interest in the role of asymptomatic infections in COVIF for two major reasons. 
+First, the proportion of infections that are asymptomatic is critical to attempts to estimate the likely burden of severe outcomes (including mortality) when the virus spreads through a population.
+Second, understanding the possible role of \emph{transmission} by asymptomatic individuals is crucial to planning surveillance and control efforts.
+
+Here, we focus on a third effect. 
+If asymptomatic cases are important for transmission, they also have the potential to affect estimates of key epidemiological parameters. 
+Here, we investigate the relationship between individual-level features of asymptomatic cases (e.g., the probability of initiating an asymptomatic case, asymptomatic case duration, and the transmission rates from asymptomatic individuals) to dynamics at the population scale.
+That is, rather than focusing on the prevalence
 of asymptomatic cases, we are interested in understanding the
@@
 
-To begin, consider a renewal equation variant in which incidence $i$ is divided into two categories -- $i_a$ and $i_s$ -- corresponding to incidence of asymptomatic and symptomatic cases, respectively.
-Both types of individuals can infect others, but, they differ in their intrinsic reproduction numbers, ${\cal{R}}_a$ and ${\cal{R}}_s$, as well as intrinsic generation-interval distributions, $g_a(\tau)$ and $g_s(\tau)$, reflecting their differences in the abilities to transmit and the courses of infection.
+We model viral spread using a renewal-equation framework, with incidence $i$ is divided into two categories -- $i_a$ and $i_s$ -- corresponding to incidence of asymptomatic and symptomatic cases, respectively.
+Both types of individuals can infect others, but they differ in their intrinsic reproduction numbers, ${\cal{R}}_a$ and ${\cal{R}}_s$, as well as intrinsic generation-interval distributions, $g_a(\tau)$ and $g_s(\tau)$.
 Generation intervals, which are defined as the time between when an individual is infected and when that individual infects another person \citep{svensson2007note}, depend on the natural history of infection:
-an individual with subclinical, and fast-clearing, symptoms is likely to have short generation intervals, whereas an individual with mild, but long-lasting, symptoms is likely to have long generation intervals.
-In total, the dynamics of susceptibles and incidence are:
+individuals with subclinical cases may have fast clearance and short generation intervals, or slow viral reproduction and long generation intervals.
+
+Neglecting births and loss of immunity on the time scale of the outbreak, the dynamics of susceptibles and incidence are:
 \begin{eqnarray}
@@
 \end{eqnarray}
-Here, $p$ is the fraction of asymptomatic cases that are generated for each infected individual ($i_a(t)= p i(t)$), and $1-p$ is the fraction of symptomatic cases that are generated for each infected individual ($i_s(t)= (1-p) i(t)$).
+Here, $p$ is the proportion of \emph{incident cases} that are asymptomatic.
 
-%To begin, consider a SEIR model variant in which there are two infectious categories --
-%$I_a$ and $I_s$ -- corresponding to asymptomatic and symptomatic cases,
-%respectively. Both types of individuals can infect others, but,
-%only symptomatic cases can lead to fatalities, denoted
-%by the $D$ category. In total, the dynamics of susceptibles, exposed,
-%infectious, recovered, and dead are:
-%\begin{eqnarray}
-%\dot{S}&=&-\beta_a S I_a -\beta_s S I_s \\
-%\dot{E}&=&\beta_a S I_a +\beta_s S I_s -\gamma_e E\\
-%\dot{I}_a&=&p\gamma_e E-\gamma_a I_a\\
-%\dot{I}_s&=&(1-p)\gamma_e E-\gamma_s I_s\\
-%\dot{R}&=&\gamma_a I_a + (1-f)\gamma_s I_s \\
-%\dot{D}&=&f\gamma_s I_s.
-%\end{eqnarray}
-%Here, $\beta_a$ and $\beta_s$ denote transmission rates,
-%$\gamma_e$ denotes the transition from exposed to infectious,
-%$p$ is the fraction of asymptomatic cases that
-%are generated for each exposed individual,
-%$1-p$ is the fraction of symptomatic cases that
-%are generated for each exposed individual,
-%$\gamma_a$ and $\gamma_s$ denote recovery rates,
-%and $f$ denotes the case fatality ratio for symptomatic cases.
-
-The basic reproduction number, ${\cal{R}}_0$, characterize the strength of an epidemic in an otherwise susceptible population \citep{anderson1992infectious}:
+The basic reproduction number of this system \citep{anderson1992infectious} is:
 \begin{equation}
@@
 \end{equation}
-We define the intrinsic proportions of asymptomatic and symptomatic transmission as their relative contribution toward the basic reproduction number:
-\begin{eqnarray}
-z &=& p {\cal{R}}_a/{\cal{R}}_{0},\\
+We define the ``intrinsic'' proportion of asymptomatic transmission as the relative contribution of asymptomatic cases to the basic reproduction number:
+\begin{equation}
+z = p {\cal{R}}_a/{\cal{R}}_{0}
+\end{equation}
+Note that the intrinsic proportion of symptomatic transmission satisfies
+\begin{equation}
 1-z &=& (1-p) {\cal{R}}_s/{\cal{R}}_{0}.
-\end{eqnarray}
+\end{equation}
+
 Then, the intrinsic generation-interval distribution depends on the intrinsic proportion of asymptomatic vs.~symptomatic transmission and their corresponding intrinsic generation-interval distributions:

### 2020-03-06 short.body.tex
Attempted merge, but I'm confused (there's something going on with file format)

@@
-Epidemic outbreaks include a spectrum of illness, including
-asymptomatic cases that can be mild and/or subclinical.
-As such, symptomatic cases are the predominant focus of treatment and usually represent
-the bulk of reported cases. However, infected individuals who are asymptomatic
-yet infectious can be a critical, albeit poorly characterized
-factor in the spread of pathogens, as well as 
-present challenges for control.
-Asymptomatic individuals
-are hard to trace, unlikely to self-isolate,
-may move outside of quarantine,  
-retain normal social and travel patterns, and potentially spark new
-outbreaks.
+In an epidemic, symptomatic cases are the predominant focus of treatment and usually represent the bulk of reported cases. 
+However, infected individuals who are asymptomatic yet infectious can be a critical factor in the spread of some pathogens.
+Asymptomatic individuals are hard to trace, unlikely to self-isolate, and are likely to retain normal social and travel patterns.
 The COVID-19 outbreak has raised significant
 questions regarding the role of asymptomatic cases~\citep{fauci_nejm2020}.
-%For example, the incidence of asymptomatic
-%infection was estimated to be
-%approximately 33\% (or higher) 
-%from an outbreak of COVID-19 on the Princess Cruises ship~\citep{mizumoto_2020}.
 A key focus has been on estimating asymptomatic prevalence (see~\citep{mizumoto_2020}), e.g., what fraction of individuals have asymptomatic infections relative to those with symptomatic infections?
@@
 %with severe symptoms?
-There is currently a lot of interest in the role of asymptomatic infections in COVIF for two major reasons. 
+
+There is currently a lot of interest in the role of asymptomatic infections in COVID for two major reasons. 
 First, the proportion of infections that are asymptomatic is critical to attempts to estimate the likely burden of severe outcomes (including mortality) when the virus spreads through a population.
@@
 to the production of symptomatic cases.
-%Our purpose is to characterize key drivers of contribution to
-%secondary cases during an outbreak by `asymptomatic' individuals --
-%and help characterize the relevance of asymptomatic transmission to
-%outbreak dynamics and control.
 

### 2020-03-06 short.body.tex
Good night

@@
 \begin{equation}
-1-z &=& (1-p) {\cal{R}}_s/{\cal{R}}_{0}.
+1-z = (1-p) {\cal{R}}_s/{\cal{R}}_{0}.
 \end{equation}
 
-Then, the intrinsic generation-interval distribution depends on the intrinsic proportion of asymptomatic vs.~symptomatic transmission and their corresponding intrinsic generation-interval distributions:
+The intrinsic generation-interval distribution depends on the intrinsic proportion of asymptomatic vs.~symptomatic transmission and their corresponding intrinsic generation-interval distributions:
 \begin{equation}

### 2020-03-06 short.body.tex
edits

@@
+\section{Introduction}
+
 In an epidemic, symptomatic cases are the predominant focus of treatment and usually represent the bulk of reported cases. 
-However, infected individuals who are asymptomatic yet infectious can be a critical factor in the spread of some pathogens.
+However, infected individuals who are asymptomatic yet infectious can be a critical factor in the spread of some pathogens \citep{fraser2004factors}.
 Asymptomatic individuals are hard to trace, unlikely to self-isolate, and are likely to retain normal social and travel patterns.
@@
 
-There is currently a lot of interest in the role of asymptomatic infections in COVID for two major reasons. 
+There is currently a lot of interest in the role of asymptomatic infections in SARS-CoV-2 for two major reasons. 
 First, the proportion of infections that are asymptomatic is critical to attempts to estimate the likely burden of severe outcomes (including mortality) when the virus spreads through a population.
@@
 
-We model viral spread using a renewal-equation framework, with incidence $i$ is divided into two categories -- $i_a$ and $i_s$ -- corresponding to incidence of asymptomatic and symptomatic cases, respectively.
+\section{Methods}
+
+We model viral spread using a renewal-equation framework \citep{heesterbeek1996concept}, which allows us to model the current incidence of infected individuals as a function of previous incidence and how infectiousness of an infected individual varies over the course of their infection;
+in Appendix, we show that results derived from a compartmental model is a special case of the result we present here.
+We divide incidence $i$ into two categories -- $i_a$ and $i_s$ -- corresponding to incidence of asymptomatic and symptomatic cases, respectively.
 Both types of individuals can infect others, but they differ in their intrinsic reproduction numbers, ${\cal{R}}_a$ and ${\cal{R}}_s$, as well as intrinsic generation-interval distributions, $g_a(\tau)$ and $g_s(\tau)$.
@@
 
-The basic reproduction number of this system \citep{anderson1992infectious} is:
+The basic reproduction number -- the expected number of secondary cases generated by an average primary case in a fully susceptible population \citep{anderson1992infectious} -- of this system is:
 \begin{equation}
@@
 \begin{equation}
-z = p {\cal{R}}_a/{\cal{R}}_{0}
+z = p {\cal{R}}_a/{\cal{R}}_{0}.
 \end{equation}
@@
 
-Here, given $1/r=7$ days, $\bar G_s=6$ days, and $\kappa_s=0.5$, we evaluate the impacts of intrinsic proportion of asymptomatic transmission $z$ on the realized relevance of asymptomatic infection, given variation in relative mean generation interval $\bar G_a/\bar G_s$ and relative generation-interval dispersion $\kappa_a/\kappa_s$ of asymptomatic cases.
+Here, given $1/r=7$ days, $\bar G_s=7$ days, and $\kappa_s=0.5$, we evaluate the impacts of intrinsic proportion of asymptomatic transmission $z$ on the realized relevance of asymptomatic infection, given variation in relative mean generation interval $\bar G_a/\bar G_s$ and relative generation-interval dispersion $\kappa_a/\kappa_s$ of asymptomatic cases.
 We vary $\bar G_a/\bar G_s$ and $\kappa_a/\kappa_s$ between 0.5 and 2 one at a time, and infer $q$ and ${\cal{R}}_0$ compatible with an estimated value of $r$ from case data given the generation interval distributions of asymptomatic and asymptomatic cases.
+
+\section{Results}
+
 Across the ranges of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.relevance}A,C).
-When the mean asymptomatic generation interval is longer than the mean symptomatic generation interval, $q$ decreases because short generation intervals (i.e., fast transmission) caused by symptomatic individuals drive the transmission during the growth phase (Figure~\ref{fig.relevance}A).
-On the other hand, assuming a wide generation-interval distribution (higher $\kappa_a$) for asymptomatic individuals increases $q$ because the amount of short generation intervals (i.e., the proportion of faster transmission by asymptomatic individuals) increases (Figure~\ref{fig.relevance}C).
+As the relative mean generation interval of asymptomatic cases, $\bar G_a/\bar G_s$, increases, $q$ decreases because symptomatic cases are more likely to have short generation intervals (i.e., fast transmission events), which drive the spread during the growth phase (Figure~\ref{fig.relevance}A).
+On the other hand, as the relative generation-interval dispersion of asymptomatic cases, $\kappa_a/\kappa_s$, increases, $q$ also increases because the amount of short asymptomatic generation intervals (i.e., the proportion of faster transmission by asymptomatic individuals) increases (Figure~\ref{fig.relevance}C).
 
-Figure~\ref{fig.relevance}C shows that when $\bar G_s<\bar G_a$, then the strength ${\cal{R}}_0$ increases with $z$.
+Figure~\ref{fig.relevance}B compares the effect of relative mean generation interval of asymptomatic cases, $\bar G_a/\bar G_s$, on ${\cal{R}}_0$.
+When $\bar G_s < \bar G_a$, then the strength ${\cal{R}}_0$ increases with $z$.
 This increase arises because asymptomatic infections that have long generation intervals increase the duration of overall generation intervals (see~\citep{park_2019practical})
-Conversely, when $\bar G_a > \bar G_s$ then the strength ${\cal{R}}_0$ decreases with $z$ because short generation intervals of asymptomatic cases reduce the overall mean generation interval.
-Likewise, the amount of dispersion in the generation intervals of asymptomatic cases $\kappa_a$ affect the amount of dispersion in the overall generation intervals; 
-therefore, depending on whether $\kappa_a$ is larger or smaller than $\kappa_s$, increase in the proportion of asymptomatic transmission $z$ can either decrease or increase the strength ${\cal{R}}_0$ (Figure~\ref{fig.relevance}D).
+Conversely, when $\bar G_s > \bar G_a$ then the strength ${\cal{R}}_0$ decreases with $z$ because short generation intervals of asymptomatic cases reduce the overall mean generation interval.
+
+Likewise, Figure~\ref{fig.relevance}D compares the effect of relative generation-interval dispersion of asymptomatic cases, $\kappa_a/\kappa_s$, on ${\cal{R}}_0$.
+Depending on whether $\kappa_a$ is larger or smaller than $\kappa_s$, increase in the proportion of asymptomatic transmission $z$ can either decrease or increase the strength ${\cal{R}}_0$.
 In other words, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread, it can be over- or under- estimated depending on the relative mean and dispersion in generation intervals of asymptomatic and symptomatic individuals.
@@
 
-The present findings highlight the need to characterize
-the course of infection of asymptomatic cases and their consequences
-not only for contact tracing but for constraining
-uncertainty in the strength of the ongoing COVID-19 outbreak~\citep{park_preprint}.
-The present findings are also consistent with
-a recent generalization linking speed, strength, and
-generation intervals, such that
-for a given observed speed
-increases in the mean generation interval imply
-larger reproduction number~\citep{park_2019practical}. Hence, reports of individuals
-with mild, persistent cases 
-suggest the possibility that the mean generation interval for COVID-19
-could be longer than estimated from symptomatic cases alone - possibly
-increasing ${\cal{R}}_0$ and driving a larger fraction of secondary cases
-(see Figure~\ref{fig.relevance} top row).
-However, if asymptomatic cases tend to have shorter infection, then
-current estimates of ${\cal{R}}_0$ may be over-estimates of the
-underlying strength (see Figure~\ref{fig.relevance} bottom row).
-Finally, it is important to note we focused here on the exponential
-phase, but that the asymptomatic relevance $q$ is time-dependent, and will
-vary given the population state structure of infected individuals.  Such
-variation in the ratio of asymptomatic to symptomatic cases
-will also impact estimates of case fatality rates insofar
-as many asymptomatic cases are not counted, particularly early in an outbreak.
-Future work might also consider the ways in which asymptomatic individuals
-modulate resurgent epidemics in a networked metapopulation~\citep{watts_pnas2005}.
+\section{Discussion}
+
+The present findings highlight the need to characterize the course of infection of asymptomatic cases and their consequences not only for contact tracing but for constraining uncertainty in the strength of the ongoing COVID-19 outbreak~\citep{park_preprint}.
+The present findings are also consistent with a recent generalization linking speed, strength, and generation intervals, such that for a given observed speed increases in the mean generation interval imply larger reproduction number~\citep{park_2019practical}.
+Hence, reports of individuals with mild, persistent cases suggest the possibility that the mean generation interval for COVID-19 could be longer than estimated from symptomatic cases alone - possibly increasing ${\cal{R}}_0$ (Figure~\ref{fig.relevance}B).
+However, if asymptomatic cases tend to have shorter infection, then current estimates of ${\cal{R}}_0$ may be over-estimates of the underlying strength (Figure~\ref{fig.relevance}B), although asymptomatic cases may be driving a larger fraction of secondary cases than we would expect when both asymptomatic and symptomatic cases have identical generation-interval distributions (Figure~\ref{fig.relevance}A).
+
+Finally, it is important to note we focused here on the exponential phase, but that the asymptomatic relevance $q$ is time-dependent, and will vary given the population state structure of infected individuals.
+Such variation in the ratio of asymptomatic to symptomatic cases will also impact estimates of case fatality rates insofar as many asymptomatic cases are not counted, particularly early in an outbreak.
+Future work might also consider the ways in which asymptomatic individuals modulate resurgent epidemics in a networked metapopulation~\citep{watts_pnas2005}.
+Characterizing the role of asymptomatic individuals in driving the persistence of the epidemic will be critical for assessing the post-pandemic outcome \citep{lipsitch_preprint}.
 
@@
 \caption{Relevance of asymptomatic transmission given variation in
-probability that a given, newly infected individual is asymptomatic. (Top) Long/short generation intervals of asymptomatic cases increase/decrease ${\cal{R}}_0$ with decreasing/increasing relevance.
-(Bottom) Wide/narrow generation intervals of asymptomatic cases decrease/increase ${\cal{R}}_0$ with increasing/decreasing relevance.
+probability that a given, newly infected individual is asymptomatic. 
+(A) Long/short generation intervals of asymptomatic cases decrease/increase the relevance of asymptomatic cases, $q$.
+(B) Long/short generation intervals of asymptomatic cases increase/decrease the basic reproduction number ${\cal{R}}_0$.
+(C) Wide/narrow generation intervals of asymptomatic cases increase/decrease the relevance of asymptomatic cases, $q$.
+(D) Wide/narrow generation intervals of asymptomatic cases decrease/increase the basic reproduction number ${\cal{R}}_0$.
+For panels A--B, we vary relative mean generation interval of asymptomatic cases, $\bar G_a/\bar G_s$, while assuming $\kappa_a = \kappa_s$.
+For panels C--D, we vary relative generation-interval dispersion of asymptomatic cases, $\kappa_a/\kappa_s$, while assuming $G_a = G_s$.
+As our baseline parameters, we assume $1/r=7$ days, $\bar G_s=7$ days, and $\kappa_s=0.5$.
 % Technically, renewal equations provide a route to connect

### 2020-03-06 figheatmap.R

@@ -1,5 +1,5 @@
 library(emdbook)
-library(ggplot2); theme_set(theme_bw())
+library(ggplot2); theme_set(theme_bw(base_family = "Times"))
 
 r <- 1/7
 G_s <- 7
@@ -26,9 +26,9 @@ figdata <- data.frame(
 g0 <- ggplot(figdata) +
   geom_raster(aes(relG, z, fill=q)) +
   geom_contour(aes(relG, z, z=q), col="white") +
-  scale_x_log10("Relative mean asymptomatic generation interval", expand=c(0, 0),
+  scale_x_log10(expression(paste("Relative mean asymptomatic generation interval, ", italic(G[a]/G[s]))), expand=c(0, 0),
                      breaks=c(0.5, 1, 2)) +
-  scale_y_continuous("Intrinsic proportion of asymptomatic transmission", expand=c(0, 0),
+  scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +
   scale_fill_gradientn(colors=c("#2B4162", "#40E0D0", "#FF8C00", "#FF0080"),
@@ -37,7 +37,7 @@ g0 <- ggplot(figdata) +
   ggtitle("A. Relevance of asymptomatic cases") +
   theme(
     legend.title = element_blank(),
-    legend.key.height = unit(1.6, "cm")
+    legend.key.height = unit(1.8, "cm")
   )
 
-ggsave("figheatmap.pdf", g0, width=5, height=4)
+ggsave("figheatmap.pdf", g0, width=5.3, height=4.3)

### 2020-03-06 figheatmap_R0.R

@@ -1,5 +1,5 @@
 library(emdbook)
-library(ggplot2); theme_set(theme_bw())
+library(ggplot2); theme_set(theme_bw(base_family = "Times"))
 
 r <- 1/7
 G_s <- 7
@@ -26,10 +26,10 @@ figdata <- data.frame(
 g0 <- ggplot(figdata) +
   geom_raster(aes(relG, z, fill=R0)) +
   geom_contour(aes(relG, z, z=R0), col="white") +
-  scale_x_log10("Relative mean asymptomatic generation interval", expand=c(0, 0),
+  scale_x_log10(expression(paste("Relative mean asymptomatic generation interval, ", italic(G[a]/G[s]))), expand=c(0, 0),
                 breaks=c(0.5, 1, 2),
                 limits=c(0.5, 2)) +
-  scale_y_continuous("Intrinsic proportion of asymptomatic transmission", expand=c(0, 0),
+  scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +
   scale_fill_gradientn(colors=c("#2B4162", "#40E0D0", "#FF8C00", "#FF0080"),
@@ -38,7 +38,7 @@ g0 <- ggplot(figdata) +
   ggtitle("B. Basic reproduction number") +
   theme(
     legend.title = element_blank(),
-    legend.key.height = unit(1.6, "cm")
+    legend.key.height = unit(1.8, "cm")
   )
 
-ggsave("figheatmap_R0.pdf", g0, width=5, height=4)
+ggsave("figheatmap_R0.pdf", g0, width=5.3, height=4.3)

### 2020-03-06 figheatmap_kappa.R

@@ -1,5 +1,5 @@
 library(emdbook)
-library(ggplot2); theme_set(theme_bw())
+library(ggplot2); theme_set(theme_bw(base_family = "Times"))
 
 r <- 1/7
 G_s <- 7
@@ -26,10 +26,10 @@ figdata <- data.frame(
 g0 <- ggplot(figdata) +
   geom_raster(aes(relkappa, z, fill=q)) +
   geom_contour(aes(relkappa, z, z=q), col="white") +
-  scale_x_log10("Relative asymptomatic generation-interval dispersion", expand=c(0, 0),
+  scale_x_log10(expression(paste("Relative asymptomatic generation-interval dispersion, ", italic(kappa[a]/kappa[s]))), expand=c(0, 0),
                 breaks=c(0.5, 1, 2),
                 limits=c(0.5, 2)) +
-  scale_y_continuous("Intrinsic proportion of asymptomatic transmission", expand=c(0, 0),
+  scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +
   scale_fill_gradientn(colors=c("#2B4162", "#40E0D0", "#FF8C00", "#FF0080"),
@@ -38,7 +38,7 @@ g0 <- ggplot(figdata) +
   ggtitle("C. Relevance of asymptomatic cases") +
   theme(
     legend.title = element_blank(),
-    legend.key.height = unit(1.6, "cm")
+    legend.key.height = unit(1.8, "cm")
   )
 
-ggsave("figheatmap_kappa.pdf", g0, width=5, height=4)
+ggsave("figheatmap_kappa.pdf", g0, width=5.3, height=4.3)

### 2020-03-06 figheatmap_kappa_R0.R

@@ -1,5 +1,5 @@
 library(emdbook)
-library(ggplot2); theme_set(theme_bw())
+library(ggplot2); theme_set(theme_bw(base_family = "Times"))
 
 r <- 1/7
 G_s <- 7
@@ -26,10 +26,10 @@ figdata <- data.frame(
 g0 <- ggplot(figdata) +
   geom_raster(aes(relkappa, z, fill=R0)) +
   geom_contour(aes(relkappa, z, z=R0), col="white") +
-  scale_x_log10("Relative asymptomatic generation-interval dispersion", expand=c(0, 0),
+  scale_x_log10(expression(paste("Relative asymptomatic generation-interval dispersion, ", italic(kappa[a]/kappa[s]))), expand=c(0, 0),
                 breaks=c(0.5, 1, 2),
                 limits=c(0.5, 2)) +
-  scale_y_continuous("Intrinsic proportion of asymptomatic transmission", expand=c(0, 0),
+  scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +
   scale_fill_gradientn(colors=c("#2B4162", "#40E0D0", "#FF8C00", "#FF0080"),
@@ -38,7 +38,7 @@ g0 <- ggplot(figdata) +
   ggtitle("D. Basic reproduction number") +
   theme(
     legend.title = element_blank(),
-    legend.key.height = unit(1.6, "cm")
+    legend.key.height = unit(1.8, "cm")
   )
 
-ggsave("figheatmap_kappa_R0.pdf", g0, width=5, height=4)
+ggsave("figheatmap_kappa_R0.pdf", g0, width=5.3, height=4.3)

### 2020-03-07 appendix.tex
tweaking stuff

\section*{Supplementary Materials}
\renewcommand\thefigure{S\arabic{figure}}
\renewcommand\theequation{S\arabic{equation}}
\setcounter{figure}{0}
\setcounter{equation}{0}

\subsection*{A compartmental model for asymptomatic/symptomatic cases}

Consider a SEIR model variant in which an infected individual can be either asymptomatic, $I_a$, or symptomatic, $I_s$.
While both cases can recover, we assume that only symptomatic cases can lead to fatalities, denoted
by the $D$ category.
In total, the dynamics of susceptibles, exposed, infectious, recovered, and dead are:
\begin{eqnarray}
\dot{S}&=&-\beta_a S I_a -\beta_s S I_s \\
\dot{E}&=&\beta_a S I_a +\beta_s S I_s -\gamma_e E\\
\dot{I}_a&=&p\gamma_e E-\gamma_a I_a\\
\dot{I}_s&=&(1-p)\gamma_e E-\gamma_s I_s\\
\dot{R}&=&\gamma_a I_a + (1-f)\gamma_s I_s \\
\dot{D}&=&f\gamma_s I_s.
\end{eqnarray}
Here, $\beta_a$ and $\beta_s$ denote transmission rates,
$\gamma_e$ denotes the transition from exposed to infectious,
$p$ is the fraction of asymptomatic cases that
are generated for each exposed individual,
$1-p$ is the fraction of symptomatic cases that
are generated for each exposed individual,
$\gamma_a$ and $\gamma_s$ denote recovery rates,
and $f$ denotes the case fatality ratio for symptomatic cases.

Given that the number of infected individuals increase exponentially at rate $r$ initially, the equations
for the infectious cases can be rewritten given the ansatz
$E(t)=c_e e^{rt}$,
$I_a(t)=c_a e^{rt}$,
$I_s(t)=c_s e^{rt}$.
Then, it follows that 
\begin{eqnarray}
r c_a&=&p\gamma_e c_e-\gamma_a c_a,\\
r c_s&=&(1-p)\gamma_e c_e-\gamma_s c_s,
\end{eqnarray} 
which implies that
\begin{equation}
\frac{c_a}{c_s}=\frac{p}{1-p}\left[\frac{r+\gamma_s}{r+\gamma_a}\right].
\end{equation}
Therefore, the ratio of secondary case production caused by asymptomatic vs.~symptomatic
individuals during the exponential phase should be
\begin{equation}
\frac{q}{1-q} = \left(\frac{\beta_a}{\beta_s}\right)\frac{p}{1-p}\left[\frac{r+\gamma_s}{r+\gamma_a}\right],
\end{equation}
where $q$ is the fraction of new secondary cases caused by
asymptomatic individuals.

The basic reproduction number of this system is:
\begin{equation}
{\cal{R}}_{0}= p {\cal{R}}_a + (1-p) {\cal{R}}_s,
\end{equation}
where 
\begin{eqnarray}
{\cal{R}}_a &=& \frac{\beta_a}{\gamma_a},\\
{\cal{R}}_s &=& \frac{\beta_s}{\gamma_s}.
\end{eqnarray}
The generation-interval distributions for asymptomatic and symptomatic individuals follow the same functional form as the corresponding generation-interval distribution for a single-type SEIR model since both asymptomatic and symptomatic individuals have exponenitally distributed latent and infectious periods \citep{svensson2015influence}:
\begin{eqnarray}
g_a(\tau) &=& \frac{\gamma_e \gamma_a}{\gamma_e - \gamma_a} \left(\exp(-\gamma_a \tau) - \exp(-\gamma_e \tau)\right),\\
g_s(\tau) &=& \frac{\gamma_e \gamma_s}{\gamma_e - \gamma_s} \left(\exp(-\gamma_s \tau) - \exp(-\gamma_e \tau)\right).
\end{eqnarray}
It immediately follows that 
\begin{equation}
\left(\frac{z}{1-z}\right)\left[\frac{\int_0^\infty \exp(-r\tau) g_a(\tau) \mathrm{d}\tau}{\int_0^\infty \exp(-r\tau) g_s(\tau) \mathrm{d}\tau}\right] = \left(\frac{\beta_a}{\beta_s}\right)\frac{p}{1-p}\left[\frac{r+\gamma_s}{r+\gamma_a}\right],
\end{equation}
where $z = p {\cal{R}}_a/{\cal{R}}_{0}$ and $1-z=(1-p) {\cal{R}}_s/{\cal{R}}_{0}$.

\pagebreak

\subsection*{Supplementary figures}

\begin{figure*}[b!]
\begin{center}
\includegraphics[width=0.4\textwidth]{figheatmap_kappa.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.4\textwidth]{figheatmap_kappa_R0.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
the generation-interval dispersion of asymptomatic cases.
(A) Wide/narrow generation intervals of asymptomatic cases increase/decrease the relevance of asymptomatic cases, $q$.
(B) Wide/narrow generation intervals of asymptomatic cases decrease/increase the basic reproduction number ${\cal{R}}_0$.
Here, we vary relative generation-interval dispersion of asymptomatic cases, $\kappa_a/\kappa_s$, while assuming $G_a = G_s$.
As our baseline parameters, we assume $1/r=7$ days, $\bar G_s=7$ days, and $\kappa_s=0.5$.}
\end{center}
\end{figure*}

### 2020-03-07 short.body.tex
tweaking stuff

@@
 
+\begin{figure*}[b!]
+\begin{center}
+\includegraphics[width=0.4\textwidth]{figheatmap.pdf}
+\mbox{\hspace{0.05\textwidth}}
+\includegraphics[width=0.4\textwidth]{figheatmap_R0.pdf}
+\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
+the mean generation interval of asymptomatic cases. 
+(A) Long/short generation intervals of asymptomatic cases decrease/increase the relevance of asymptomatic cases, $q$.
+(B) Long/short generation intervals of asymptomatic cases increase/decrease the basic reproduction number ${\cal{R}}_0$.
+(C) Wide/narrow generation intervals of asymptomatic cases increase/decrease the relevance of asymptomatic cases, $q$.
+(D) Wide/narrow generation intervals of asymptomatic cases decrease/increase the basic reproduction number ${\cal{R}}_0$.
+Here, we vary relative mean generation interval of asymptomatic cases, $\bar G_a/\bar G_s$, while assuming $\kappa_a = \kappa_s$.
+As our baseline parameters, we assume $1/r=7$ days, $\bar G_s=7$ days, and $\kappa_s=0.5$.
+\label{fig.relevance}}
+\end{center}
+\end{figure*}
+
 Across the ranges of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.relevance}A,C).
@@
 Characterizing the role of asymptomatic individuals in driving the persistence of the epidemic will be critical for assessing the post-pandemic outcome \citep{lipsitch_preprint}.
-
-\begin{figure*}[b!]
-\begin{center}
-\includegraphics[width=0.4\textwidth]{figheatmap.pdf}
-\mbox{\hspace{0.05\textwidth}}
-\includegraphics[width=0.4\textwidth]{figheatmap_R0.pdf}\\
-\mbox{}\\
-\includegraphics[width=0.4\textwidth]{figheatmap_kappa.pdf}
-\mbox{\hspace{0.05\textwidth}}
-\includegraphics[width=0.4\textwidth]{figheatmap_kappa_R0.pdf}
-\caption{Relevance of asymptomatic transmission given variation in
-probability that a given, newly infected individual is asymptomatic. 
-(A) Long/short generation intervals of asymptomatic cases decrease/increase the relevance of asymptomatic cases, $q$.
-(B) Long/short generation intervals of asymptomatic cases increase/decrease the basic reproduction number ${\cal{R}}_0$.
-(C) Wide/narrow generation intervals of asymptomatic cases increase/decrease the relevance of asymptomatic cases, $q$.
-(D) Wide/narrow generation intervals of asymptomatic cases decrease/increase the basic reproduction number ${\cal{R}}_0$.
-For panels A--B, we vary relative mean generation interval of asymptomatic cases, $\bar G_a/\bar G_s$, while assuming $\kappa_a = \kappa_s$.
-For panels C--D, we vary relative generation-interval dispersion of asymptomatic cases, $\kappa_a/\kappa_s$, while assuming $G_a = G_s$.
-As our baseline parameters, we assume $1/r=7$ days, $\bar G_s=7$ days, and $\kappa_s=0.5$.
-% Technically, renewal equations provide a route to connect
-% observed increases in case counts, i.e., ${\cal{R}}_0 = \frac{1}{M(-r)}$
-% where $M(-r)=\int_0^{\infty}\mathrm{d} a e^{-ra}g(a)$.
-% For the present model,
-% $M(r)=qM_E(-r)M_{I_a}(-r)+(1-q)M_E(-r)M_{I_s}(-r)$
-% where each of the component functions are $M_E(-r)=\frac{\gamma_e}{\gamma_e+r}$,
-% $M_{I_a}(-r)=\frac{\gamma_a}{\gamma_a+r}$, 
-% $M_{I_s}(-r)=\frac{\gamma_s}{\gamma_s+r}$,
-% and $q$ is the fraction of realized new secondary cases caused by
-% asymptomatic individuals.  In all of these heatmaps, $\gamma_e=1/4$,
-% $\gamma_s=1/10$, and $r=1/7$. Here, the average duration
-% in symptomatic and asymptomatic states are $T_s=1/\gamma_s$ and 
-% $T_a=1/\gamma_a$, respectively. Here the filled circle denotes ${\cal{R}}_0\approx 3.12$
-% in the event of $p=0$ and $\beta_a=0$, and the open symbols are for $\beta_a/\beta_s=0.5$ and 
-% $p=0.5$ and $p=0.9$ for reference.
-%Renewal equations provide a route to connect
-%observed increases in case counts, i.e.,
-%\begin{equation}
-%{\cal{R}}_0 = \frac{1}{M(-r)}
-%\end{equation}
-%where $r$ is the speed of the disease spread and 
-%$M(r)$ is related to 
-%$g(a)$ (the normalized age of transmission) such that 
-%\begin{equation}
-%M(r)=\int_0^{\infty}\mathrm{d} a e^{ra}g(a).
-%\end{equation}
-%For the present model, the moment generating function is
-%\begin{equation}
-%M(r)=qM_E(r)M_{I_a}(r)+(1-q)M_E(r)M_{I_s}(r)
-%\end{equation}
-%where each of the component functions are $M_E(-r)=\frac{\gamma_e}{\gamma_e+r}$,
-%$M_{I_a}(-r)=\frac{\gamma_a}{\gamma_a+r}$, 
-%$M_{I_s}(-r)=\frac{\gamma_s}{\gamma_s+r}$,
-%and $q$ is the fraction of realized new secondary cases caused by
-%asymptomatic individuals. 
-%The relevance $q$ is an unknown feature of
-\label{fig.relevance}}
-\end{center}
-\end{figure*}
 

### 2020-03-07 figheatmap_kappa.R

@@ -35,7 +35,7 @@ g0 <- ggplot(figdata) +
   scale_fill_gradientn(colors=c("#2B4162", "#40E0D0", "#FF8C00", "#FF0080"),
                        limits=c(0, 1),
                        breaks=0:5*2/10) +
-  ggtitle("C. Relevance of asymptomatic cases") +
+  ggtitle("A. Relevance of asymptomatic cases") +
   theme(
     legend.title = element_blank(),
     legend.key.height = unit(1.8, "cm")

### 2020-03-07 figheatmap_kappa_R0.R

@@ -35,7 +35,7 @@ g0 <- ggplot(figdata) +
   scale_fill_gradientn(colors=c("#2B4162", "#40E0D0", "#FF8C00", "#FF0080"),
                        limits=c(1.5, 4),
                        breaks=c(1.5, 2, 2.5, 3.0, 3.5, 4)) +
-  ggtitle("D. Basic reproduction number") +
+  ggtitle("B. Basic reproduction number") +
   theme(
     legend.title = element_blank(),
     legend.key.height = unit(1.8, "cm")

### 2020-03-07 appendix.tex
update

@@
 
-Consider a SEIR model variant in which an infected individual can be either asymptomatic, $I_a$, or symptomatic, $I_s$.
+Consider an SEIR model variant in which an infected individual can be either asymptomatic, $I_a$, or symptomatic, $I_s$.
 While both cases can recover, we assume that only symptomatic cases can lead to fatalities, denoted
@@
 
-\begin{figure*}[b!]
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics[width=0.4\textwidth]{figheatmap_02.pdf}
+\mbox{\hspace{0.05\textwidth}}
+\includegraphics[width=0.4\textwidth]{figheatmap_R0_02.pdf}
+\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
+the mean generation interval of asymptomatic cases when generation-interval distributions are narrow. 
+See Figure 1 in the main text for figure caption.
+Here, we assume $1/r=7$ days, $\bar G_s=7$ days, and $\kappa_s=\kappa_a=0.2$.
+}
+\end{center}
+\end{figure*}
+
+\pagebreak
+
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics[width=0.4\textwidth]{figheatmap_08.pdf}
+\mbox{\hspace{0.05\textwidth}}
+\includegraphics[width=0.4\textwidth]{figheatmap_R0_08.pdf}
+\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
+the mean generation interval of asymptomatic cases when generation-interval distributions are wide. 
+See Figure 1 in the main text for figure caption.
+Here, we assume $1/r=7$ days, $\bar G_s=7$ days, and $\kappa_s=\kappa_a=0.8$.
+}
+\end{center}
+\end{figure*}
+
+\pagebreak
+
+\begin{figure*}[!ht]
 \begin{center}
@@
 (B) Wide/narrow generation intervals of asymptomatic cases decrease/increase the basic reproduction number ${\cal{R}}_0$.
-Here, we vary relative generation-interval dispersion of asymptomatic cases, $\kappa_a/\kappa_s$, while assuming $G_a = G_s$.
-As our baseline parameters, we assume $1/r=7$ days, $\bar G_s=7$ days, and $\kappa_s=0.5$.}
+As our baseline parameters, we assume $1/r=7$ days, $\bar G_s=G_a=7$ days, and $\kappa_s=0.5$.}
 \end{center}

### 2020-03-07 figheatmap_02.R

@@ -1,0 +1,43 @@
+library(emdbook)
+library(ggplot2); theme_set(theme_bw(base_family = "Times"))
+
+r <- 1/7
+G_s <- 7
+kappa_s <- 0.2
+kappa_a <- 0.2
+
+z <- seq(0.01, 0.99, by=0.005)
+relG <- exp(seq(log(0.5), log(2), by=0.005))
+
+qodds <- apply2d(
+  "*", 
+  z/(1-z),
+  (1 + kappa_s * r * G_s)^(1/kappa_s)/(1 + kappa_a * r * relG * G_s)^(1/kappa_a)
+)
+
+qvals <- qodds/(1+qodds)
+
+figdata <- data.frame(
+  q=c(qvals),
+  z=rep(z, length(relG)),
+  relG=rep(relG, each=length(z))
+)
+
+g0 <- ggplot(figdata) +
+  geom_raster(aes(relG, z, fill=q)) +
+  geom_contour(aes(relG, z, z=q), col="white") +
+  scale_x_log10(expression(paste("Relative mean asymptomatic generation interval, ", italic(G[a]/G[s]))), expand=c(0, 0),
+                     breaks=c(0.5, 1, 2)) +
+  scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),
+                     limits=c(0, 1),
+                     breaks=0:10/10) +
+  scale_fill_gradientn(colors=c("#2B4162", "#40E0D0", "#FF8C00", "#FF0080"),
+                       limits=c(0, 1),
+                       breaks=0:5*2/10) +
+  ggtitle("A. Relevance of asymptomatic cases") +
+  theme(
+    legend.title = element_blank(),
+    legend.key.height = unit(1.8, "cm")
+  )
+
+ggsave("figheatmap_02.pdf", g0, width=5.3, height=4.3)

### 2020-03-07 figheatmap_08.R

@@ -1,0 +1,43 @@
+library(emdbook)
+library(ggplot2); theme_set(theme_bw(base_family = "Times"))
+
+r <- 1/7
+G_s <- 7
+kappa_s <- 0.8
+kappa_a <- 0.8
+
+z <- seq(0.01, 0.99, by=0.005)
+relG <- exp(seq(log(0.5), log(2), by=0.005))
+
+qodds <- apply2d(
+  "*", 
+  z/(1-z),
+  (1 + kappa_s * r * G_s)^(1/kappa_s)/(1 + kappa_a * r * relG * G_s)^(1/kappa_a)
+)
+
+qvals <- qodds/(1+qodds)
+
+figdata <- data.frame(
+  q=c(qvals),
+  z=rep(z, length(relG)),
+  relG=rep(relG, each=length(z))
+)
+
+g0 <- ggplot(figdata) +
+  geom_raster(aes(relG, z, fill=q)) +
+  geom_contour(aes(relG, z, z=q), col="white") +
+  scale_x_log10(expression(paste("Relative mean asymptomatic generation interval, ", italic(G[a]/G[s]))), expand=c(0, 0),
+                     breaks=c(0.5, 1, 2)) +
+  scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),
+                     limits=c(0, 1),
+                     breaks=0:10/10) +
+  scale_fill_gradientn(colors=c("#2B4162", "#40E0D0", "#FF8C00", "#FF0080"),
+                       limits=c(0, 1),
+                       breaks=0:5*2/10) +
+  ggtitle("A. Relevance of asymptomatic cases") +
+  theme(
+    legend.title = element_blank(),
+    legend.key.height = unit(1.8, "cm")
+  )
+
+ggsave("figheatmap_08.pdf", g0, width=5.3, height=4.3)

### 2020-03-07 figheatmap_R0_02.R

@@ -1,0 +1,44 @@
+library(emdbook)
+library(ggplot2); theme_set(theme_bw(base_family = "Times"))
+
+r <- 1/7
+G_s <- 7
+kappa_s <- 0.2
+kappa_a <- 0.2
+
+z <- seq(0.01, 0.99, by=0.005)
+relG <- exp(seq(log(0.5), log(2), by=0.01))
+
+R0 <- apply2d(
+  function(x, y) {
+    1/((1-x) * (1 + kappa_s * r * G_s)^(-1/kappa_s) + x * (1 + kappa_a * r * y * G_s)^(-1/kappa_a))
+  }, 
+  z,
+  relG
+)
+
+figdata <- data.frame(
+  R0=c(R0),
+  z=rep(z, length(relG)),
+  relG=rep(relG, each=length(z))
+)
+
+g0 <- ggplot(figdata) +
+  geom_raster(aes(relG, z, fill=R0)) +
+  geom_contour(aes(relG, z, z=R0), col="white") +
+  scale_x_log10(expression(paste("Relative mean asymptomatic generation interval, ", italic(G[a]/G[s]))), expand=c(0, 0),
+                breaks=c(0.5, 1, 2),
+                limits=c(0.5, 2)) +
+  scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),
+                     limits=c(0, 1),
+                     breaks=0:10/10) +
+  scale_fill_gradientn(colors=c("#2B4162", "#40E0D0", "#FF8C00", "#FF0080"),
+                       limits=c(1.5, 5.5),
+                       breaks=c(1.5, 2.5, 3.5, 4.5, 5.5)) +
+  ggtitle("B. Basic reproduction number") +
+  theme(
+    legend.title = element_blank(),
+    legend.key.height = unit(1.8, "cm")
+  )
+
+ggsave("figheatmap_R0_02.pdf", g0, width=5.3, height=4.3)

### 2020-03-07 figheatmap_R0_08.R

@@ -1,0 +1,44 @@
+library(emdbook)
+library(ggplot2); theme_set(theme_bw(base_family = "Times"))
+
+r <- 1/7
+G_s <- 7
+kappa_s <- 0.8
+kappa_a <- 0.8
+
+z <- seq(0.01, 0.99, by=0.005)
+relG <- exp(seq(log(0.5), log(2), by=0.01))
+
+R0 <- apply2d(
+  function(x, y) {
+    1/((1-x) * (1 + kappa_s * r * G_s)^(-1/kappa_s) + x * (1 + kappa_a * r * y * G_s)^(-1/kappa_a))
+  }, 
+  z,
+  relG
+)
+
+figdata <- data.frame(
+  R0=c(R0),
+  z=rep(z, length(relG)),
+  relG=rep(relG, each=length(z))
+)
+
+g0 <- ggplot(figdata) +
+  geom_raster(aes(relG, z, fill=R0)) +
+  geom_contour(aes(relG, z, z=R0), col="white") +
+  scale_x_log10(expression(paste("Relative mean asymptomatic generation interval, ", italic(G[a]/G[s]))), expand=c(0, 0),
+                breaks=c(0.5, 1, 2),
+                limits=c(0.5, 2)) +
+  scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),
+                     limits=c(0, 1),
+                     breaks=0:10/10) +
+  scale_fill_gradientn(colors=c("#2B4162", "#40E0D0", "#FF8C00", "#FF0080"),
+                       limits=c(1.5, 3.5),
+                       breaks=c(1.5, 2, 2.5, 3.0, 3.5)) +
+  ggtitle("B. Basic reproduction number") +
+  theme(
+    legend.title = element_blank(),
+    legend.key.height = unit(1.8, "cm")
+  )
+
+ggsave("figheatmap_R0_08.pdf", g0, width=5.3, height=4.3)

### 2020-03-07 short.body.tex
k i think this color scheme is more or less ok for now

@@
 A key focus has been on estimating asymptomatic prevalence (see~\citep{mizumoto_2020}), e.g., what fraction of individuals have asymptomatic infections relative to those with symptomatic infections?
-%.(i) What fraction of newly infected individuals
-%have mild and/or subclinical infections rather than severe and/or
-%clinical infections? (ii) What is the time-scale over which 
-%individuals who have mild and/or subclinical cases remain
-%infectious? (iii) How infectious are individuals
-%with mild and/or subclinical infections relative to those
-%with severe symptoms?
 
@@
 
-We model viral spread using a renewal-equation framework \citep{heesterbeek1996concept}, which allows us to model the current incidence of infected individuals as a function of previous incidence and how infectiousness of an infected individual varies over the course of their infection;
-in Appendix, we show that results derived from a compartmental model is a special case of the result we present here.
+We model viral spread using a renewal-equation framework \citep{heesterbeek1996concept}, which allows us to model the current incidence of infected individuals as a function of previous incidence and how infectiousness of an infected individual varies over the course of their infection.
 We divide incidence $i$ into two categories -- $i_a$ and $i_s$ -- corresponding to incidence of asymptomatic and symptomatic cases, respectively.
@@
 individuals with subclinical cases may have fast clearance and short generation intervals, or slow viral reproduction and long generation intervals.
+The shape of the generation-interval distribution characterizes the relationship between the epidemic growth rate $r$ and the reproduction number \citep{wallinga2007generation}.
 
@@
 
+In order to understand how the shape of asymptomatic and symptomatic generation-interval distributions affects $q$ and $\mathcal R_0$, we summarize the distributions in terms of their means and dispersions.
 Assuming that the intrinsic generation-interval distributions for asymptomatic and symptomatic cases follow gamma distributions with different means, $\bar G_a$ and  $\bar G_s$, and dispersions (represented by squared coefficients of variations), $\kappa_a$ and $\kappa_s$.
@@
 The consequences for outbreak potential further depends on the relative lengths of generation intervals as well as the relative amount of dispersions in them.
-
-%The basic reproduction number, ${\cal{R}}_0$,
-%characterize the strength of an epidemic outbreak in an other
-%wise susceptible population:
-%\begin{equation}
-%{\cal{R}}_{0}= p\left(\frac{\beta_a}{\gamma_a}\right)+ (1-p)\left(\frac{\beta_s}{\gamma_s}\right)
-%\end{equation}
-%Pooling estimates via a Bayesian approach applied to the early stages of Wuhan case data,
-%suggests ${\cal{R}}_0\approx 3.0$ 
-%with a 95\% confidence interval from 2-4.5.  Yet, that information
-%is not sufficient to disentangle the role of asymptomatic cases, i.e.,
-%what fraction of secondary cases can be ascribed to transmission
-%from asymptomatic cases vs.~symptomatic cases?  A step towards such
-%a link is enabled given the relationship between strength and speed, $r$,
-%i.e., the rate at which cases grow in number and which we assume
-%should be the same for both classes of cases.  Strength and size
-%can be related via a Gamma approximation as:
-%\begin{equation}
-%{\cal{R}}^{gamma}=(1+\kappa r \bar{G})^{1/\kappa}
-%\end{equation}
-%where $\bar{G}$ is the mean generation interval and
-%$\kappa$  is the squared coefficient of variation of
-%the generation interval.  This approximation (explored in Champredon
-%et al.) reveals why for a given observed speed,
-%increases in the mean generation interval imply
-%larger reproduction number. Reports of individuals
-%with mild cases that remain infectious for (relatively)
-%long periods suggest that the mean generation interval
-%could be longer than estimated from symptomatic cases alone - both
-%increasing ${\cal{R}}_0$ and driving more secondary cases
-%than expected. Yet the relevance of asymptomatic cases
-%depends on their realized proportion at a population level.
-
-%The number of infected cases is expected
-%to increase exponentially at rate $r$ at the outset of an outbreak.  We note
-%that, in practice,
-%counted cases may largely be of the symptomatic type. 
-%Hence, we ask: is the expected ratio of $I_a/I_s$ 
-%during the outbreak phase the same or different
-%than $p/(1-p)$?
-In other words, is the ratio of asymptomatic to symptomatic cases population-wide approximately equal to the ratio of asymptomatic to symptomatic cases generated by newly exposed individuals?
-%To answer this question, note that the equations
-%for the infectious cases can be rewritten given the ansatz
-%$E(t)=c_e e^{rt}$,
-%$I_a(t)=c_a e^{rt}$,
-%$I_s(t)=c_s e^{rt}$,
-%given the prefactors $c_e$, $c_a$, and $c_s$
-%such that
-%\begin{eqnarray}
-%r c_a&=&p\gamma_e c_e-\gamma_a c_a,\\
-%r c_s&=&(1-p)\gamma_e c_e-\gamma_s c_s,
-%\end{eqnarray} 
-%which implies that
-%\begin{eqnarray}
-%c_a(r+\gamma_a)&=&p\gamma_e c_e,\\
-%c_s(r+\gamma_s)&=&(1-p)\gamma_e c_e.
-%\end{eqnarray} 
-%Taking the ratio of these two equations yieldds
-%\begin{equation}
-%\frac{c_a}{c_s}=\frac{p}{1-p}\left[\frac{r+\gamma_s}{r+\gamma_a}\right].
-%\label{eq.relevance}
-%\end{equation}
-%Alternatively, this same equation can be written as:
-%\begin{equation}
-%\frac{c_a}{c_s}=\frac{p}{1-p}\left[\frac{1+\tau/T_s}{1+\tau/T_a}\right]
-%\end{equation}
-%where $\tau$ is the characteristic time of exponential case increase,
-%$T_s$ is the average period of symptomatic infectious periods,
-%and $T_a$ is the average period of asymptomatic infectious periods. 
-%Hence, we conclude that, during the exponential
-%growth phase, the intrinsic
-%ratio of asymptomatic to symptomatic cases ($p/(1-p)$) may differ from
-%the realized ratio at the population level ($c_a/c_s$).  
-%%This difference
-%suggests that additional steps are required to link asymptomatic features
-%at the individual to the population scale, i.e., by including
-%the unknown transmission rates, $\beta_a$ and $\beta_s$.
-%Indeed, the ratio of secondary case production caused by asymptomatic vs.~symptomatic
-%individuals during the exponential phase should be
-%\begin{equation}
-%\frac{q}{1-q} = \left(\frac{\beta_a}{\beta_s}\right)\frac{p}{1-p}\left[\frac{r+\gamma_s}{r+\gamma_a}\right],
-%\label{eq.qratio}
-%\end{equation}
-%where $q$ is the fraction of new secondary cases caused by
-%asymptomatic individuals or `relevance' of asymptomatic cases.
-%The value of $q$ is an unknown feature of
-%outbreaks at the population scale, distinct from $p$ the probability of becoming
-%asymptomatic upon infection. 
-%As is apparent from Eq.~\req{eq.qratio}, relevance increases
-%with both $p$ and $\beta_a/\beta_s$. However, the consequences
-%for outbreak potential depends on the relative duration of infectiousness.
-
-Here, given $1/r=7$ days, $\bar G_s=7$ days, and $\kappa_s=0.5$, we evaluate the impacts of intrinsic proportion of asymptomatic transmission $z$ on the realized relevance of asymptomatic infection, given variation in relative mean generation interval $\bar G_a/\bar G_s$ and relative generation-interval dispersion $\kappa_a/\kappa_s$ of asymptomatic cases.
-We vary $\bar G_a/\bar G_s$ and $\kappa_a/\kappa_s$ between 0.5 and 2 one at a time, and infer $q$ and ${\cal{R}}_0$ compatible with an estimated value of $r$ from case data given the generation interval distributions of asymptomatic and asymptomatic cases.
+In Supplementary Materials, we use a compartmental ordinary differential equations model to show that the duration of infectious period of asymptomatic individuals affects both $q$ and $\mathcal R_0$, which is a special case of Eq.~\req{eq.qratio}.
 
@@
 (B) Long/short generation intervals of asymptomatic cases increase/decrease the basic reproduction number ${\cal{R}}_0$.
-(C) Wide/narrow generation intervals of asymptomatic cases increase/decrease the relevance of asymptomatic cases, $q$.
-(D) Wide/narrow generation intervals of asymptomatic cases decrease/increase the basic reproduction number ${\cal{R}}_0$.
-Here, we vary relative mean generation interval of asymptomatic cases, $\bar G_a/\bar G_s$, while assuming $\kappa_a = \kappa_s$.
-As our baseline parameters, we assume $1/r=7$ days, $\bar G_s=7$ days, and $\kappa_s=0.5$.
+As our baseline parameters, we assume $1/r=7$ days, $\bar G_s=7$ days, and $\kappa_s=\kappa_a=0.5$.
 \label{fig.relevance}}
@@
 
-Across the ranges of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.relevance}A,C).
+Here, given $1/r=7$ days, $\bar G_s=7$ days, and $\kappa_s=\kappa_a=0.5$, we evaluate the impacts of intrinsic proportion of asymptomatic transmission $z$ on the realized relevance of asymptomatic infection, given variation in relative mean generation interval $\bar G_a/\bar G_s$ of asymptomatic cases.
+We vary $\bar G_a/\bar G_s$ between 0.5 and 2 and infer $q$ and ${\cal{R}}_0$ compatible with an estimated value of $r$ from case data given the generation interval distributions of asymptomatic and asymptomatic cases.
+Across the ranges of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.relevance}A).
 As the relative mean generation interval of asymptomatic cases, $\bar G_a/\bar G_s$, increases, $q$ decreases because symptomatic cases are more likely to have short generation intervals (i.e., fast transmission events), which drive the spread during the growth phase (Figure~\ref{fig.relevance}A).
-On the other hand, as the relative generation-interval dispersion of asymptomatic cases, $\kappa_a/\kappa_s$, increases, $q$ also increases because the amount of short asymptomatic generation intervals (i.e., the proportion of faster transmission by asymptomatic individuals) increases (Figure~\ref{fig.relevance}C).
 
@@
 Conversely, when $\bar G_s > \bar G_a$ then the strength ${\cal{R}}_0$ decreases with $z$ because short generation intervals of asymptomatic cases reduce the overall mean generation interval.
+The qualitative effects of $z$ and $\bar G_a/\bar G_s$ on $q$ and ${\cal{R}}_0$ remain robust when we assume narrower ($\kappa_s = \kappa_a = 0.3$; Figure~S1) or wider ($\kappa_s = \kappa_a = 0.8$; Figure~S2) generation intervals.
 
-Likewise, Figure~\ref{fig.relevance}D compares the effect of relative generation-interval dispersion of asymptomatic cases, $\kappa_a/\kappa_s$, on ${\cal{R}}_0$.
-Depending on whether $\kappa_a$ is larger or smaller than $\kappa_s$, increase in the proportion of asymptomatic transmission $z$ can either decrease or increase the strength ${\cal{R}}_0$.
-In other words, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread, it can be over- or under- estimated depending on the relative mean and dispersion in generation intervals of asymptomatic and symptomatic individuals.
-
-%Here, given $1/r=7$ days, $1/\gamma_e=4$ days, and
-%$1/\gamma_s=10$ days, we evaluate the impacts of $p$ and $\beta_a/\beta_s$ on the
-%relevance of asymptomatic infections, given variation in 
-%$p$, $\beta_a/\beta_s$, and $\gamma_a$.  We consider two
-%scenarios, one in which asymptomatic infectiousness is short, i.e., with
-%average duration of $1/\gamma_a=5$ days,
-%and one in which asymptomatic infectiousness is long,i.e., $1/\gamma_a=20$ days.
-%We use the renewal equation formalism to explicitly link duration of infectiousness to the 
-%basic reproductive number (for technical details and example 
-%applications see~\citep{wallinga2007generation,weitz_scirep2015,champredon_2018}).
-%In brief, we
-%infer ${\cal{R}}_0$ compatible with an estimated value of $r$ from case
-%data given the generation interval distribution 
-%(set by $q$ and the duration in the exposed and infectious states).
-%By solving for $q$, we can then relate the basic
-%reproduction number to the relative transmission rates ($\beta_a/\beta_s$)
-%and the probability, $p$, of asymptomatic cases at the individual scale.
-%Figure~\ref{fig.relevance}C shows that
-%when $\gamma_a<\gamma_s$, then the strength ${\cal{R}}_0$ increases
-%with $q$. 
-%This increase arises because asymptomatic infections that resolve
-%slower increase the duration of
-%overall generation intervals (see~\citep{park_2019practical}). In contrast,
-%Figure~\ref{fig.relevance}D show that
-%when $\gamma_a>\gamma_s$ then
-%the strength ${\cal{R}}_0$ decreases with $q$.  
-%This decrease arises because asymptomatic infections that resolve
-%faster decrease the duration of
-%overall generation intervals (again, see~\citep{park_2019practical}). In both 
-%cases, the dependence of ${\cal{R}}_0$ on $q$ is
-%compared to a baseline of 
-%${\cal{R}}_0\approx 3.1$ in a model with no secondary
-%case production from asymptomatic infections (see filled
-%circle at bottom left of Figure~\ref{fig.relevance}C-D.
-%In other words, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread, it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
+Relative generation-interval dispersion of asymptomatic cases $\kappa_a/\kappa_s$ also have qualitatively similar effects on $q$ and ${\cal{R}}_0$.
+When the asymptomatic cases have a wider/narrower generation-interval distribution, higher intrinsic proportion of asymptomatic transmission $z$ increases/decreases the relevance of asymptomatic transmission $q$ but decreases/increases the basic reproduction number (Figure~S3).
+Since a wider generation-interval distribution has a higher proportion of early transmission, it has qualitatively similar effects on $q$ and ${\cal{R}}_0$ as a generation-interval distribution with a small mean.
 

### 2020-03-07 figheatmap.R

@@ -31,7 +31,7 @@ g0 <- ggplot(figdata) +
   scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +
-  scale_fill_gradientn(colors=c("#2B4162", "#40E0D0", "#FF8C00", "#FF0080"),
+  scale_fill_gradientn(colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
                        limits=c(0, 1),
                        breaks=0:5*2/10) +
   ggtitle("A. Relevance of asymptomatic cases") +

### 2020-03-07 figheatmap_03.R

@@ -31,7 +31,7 @@ g0 <- ggplot(figdata) +
   scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +
-  scale_fill_gradientn(colors=c("#2B4162", "#40E0D0", "#FF8C00", "#FF0080"),
+  scale_fill_gradientn(colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
                        limits=c(0, 1),
                        breaks=0:5*2/10) +
   ggtitle("A. Relevance of asymptomatic cases") +
@@ -40,4 +40,4 @@ g0 <- ggplot(figdata) +
     legend.key.height = unit(1.8, "cm")
   )
 
-ggsave("figheatmap_02.pdf", g0, width=5.3, height=4.3)
+ggsave("figheatmap_03.pdf", g0, width=5.3, height=4.3)

### 2020-03-07 figheatmap_R0.R

@@ -32,9 +32,9 @@ g0 <- ggplot(figdata) +
   scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +
-  scale_fill_gradientn(colors=c("#2B4162", "#40E0D0", "#FF8C00", "#FF0080"),
-                       limits=c(1.5, 4),
-                       breaks=c(1.5, 2, 2.5, 3.0, 3.5, 4)) +
+  scale_fill_gradientn(colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
+                       limits=c(1.5, 5),
+                       breaks=c(1.5, 2.5, 3.5, 4.5)) +
   ggtitle("B. Basic reproduction number") +
   theme(
     legend.title = element_blank(),

### 2020-03-07 figheatmap_R0_03.R

@@ -3,8 +3,8 @@ library(ggplot2); theme_set(theme_bw(base_family = "Times"))
 
 r <- 1/7
 G_s <- 7
-kappa_s <- 0.2
-kappa_a <- 0.2
+kappa_s <- 0.3
+kappa_a <- 0.3
 
 z <- seq(0.01, 0.99, by=0.005)
 relG <- exp(seq(log(0.5), log(2), by=0.01))
@@ -32,13 +32,13 @@ g0 <- ggplot(figdata) +
   scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +
-  scale_fill_gradientn(colors=c("#2B4162", "#40E0D0", "#FF8C00", "#FF0080"),
-                       limits=c(1.5, 5.5),
-                       breaks=c(1.5, 2.5, 3.5, 4.5, 5.5)) +
+  scale_fill_gradientn(colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
+                       limits=c(1.5, 5),
+                       breaks=c(1.5, 2.5, 3.5, 4.5)) +
   ggtitle("B. Basic reproduction number") +
   theme(
     legend.title = element_blank(),
     legend.key.height = unit(1.8, "cm")
   )
 
-ggsave("figheatmap_R0_02.pdf", g0, width=5.3, height=4.3)
+ggsave("figheatmap_R0_03.pdf", g0, width=5.3, height=4.3)

### 2020-03-07 figheatmap_R0_08.R

@@ -32,9 +32,9 @@ g0 <- ggplot(figdata) +
   scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +
-  scale_fill_gradientn(colors=c("#2B4162", "#40E0D0", "#FF8C00", "#FF0080"),
-                       limits=c(1.5, 3.5),
-                       breaks=c(1.5, 2, 2.5, 3.0, 3.5)) +
+  scale_fill_gradientn(colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
+                       limits=c(1.5, 5),
+                       breaks=c(1.5, 2.5, 3.5, 4.5)) +
   ggtitle("B. Basic reproduction number") +
   theme(
     legend.title = element_blank(),

### 2020-03-07 figheatmap_kappa.R

@@ -32,7 +32,7 @@ g0 <- ggplot(figdata) +
   scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +
-  scale_fill_gradientn(colors=c("#2B4162", "#40E0D0", "#FF8C00", "#FF0080"),
+  scale_fill_gradientn(colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
                        limits=c(0, 1),
                        breaks=0:5*2/10) +
   ggtitle("A. Relevance of asymptomatic cases") +

### 2020-03-07 abs.tex
more edits

@@
-{\footnotesize We analyze a mechanistic model of a coronavirus-like pathogen
-to assess the impact of asymptomatic cases on epidemic potential
--- as measured both by the basic reproduction
+{\footnotesize We assess the impact of asymptomatic cases on epidemic potential of COVID-19 (and COVID-19 like pathogens) -- as measured both by the basic reproduction
 number and the fraction of new secondary cases attributable to asymptomatic
 individuals. As we show, the impact of asymptomatic
-cases depends on the generation intervals of asymptomatic cases.  
-If the generation intervals of asymptomatic cases differs than that 
+cases depends on their generation intervals.  
+If the generation intervals of asymptomatic cases differs from that 
 of symptomatic cases, then estimates of the basic reproductive ratio which do not explicitly account for asymptomatic cases may be systematically biased.

### 2020-03-07 acknowledge.tex
tweaking stuff
update
more edits

@@
 This work was supported, in part,
-by support from the Army Research Office (W911NF1910384).
+by support from the Army Research Office to JSW (W911NF1910384).
 
 \noindent
-\textbf{Data Availabililty:} All code is available at weitzgroup.github.io.
+\textbf{Data Availabililty:} All code is available at https://github.com/mac-theobio/coronavirus\_asymptomatic.

### 2020-03-07 appendix.tex
k i think this color scheme is more or less ok for now
more edits

@@
 \end{eqnarray}
-The generation-interval distributions for asymptomatic and symptomatic individuals follow the same functional form as the corresponding generation-interval distribution for a single-type SEIR model since both asymptomatic and symptomatic individuals have exponenitally distributed latent and infectious periods \citep{svensson2015influence}:
+The generation-interval distributions for asymptomatic and symptomatic individuals follow the same functional form as the corresponding generation-interval distribution for a single-type SEIR model since both asymptomatic and symptomatic individuals have exponentially distributed latent and infectious periods \citep{svensson2015influence}:
 \begin{eqnarray}
@@
 \begin{center}
-\includegraphics[width=0.4\textwidth]{figheatmap_02.pdf}
+\includegraphics[width=0.4\textwidth]{figheatmap_03.pdf}
 \mbox{\hspace{0.05\textwidth}}
-\includegraphics[width=0.4\textwidth]{figheatmap_R0_02.pdf}
+\includegraphics[width=0.4\textwidth]{figheatmap_R0_03.pdf}
 \caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
 the mean generation interval of asymptomatic cases when generation-interval distributions are narrow. 
+We vary $G_a/G_s$ while assuming $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.3$.
 See Figure 1 in the main text for figure caption.
-Here, we assume $1/r=7$ days, $\bar G_s=7$ days, and $\kappa_s=\kappa_a=0.2$.
 }
@@
 the mean generation interval of asymptomatic cases when generation-interval distributions are wide. 
+We vary $G_a/G_s$ while assuming $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.8$.
 See Figure 1 in the main text for figure caption.
-Here, we assume $1/r=7$ days, $\bar G_s=7$ days, and $\kappa_s=\kappa_a=0.8$.
 }
@@
 (B) Wide/narrow generation intervals of asymptomatic cases decrease/increase the basic reproduction number ${\cal{R}}_0$.
-As our baseline parameters, we assume $1/r=7$ days, $\bar G_s=G_a=7$ days, and $\kappa_s=0.5$.}
+We vary $\kappa_a/\kappa_s$ while assuming $1/r=7$ days, $\bar G_s=\bar G_a=8$ days, and $\kappa_s=0.5$.
+The solid, white lines represent the contours.
+}
 \end{center}

### 2020-03-07 short.body.tex
more edits

@@
 
-There is currently a lot of interest in the role of asymptomatic infections in SARS-CoV-2 for two major reasons. 
+There is significant ongoing interest in asymptomatic infections in COVID-19 for two major reasons. 
 First, the proportion of infections that are asymptomatic is critical to attempts to estimate the likely burden of severe outcomes (including mortality) when the virus spreads through a population.
@@
 Here, we focus on a third effect. 
-If asymptomatic cases are important for transmission, they also have the potential to affect estimates of key epidemiological parameters. 
+If asymptomatic cases are important for transmission, they also have the potential to affect estimates of key parameters of disease spread such as the basic reproduction number ${\cal{R}}_0$ (i.e., the expected number of secondary cases generated by an average primary case in a fully susceptible population \citep{anderson1992infectious}).
 Here, we investigate the relationship between individual-level features of asymptomatic cases (e.g., the probability of initiating an asymptomatic case, asymptomatic case duration, and the transmission rates from asymptomatic individuals) to dynamics at the population scale.
@@
 
-We model viral spread using a renewal-equation framework \citep{heesterbeek1996concept}, which allows us to model the current incidence of infected individuals as a function of previous incidence and how infectiousness of an infected individual varies over the course of their infection.
+We model viral spread using a renewal-equation framework \citep{heesterbeek1996concept}, which allows us to model the current incidence of infected individuals (i.e., the the rate at which new infections occur in the population) as a function of previous incidence and how infectiousness of an infected individual varies over the course of their infection.
 We divide incidence $i$ into two categories -- $i_a$ and $i_s$ -- corresponding to incidence of asymptomatic and symptomatic cases, respectively.
-Both types of individuals can infect others, but they differ in their intrinsic reproduction numbers, ${\cal{R}}_a$ and ${\cal{R}}_s$, as well as intrinsic generation-interval distributions, $g_a(\tau)$ and $g_s(\tau)$.
+Newly infected individuals that are either asymptomatically or symptomatically infected can transmit the disease to others, but they differ in their intrinsic reproduction numbers, ${\cal{R}}_a$ and ${\cal{R}}_s$, respectively, as well as intrinsic generation-interval distributions, $g_a(\tau)$ and $g_s(\tau)$.
 Generation intervals, which are defined as the time between when an individual is infected and when that individual infects another person \citep{svensson2007note}, depend on the natural history of infection:
-individuals with subclinical cases may have fast clearance and short generation intervals, or slow viral reproduction and long generation intervals.
+individuals with subclinical infections may have fast clearance and short generation intervals, or slow viral reproduction and long generation intervals (cf. \citep{roberts2007model}).
 The shape of the generation-interval distribution characterizes the relationship between the epidemic growth rate $r$ and the reproduction number \citep{wallinga2007generation}.
@@
 \dot{S}&=&-i(t) \\
-i(t)&=&\mathcal R_a S \int_0^\infty i_a(t-\tau) g_a(\tau) \mathrm{d}\tau + \mathcal R_s S \int_0^\infty i_s(t-\tau) g_s(\tau) \mathrm{d}\tau.
+i(t)&=&\mathcal R_a S(t) \int_0^\infty i_a(t-\tau) g_a(\tau) \mathrm{d}\tau + \mathcal R_s S(t) \int_0^\infty i_s(t-\tau) g_s(\tau) \mathrm{d}\tau.
 \end{eqnarray}
-Here, $p$ is the proportion of \emph{incident cases} that are asymptomatic.
-
-The basic reproduction number -- the expected number of secondary cases generated by an average primary case in a fully susceptible population \citep{anderson1992infectious} -- of this system is:
+The basic reproduction number of this system is:
 \begin{equation}
-{\cal{R}}_{0}= p {\cal{R}}_a + (1-p) {\cal{R}}_s.
+{\cal{R}}_{0}= p {\cal{R}}_a + (1-p) {\cal{R}}_s,
 \end{equation}
+where $p$ is the proportion of \emph{incident cases} that are asymptomatic.
 We define the ``intrinsic'' proportion of asymptomatic transmission as the relative contribution of asymptomatic cases to the basic reproduction number:
@@
 \begin{equation}
-i(t) = {\cal{R}}_{0} \int_0^\infty i(t-\tau) g(\tau) \mathrm{d} \tau.
+i(t) = {\cal{R}}_{0} S(t) \int_0^\infty i(t-\tau) g(\tau) \mathrm{d} \tau.
 \end{equation}
@@
 The number of infected cases is expected to increase exponentially at rate $r$ at the outset of an outbreak. We note that, in practice, counted cases may largely be of the symptomatic type.
-Hence, we ask: is the expected ratio of incidence caused by asymptomatic cases vs.~symptomatic cases during the outbreak phase the same or different than $z/(1-z)$?
-The ratio of secondary case production caused by asymptomatic vs.~symptomatic individuals during the exponential phase should be
+Hence, we ask: is the expected ratio of incidence caused by asymptomatic cases vs.~symptomatic cases during the outbreak phase the same or different from $z/(1-z)$?
+The ratio of secondary case production caused by asymptomatic vs.~symptomatic individuals over the course of an ongoing epidemic is
 \begin{equation}
-\frac{q}{1-q}=\left(\frac{z}{1-z}\right)\left[\frac{\int_0^\infty \exp(-r\tau) g_a(\tau) \mathrm{d}\tau}{\int_0^\infty \exp(-r\tau) g_s(\tau) \mathrm{d}\tau}\right],
+\frac{q}{1-q}=\frac{\mathcal R_a S(t) \int_0^\infty i_a(t-\tau) g_a(\tau) \mathrm{d}\tau}{\mathcal R_s S(t) \int_0^\infty i_s(t-\tau) g_s(\tau) \mathrm{d}\tau},
+\end{equation}
+where $q$ is the fraction of new secondary cases caused by asymptomatic individuals or `relevance' of asymptomatic cases.
+Assuming that the incidence grows exponentially during the outbreak phase (i.e., $i(t) = i(0) \exp(r t)$) and substituting $i_a(t) = p i(t)$ and $i_s(t) = (1-p) i(t)$, we have
+\begin{equation}
+\frac{q}{1-q}=\left(\frac{z}{1-z}\right)\left[\frac{\int_0^\infty \exp(-r\tau) g_a(\tau) \mathrm{d}\tau}{\int_0^\infty \exp(-r\tau) g_s(\tau) \mathrm{d}\tau}\right].
 \label{eq.qratio}
 \end{equation}
-where $q$ is the fraction of new secondary cases caused by asymptomatic individuals or `relevance' of asymptomatic cases. 
 The value of $q$ is an unknown feature of outbreaks at the population scale, distinct from $p$ the probability of becoming asymptomatic upon infection or $z$ the intrinsic proportion of asymptomatic transmission.
@@
 In order to understand how the shape of asymptomatic and symptomatic generation-interval distributions affects $q$ and $\mathcal R_0$, we summarize the distributions in terms of their means and dispersions.
-Assuming that the intrinsic generation-interval distributions for asymptomatic and symptomatic cases follow gamma distributions with different means, $\bar G_a$ and  $\bar G_s$, and dispersions (represented by squared coefficients of variations), $\kappa_a$ and $\kappa_s$.
-Then, we have
+Assuming that the intrinsic generation-interval distributions for asymptomatic and symptomatic cases follow gamma distributions with different means, $\bar G_a$ and $\bar G_s$, and dispersions (represented by squared coefficients of variations), $\kappa_a$ and $\kappa_s$ \citep{park_2019practical},
+we have
 \begin{equation}
@@
 The consequences for outbreak potential further depends on the relative lengths of generation intervals as well as the relative amount of dispersions in them.
-In Supplementary Materials, we use a compartmental ordinary differential equations model to show that the duration of infectious period of asymptomatic individuals affects both $q$ and $\mathcal R_0$, which is a special case of Eq.~\req{eq.qratio}.
+In Supplementary Materials, we use a compartmental ordinary differential equation model to show that the duration of infectious period of asymptomatic individuals affects both $q$ and $\mathcal R_0$, which is a special case of Eq.~\req{eq.qratio}.
 
@@
 (B) Long/short generation intervals of asymptomatic cases increase/decrease the basic reproduction number ${\cal{R}}_0$.
-As our baseline parameters, we assume $1/r=7$ days, $\bar G_s=7$ days, and $\kappa_s=\kappa_a=0.5$.
+We vary $G_a/G_s$ while assuming $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.5$.
+The solid, white lines represent the contours.
+The solid, black lines represent the example scenario that assumes $p = 0.35$ and $\mathcal R_a = 0.5 \mathcal R_s$.
+The solid, black circle represents the baseline value that does not explicitly account for asymptomatic transmission; depending on whether $G_a$ is smaller or bigger than $G_s$, the baseline value over- or under-estimates the true $\mathcal R_0$.
 \label{fig.relevance}}
@@
 
-Here, given $1/r=7$ days, $\bar G_s=7$ days, and $\kappa_s=\kappa_a=0.5$, we evaluate the impacts of intrinsic proportion of asymptomatic transmission $z$ on the realized relevance of asymptomatic infection, given variation in relative mean generation interval $\bar G_a/\bar G_s$ of asymptomatic cases.
-We vary $\bar G_a/\bar G_s$ between 0.5 and 2 and infer $q$ and ${\cal{R}}_0$ compatible with an estimated value of $r$ from case data given the generation interval distributions of asymptomatic and asymptomatic cases.
+We evaluate the impacts of intrinsic proportion of asymptomatic transmission $z$ on the realized relevance of asymptomatic infection $q$ and the basic reproduction number ${\cal{R}}_0$, given variation in relative mean generation interval $\bar G_a/\bar G_s$ of asymptomatic cases, using parameter values that are consistent with earlier COVID-19 models \citep{park_preprint}: $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.5$.
+We vary $\bar G_a/\bar G_s$ between 0.5 and 2 and infer $q$ and ${\cal{R}}_0$ compatible with an estimated value of $r$ from case data given the generation interval distributions of asymptomatic and symptomatic cases.
 Across the ranges of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.relevance}A).
@@
 When $\bar G_s < \bar G_a$, then the strength ${\cal{R}}_0$ increases with $z$.
-This increase arises because asymptomatic infections that have long generation intervals increase the duration of overall generation intervals (see~\citep{park_2019practical})
+This increase arises because asymptomatic infections that have long generation intervals increase the duration of overall generation intervals (see~\citep{park_2019practical}).
 Conversely, when $\bar G_s > \bar G_a$ then the strength ${\cal{R}}_0$ decreases with $z$ because short generation intervals of asymptomatic cases reduce the overall mean generation interval.
@@
 
+As an example, we assume that 35\% of the newly infected cases are asymptomatic \citep{mizumoto_2020} and that the asymptomatic cases are as half as infectious as the symptomatic ones (i.e., $\mathcal R_a = 0.5 \mathcal R_s$).
+The intrinsic proportion of asymptomatic transmission $z$ is 0.27, but asymptomatic cases can account for anywhere between 17\% and 35\% of infection during the exponential growth phase across the range of mean asymptomatic generation interval we explore (Figure~\ref{fig.relevance}A).
+Likewise, the basic reproduction number ranges between 2.2 and 2.8 (Figure~\ref{fig.relevance}B).
+Therefore, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread ($\mathcal R_0=2.5$; black circle in Figure~\ref{fig.relevance}B), it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
+
+% In both cases, the dependence of R0 on q is compared to a baseline of R0 ≈ 3.1 in a model with no secondary case production from asymptomatic infections (see filled circle at bottom left of Figure 1C-D.
+% In other words, when R0 is estimated without explicitly accounting for asymptomatic spread, it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
+
 Relative generation-interval dispersion of asymptomatic cases $\kappa_a/\kappa_s$ also have qualitatively similar effects on $q$ and ${\cal{R}}_0$.
 When the asymptomatic cases have a wider/narrower generation-interval distribution, higher intrinsic proportion of asymptomatic transmission $z$ increases/decreases the relevance of asymptomatic transmission $q$ but decreases/increases the basic reproduction number (Figure~S3).
-Since a wider generation-interval distribution has a higher proportion of early transmission, it has qualitatively similar effects on $q$ and ${\cal{R}}_0$ as a generation-interval distribution with a small mean.
+Since a wider generation-interval distribution has a higher proportion of early transmission than a narrow one, increasing the generation-interval dispersion has qualitatively similar effects on $q$ and ${\cal{R}}_0$ as decreasing the mean generation interval.
 
@@
 
-The present findings highlight the need to characterize the course of infection of asymptomatic cases and their consequences not only for contact tracing but for constraining uncertainty in the strength of the ongoing COVID-19 outbreak~\citep{park_preprint}.
+Much is still unknown about course of asymptomatic infection compared to symptomatic infection in COVID-19. 
+Our current work highlights the need to characterize the duration of asymptomatic infections, relative to that of symptomatic ones, and their consequences not only for contact tracing but for precise estimation of the strength of the ongoing COVID-19 outbreak~\citep{park_preprint}.
 The present findings are also consistent with a recent generalization linking speed, strength, and generation intervals, such that for a given observed speed increases in the mean generation interval imply larger reproduction number~\citep{park_2019practical}.
-Hence, reports of individuals with mild, persistent cases suggest the possibility that the mean generation interval for COVID-19 could be longer than estimated from symptomatic cases alone - possibly increasing ${\cal{R}}_0$ (Figure~\ref{fig.relevance}B).
+
+If mild, asymptomatic infections are more persistent than severe, symptomatic ones, the mean generation interval for COVID-19 could be longer than estimated from symptomatic cases alone - possibly increasing ${\cal{R}}_0$ (Figure~\ref{fig.relevance}B).
 However, if asymptomatic cases tend to have shorter infection, then current estimates of ${\cal{R}}_0$ may be over-estimates of the underlying strength (Figure~\ref{fig.relevance}B), although asymptomatic cases may be driving a larger fraction of secondary cases than we would expect when both asymptomatic and symptomatic cases have identical generation-interval distributions (Figure~\ref{fig.relevance}A).
+Therefore, current estimates of ${\cal{R}}_0$ that do not account for asymptomatic cases may be systematically biased.
 

### 2020-03-07 figheatmap.R

@@ -2,11 +2,11 @@ library(emdbook)
 library(ggplot2); theme_set(theme_bw(base_family = "Times"))
 
 r <- 1/7
-G_s <- 7
+G_s <- 8
 kappa_s <- 0.5
 kappa_a <- 0.5
 
-z <- seq(0.01, 0.99, by=0.005)
+z <- seq(0.01, 0.99, by=0.01)
 relG <- exp(seq(log(0.5), log(2), by=0.005))
 
 qodds <- apply2d(
@@ -23,9 +23,22 @@ figdata <- data.frame(
   relG=rep(relG, each=length(z))
 )
 
+example_p <- 0.35
+example_R_a <- 0.5
+example_R_s <- 1
+example_z <- example_p * example_R_a/(1-example_p)
+example_qodds <- example_z/(1-example_z) *  (1 + kappa_s * r * G_s)^(1/kappa_s)/(1 + kappa_a * r * relG * G_s)^(1/kappa_a)
+example_q <- example_qodds/(1+example_qodds)
+range(example_q)
+
+example_qodds2 <- example_z/(1-example_z) *  (1 + kappa_s * r * G_s)^(1/kappa_s)/(1 + kappa_a * r * G_s)^(1/kappa_a)
+example_q2 <- example_qodds2/(1+example_qodds2)
+
 g0 <- ggplot(figdata) +
   geom_raster(aes(relG, z, fill=q)) +
   geom_contour(aes(relG, z, z=q), col="white") +
+  geom_hline(yintercept=example_z, col="black", lwd=1) +
+  geom_point(aes(x=1, y=example_z, fill=example_q2), size=5, col="black", shape=21, stroke=1) +
   scale_x_log10(expression(paste("Relative mean asymptomatic generation interval, ", italic(G[a]/G[s]))), expand=c(0, 0),
                      breaks=c(0.5, 1, 2)) +
   scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),

### 2020-03-07 figheatmap_03.R

@@ -2,7 +2,7 @@ library(emdbook)
 library(ggplot2); theme_set(theme_bw(base_family = "Times"))
 
 r <- 1/7
-G_s <- 7
+G_s <- 8
 kappa_s <- 0.2
 kappa_a <- 0.2
 

### 2020-03-07 figheatmap_08.R

@@ -2,7 +2,7 @@ library(emdbook)
 library(ggplot2); theme_set(theme_bw(base_family = "Times"))
 
 r <- 1/7
-G_s <- 7
+G_s <- 8
 kappa_s <- 0.8
 kappa_a <- 0.8
 

### 2020-03-07 figheatmap_R0.R

@@ -2,11 +2,11 @@ library(emdbook)
 library(ggplot2); theme_set(theme_bw(base_family = "Times"))
 
 r <- 1/7
-G_s <- 7
+G_s <- 8
 kappa_s <- 0.5
 kappa_a <- 0.5
 
-z <- seq(0.01, 0.99, by=0.005)
+z <- seq(0.01, 0.99, by=0.01)
 relG <- exp(seq(log(0.5), log(2), by=0.01))
 
 R0 <- apply2d(
@@ -23,9 +23,21 @@ figdata <- data.frame(
   relG=rep(relG, each=length(z))
 )
 
+example_p <- 0.35
+example_R_a <- 0.5
+example_R_s <- 1
+example_z <- example_p * example_R_a/(1-example_p)
+example_R0 <- 1/((1-example_z) * (1 + kappa_s * r * G_s)^(-1/kappa_s) + example_z * (1 + kappa_a * r * relG * G_s)^(-1/kappa_a))
+example_R02 <- 1/((1-example_z) * (1 + kappa_s * r * G_s)^(-1/kappa_s) + example_z * (1 + kappa_a * r * G_s)^(-1/kappa_a))
+range(example_R0)
+
 g0 <- ggplot(figdata) +
   geom_raster(aes(relG, z, fill=R0)) +
   geom_contour(aes(relG, z, z=R0), col="white") +
+  geom_hline(yintercept=example_z, col="black", lwd=1) +
+  geom_point(aes(x=1, y=example_z, fill=example_R02), size=5, col="black", shape=21, stroke=1) +
+  geom_text(aes(x=1*1.5, y=example_z+0.05, label="underestimated")) +
+  geom_text(aes(x=1/1.5, y=example_z+0.05, label="overestimated")) +
   scale_x_log10(expression(paste("Relative mean asymptomatic generation interval, ", italic(G[a]/G[s]))), expand=c(0, 0),
                 breaks=c(0.5, 1, 2),
                 limits=c(0.5, 2)) +
@@ -33,8 +45,8 @@ g0 <- ggplot(figdata) +
                      limits=c(0, 1),
                      breaks=0:10/10) +
   scale_fill_gradientn(colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
-                       limits=c(1.5, 5),
-                       breaks=c(1.5, 2.5, 3.5, 4.5)) +
[…]

### 2020-03-07 figheatmap_R0_03.R

@@ -2,7 +2,7 @@ library(emdbook)
 library(ggplot2); theme_set(theme_bw(base_family = "Times"))
 
 r <- 1/7
-G_s <- 7
+G_s <- 8
 kappa_s <- 0.3
 kappa_a <- 0.3
 
@@ -33,8 +33,8 @@ g0 <- ggplot(figdata) +
                      limits=c(0, 1),
                      breaks=0:10/10) +
   scale_fill_gradientn(colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
-                       limits=c(1.5, 5),
-                       breaks=c(1.5, 2.5, 3.5, 4.5)) +
+                       limits=c(1.5, 6),
+                       breaks=c(1.5, 2.5, 3.5, 4.5, 5.5)) +
   ggtitle("B. Basic reproduction number") +
   theme(
     legend.title = element_blank(),

### 2020-03-07 figheatmap_R0_08.R

@@ -2,7 +2,7 @@ library(emdbook)
 library(ggplot2); theme_set(theme_bw(base_family = "Times"))
 
 r <- 1/7
-G_s <- 7
+G_s <- 8
 kappa_s <- 0.8
 kappa_a <- 0.8
 
@@ -33,8 +33,8 @@ g0 <- ggplot(figdata) +
                      limits=c(0, 1),
                      breaks=0:10/10) +
   scale_fill_gradientn(colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
-                       limits=c(1.5, 5),
-                       breaks=c(1.5, 2.5, 3.5, 4.5)) +
+                       limits=c(1.5, 6),
+                       breaks=c(1.5, 2.5, 3.5, 4.5, 5.5)) +
   ggtitle("B. Basic reproduction number") +
   theme(
     legend.title = element_blank(),

### 2020-03-07 figheatmap_kappa.R

@@ -2,8 +2,8 @@ library(emdbook)
 library(ggplot2); theme_set(theme_bw(base_family = "Times"))
 
 r <- 1/7
-G_s <- 7
-G_a <- 7
+G_s <- 8
+G_a <- 8
 kappa_s <- 0.5
 
 z <- seq(0.01, 0.99, by=0.005)

### 2020-03-07 figheatmap_kappa_R0.R

@@ -2,8 +2,8 @@ library(emdbook)
 library(ggplot2); theme_set(theme_bw(base_family = "Times"))
 
 r <- 1/7
-G_s <- 7
-G_a <- 7
+G_s <- 8
+G_a <- 8
 kappa_s <- 0.5
 
 z <- seq(0.01, 0.99, by=0.005)
@@ -33,8 +33,8 @@ g0 <- ggplot(figdata) +
                      limits=c(0, 1),
                      breaks=0:10/10) +
   scale_fill_gradientn(colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
-                       limits=c(1.5, 5),
-                       breaks=c(1.5, 2.5, 3.5, 4.5)) +
+                       limits=c(1.5, 6),
+                       breaks=c(1.5, 2.5, 3.5, 4.5, 5.5)) +
   ggtitle("B. Basic reproduction number") +
   theme(
     legend.title = element_blank(),

### 2020-03-07 abs.tex
push

@@
 {\footnotesize We assess the impact of asymptomatic cases on epidemic potential of COVID-19 (and COVID-19 like pathogens) -- as measured both by the basic reproduction 
-number and the fraction of new secondary cases attributable to asymptomatic
+number (i.e., the expected number of secondary cases generated by an average primary case in a fully susceptible population) and the fraction of new secondary cases attributable to asymptomatic
 individuals. As we show, the impact of asymptomatic
-cases depends on their generation intervals.  
+cases depends on their generation intervals (i.e., time between when an individual is infected and when that individual infects another person).
 If the generation intervals of asymptomatic cases differs from that 
-of symptomatic cases, then estimates of the basic reproductive ratio which do not explicitly account for asymptomatic cases may be systematically biased.
+of symptomatic cases, then estimates of the basic reproduction number which do not explicitly account for asymptomatic cases may be systematically biased.
 Specifically, if asymptomatic cases have a shorter generation interval,

### 2020-03-07 short.body.tex
push

@@
 If asymptomatic cases are important for transmission, they also have the potential to affect estimates of key parameters of disease spread such as the basic reproduction number ${\cal{R}}_0$ (i.e., the expected number of secondary cases generated by an average primary case in a fully susceptible population \citep{anderson1992infectious}).
-Here, we investigate the relationship between individual-level features of asymptomatic cases (e.g., the probability of initiating an asymptomatic case, asymptomatic case duration, and the transmission rates from asymptomatic individuals) to dynamics at the population scale.
+Here, we investigate the relationship between individual-level features of asymptomatic cases (e.g., the probability of initiating an asymptomatic case, asymptomatic case duration, and the transmission rates from asymptomatic individuals), which are represented by a generation-interval distribution, to dynamics at the population scale.
 That is, rather than focusing on the prevalence
 of asymptomatic cases, we are interested in understanding the
-relevance of asymptomatic infections to secondary case production -- including
-to the production of symptomatic cases.
+relevance of asymptomatic infections to secondary case production.
 
@@
 \end{equation}
-where $p$ is the proportion of \emph{incident cases} that are asymptomatic.
+where $p$ is the proportion of \emph{incident cases} that are asymptomatic: $i_a(t) = p i(t)$.
 We define the ``intrinsic'' proportion of asymptomatic transmission as the relative contribution of asymptomatic cases to the basic reproduction number:
@@
 
-The intrinsic generation-interval distribution depends on the intrinsic proportion of asymptomatic vs.~symptomatic transmission and their corresponding intrinsic generation-interval distributions:
+The intrinsic generation-interval distribution \citep{champredon2015intrinsic} depends on the intrinsic proportion of asymptomatic vs.~symptomatic transmission and their corresponding intrinsic generation-interval distributions:
 \begin{equation}
@@
 
-The number of infected cases is expected to increase exponentially at rate $r$ at the outset of an outbreak. We note that, in practice, counted cases may largely be of the symptomatic type.
+% The number of infected cases is expected to increase exponentially at rate $r$ at the outset of an outbreak.
+We note that, in practice, counted cases may largely be of the symptomatic type.
 Hence, we ask: is the expected ratio of incidence caused by asymptomatic cases vs.~symptomatic cases during the outbreak phase the same or different from $z/(1-z)$?
@@
 The consequences for outbreak potential further depends on the relative lengths of generation intervals as well as the relative amount of dispersions in them.
-In Supplementary Materials, we use a compartmental ordinary differential equation model to show that the duration of infectious period of asymptomatic individuals affects both $q$ and $\mathcal R_0$, which is a special case of Eq.~\req{eq.qratio}.
+In Supplementary Materials, we use a compartmental ordinary differential equation model to show that the duration of infectious period of asymptomatic individuals affects both $q$ and $\mathcal R_0$, which is a special case of Eq.~\req{eq.qratio}; we also show that prevalence of asymptomatic/symptomatic cases differs from $p$ and $1-p$.
 
@@
 We evaluate the impacts of intrinsic proportion of asymptomatic transmission $z$ on the realized relevance of asymptomatic infection $q$ and the basic reproduction number ${\cal{R}}_0$, given variation in relative mean generation interval $\bar G_a/\bar G_s$ of asymptomatic cases, using parameter values that are consistent with earlier COVID-19 models \citep{park_preprint}: $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.5$.
-We vary $\bar G_a/\bar G_s$ between 0.5 and 2 and infer $q$ and ${\cal{R}}_0$ compatible with an estimated value of $r$ from case data given the generation interval distributions of asymptomatic and symptomatic cases.
+We vary $\bar G_a/\bar G_s$ between 0.5 and 2, and infer values of $q$ and ${\cal{R}}_0$ compatible with an estimated growth rate $r$ from case data given the generation interval distributions of asymptomatic and symptomatic cases.
 Across the ranges of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.relevance}A).
@@
 
-Figure~\ref{fig.relevance}B compares the effect of relative mean generation interval of asymptomatic cases, $\bar G_a/\bar G_s$, on ${\cal{R}}_0$.
-When $\bar G_s < \bar G_a$, then the strength ${\cal{R}}_0$ increases with $z$.
-This increase arises because asymptomatic infections that have long generation intervals increase the duration of overall generation intervals (see~\citep{park_2019practical}).
+Figure~\ref{fig.relevance}B compares the effect of relative mean generation interval of asymptomatic cases, $\bar G_a/\bar G_s$, on the basic reproduction number ${\cal{R}}_0$.
+When $\bar G_s < \bar G_a$, then ${\cal{R}}_0$ increases with $z$.
+This increase arises because asymptomatic infections that have long generation intervals increase the mean of overall generation intervals (see~\citep{park_2019practical}).
 Conversely, when $\bar G_s > \bar G_a$ then the strength ${\cal{R}}_0$ decreases with $z$ because short generation intervals of asymptomatic cases reduce the overall mean generation interval.
@@
 Much is still unknown about course of asymptomatic infection compared to symptomatic infection in COVID-19. 
-Our current work highlights the need to characterize the duration of asymptomatic infections, relative to that of symptomatic ones, and their consequences not only for contact tracing but for precise estimation of the strength of the ongoing COVID-19 outbreak~\citep{park_preprint}.
+Our current work highlights the need to characterize the duration of asymptomatic infections, relative to that of symptomatic ones, and their consequences not only for contact tracing but for precise estimation of the basic reproduction number of the ongoing COVID-19 outbreak~\citep{park_preprint}.
 The present findings are also consistent with a recent generalization linking speed, strength, and generation intervals, such that for a given observed speed increases in the mean generation interval imply larger reproduction number~\citep{park_2019practical}.
@@
 If mild, asymptomatic infections are more persistent than severe, symptomatic ones, the mean generation interval for COVID-19 could be longer than estimated from symptomatic cases alone - possibly increasing ${\cal{R}}_0$ (Figure~\ref{fig.relevance}B).
-However, if asymptomatic cases tend to have shorter infection, then current estimates of ${\cal{R}}_0$ may be over-estimates of the underlying strength (Figure~\ref{fig.relevance}B), although asymptomatic cases may be driving a larger fraction of secondary cases than we would expect when both asymptomatic and symptomatic cases have identical generation-interval distributions (Figure~\ref{fig.relevance}A).
+However, if asymptomatic cases tend to have shorter infection, then current estimates of ${\cal{R}}_0$ may be over-estimates of the underlying strength (Figure~\ref{fig.relevance}B), although asymptomatic cases may be driving a larger fraction of secondary cases than we would expect without accounting for their differences (Figure~\ref{fig.relevance}A).
 Therefore, current estimates of ${\cal{R}}_0$ that do not account for asymptomatic cases may be systematically biased.

### 2020-03-07 appendix.tex
k

@@
 Consider an SEIR model variant in which an infected individual can be either asymptomatic, $I_a$, or symptomatic, $I_s$.
+We note that $I_a$ and $I_s$ represent prevalence (i.e., the total number of currently infectious individuals) of asymptomatic and symptomatic individuals; these quantities are different from $i_s$ and $i_s$ that we present in the main text, which represent incidence (i.e., the rate at which new cases are generated)  of asymptomatic and symptomatic individuals.
 While both cases can recover, we assume that only symptomatic cases can lead to fatalities, denoted
@@
 \end{equation}
-Therefore, the ratio of secondary case production caused by asymptomatic vs.~symptomatic
+The prevalence of asymptomatic and symptomatic individuals is different from $p$ and $1-p$ because prevalence measures the individuals that are currently infectious and does not account for individuals that have already recovered.
+Finally, the ratio of secondary case production caused by asymptomatic vs.~symptomatic
 individuals during the exponential phase should be

### 2020-03-07 short.body.tex
typo

@@
 The solid, black lines represent the example scenario that assumes $p = 0.35$ and $\mathcal R_a = 0.5 \mathcal R_s$.
-The solid, black circle represents the baseline value that does not explicitly account for asymptomatic transmission; depending on whether $G_a$ is smaller or bigger than $G_s$, the baseline value over- or under-estimates the true $\mathcal R_0$.
+The solid, black circles represent the baseline value that does not explicitly account for asymptomatic transmission; depending on whether $G_a$ is smaller or bigger than $G_s$, the baseline value over- or under-estimates the true $\mathcal R_0$.
 \label{fig.relevance}}

### 2020-03-07 short.body.tex
updated to 18%

@@
 The solid, white lines represent the contours.
-The solid, black lines represent the example scenario that assumes $p = 0.35$ and $\mathcal R_a = 0.5 \mathcal R_s$.
-The solid, black circles represent the baseline value that does not explicitly account for asymptomatic transmission; depending on whether $G_a$ is smaller or bigger than $G_s$, the baseline value over- or under-estimates the true $\mathcal R_0$.
+The solid, red lines represent the example scenario that assumes $p = 0.18$ and $\mathcal R_a = 0.5 \mathcal R_s$.
+The solid, red circles represent the baseline value that does not explicitly account for asymptomatic transmission; depending on whether $G_a$ is smaller or bigger than $G_s$, the baseline value over- or under-estimates the true $\mathcal R_0$.
 \label{fig.relevance}}
@@
 
-As an example, we assume that 35\% of the newly infected cases are asymptomatic \citep{mizumoto_2020} and that the asymptomatic cases are as half as infectious as the symptomatic ones (i.e., $\mathcal R_a = 0.5 \mathcal R_s$).
-The intrinsic proportion of asymptomatic transmission $z$ is 0.27, but asymptomatic cases can account for anywhere between 17\% and 35\% of infection during the exponential growth phase across the range of mean asymptomatic generation interval we explore (Figure~\ref{fig.relevance}A).
-Likewise, the basic reproduction number ranges between 2.2 and 2.8 (Figure~\ref{fig.relevance}B).
-Therefore, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread ($\mathcal R_0=2.5$; black circle in Figure~\ref{fig.relevance}B), it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
+As an example, we assume that 18\% of the newly infected cases are asymptomatic \citep{mizumoto_2020} and that the asymptomatic cases are as half as infectious as the symptomatic ones (i.e., $\mathcal R_a = 0.5 \mathcal R_s$).
+The intrinsic proportion of asymptomatic transmission $z$ is 0.11, whereas asymptomatic cases can account for anywhere between 6\% and 16\% of infection during the exponential growth phase across the range of mean asymptomatic generation interval we explore (Figure~\ref{fig.relevance}A).
+Likewise, the basic reproduction number ranges between 2.3 and 2.6 (Figure~\ref{fig.relevance}B).
+Therefore, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread ($\mathcal R_0=2.5$; red circle in Figure~\ref{fig.relevance}B), it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
 

### 2020-03-07 figheatmap.R

@@ -23,7 +23,7 @@ figdata <- data.frame(
   relG=rep(relG, each=length(z))
 )
 
-example_p <- 0.35
+example_p <- 0.18
 example_R_a <- 0.5
 example_R_s <- 1
 example_z <- example_p * example_R_a/(1-example_p)
@@ -37,8 +37,8 @@ example_q2 <- example_qodds2/(1+example_qodds2)
 g0 <- ggplot(figdata) +
   geom_raster(aes(relG, z, fill=q)) +
   geom_contour(aes(relG, z, z=q), col="white") +
-  geom_hline(yintercept=example_z, col="black", lwd=1) +
-  geom_point(aes(x=1, y=example_z, fill=example_q2), size=5, col="black", shape=21, stroke=1) +
+  geom_hline(yintercept=example_z, col="red", lwd=1) +
+  geom_point(aes(x=1, y=example_z, fill=example_q2), size=5, col="red", shape=21, stroke=1) +
   scale_x_log10(expression(paste("Relative mean asymptomatic generation interval, ", italic(G[a]/G[s]))), expand=c(0, 0),
                      breaks=c(0.5, 1, 2)) +
   scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),

### 2020-03-07 figheatmap_R0.R

@@ -23,7 +23,7 @@ figdata <- data.frame(
   relG=rep(relG, each=length(z))
 )
 
-example_p <- 0.35
+example_p <- 0.18
 example_R_a <- 0.5
 example_R_s <- 1
 example_z <- example_p * example_R_a/(1-example_p)
@@ -34,10 +34,10 @@ range(example_R0)
 g0 <- ggplot(figdata) +
   geom_raster(aes(relG, z, fill=R0)) +
   geom_contour(aes(relG, z, z=R0), col="white") +
-  geom_hline(yintercept=example_z, col="black", lwd=1) +
-  geom_point(aes(x=1, y=example_z, fill=example_R02), size=5, col="black", shape=21, stroke=1) +
-  geom_text(aes(x=1*1.5, y=example_z+0.05, label="underestimated")) +
-  geom_text(aes(x=1/1.5, y=example_z+0.05, label="overestimated")) +
+  geom_hline(yintercept=example_z, col="red", lwd=1) +
+  geom_point(aes(x=1, y=example_z, fill=example_R02), size=5, col="red", shape=21, stroke=1) +
+  geom_text(aes(x=1*1.5, y=example_z+0.05, label="underestimated"), col="red") +
+  geom_text(aes(x=1/1.5, y=example_z+0.05, label="overestimated"), col="red") +
   scale_x_log10(expression(paste("Relative mean asymptomatic generation interval, ", italic(G[a]/G[s]))), expand=c(0, 0),
                 breaks=c(0.5, 1, 2),
                 limits=c(0.5, 2)) +

### 2020-03-08 short.body.tex
new fig

@@
 We vary $G_a/G_s$ while assuming $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.5$.
-The solid, white lines represent the contours.
-The solid, red lines represent the example scenario that assumes $p = 0.18$ and $\mathcal R_a = 0.5 \mathcal R_s$.
-The solid, red circles represent the baseline value that does not explicitly account for asymptomatic transmission; depending on whether $G_a$ is smaller or bigger than $G_s$, the baseline value over- or under-estimates the true $\mathcal R_0$.
+The white lines represent the contours.
+The white circles represent the baseline value that does not explicitly account for asymptomatic transmission; depending on whether $G_a$ is smaller or bigger than $G_s$, the baseline value over- or under-estimates the true $\mathcal R_0$.
 \label{fig.relevance}}

### 2020-03-08 figheatmap.R

@@ -37,8 +37,8 @@ example_q2 <- example_qodds2/(1+example_qodds2)
 g0 <- ggplot(figdata) +
   geom_raster(aes(relG, z, fill=q)) +
   geom_contour(aes(relG, z, z=q), col="white") +
-  geom_hline(yintercept=example_z, col="red", lwd=1) +
-  geom_point(aes(x=1, y=example_z, fill=example_q2), size=5, col="red", shape=21, stroke=1) +
+  # geom_hline(yintercept=example_z, col="red", lwd=1) +
+  geom_point(aes(x=1, y=example_z, fill=example_q2), size=5, col="white", shape=1, stroke=1) +
   scale_x_log10(expression(paste("Relative mean asymptomatic generation interval, ", italic(G[a]/G[s]))), expand=c(0, 0),
                      breaks=c(0.5, 1, 2)) +
   scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),

### 2020-03-08 figheatmap_R0.R

@@ -33,11 +33,11 @@ range(example_R0)
 
 g0 <- ggplot(figdata) +
   geom_raster(aes(relG, z, fill=R0)) +
-  geom_contour(aes(relG, z, z=R0), col="white") +
-  geom_hline(yintercept=example_z, col="red", lwd=1) +
-  geom_point(aes(x=1, y=example_z, fill=example_R02), size=5, col="red", shape=21, stroke=1) +
-  geom_text(aes(x=1*1.5, y=example_z+0.05, label="underestimated"), col="red") +
-  geom_text(aes(x=1/1.5, y=example_z+0.05, label="overestimated"), col="red") +
+  geom_contour(aes(relG, z, z=R0), col="white", bins=9) +
+  # geom_hline(yintercept=example_z, col="red", lwd=1) +
+  geom_point(aes(x=1, y=example_z, fill=example_R02), size=5, col="white", stroke=1, shape=1) +
+  annotate(geom="text", x=1*sqrt(2), y=0.03, label="underestimated", col="white") +
+  annotate(geom="text", x=1/sqrt(2), y=0.03, label="overestimated", col="white") +
   scale_x_log10(expression(paste("Relative mean asymptomatic generation interval, ", italic(G[a]/G[s]))), expand=c(0, 0),
                 breaks=c(0.5, 1, 2),
                 limits=c(0.5, 2)) +

### 2020-03-08 appendix.tex
update
I'm going to stop fiddling...

@@
 the mean generation interval of asymptomatic cases when generation-interval distributions are narrow. 
-We vary $G_a/G_s$ while assuming $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.3$.
+Here, we assume $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.3$.
 See Figure 1 in the main text for figure caption.
@@
 the mean generation interval of asymptomatic cases when generation-interval distributions are wide. 
-We vary $G_a/G_s$ while assuming $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.8$.
+Here, we assume $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.8$.
 See Figure 1 in the main text for figure caption.
@@
 (B) Wide/narrow generation intervals of asymptomatic cases decrease/increase the basic reproduction number ${\cal{R}}_0$.
-We vary $\kappa_a/\kappa_s$ while assuming $1/r=7$ days, $\bar G_s=\bar G_a=8$ days, and $\kappa_s=0.5$.
-The solid, white lines represent the contours.
+The white, solid lines represent the contour lines.
+Here, we assume $1/r=7$ days, $\bar G_s=\bar G_a=8$ days, and $\kappa_s=0.5$.
 }

### 2020-03-08 short.body.tex
I'm going to stop fiddling...

@@
 (B) Long/short generation intervals of asymptomatic cases increase/decrease the basic reproduction number ${\cal{R}}_0$.
-We vary $G_a/G_s$ while assuming $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.5$.
-The white lines represent the contours.
-The white circles represent the baseline value that does not explicitly account for asymptomatic transmission; depending on whether $G_a$ is smaller or bigger than $G_s$, the baseline value over- or under-estimates the true $\mathcal R_0$.
+Depending on whether $G_a$ is smaller (left side of the white, dashed line) or bigger (right side of the white, dashed line) than $G_s$, naive estimate that does not explicitly account for asymptomatic transmission over- or under-estimates the true $\mathcal R_0$.
+The white circles represent the baseline value at $p=0.18$ and $\mathcal R_a = 0.5 \mathcal R_s$.
+The white, solid lines represent the contour lines.
+Here, we assume $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.5$.
 \label{fig.relevance}}
@@
 As an example, we assume that 18\% of the newly infected cases are asymptomatic \citep{mizumoto_2020} and that the asymptomatic cases are as half as infectious as the symptomatic ones (i.e., $\mathcal R_a = 0.5 \mathcal R_s$).
-The intrinsic proportion of asymptomatic transmission $z$ is 0.11, whereas asymptomatic cases can account for anywhere between 6\% and 16\% of infection during the exponential growth phase across the range of mean asymptomatic generation interval we explore (Figure~\ref{fig.relevance}A).
-Likewise, the basic reproduction number ranges between 2.3 and 2.6 (Figure~\ref{fig.relevance}B).
-Therefore, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread ($\mathcal R_0=2.5$; red circle in Figure~\ref{fig.relevance}B), it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
+The intrinsic proportion of asymptomatic transmission $z$ is 0.11 (white circle in Figure~\ref{fig.relevance}A), but asymptomatic cases can account for anywhere between 6\% and 16\% of infection during the exponential growth phase across the range of mean asymptomatic generation interval we explore.
+Likewise, the basic reproduction number ranges between 2.3 and 2.6.
+Therefore, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread ($\mathcal R_0=2.5$; white circle in Figure~\ref{fig.relevance}B), it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
 

### 2020-03-08 figheatmap_R0.R

@@ -34,8 +34,9 @@ range(example_R0)
 g0 <- ggplot(figdata) +
   geom_raster(aes(relG, z, fill=R0)) +
   geom_contour(aes(relG, z, z=R0), col="white", bins=9) +
+  geom_vline(xintercept=1, lty=2, col="white", lwd=0.8) +
   # geom_hline(yintercept=example_z, col="red", lwd=1) +
-  geom_point(aes(x=1, y=example_z, fill=example_R02), size=5, col="white", stroke=1, shape=1) +
+  geom_point(aes(x=1, y=example_z, fill=example_R02), size=5, col="white", stroke=1, shape=21) +
   annotate(geom="text", x=1*sqrt(2), y=0.03, label="underestimated", col="white") +
   annotate(geom="text", x=1/sqrt(2), y=0.03, label="overestimated", col="white") +
   scale_x_log10(expression(paste("Relative mean asymptomatic generation interval, ", italic(G[a]/G[s]))), expand=c(0, 0),

### 2020-03-08 appendix.tex
misc edits

@@
 \end{equation}
-The prevalence of asymptomatic and symptomatic individuals is different from $p$ and $1-p$ because prevalence measures the individuals that are currently infectious and does not account for individuals that have already recovered.
+This shows that the prevalence of asymptomatic and symptomatic individuals is different from $p$ and $1-p$ because prevalence measures the individuals that are currently infectious and does not account for individuals that have already recovered.
 Finally, the ratio of secondary case production caused by asymptomatic vs.~symptomatic

### 2020-03-08 short.body.tex
misc edits

@@
 In order to understand how the shape of asymptomatic and symptomatic generation-interval distributions affects $q$ and $\mathcal R_0$, we summarize the distributions in terms of their means and dispersions.
-Assuming that the intrinsic generation-interval distributions for asymptomatic and symptomatic cases follow gamma distributions with different means, $\bar G_a$ and $\bar G_s$, and dispersions (represented by squared coefficients of variations), $\kappa_a$ and $\kappa_s$ \citep{park_2019practical},
+Assuming that the intrinsic generation-interval distributions for asymptomatic and symptomatic cases follow gamma distributions \citep{park_2019practical} with different means, $\bar G_a$ and $\bar G_s$, and dispersions (represented by squared coefficients of variations), $\kappa_a$ and $\kappa_s$,
 we have
@@
 (B) Long/short generation intervals of asymptomatic cases increase/decrease the basic reproduction number ${\cal{R}}_0$.
-Depending on whether $G_a$ is smaller (left side of the white, dashed line) or bigger (right side of the white, dashed line) than $G_s$, naive estimate that does not explicitly account for asymptomatic transmission over- or under-estimates the true $\mathcal R_0$.
-The white circles represent the baseline value at $p=0.18$ and $\mathcal R_a = 0.5 \mathcal R_s$.
+Depending on whether $\bar G_a$ is smaller (left side of the white, dashed line) or bigger (right side of the white, dashed line) than $\bar G_s$, naive estimate that does not explicitly account for asymptomatic transmission (white, dashed line) over- or under-estimates the true $\mathcal R_0$.
 The white, solid lines represent the contour lines.
@@
 Conversely, when $\bar G_s > \bar G_a$ then the strength ${\cal{R}}_0$ decreases with $z$ because short generation intervals of asymptomatic cases reduce the overall mean generation interval.
+Therefore, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread (white, dashed line in Figure~\ref{fig.relevance}B), it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
 The qualitative effects of $z$ and $\bar G_a/\bar G_s$ on $q$ and ${\cal{R}}_0$ remain robust when we assume narrower ($\kappa_s = \kappa_a = 0.3$; Figure~S1) or wider ($\kappa_s = \kappa_a = 0.8$; Figure~S2) generation intervals.
-
-As an example, we assume that 18\% of the newly infected cases are asymptomatic \citep{mizumoto_2020} and that the asymptomatic cases are as half as infectious as the symptomatic ones (i.e., $\mathcal R_a = 0.5 \mathcal R_s$).
-The intrinsic proportion of asymptomatic transmission $z$ is 0.11 (white circle in Figure~\ref{fig.relevance}A), but asymptomatic cases can account for anywhere between 6\% and 16\% of infection during the exponential growth phase across the range of mean asymptomatic generation interval we explore.
-Likewise, the basic reproduction number ranges between 2.3 and 2.6.
-Therefore, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread ($\mathcal R_0=2.5$; white circle in Figure~\ref{fig.relevance}B), it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
-
-% In both cases, the dependence of R0 on q is compared to a baseline of R0 ≈ 3.1 in a model with no secondary case production from asymptomatic infections (see filled circle at bottom left of Figure 1C-D.
-% In other words, when R0 is estimated without explicitly accounting for asymptomatic spread, it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
 

### 2020-03-08 figheatmap.R

@@ -38,7 +38,7 @@ g0 <- ggplot(figdata) +
   geom_raster(aes(relG, z, fill=q)) +
   geom_contour(aes(relG, z, z=q), col="white") +
   # geom_hline(yintercept=example_z, col="red", lwd=1) +
-  geom_point(aes(x=1, y=example_z, fill=example_q2), size=5, col="white", shape=1, stroke=1) +
+  # geom_point(aes(x=1, y=example_z, fill=example_q2), size=5, col="white", shape=1, stroke=1) +
   scale_x_log10(expression(paste("Relative mean asymptomatic generation interval, ", italic(G[a]/G[s]))), expand=c(0, 0),
                      breaks=c(0.5, 1, 2)) +
   scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),

### 2020-03-08 figheatmap_R0.R

@@ -36,7 +36,7 @@ g0 <- ggplot(figdata) +
   geom_contour(aes(relG, z, z=R0), col="white", bins=9) +
   geom_vline(xintercept=1, lty=2, col="white", lwd=0.8) +
   # geom_hline(yintercept=example_z, col="red", lwd=1) +
-  geom_point(aes(x=1, y=example_z, fill=example_R02), size=5, col="white", stroke=1, shape=21) +
+  # geom_point(aes(x=1, y=example_z, fill=example_R02), size=5, col="white", stroke=1, shape=21) +
   annotate(geom="text", x=1*sqrt(2), y=0.03, label="underestimated", col="white") +
   annotate(geom="text", x=1/sqrt(2), y=0.03, label="overestimated", col="white") +
   scale_x_log10(expression(paste("Relative mean asymptomatic generation interval, ", italic(G[a]/G[s]))), expand=c(0, 0),

### 2020-03-08 short.body.tex
lunch time

@@
 Asymptomatic individuals are hard to trace, unlikely to self-isolate, and are likely to retain normal social and travel patterns.
+
+\jd{Delete this \P\ and roll the citations appropriately into the next one.}
 The COVID-19 outbreak has raised significant
@@
 If asymptomatic cases are important for transmission, they also have the potential to affect estimates of key parameters of disease spread such as the basic reproduction number ${\cal{R}}_0$ (i.e., the expected number of secondary cases generated by an average primary case in a fully susceptible population \citep{anderson1992infectious}).
-Here, we investigate the relationship between individual-level features of asymptomatic cases (e.g., the probability of initiating an asymptomatic case, asymptomatic case duration, and the transmission rates from asymptomatic individuals), which are represented by a generation-interval distribution, to dynamics at the population scale.
-That is, rather than focusing on the prevalence
-of asymptomatic cases, we are interested in understanding the
-relevance of asymptomatic infections to secondary case production.
+Thus, we investigate the relationship between individual-level features of asymptomatic cases (e.g., the probability that an infection is asymptomatic, asymptomatic case duration, transmission by asymptomatic individuals) to dynamics at the population scale.
 
@@
 
+\jd{Where should we citect champredon2015intrinsic if I delete the stuff below?}
+
 The intrinsic generation-interval distribution \citep{champredon2015intrinsic} depends on the intrinsic proportion of asymptomatic vs.~symptomatic transmission and their corresponding intrinsic generation-interval distributions:
@@
 
-% The number of infected cases is expected to increase exponentially at rate $r$ at the outset of an outbreak.
-We note that, in practice, counted cases may largely be of the symptomatic type.
-Hence, we ask: is the expected ratio of incidence caused by asymptomatic cases vs.~symptomatic cases during the outbreak phase the same or different from $z/(1-z)$?
-The ratio of secondary case production caused by asymptomatic vs.~symptomatic individuals over the course of an ongoing epidemic is
+The intrinsic proporton of asymptomatic transmission $z$ is a useful benchmark, but does not necessarily reflect the realized proportion of asymptomatic transmission, unless both types of infection have the same generation-interval distribution.
+The \emph{realized} proportion of asymptomatic transmission, $q$ at time $t$ is given by:
 \begin{equation}
@@
 \end{equation}
-where $q$ is the fraction of new secondary cases caused by asymptomatic individuals or `relevance' of asymptomatic cases.
-Assuming that the incidence grows exponentially during the outbreak phase (i.e., $i(t) = i(0) \exp(r t)$) and substituting $i_a(t) = p i(t)$ and $i_s(t) = (1-p) i(t)$, we have
+During the period of exponential growth, we assume $S$ remains nearly constant, and $i(t)$ is proportional to $\exp(r t)$, and simplify: 
 \begin{equation}
@@
 \end{equation}
-The value of $q$ is an unknown feature of outbreaks at the population scale, distinct from $p$ the probability of becoming asymptomatic upon infection or $z$ the intrinsic proportion of asymptomatic transmission.
+
+\jd{Hi, Daniel!}
 

### 2020-03-08 short.body.tex
ok

@@
 
-\jd{Delete this \P\ and roll the citations appropriately into the next one.}
-The COVID-19 outbreak has raised significant
-questions regarding the role of asymptomatic cases~\citep{fauci_nejm2020}.
-A key focus has been on estimating asymptomatic prevalence (see~\citep{mizumoto_2020}), e.g., what fraction of individuals have asymptomatic infections relative to those with symptomatic infections?
-
-There is significant ongoing interest in asymptomatic infections in COVID-19 for two major reasons. 
-First, the proportion of infections that are asymptomatic is critical to attempts to estimate the likely burden of severe outcomes (including mortality) when the virus spreads through a population.
+There is significant ongoing interest in asymptomatic infections in COVID-19 for two major reasons~\citep{fauci_nejm2020}. 
+First, the proportion of infections that are asymptomatic (see~\citep{mizumoto_2020}) is critical to attempts to estimate the likely burden of severe outcomes (including mortality) when the virus spreads through a population.
 Second, understanding the possible role of \emph{transmission} by asymptomatic individuals is crucial to planning surveillance and control efforts.
@@
 We divide incidence $i$ into two categories -- $i_a$ and $i_s$ -- corresponding to incidence of asymptomatic and symptomatic cases, respectively.
-Newly infected individuals that are either asymptomatically or symptomatically infected can transmit the disease to others, but they differ in their intrinsic reproduction numbers, ${\cal{R}}_a$ and ${\cal{R}}_s$, respectively, as well as intrinsic generation-interval distributions, $g_a(\tau)$ and $g_s(\tau)$.
+Newly infected individuals that are either asymptomatically or symptomatically infected can transmit the disease to others, but they differ in their intrinsic reproduction numbers, ${\cal{R}}_a$ and ${\cal{R}}_s$, respectively, as well as intrinsic generation-interval distributions \citep{champredon2015intrinsic}, $g_a(\tau)$ and $g_s(\tau)$.
 Generation intervals, which are defined as the time between when an individual is infected and when that individual infects another person \citep{svensson2007note}, depend on the natural history of infection:
@@
 \end{equation}
-
-\jd{Where should we citect champredon2015intrinsic if I delete the stuff below?}
-
-The intrinsic generation-interval distribution \citep{champredon2015intrinsic} depends on the intrinsic proportion of asymptomatic vs.~symptomatic transmission and their corresponding intrinsic generation-interval distributions:
-\begin{equation}
-g(\tau) = z g_a(\tau) + (1-z) g_s(\tau),
-\end{equation}
-which allows us to express incidence of infection as a renewal process that depends on previous incidence:
-\begin{equation}
-i(t) = {\cal{R}}_{0} S(t) \int_0^\infty i(t-\tau) g(\tau) \mathrm{d} \tau.
-\end{equation}
 Yet, this information is not sufficient to disentangle the role of asymptomatic cases, i.e., what fraction of secondary cases can be ascribed to \emph{realized} transmission from asymptomatic cases vs.~symptomatic cases?
@@
 \end{equation}
-
-\jd{Hi, Daniel!}
 

### 2020-03-08 short.body.tex
Methods

@@
 \begin{equation}
-\frac{q}{1-q}=\left(\frac{z}{1-z}\right)\left[\frac{\int_0^\infty \exp(-r\tau) g_a(\tau) \mathrm{d}\tau}{\int_0^\infty \exp(-r\tau) g_s(\tau) \mathrm{d}\tau}\right].
+\frac{q}{1-q}=\left(\frac{z}{1-z}\right)\frac{\delta_a}{\delta_s}.
 \label{eq.qratio}
 \end{equation}
+Here, $\delta_c$ for each of the two classes is the average ``discount'' of a new infection -- the average relative contribution of a secondary infection to the epidemic, taking exponential growth into account:
+\begin{equation}
+	\delta_c = \int_0^\infty \exp(-r\tau) g_c(\tau) \mathrm{d}\tau.
+\end{equation}
+$\delta_c<1$ and grows smaller as the ``effective'' generation interval grows longer.
+Thus, the realized proportion of asymptomatic infections will be increased (resp., decreased) if transmission is relatively faster (slower) along the asymptomatic route.
+This ``effective'' generation interval depends both on the mean generation interval and on the relative variation in the generation-interval distribution, the ``dispersion'': more variation in generation intervals leads to more opportunities for fast spread and thus to shorter effective generation intervals.
 
+\jd{Lose this \P.
+Move what's needed about gamma approximation to supp.
+We also need some text somewhere in main about how we use this approximation (and about how others do, both implicitly and explicitly).}
 In order to understand how the shape of asymptomatic and symptomatic generation-interval distributions affects $q$ and $\mathcal R_0$, we summarize the distributions in terms of their means and dispersions.

### 2020-03-08 short.body.tex
cooperate with Daniel

@@
 \includegraphics[width=0.4\textwidth]{figheatmap_R0.pdf}
-\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
+\caption{Effects of intrinsic proportion of asymptomatic transmission on the realized proportion of asymptomatic transmission and basic reproduction number, given variation in
 the mean generation interval of asymptomatic cases. 
-(A) Long/short generation intervals of asymptomatic cases decrease/increase the relevance of asymptomatic cases, $q$.
+(A) Increasing the speed of asymptomatic transmission (shorter generation intervals) increases the importance of asymptomatic cases in transmission, $q$.
 (B) Long/short generation intervals of asymptomatic cases increase/decrease the basic reproduction number ${\cal{R}}_0$.
@@
 Here, we assume $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.5$.
-\label{fig.relevance}}
+\label{fig.importance}}
 \end{center}
@@
 
-We evaluate the impacts of intrinsic proportion of asymptomatic transmission $z$ on the realized relevance of asymptomatic infection $q$ and the basic reproduction number ${\cal{R}}_0$, given variation in relative mean generation interval $\bar G_a/\bar G_s$ of asymptomatic cases, using parameter values that are consistent with earlier COVID-19 models \citep{park_preprint}: $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.5$.
+We explore the effects of different assumptions about duration and effectiveness of asymptomatic transmission on the importance of asymptomatic transmission and estimates of the realized relevance of asymptomatic infection $q$ and the basic reproduction number ${\cal{R}}_0$, given variation in relative mean generation interval $\bar G_a/\bar G_s$ of asymptomatic cases, using parameter values that are consistent with earlier COVID-19 models \citep{park_preprint}: $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.5$.
 We vary $\bar G_a/\bar G_s$ between 0.5 and 2, and infer values of $q$ and ${\cal{R}}_0$ compatible with an estimated growth rate $r$ from case data given the generation interval distributions of asymptomatic and symptomatic cases.

### 2020-03-08 short.body.tex
time for some housework

@@
 
-We explore the effects of different assumptions about duration and effectiveness of asymptomatic transmission on the importance of asymptomatic transmission and estimates of the realized relevance of asymptomatic infection $q$ and the basic reproduction number ${\cal{R}}_0$, given variation in relative mean generation interval $\bar G_a/\bar G_s$ of asymptomatic cases, using parameter values that are consistent with earlier COVID-19 models \citep{park_preprint}: $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.5$.
-We vary $\bar G_a/\bar G_s$ between 0.5 and 2, and infer values of $q$ and ${\cal{R}}_0$ compatible with an estimated growth rate $r$ from case data given the generation interval distributions of asymptomatic and symptomatic cases.
-Across the ranges of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.relevance}A).
-As the relative mean generation interval of asymptomatic cases, $\bar G_a/\bar G_s$, increases, $q$ decreases because symptomatic cases are more likely to have short generation intervals (i.e., fast transmission events), which drive the spread during the growth phase (Figure~\ref{fig.relevance}A).
+We explore the effects of different assumptions about duration and effectiveness of asymptomatic transmission on the importance of asymptomatic transmission and estimates of the basic reproduction number ${\cal{R}}_0$.
+In particular, we vary assumptions about intrinsic proportion of asymptomatic transmission $z$ and its mean generation interval $\bar G_a$, using parameter values that are consistent with earlier COVID-19 models \citep{park_preprint}: $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.5$.
+We vary the ratio of generation intervals $\bar G_a/\bar G_s$ from 0.5 and 2, and infer values of $q$ and ${\cal{R}}_0$ compatible with an estimated growth rate $r$ from case data given the generation interval distributions of asymptomatic and symptomatic cases.
 
-Figure~\ref{fig.relevance}B compares the effect of relative mean generation interval of asymptomatic cases, $\bar G_a/\bar G_s$, on the basic reproduction number ${\cal{R}}_0$.
+Across the range of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.importance}A).
+As the relative mean generation interval of asymptomatic transmission, $\bar G_a/\bar G_s$, increases, $q$ decreases because symptomatic cases are more likely to have short generation intervals (i.e., fast transmission events), which drive the spread during the growth phase (Figure~\ref{fig.importance}A).
+
+Figure~\ref{fig.importance}B compares the effect of relative mean generation interval of asymptomatic cases, $\bar G_a/\bar G_s$, on the basic reproduction number ${\cal{R}}_0$.
 When $\bar G_s < \bar G_a$, then ${\cal{R}}_0$ increases with $z$.
@@
 Conversely, when $\bar G_s > \bar G_a$ then the strength ${\cal{R}}_0$ decreases with $z$ because short generation intervals of asymptomatic cases reduce the overall mean generation interval.
-Therefore, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread (white, dashed line in Figure~\ref{fig.relevance}B), it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
+Therefore, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread (white, dashed line in Figure~\ref{fig.importance}B), it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
 The qualitative effects of $z$ and $\bar G_a/\bar G_s$ on $q$ and ${\cal{R}}_0$ remain robust when we assume narrower ($\kappa_s = \kappa_a = 0.3$; Figure~S1) or wider ($\kappa_s = \kappa_a = 0.8$; Figure~S2) generation intervals.
@@
 Relative generation-interval dispersion of asymptomatic cases $\kappa_a/\kappa_s$ also have qualitatively similar effects on $q$ and ${\cal{R}}_0$.
-When the asymptomatic cases have a wider/narrower generation-interval distribution, higher intrinsic proportion of asymptomatic transmission $z$ increases/decreases the relevance of asymptomatic transmission $q$ but decreases/increases the basic reproduction number (Figure~S3).
+When the asymptomatic cases have a wider/narrower generation-interval distribution, higher intrinsic proportion of asymptomatic transmission $z$ increases/decreases the realized proportion of asymptomatic transmission $q$ but decreases/increases the basic reproduction number (Figure~S3).
 Since a wider generation-interval distribution has a higher proportion of early transmission than a narrow one, increasing the generation-interval dispersion has qualitatively similar effects on $q$ and ${\cal{R}}_0$ as decreasing the mean generation interval.
@@
 
-If mild, asymptomatic infections are more persistent than severe, symptomatic ones, the mean generation interval for COVID-19 could be longer than estimated from symptomatic cases alone - possibly increasing ${\cal{R}}_0$ (Figure~\ref{fig.relevance}B).
-However, if asymptomatic cases tend to have shorter infection, then current estimates of ${\cal{R}}_0$ may be over-estimates of the underlying strength (Figure~\ref{fig.relevance}B), although asymptomatic cases may be driving a larger fraction of secondary cases than we would expect without accounting for their differences (Figure~\ref{fig.relevance}A).
+If mild, asymptomatic infections are more persistent than severe, symptomatic ones, the mean generation interval for COVID-19 could be longer than estimated from symptomatic cases alone - possibly increasing ${\cal{R}}_0$ (Figure~\ref{fig.importance}B).
+However, if asymptomatic cases tend to have shorter infection, then current estimates of ${\cal{R}}_0$ may be over-estimates of the underlying strength (Figure~\ref{fig.importance}B), although asymptomatic cases may be driving a larger fraction of secondary cases than we would expect without accounting for their differences (Figure~\ref{fig.importance}A).
 Therefore, current estimates of ${\cal{R}}_0$ that do not account for asymptomatic cases may be systematically biased.
 
-Finally, it is important to note we focused here on the exponential phase, but that the asymptomatic relevance $q$ is time-dependent, and will vary given the population state structure of infected individuals.
+Finally, it is important to note we focused here on the exponential phase, but that the realized proportion of asymptomatic transmission $q$ is time-dependent, and will vary given the population state structure of infected individuals.
 Such variation in the ratio of asymptomatic to symptomatic cases will also impact estimates of case fatality rates insofar as many asymptomatic cases are not counted, particularly early in an outbreak.
@@
 %the need to characterize the epidemiological characteristics of asymptomatic transmission.
-
-%than expected. Yet the relevance of asymptomatic cases
-%depends on their realized proportion at a population level.
 

### 2020-03-08 short.body.tex
euler lotka

@@
 where $p$ is the proportion of \emph{incident cases} that are asymptomatic: $i_a(t) = p i(t)$.
-We define the ``intrinsic'' proportion of asymptomatic transmission as the relative contribution of asymptomatic cases to the basic reproduction number:
+The corresponding intrinsic generation-interval distribution of an average infected individual is given by: 
+\begin{equation}
+g(\tau) = z g_a(\tau) + (1-z) g_s(\tau),
+\end{equation}
+where we define the ``intrinsic'' proportion of asymptomatic transmission $z$ as the relative contribution of asymptomatic cases to the basic reproduction number:
 \begin{equation}
@@
 
-\jd{Lose this \P.
-Move what's needed about gamma approximation to supp.
-We also need some text somewhere in main about how we use this approximation (and about how others do, both implicitly and explicitly).}
-In order to understand how the shape of asymptomatic and symptomatic generation-interval distributions affects $q$ and $\mathcal R_0$, we summarize the distributions in terms of their means and dispersions.
-Assuming that the intrinsic generation-interval distributions for asymptomatic and symptomatic cases follow gamma distributions \citep{park_2019practical} with different means, $\bar G_a$ and $\bar G_s$, and dispersions (represented by squared coefficients of variations), $\kappa_a$ and $\kappa_s$,
-we have
-\begin{equation}
-\frac{q}{1-q}=\left(\frac{z}{1-z}\right)\left[\frac{(1 + \kappa_s r \bar G_s)^{1/\kappa_s}}{(1 + \kappa_a r \bar G_a)^{1/\kappa_a}}\right].
-\label{eq.gammaratio}
-\end{equation}
-As is apparent from Eq.~\req{eq.qratio}, relevance $q$ increases with $z$, i.e., with both $p$ and $\mathcal R_a/\mathcal R_s$.
-The consequences for outbreak potential further depends on the relative lengths of generation intervals as well as the relative amount of dispersions in them.
-In Supplementary Materials, we use a compartmental ordinary differential equation model to show that the duration of infectious period of asymptomatic individuals affects both $q$ and $\mathcal R_0$, which is a special case of Eq.~\req{eq.qratio}; we also show that prevalence of asymptomatic/symptomatic cases differs from $p$ and $1-p$.
+\swp{Need to put this somewhere: In Supplementary Materials, we use a compartmental ordinary differential equation model to show that the duration of infectious period of asymptomatic individuals affects both $q$ and $\mathcal R_0$, which is a special case of Eq.~\req{eq.qratio}; we also show that prevalence of asymptomatic/symptomatic cases differs from $p$ and $1-p$.}
+
+We explore the effects of different assumptions about speed and effectiveness of asymptomatic transmission on the importance of asymptomatic transmission and estimates of the basic reproduction number ${\cal{R}}_0$.
+We parameterize the generation interval distributions of asymptomatic and symptomatic cases based on their means, $\bar G_a$ and $\bar G_s$, and dispersions (represented by squared coefficients of variations), $\kappa_a$ and $\kappa_s$, assuming that they follow gamma distributions (see Appendix).
+We assume that epidemic growth rate $r$ and the generation-interval distribution of symptomatic case are known using parameter values that are consistent with earlier COVID-19 models \citep{park_preprint}: $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=0.5$; for simplicity, we assume $\kappa_s=\kappa_a$ but relax this assumption in Appendix.
+We then vary the ratio of generation intervals $\bar G_a/\bar G_s$ from 0.5 and 2, and infer values of $q$ and ${\cal{R}}_0$ compatible with an estimated growth rate $r$ given the generation interval distributions of asymptomatic and symptomatic cases using the Euler-Lotka equation (Appendix).
 
@@
 \end{figure*}
-
-We explore the effects of different assumptions about duration and effectiveness of asymptomatic transmission on the importance of asymptomatic transmission and estimates of the basic reproduction number ${\cal{R}}_0$.
-In particular, we vary assumptions about intrinsic proportion of asymptomatic transmission $z$ and its mean generation interval $\bar G_a$, using parameter values that are consistent with earlier COVID-19 models \citep{park_preprint}: $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.5$.
-We vary the ratio of generation intervals $\bar G_a/\bar G_s$ from 0.5 and 2, and infer values of $q$ and ${\cal{R}}_0$ compatible with an estimated growth rate $r$ from case data given the generation interval distributions of asymptomatic and symptomatic cases.
 

### 2020-03-08 short.body.tex
done

@@
 We assume that epidemic growth rate $r$ and the generation-interval distribution of symptomatic case are known using parameter values that are consistent with earlier COVID-19 models \citep{park_preprint}: $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=0.5$; for simplicity, we assume $\kappa_s=\kappa_a$ but relax this assumption in Appendix.
-We then vary the ratio of generation intervals $\bar G_a/\bar G_s$ from 0.5 and 2, and infer values of $q$ and ${\cal{R}}_0$ compatible with an estimated growth rate $r$ given the generation interval distributions of asymptomatic and symptomatic cases using the Euler-Lotka equation (Appendix).
+We then vary the ratio of generation intervals $\bar G_a/\bar G_s$ from 0.5 and 2, and infer values of $q$ using Eq.~\req{eq.qratio} and ${\cal{R}}_0$ using the Euler-Lotka equation:
+\begin{equation}
+\frac{1}{\mathcal R_0} = \int \exp(-\r tau) g(\tau) \mathrm{d} \tau.
+\end{equation
 

### 2020-03-08 short.body.tex
Cleaning up a bit.

@@
 \end{equation}
-$\delta_c<1$ and grows smaller as the ``effective'' generation interval grows longer.
+$\delta_c<1$ and grows smaller as the generation interval grows longer.
 Thus, the realized proportion of asymptomatic infections will be increased (resp., decreased) if transmission is relatively faster (slower) along the asymptomatic route.
-This ``effective'' generation interval depends both on the mean generation interval and on the relative variation in the generation-interval distribution, the ``dispersion'': more variation in generation intervals leads to more opportunities for fast spread and thus to shorter effective generation intervals.
-
-\swp{Need to put this somewhere: In Supplementary Materials, we use a compartmental ordinary differential equation model to show that the duration of infectious period of asymptomatic individuals affects both $q$ and $\mathcal R_0$, which is a special case of Eq.~\req{eq.qratio}; we also show that prevalence of asymptomatic/symptomatic cases differs from $p$ and $1-p$.}
+The discount $\delta$ also depends on the relative variation in the generation-interval distribution, the ``dispersion'': more variation in generation intervals leads to more opportunities for fast spread and thus to higher values of $\delta$ (similar to shorter average generation intervals).
+In the supplementary material, we use ODEs to give a concrete example of how differences in generation intervals affect both $q$ and estimates of $\mathcal R_0$.
 
@@
 \begin{equation}
-\frac{1}{\mathcal R_0} = \int \exp(-\r tau) g(\tau) \mathrm{d} \tau.
-\end{equation
+\frac{1}{\mathcal R_0} = \int \exp(-r \tau) g(\tau) \mathrm{d} \tau.
+\end{equation}
 

### 2020-03-08 short.body.tex
Methods

@@
 The discount $\delta$ also depends on the relative variation in the generation-interval distribution, the ``dispersion'': more variation in generation intervals leads to more opportunities for fast spread and thus to higher values of $\delta$ (similar to shorter average generation intervals).
-In the supplementary material, we use ODEs to give a concrete example of how differences in generation intervals affect both $q$ and estimates of $\mathcal R_0$.
 
-We explore the effects of different assumptions about speed and effectiveness of asymptomatic transmission on the importance of asymptomatic transmission and estimates of the basic reproduction number ${\cal{R}}_0$.
-We parameterize the generation interval distributions of asymptomatic and symptomatic cases based on their means, $\bar G_a$ and $\bar G_s$, and dispersions (represented by squared coefficients of variations), $\kappa_a$ and $\kappa_s$, assuming that they follow gamma distributions (see Appendix).
-We assume that epidemic growth rate $r$ and the generation-interval distribution of symptomatic case are known using parameter values that are consistent with earlier COVID-19 models \citep{park_preprint}: $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=0.5$; for simplicity, we assume $\kappa_s=\kappa_a$ but relax this assumption in Appendix.
-We then vary the ratio of generation intervals $\bar G_a/\bar G_s$ from 0.5 and 2, and infer values of $q$ using Eq.~\req{eq.qratio} and ${\cal{R}}_0$ using the Euler-Lotka equation:
+To estimate the effects of assumptions about asymptomatic transmission on the importance of asymptomatic transmission and estimates of the basic reproduction number ${\cal{R}}_0$, we parameterize the generation interval distributions of asymptomatic and symptomatic cases based on their means, $\bar G_a$ and $\bar G_s$, and dispersions, $\kappa_a$ and $\kappa_s$.
+We assume that generation intervals are gamma distributed, and we set the dispersion to be equal to the squared coefficient of variation (the reciprocal of the gamma shape parameter, see Appendix).
+We assume that epidemic growth rate $r$ and the generation-interval distribution of symptomatic case are known, using parameter values that are consistent with earlier COVID-19 models \citep{park_preprint}: $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=0.5$.
+We infer values of $q$ using Eq.~\req{eq.qratio} and ${\cal{R}}_0$ using the Euler-Lotka equation:
 \begin{equation}
@@
 \end{equation}
+In the supplementary material, we also use ODEs to give a concrete example of how differences in generation intervals affect both $q$ and estimates of $\mathcal R_0$.
 
@@
 
+We explore the effects of different assumptions about speed and effectiveness of asymptomatic transmission on the importance of asymptomatic transmission and estimates of the basic reproduction number ${\cal{R}}_0$, using a gamma assumption (see Methods).
 Across the range of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.importance}A).

### 2020-03-08 short.body.tex
Hand over

@@
 (A) Increasing the speed of asymptomatic transmission (shorter generation intervals) increases the importance of asymptomatic cases in transmission, $q$.
-(B) Long/short generation intervals of asymptomatic cases increase/decrease the basic reproduction number ${\cal{R}}_0$.
-Depending on whether $\bar G_a$ is smaller (left side of the white, dashed line) or bigger (right side of the white, dashed line) than $\bar G_s$, naive estimate that does not explicitly account for asymptomatic transmission (white, dashed line) over- or under-estimates the true $\mathcal R_0$.
-The white, solid lines represent the contour lines.
+(B) Increasing generation intervals of asymptomatic cases increases the basic reproduction number ${\cal{R}}_0$; 
+When $\bar G_a$ is smaller (larger) than $\bar G_s$, estimates based on the observed generation distribution for symptomatic cases (dashed line) are expected to over- (under-) estimate the true $\mathcal R_0$.
+Solid lines show contours for \Ro\ values. 
 Here, we assume $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.5$.
@@
 
-Figure~\ref{fig.importance}B compares the effect of relative mean generation interval of asymptomatic cases, $\bar G_a/\bar G_s$, on the basic reproduction number ${\cal{R}}_0$.
-When $\bar G_s < \bar G_a$, then ${\cal{R}}_0$ increases with $z$.
-This increase arises because asymptomatic infections that have long generation intervals increase the mean of overall generation intervals (see~\citep{park_2019practical}).
-Conversely, when $\bar G_s > \bar G_a$ then the strength ${\cal{R}}_0$ decreases with $z$ because short generation intervals of asymptomatic cases reduce the overall mean generation interval.
+Figure~\ref{fig.importance}B shows the effect of different assumptions about the generation interval of asymptomatic cases, $\bar G_a$, on the basic reproduction number ${\cal{R}}_0$.
+When $\bar G_a$ is long compared to $\bar G_s$, then we are effectively assuming a longer mean for the overall generation interval. 
+This assumption leads to a larger estimate of \Ro\ for i fixed value of $r$. (see~\citep{park_2019practical}).
+Conversely, when $\bar G_a < \bar G_s$, generation intervals are shorter, leading to lower estimates of the epidemic strength \Ro.
+Both of these effects are stronger when the intrinsic proportion of asymptomatic transmission $z$ increases (and disappear as $z\to0$).
 Therefore, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread (white, dashed line in Figure~\ref{fig.importance}B), it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
@@
 
-Relative generation-interval dispersion of asymptomatic cases $\kappa_a/\kappa_s$ also have qualitatively similar effects on $q$ and ${\cal{R}}_0$.
-When the asymptomatic cases have a wider/narrower generation-interval distribution, higher intrinsic proportion of asymptomatic transmission $z$ increases/decreases the realized proportion of asymptomatic transmission $q$ but decreases/increases the basic reproduction number (Figure~S3).
+Relative generation-interval dispersion of asymptomatic cases $\kappa_a/\kappa_s$ have similar, but smaller, effects on $q$ and ${\cal{R}}_0$ (Figure~S3).
 Since a wider generation-interval distribution has a higher proportion of early transmission than a narrow one, increasing the generation-interval dispersion has qualitatively similar effects on $q$ and ${\cal{R}}_0$ as decreasing the mean generation interval.

### 2020-03-08 appendix.tex
edits

@@
 \setcounter{equation}{0}
+
+\subsection*{A gamma approximation to generation-interval distributions}
+
+Assuming that the intrinsic generation-interval distribution for each class (asymptomatic and symptomatic) follows a gamma distribution with mean $\bar G_c$ and dispersion $\kappa_c$, the average discount of a new infection can be written as:
+\begin{equation}
+\delta_c = (1 + \kappa_c r \bar G_c)^{-1/\kappa_c},
+\end{equation}
+which shows that the average discount increases with smaller $\bar G_c$ and with larger $\kappa_c$.
+Then, the odds of the realized proportion of asymptomatic transmission can be written as:
+\begin{equation}
+\frac{q}{1-q}=\left(\frac{z}{1-z}\right)\left[\frac{(1 + \kappa_s r \bar G_s)^{1/\kappa_s}}{(1 + \kappa_a r \bar G_a)^{1/\kappa_a}}\right],
+\end{equation}
+where $\bar G_a$ and $\bar G_s$ are the mean generation intervals for asymptomatic and symptomatic cases, and $\kappa_a$ and $\kappa_s$ are the generation-interval dispersions for asymptomatic and symptomatic cases.
+Finally, the basic reproduction number is calculated by
+\begin{equation}
+\mathcal R_0 = \left(z (1 + \kappa_a r \bar G_a)^{-1/\kappa_a} + (1-z) (1 + \kappa_s r \bar G_s)^{-1/\kappa_s}\right)^{-1}.
+\end{equation}
 

### 2020-03-08 short.body.tex
edits
update citation

@@
 
-There is significant ongoing interest in asymptomatic infections in COVID-19 for two major reasons~\citep{fauci_nejm2020}. 
-First, the proportion of infections that are asymptomatic (see~\citep{mizumoto_2020}) is critical to attempts to estimate the likely burden of severe outcomes (including mortality) when the virus spreads through a population.
-Second, understanding the possible role of \emph{transmission} by asymptomatic individuals is crucial to planning surveillance and control efforts.
+There is significant ongoing interest in asymptomatic infections in COVID-19 for two major reasons. 
+First, the proportion of infections that are asymptomatic (see~\citep{mizumoto_2020}) is critical to attempts to estimate the likely burden of severe outcomes (including mortality \citep{fauci_nejm2020}) when the virus spreads through a population.
+Second, understanding the possible role of \emph{transmission} by asymptomatic individuals is crucial to planning surveillance and control efforts \citep{fraser2004factors}.
 
@@
 We assume that epidemic growth rate $r$ and the generation-interval distribution of symptomatic case are known, using parameter values that are consistent with earlier COVID-19 models \citep{park_preprint}: $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=0.5$.
-We infer values of $q$ using Eq.~\req{eq.qratio} and ${\cal{R}}_0$ using the Euler-Lotka equation:
+We infer values of $q$ using Eq.~\req{eq.qratio} and ${\cal{R}}_0$ using the Euler-Lotka equation \citep{lotka1907relation}:
 \begin{equation}

### 2020-03-08 short.body.tex
typos

@@
 
-The intrinsic proporton of asymptomatic transmission $z$ is a useful benchmark, but does not necessarily reflect the realized proportion of asymptomatic transmission, unless both types of infection have the same generation-interval distribution.
+The intrinsic proportion of asymptomatic transmission $z$ is a useful benchmark, but does not necessarily reflect the realized proportion of asymptomatic transmission, unless both types of infection have the same generation-interval distribution.
 The \emph{realized} proportion of asymptomatic transmission, $q$ at time $t$ is given by:
@@
 To estimate the effects of assumptions about asymptomatic transmission on the importance of asymptomatic transmission and estimates of the basic reproduction number ${\cal{R}}_0$, we parameterize the generation interval distributions of asymptomatic and symptomatic cases based on their means, $\bar G_a$ and $\bar G_s$, and dispersions, $\kappa_a$ and $\kappa_s$.
-We assume that generation intervals are gamma distributed, and we set the dispersion to be equal to the squared coefficient of variation (the reciprocal of the gamma shape parameter, see Appendix).
+We assume that generation intervals are gamma distributed, and we set the dispersion to be equal to the squared coefficient of variation (the reciprocal of the gamma shape parameter, see Supplementary Materials).
 We assume that epidemic growth rate $r$ and the generation-interval distribution of symptomatic case are known, using parameter values that are consistent with earlier COVID-19 models \citep{park_preprint}: $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=0.5$.
@@
 \end{equation}
-In the supplementary material, we also use ODEs to give a concrete example of how differences in generation intervals affect both $q$ and estimates of $\mathcal R_0$.
+In Supplementary Materials, we also use an ordinary differential equation model to give a concrete example of how differences in generation intervals affect both $q$ and estimates of $\mathcal R_0$.
 
@@
 When $\bar G_a$ is long compared to $\bar G_s$, then we are effectively assuming a longer mean for the overall generation interval. 
-This assumption leads to a larger estimate of \Ro\ for i fixed value of $r$. (see~\citep{park_2019practical}).
+This assumption leads to a larger estimate of \Ro\ for a fixed value of $r$. (see~\citep{park_2019practical}).
 Conversely, when $\bar G_a < \bar G_s$, generation intervals are shorter, leading to lower estimates of the epidemic strength \Ro.

### 2020-03-08 short.body.tex
add

@@
 \end{equation}
-During the period of exponential growth, we assume $S$ remains nearly constant, and $i(t)$ is proportional to $\exp(r t)$, and simplify: 
+During the period of exponential growth, we assume $S$ remains nearly constant, and $i(t)$ is proportional to $\exp(r t)$, and simplify by recalling that $i_a(t)= p i(t)$, $i_s(t)=(1-p)i(t)$ such that:
 \begin{equation}

### 2020-03-09 figheatmap_R0.tex
push all files

% Created by tikzDevice version 0.12.3 on 2020-03-09 11:51:36
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (397.48,325.21);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (397.48,325.21);
\end{scope}
\begin{scope}
\path[clip] ( 34.16, 30.69) rectangle (338.79,302.56);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 34.16, 30.69) rectangle (338.79,302.56);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 44.28) --
	(338.79, 44.28);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 71.47) --
	(338.79, 71.47);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 98.65) --
	(338.79, 98.65);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,125.84) --
	(338.79,125.84);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,153.03) --
	(338.79,153.03);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,180.22) --
	(338.79,180.22);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,207.40) --
	(338.79,207.40);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,234.59) --
	(338.79,234.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,261.78) --
	(338.79,261.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,288.96) --
	(338.79,288.96);

\path[draw=drawColor,line width= 0.3pt,line join=round] (110.31, 30.69) --
	(110.31,302.56);

\path[draw=drawColor,line width= 0.3pt,line join=round] (262.63, 30.69) --
	(262.63,302.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 30.69) --
	(338.79, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 57.87) --
	(338.79, 57.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 85.06) --
	(338.79, 85.06);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,112.25) --
	(338.79,112.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,139.43) --
	(338.79,139.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,166.62) --
	(338.79,166.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,193.81) --
	(338.79,193.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,221.00) --
	(338.79,221.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,248.18) --
	(338.79,248.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,275.37) --
	(338.79,275.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,302.56) --
	(338.79,302.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 30.69) --
	( 34.16,302.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (186.47, 30.69) --
	(186.47,302.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (338.79, 30.69) --
	(338.79,302.56);
\node[inner sep=0pt,outer sep=0pt,anchor=south west,rotate=  0.00] at ( 35.25,  32.05) {
	\pgfimage[width=303.25pt,height=269.15pt,interpolate=false]{figheatmap_R0_ras1}};
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,192.10) --
	( 35.87,193.81) --
	( 36.35,194.30) --
	( 38.51,196.53) --
	( 38.55,196.57) --
	( 40.75,198.92) --
	( 41.05,199.25) --
	( 42.95,201.34) --
	( 43.50,201.97) --
	( 45.14,203.83) --
	( 45.87,204.68) --
	( 47.34,206.41) --
	( 48.16,207.40) --
	( 49.54,209.08) --
	( 50.38,210.12) --
	( 51.74,211.84) --
	( 52.52,212.84) --
	( 53.93,214.69) --
	( 54.59,215.56) --
	( 56.13,217.64) --
	( 56.60,218.28) --
	( 58.33,220.69) --
	( 58.54,221.00) --
	( 60.43,223.71) --
	( 60.53,223.85) --
	( 62.26,226.43) --
	( 62.72,227.14) --
	( 64.03,229.15) --
	( 64.92,230.54) --
	( 65.76,231.87) --
	( 67.12,234.07) --
	( 67.43,234.59) --
	( 69.06,237.31) --
	( 69.32,237.74) --
	( 70.64,240.03) --
	( 71.51,241.56) --
	( 72.18,242.75) --
	( 73.68,245.46) --
	( 73.71,245.53) --
	( 75.13,248.18) --
	( 75.91,249.66) --
	( 76.55,250.90) --
	( 77.94,253.62) --
	( 78.11,253.96) --
	( 79.28,256.34) --
	( 80.30,258.44) --
	( 80.60,259.06) --
	( 81.88,261.78) --
	( 82.50,263.12) --
	( 83.13,264.50) --
	( 84.35,267.21) --
	( 84.70,268.01) --
	( 85.54,269.93) --
	( 86.70,272.65) --
	( 86.90,273.11) --
	( 87.83,275.37) --
	( 88.95,278.09) --
	( 89.09,278.45) --
	( 90.03,280.81) --
	( 91.09,283.53) --
	( 91.29,284.04) --
	( 92.12,286.25) --
	( 93.14,288.96) --
	( 93.49,289.91) --
	( 94.13,291.68) --
	( 95.10,294.40) --
	( 95.69,296.06) --
	( 96.05,297.12) --
	( 96.98,299.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 90.39) --
	( 34.45, 90.50) --
	( 36.35, 91.21) --
	( 38.55, 92.05) --
	( 40.75, 92.91) --
	( 41.50, 93.22) --
	( 42.95, 93.81) --
	( 45.14, 94.73) --
	( 47.34, 95.69) --
	( 47.90, 95.94) --
	( 49.54, 96.67) --
	( 51.74, 97.69) --
	( 53.75, 98.65) --
	( 53.93, 98.75) --
	( 56.13, 99.84) --
	( 58.33,100.97) --
	( 59.10,101.37) --
	( 60.53,102.14) --
	( 62.72,103.35) --
	( 64.02,104.09) --
	( 64.92,104.61) --
	( 67.12,105.92) --
	( 68.57,106.81) --
	( 69.32,107.28) --
	( 71.51,108.69) --
	( 72.78,109.53) --
	( 73.71,110.15) --
	( 75.91,111.68) --
	( 76.70,112.25) --
	( 78.11,113.27) --
	( 80.30,114.93) --
	( 80.35,114.97) --
	( 82.50,116.66) --
	( 83.76,117.68) --
	( 84.70,118.47) --
	( 86.90,120.36) --
	( 86.95,120.40) --
	( 89.09,122.33) --
	( 89.94,123.12) --
	( 91.29,124.40) --
	( 92.76,125.84) --
	( 93.49,126.57) --
	( 95.42,128.56) --
	( 95.69,128.84) --
	( 97.88,131.23) --
	( 97.92,131.28) --
	(100.08,133.75) --
	(100.29,134.00) --
	(102.28,136.40) --
	(102.53,136.72) --
	(104.47,139.19) --
	(104.66,139.43) --
	(106.67,142.14) --
	(106.69,142.15) --
	(108.61,144.87) --
	(108.87,145.25) --
	(110.44,147.59) --
	(111.07,148.56) --
	(112.18,150.31) --
	(113.26,152.06) --
	(113.85,153.03) --
	(115.44,155.75) --
	(115.46,155.78) --
	(116.97,158.47) --
	(117.66,159.74) --
	(118.43,161.18) --
	(119.83,163.90) --
	(119.86,163.97) --
	(121.17,166.62) --
	(122.05,168.48) --
	(122.45,169.34) --
	(123.69,172.06) --
	(124.25,173.32) --
	(124.88,174.78) --
	(126.03,177.50) --
	(126.45,178.52) --
	(127.13,180.22) --
	(128.20,182.93) --
	(128.65,184.12) --
	(129.22,185.65) --
	(130.21,188.37) --
	(130.84,190.16) --
	(131.17,191.09) --
	(132.09,193.81) --
	(132.99,196.53) --
	(133.04,196.70) --
	(133.85,199.25) --
	(134.69,201.97) --
	(135.24,203.80) --
	(135.50,204.68) --
	(136.28,207.40) --
	(137.04,210.12) --
	(137.44,211.55) --
	(137.78,212.84) --
	(138.50,215.56) --
	(139.20,218.28) --
	(139.63,220.03) --
	(139.87,221.00) --
	(140.53,223.71) --
	(141.17,226.43) --
	(141.79,229.15) --
	(141.83,229.35) --
	(142.39,231.87) --
	(142.98,234.59) --
	(143.55,237.31) --
	(144.03,239.63) --
	(144.11,240.03) --
	(144.65,242.75) --
	(145.18,245.46) --
	(145.69,248.18) --
	(146.20,250.90) --
	(146.23,251.05) --
	(146.69,253.62) --
	(147.17,256.34) --
	(147.63,259.06) --
	(148.09,261.78) --
	(148.42,263.79) --
	(148.54,264.50) --
	(148.97,267.21) --
	(149.40,269.93) --
	(149.81,272.65) --
	(150.22,275.37) --
	(150.62,278.09) --
	(150.62,278.09) --
	(151.01,280.81) --
	(151.39,283.53) --
	(151.76,286.25) --
	(152.13,288.96) --
	(152.48,291.68) --
	(152.82,294.27) --
	(152.84,294.40) --
	(153.18,297.12) --
	(153.51,299.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41, 48.53) --
	(335.21, 48.76) --
	(333.01, 48.99) --
	(330.81, 49.24) --
	(328.62, 49.49) --
	(326.69, 49.72) --
	(326.42, 49.75) --
	(324.22, 50.02) --
	(322.02, 50.29) --
	(319.83, 50.58) --
	(317.63, 50.87) --
	(315.43, 51.18) --
	(313.23, 51.50) --
	(311.04, 51.83) --
	(308.84, 52.17) --
	(307.21, 52.44) --
	(306.64, 52.53) --
	(304.44, 52.90) --
	(302.25, 53.28) --
	(300.05, 53.68) --
	(297.85, 54.09) --
	(295.65, 54.53) --
	(293.46, 54.98) --
	(292.63, 55.15) --
	(291.26, 55.45) --
	(289.06, 55.94) --
	(286.86, 56.45) --
	(284.67, 56.99) --
	(282.47, 57.55) --
	(281.27, 57.87) --
	(280.27, 58.14) --
	(278.07, 58.76) --
	(275.88, 59.41) --
	(273.68, 60.09) --
	(272.15, 60.59) --
	(271.48, 60.81) --
	(269.28, 61.57) --
	(267.09, 62.37) --
	(264.89, 63.22) --
	(264.66, 63.31) --
	(262.69, 64.11) --
	(260.49, 65.06) --
	(258.39, 66.03) --
	(258.30, 66.07) --
	(256.10, 67.14) --
	(253.90, 68.29) --
	(253.06, 68.75) --
	(251.70, 69.51) --
	(249.51, 70.82) --
	(248.47, 71.47) --
	(247.31, 72.22) --
	(245.11, 73.73) --
	(244.48, 74.19) --
	(242.92, 75.36) --
	(240.98, 76.90) --
	(240.72, 77.12) --
	(238.52, 79.03) --
	(237.88, 79.62) --
	(236.32, 81.11) --
	(235.11, 82.34) --
	(234.13, 83.39) --
	(232.63, 85.06) --
	(231.93, 85.88) --
	(230.39, 87.78) --
	(229.73, 88.63) --
	(228.36, 90.50) --
	(227.53, 91.68) --
	(226.51, 93.22) --
	(225.34, 95.07) --
	(224.81, 95.94) --
	(223.26, 98.65) --
	(223.14, 98.87) --
	(221.82,101.37) --
	(220.94,103.16) --
	(220.50,104.09) --
	(219.27,106.81) --
	(218.74,108.03) --
	(218.12,109.53) --
	(217.06,112.25) --
	(216.55,113.62) --
	(216.06,114.97) --
	(215.13,117.68) --
	(214.35,120.09) --
	(214.25,120.40) --
	(213.42,123.12) --
	(212.65,125.84) --
	(212.15,127.67) --
	(211.91,128.56) --
	(211.22,131.28) --
	(210.56,134.00) --
	(209.95,136.67) --
	(209.94,136.72) --
	(209.35,139.43) --
	(208.79,142.15) --
	(208.25,144.87) --
	(207.76,147.53) --
	(207.75,147.59) --
	(207.26,150.31) --
	(206.79,153.03) --
	(206.35,155.75) --
	(205.92,158.47) --
	(205.56,160.90) --
	(205.52,161.18) --
	(205.12,163.90) --
	(204.75,166.62) --
	(204.39,169.34) --
	(204.04,172.06) --
	(203.71,174.78) --
	(203.39,177.50) --
	(203.36,177.75) --
	(203.08,180.22) --
	(202.78,182.93) --
	(202.49,185.65) --
	(202.22,188.37) --
	(201.95,191.09) --
	(201.69,193.81) --
	(201.44,196.53) --
	(201.20,199.25) --
	(201.16,199.64) --
	(200.96,201.97) --
	(200.73,204.68) --
	(200.51,207.40) --
	(200.30,210.12) --
	(200.09,212.84) --
	(199.89,215.56) --
	(199.70,218.28) --
	(199.51,221.00) --
	(199.32,223.71) --
	(199.14,226.43) --
	(198.97,229.15) --
	(198.97,229.24) --
	(198.80,231.87) --
	(198.64,234.59) --
	(198.47,237.31) --
	(198.32,240.03) --
	(198.17,242.75) --
	(198.02,245.46) --
	(197.87,248.18) --
	(197.73,250.90) --
	(197.59,253.62) --
	(197.46,256.34) --
	(197.33,259.06) --
	(197.20,261.78) --
	(197.08,264.50) --
	(196.95,267.21) --
	(196.83,269.93) --
	(196.77,271.48) --
	(196.72,272.65) --
	(196.60,275.37) --
	(196.49,278.09) --
	(196.38,280.81) --
	(196.27,283.53) --
	(196.17,286.25) --
	(196.07,288.96) --
	(195.97,291.68) --
	(195.87,294.40) --
	(195.77,297.12) --
	(195.68,299.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41,112.42) --
	(335.21,113.46) --
	(333.01,114.54) --
	(332.16,114.97) --
	(330.81,115.65) --
	(328.62,116.79) --
	(326.96,117.68) --
	(326.42,117.98) --
	(324.22,119.20) --
	(322.14,120.40) --
	(322.02,120.47) --
	(319.83,121.78) --
	(317.66,123.12) --
	(317.63,123.14) --
	(315.43,124.54) --
	(313.48,125.84) --
	(313.23,126.00) --
	(311.04,127.51) --
	(309.56,128.56) --
	(308.84,129.08) --
	(306.64,130.71) --
	(305.89,131.28) --
	(304.44,132.40) --
	(302.44,134.00) --
	(302.25,134.16) --
	(300.05,135.98) --
	(299.19,136.72) --
	(297.85,137.88) --
	(296.13,139.43) --
	(295.65,139.87) --
	(293.46,141.93) --
	(293.23,142.15) --
	(291.26,144.09) --
	(290.48,144.87) --
	(289.06,146.34) --
	(287.88,147.59) --
	(286.86,148.69) --
	(285.41,150.31) --
	(284.67,151.15) --
	(283.06,153.03) --
	(282.47,153.73) --
	(280.82,155.75) --
	(280.27,156.43) --
	(278.68,158.47) --
	(278.07,159.26) --
	(276.64,161.18) --
	(275.88,162.23) --
	(274.69,163.90) --
	(273.68,165.36) --
	(272.83,166.62) --
	(271.48,168.66) --
	(271.04,169.34) --
	(269.33,172.06) --
	(269.28,172.13) --
	(267.68,174.78) --
	(267.09,175.79) --
	(266.10,177.50) --
	(264.89,179.67) --
	(264.59,180.22) --
	(263.13,182.93) --
	(262.69,183.77) --
	(261.72,185.65) --
	(260.49,188.11) --
	(260.37,188.37) --
	(259.06,191.09) --
	(258.30,192.73) --
	(257.80,193.81) --
	(256.59,196.53) --
	(256.10,197.64) --
	(255.41,199.25) --
	(254.28,201.97) --
	(253.90,202.88) --
	(253.18,204.68) --
	(252.12,207.40) --
	(251.70,208.48) --
	(251.09,210.12) --
	(250.09,212.84) --
	(249.51,214.47) --
	(249.12,215.56) --
	(248.18,218.28) --
	(247.31,220.90) --
	(247.28,221.00) --
	(246.39,223.71) --
	(245.54,226.43) --
	(245.11,227.81) --
	(244.70,229.15) --
	(243.89,231.87) --
	(243.11,234.59) --
	(242.92,235.26) --
	(242.34,237.31) --
	(241.59,240.03) --
	(240.87,242.75) --
	(240.72,243.33) --
	(240.16,245.46) --
	(239.47,248.18) --
	(238.81,250.90) --
	(238.52,252.08) --
	(238.15,253.62) --
	(237.51,256.34) --
	(236.89,259.06) --
	(236.32,261.61) --
	(236.29,261.78) --
	(235.69,264.50) --
	(235.11,267.21) --
	(234.55,269.93) --
	(234.13,272.03) --
	(234.00,272.65) --
	(233.46,275.37) --
	(232.93,278.09) --
	(232.42,280.81) --
	(231.93,283.46) --
	(231.92,283.53) --
	(231.42,286.25) --
	(230.94,288.96) --
	(230.46,291.68) --
	(230.00,294.40) --
	(229.73,296.05) --
	(229.55,297.12) --
	(229.11,299.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41,163.53) --
	(336.92,163.90) --
	(335.21,165.22) --
	(333.45,166.62) --
	(333.01,166.97) --
	(330.81,168.77) --
	(330.14,169.34) --
	(328.62,170.64) --
	(326.99,172.06) --
	(326.42,172.57) --
	(324.22,174.56) --
	(323.98,174.78) --
	(322.02,176.61) --
	(321.11,177.50) --
	(319.83,178.75) --
	(318.36,180.22) --
	(317.63,180.95) --
	(315.72,182.93) --
	(315.43,183.24) --
	(313.23,185.61) --
	(313.19,185.65) --
	(311.04,188.06) --
	(310.77,188.37) --
	(308.84,190.61) --
	(308.43,191.09) --
	(306.64,193.25) --
	(306.19,193.81) --
	(304.44,196.00) --
	(304.03,196.53) --
	(302.25,198.86) --
	(301.95,199.25) --
	(300.05,201.83) --
	(299.95,201.97) --
	(298.02,204.68) --
	(297.85,204.92) --
	(296.15,207.40) --
	(295.65,208.14) --
	(294.35,210.12) --
	(293.46,211.50) --
	(292.60,212.84) --
	(291.26,215.00) --
	(290.92,215.56) --
	(289.29,218.28) --
	(289.06,218.66) --
	(287.71,221.00) --
	(286.86,222.48) --
	(286.17,223.71) --
	(284.69,226.43) --
	(284.67,226.48) --
	(283.25,229.15) --
	(282.47,230.67) --
	(281.85,231.87) --
	(280.50,234.59) --
	(280.27,235.05) --
	(279.18,237.31) --
	(278.07,239.66) --
	(277.90,240.03) --
	(276.66,242.75) --
	(275.88,244.49) --
	(275.45,245.46) --
	(274.27,248.18) --
	(273.68,249.58) --
	(273.12,250.90) --
	(272.01,253.62) --
	(271.48,254.93) --
	(270.92,256.34) --
	(269.86,259.06) --
	(269.28,260.57) --
	(268.83,261.78) --
	(267.82,264.50) --
	(267.09,266.53) --
	(266.84,267.21) --
	(265.88,269.93) --
	(264.95,272.65) --
	(264.89,272.82) --
	(264.03,275.37) --
	(263.14,278.09) --
	(262.69,279.49) --
	(262.27,280.81) --
	(261.42,283.53) --
	(260.59,286.25) --
	(260.49,286.55) --
	(259.77,288.96) --
	(258.98,291.68) --
	(258.30,294.06) --
	(258.20,294.40) --
	(257.44,297.12) --
	(256.69,299.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41,205.34) --
	(335.37,207.40) --
	(335.21,207.57) --
	(333.01,209.87) --
	(332.78,210.12) --
	(330.81,212.24) --
	(330.27,212.84) --
	(328.62,214.69) --
	(327.86,215.56) --
	(326.42,217.22) --
	(325.53,218.28) --
	(324.22,219.84) --
	(323.28,221.00) --
	(322.02,222.55) --
	(321.10,223.71) --
	(319.83,225.35) --
	(319.00,226.43) --
	(317.63,228.25) --
	(316.96,229.15) --
	(315.43,231.26) --
	(314.99,231.87) --
	(313.23,234.37) --
	(313.08,234.59) --
	(311.23,237.31) --
	(311.04,237.60) --
	(309.44,240.03) --
	(308.84,240.95) --
	(307.69,242.75) --
	(306.64,244.43) --
	(306.00,245.46) --
	(304.44,248.04) --
	(304.36,248.18) --
	(302.76,250.90) --
	(302.25,251.79) --
	(301.21,253.62) --
	(300.05,255.70) --
	(299.70,256.34) --
	(298.23,259.06) --
	(297.85,259.76) --
	(296.79,261.78) --
	(295.65,264.00) --
	(295.40,264.50) --
	(294.04,267.21) --
	(293.46,268.41) --
	(292.72,269.93) --
	(291.43,272.65) --
	(291.26,273.02) --
	(290.17,275.37) --
	(289.06,277.83) --
	(288.95,278.09) --
	(287.75,280.81) --
	(286.86,282.85) --
	(286.58,283.53) --
	(285.43,286.25) --
	(284.67,288.11) --
	(284.32,288.96) --
	(283.23,291.68) --
	(282.47,293.62) --
	(282.16,294.40) --
	(281.12,297.12) --
	(280.27,299.39) --
	(280.10,299.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41,240.19) --
	(335.30,242.75) --
	(335.21,242.86) --
	(333.13,245.46) --
	(333.01,245.62) --
	(331.03,248.18) --
	(330.81,248.47) --
	(328.99,250.90) --
	(328.62,251.41) --
	(327.01,253.62) --
	(326.42,254.44) --
	(325.08,256.34) --
	(324.22,257.58) --
	(323.21,259.06) --
	(322.02,260.83) --
	(321.40,261.78) --
	(319.83,264.19) --
	(319.63,264.50) --
	(317.91,267.21) --
	(317.63,267.67) --
	(316.24,269.93) --
	(315.43,271.27) --
	(314.61,272.65) --
	(313.23,275.01) --
	(313.03,275.37) --
	(311.48,278.09) --
	(311.04,278.88) --
	(309.97,280.81) --
	(308.84,282.90) --
	(308.50,283.53) --
	(307.07,286.25) --
	(306.64,287.07) --
	(305.67,288.96) --
	(304.44,291.40) --
	(304.31,291.68) --
	(302.97,294.40) --
	(302.25,295.91) --
	(301.67,297.12) --
	(300.40,299.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41,269.68) --
	(337.22,269.93) --
	(335.26,272.65) --
	(335.21,272.73) --
	(333.36,275.37) --
	(333.01,275.87) --
	(331.50,278.09) --
	(330.81,279.11) --
	(329.69,280.81) --
	(328.62,282.47) --
	(327.94,283.53) --
	(326.42,285.94) --
	(326.23,286.25) --
	(324.56,288.96) --
	(324.22,289.52) --
	(322.93,291.68) --
	(322.02,293.22) --
	(321.34,294.40) --
	(319.83,297.06) --
	(319.79,297.12) --
	(318.28,299.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41,294.95) --
	(335.98,297.12) --
	(335.21,298.32) --
	(334.24,299.84);

\path[draw=drawColor,line width= 0.9pt,dash pattern=on 4pt off 4pt ,line join=round] (186.47, 30.69) -- (186.47,302.56);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (262.63, 35.04) {underestimated};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (110.31, 35.04) {overestimated};
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.16, 30.69) rectangle (338.79,302.56);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21, 27.66) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21, 54.84) {0.1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21, 82.03) {0.2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,109.22) {0.3};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,136.40) {0.4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,163.59) {0.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,190.78) {0.6};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,217.97) {0.7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,245.15) {0.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,272.34) {0.9};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,299.53) {1.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41, 30.69) --
	( 34.16, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41, 57.87) --
	( 34.16, 57.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41, 85.06) --
	( 34.16, 85.06);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,112.25) --
	( 34.16,112.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,139.43) --
	( 34.16,139.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,166.62) --
	( 34.16,166.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,193.81) --
	( 34.16,193.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,221.00) --
	( 34.16,221.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,248.18) --
	( 34.16,248.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,275.37) --
	( 34.16,275.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,302.56) --
	( 34.16,302.56);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 27.94) --
	( 34.16, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (186.47, 27.94) --
	(186.47, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (338.79, 27.94) --
	(338.79, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 34.16, 19.68) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (186.47, 19.68) {1.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (338.79, 19.68) {2.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (186.47,  7.64) {Relative mean asymptomatic generation interval, $G_a/G_s$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,166.62) {Intrinsic proportion of asymptomatic transmission, $z$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (349.79, 25.48) rectangle (391.98,307.77);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\node[inner sep=0pt,outer sep=0pt,anchor=south west,rotate=  0.00] at (355.29,  30.98) {
	\pgfimage[width= 14.45pt,height=256.07pt,interpolate=true]{figheatmap_R0_ras2}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (375.24, 34.35) {1.5};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (375.24, 88.41) {2.5};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (375.24,142.47) {3.5};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (375.24,196.53) {4.5};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (375.24,250.59) {5.5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (355.29,293.62) {$\mathcal{R}_0$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.2pt,line join=round] (355.29, 37.38) -- (358.18, 37.38);

\path[draw=drawColor,line width= 0.2pt,line join=round] (355.29, 91.44) -- (358.18, 91.44);

\path[draw=drawColor,line width= 0.2pt,line join=round] (355.29,145.50) -- (358.18,145.50);

\path[draw=drawColor,line width= 0.2pt,line join=round] (355.29,199.56) -- (358.18,199.56);

\path[draw=drawColor,line width= 0.2pt,line join=round] (355.29,253.62) -- (358.18,253.62);

\path[draw=drawColor,line width= 0.2pt,line join=round] (366.85, 37.38) -- (369.74, 37.38);

\path[draw=drawColor,line width= 0.2pt,line join=round] (366.85, 91.44) -- (369.74, 91.44);

\path[draw=drawColor,line width= 0.2pt,line join=round] (366.85,145.50) -- (369.74,145.50);

\path[draw=drawColor,line width= 0.2pt,line join=round] (366.85,199.56) -- (369.74,199.56);

\path[draw=drawColor,line width= 0.2pt,line join=round] (366.85,253.62) -- (369.74,253.62);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 34.16,310.62) {B. Basic reproduction number};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-03-09 figheatmap_R0_03.tex
push all files

% Created by tikzDevice version 0.12.3 on 2020-03-09 11:51:45
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (397.48,325.21);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (397.48,325.21);
\end{scope}
\begin{scope}
\path[clip] ( 34.16, 30.69) rectangle (338.79,302.56);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 34.16, 30.69) rectangle (338.79,302.56);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 44.28) --
	(338.79, 44.28);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 71.47) --
	(338.79, 71.47);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 98.65) --
	(338.79, 98.65);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,125.84) --
	(338.79,125.84);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,153.03) --
	(338.79,153.03);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,180.22) --
	(338.79,180.22);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,207.40) --
	(338.79,207.40);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,234.59) --
	(338.79,234.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,261.78) --
	(338.79,261.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,288.96) --
	(338.79,288.96);

\path[draw=drawColor,line width= 0.3pt,line join=round] (110.31, 30.69) --
	(110.31,302.56);

\path[draw=drawColor,line width= 0.3pt,line join=round] (262.63, 30.69) --
	(262.63,302.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 30.69) --
	(338.79, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 57.87) --
	(338.79, 57.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 85.06) --
	(338.79, 85.06);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,112.25) --
	(338.79,112.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,139.43) --
	(338.79,139.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,166.62) --
	(338.79,166.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,193.81) --
	(338.79,193.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,221.00) --
	(338.79,221.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,248.18) --
	(338.79,248.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,275.37) --
	(338.79,275.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,302.56) --
	(338.79,302.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 30.69) --
	( 34.16,302.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (186.47, 30.69) --
	(186.47,302.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (338.79, 30.69) --
	(338.79,302.56);
\node[inner sep=0pt,outer sep=0pt,anchor=south west,rotate=  0.00] at ( 35.25,  32.72) {
	\pgfimage[width=303.25pt,height=267.79pt,interpolate=false]{figheatmap_R0_03_ras1}};
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,189.02) --
	( 34.89,189.73) --
	( 36.28,191.09) --
	( 36.35,191.16) --
	( 37.64,192.45) --
	( 38.55,193.38) --
	( 38.97,193.81) --
	( 40.28,195.17) --
	( 40.75,195.66) --
	( 41.57,196.53) --
	( 42.83,197.89) --
	( 42.95,198.01) --
	( 44.07,199.25) --
	( 45.14,200.44) --
	( 45.29,200.61) --
	( 46.48,201.97) --
	( 47.34,202.95) --
	( 47.66,203.32) --
	( 48.81,204.68) --
	( 49.54,205.55) --
	( 49.95,206.04) --
	( 51.06,207.40) --
	( 51.74,208.23) --
	( 52.16,208.76) --
	( 53.24,210.12) --
	( 53.93,211.01) --
	( 54.30,211.48) --
	( 55.34,212.84) --
	( 56.13,213.88) --
	( 56.37,214.20) --
	( 57.37,215.56) --
	( 58.33,216.86) --
	( 58.37,216.92) --
	( 59.34,218.28) --
	( 60.31,219.64) --
	( 60.53,219.95) --
	( 61.25,221.00) --
	( 62.19,222.36) --
	( 62.72,223.14) --
	( 63.11,223.71) --
	( 64.01,225.07) --
	( 64.90,226.43) --
	( 64.92,226.46) --
	( 65.78,227.79) --
	( 66.64,229.15) --
	( 67.12,229.91) --
	( 67.49,230.51) --
	( 68.33,231.87) --
	( 69.16,233.23) --
	( 69.32,233.48) --
	( 69.98,234.59) --
	( 70.78,235.95) --
	( 71.51,237.20) --
	( 71.57,237.31) --
	( 72.35,238.67) --
	( 73.12,240.03) --
	( 73.71,241.07) --
	( 73.88,241.39) --
	( 74.63,242.75) --
	( 75.37,244.11) --
	( 75.91,245.10) --
	( 76.10,245.46) --
	( 76.82,246.82) --
	( 77.53,248.18) --
	( 78.11,249.29) --
	( 78.23,249.54) --
	( 78.92,250.90) --
	( 79.60,252.26) --
	( 80.28,253.62) --
	( 80.30,253.67) --
	( 80.94,254.98) --
	( 81.60,256.34) --
	( 82.25,257.70) --
	( 82.50,258.23) --
	( 82.89,259.06) --
	( 83.52,260.42) --
	( 84.14,261.78) --
	( 84.70,263.00) --
	( 84.76,263.14) --
	( 85.37,264.50) --
	( 85.97,265.86) --
	( 86.56,267.21) --
	( 86.90,267.98) --
	( 87.15,268.57) --
	( 87.73,269.93) --
	( 88.30,271.29) --
	( 88.87,272.65) --
	( 89.09,273.19) --
	( 89.43,274.01) --
	( 89.98,275.37) --
	( 90.53,276.73) --
	( 91.07,278.09) --
	( 91.29,278.65) --
	( 91.60,279.45) --
	( 92.13,280.81) --
	( 92.65,282.17) --
	( 93.17,283.53) --
	( 93.49,284.37) --
	( 93.68,284.89) --
	( 94.18,286.25) --
	( 94.68,287.60) --
	( 95.18,288.96) --
	( 95.67,290.32) --
	( 95.69,290.38) --
	( 96.15,291.68) --
	( 96.62,293.04) --
	( 97.10,294.40) --
	( 97.57,295.76) --
	( 97.88,296.69) --
	( 98.03,297.12) --
	( 98.48,298.48) --
	( 98.94,299.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 63.05) --
	( 35.49, 63.31) --
	( 36.35, 63.48) --
	( 38.55, 63.94) --
	( 40.75, 64.40) --
	( 41.98, 64.67) --
	( 42.95, 64.88) --
	( 45.14, 65.38) --
	( 47.34, 65.89) --
	( 47.91, 66.03) --
	( 49.54, 66.42) --
	( 51.74, 66.97) --
	( 53.35, 67.39) --
	( 53.93, 67.54) --
	( 56.13, 68.13) --
	( 58.33, 68.74) --
	( 58.37, 68.75) --
	( 60.53, 69.37) --
	( 62.72, 70.02) --
	( 63.01, 70.11) --
	( 64.92, 70.70) --
	( 67.12, 71.40) --
	( 67.32, 71.47) --
	( 69.32, 72.13) --
	( 71.32, 72.83) --
	( 71.51, 72.89) --
	( 73.71, 73.68) --
	( 75.06, 74.19) --
	( 75.91, 74.51) --
	( 78.11, 75.36) --
	( 78.55, 75.54) --
	( 80.30, 76.26) --
	( 81.83, 76.90) --
	( 82.50, 77.19) --
	( 84.70, 78.17) --
	( 84.91, 78.26) --
	( 86.90, 79.18) --
	( 87.81, 79.62) --
	( 89.09, 80.25) --
	( 90.55, 80.98) --
	( 91.29, 81.36) --
	( 93.13, 82.34) --
	( 93.49, 82.53) --
	( 95.58, 83.70) --
	( 95.69, 83.76) --
	( 97.88, 85.05) --
	( 97.90, 85.06) --
	(100.08, 86.41) --
	(100.10, 86.42) --
	(102.19, 87.78) --
	(102.28, 87.83) --
	(104.19, 89.14) --
	(104.47, 89.34) --
	(106.08, 90.50) --
	(106.67, 90.93) --
	(107.90, 91.86) --
	(108.87, 92.61) --
	(109.63, 93.22) --
	(111.07, 94.40) --
	(111.28, 94.58) --
	(112.87, 95.94) --
	(113.26, 96.29) --
	(114.38, 97.29) --
	(115.46, 98.30) --
	(115.84, 98.65) --
	(117.24,100.01) --
	(117.66,100.43) --
	(118.58,101.37) --
	(119.86,102.72) --
	(119.87,102.73) --
	(121.11,104.09) --
	(122.05,105.16) --
	(122.31,105.45) --
	(123.46,106.81) --
	(124.25,107.77) --
	(124.58,108.17) --
	(125.65,109.53) --
	(126.45,110.58) --
	(126.68,110.89) --
	(127.68,112.25) --
	(128.65,113.60) --
	(128.65,113.61) --
	(129.59,114.97) --
	(130.50,116.33) --
	(130.84,116.86) --
	(131.37,117.68) --
	(132.22,119.04) --
	(133.04,120.39) --
	(133.05,120.40) --
	(133.85,121.76) --
	(134.62,123.12) --
	(135.24,124.23) --
	(135.38,124.48) --
	(136.11,125.84) --
	(136.82,127.20) --
	(137.44,128.42) --
	(137.51,128.56) --
	(138.18,129.92) --
	(138.83,131.28) --
	(139.47,132.64) --
	(139.63,133.00) --
	(140.09,134.00) --
	(140.69,135.36) --
	(141.28,136.72) --
	(141.83,138.03) --
	(141.85,138.08) --
	(142.41,139.43) --
	(142.95,140.79) --
	(143.48,142.15) --
	(144.00,143.51) --
	(144.03,143.59) --
	(144.50,144.87) --
	(145.00,146.23) --
	(145.48,147.59) --
	(145.95,148.95) --
	(146.23,149.76) --
	(146.41,150.31) --
	(146.86,151.67) --
	(147.30,153.03) --
	(147.73,154.39) --
	(148.15,155.75) --
	(148.42,156.65) --
	(148.56,157.11) --
	(148.96,158.47) --
	(149.36,159.83) --
	(149.74,161.18) --
	(150.12,162.54) --
	(150.49,163.90) --
	(150.62,164.38) --
	(150.86,165.26) --
	(151.21,166.62) --
	(151.56,167.98) --
	(151.90,169.34) --
	(152.24,170.70) --
	(152.57,172.06) --
	(152.82,173.12) --
	(152.89,173.42) --
	(153.20,174.78) --
	(153.51,176.14) --
	(153.82,177.50) --
	(154.12,178.86) --
	(154.41,180.22) --
	(154.70,181.57) --
	(154.98,182.93) --
	(155.02,183.09) --
	(155.26,184.29) --
	(155.53,185.65) --
	(155.80,187.01) --
	(156.06,188.37) --
	(156.32,189.73) --
	(156.58,191.09) --
	(156.83,192.45) --
	(157.08,193.81) --
	(157.21,194.57) --
	(157.32,195.17) --
	(157.56,196.53) --
	(157.79,197.89) --
	(158.02,199.25) --
	(158.25,200.61) --
	(158.47,201.97) --
	(158.69,203.32) --
	(158.91,204.68) --
	(159.12,206.04) --
	(159.33,207.40) --
	(159.41,207.91) --
	(159.54,208.76) --
	(159.74,210.12) --
	(159.94,211.48) --
	(160.14,212.84) --
	(160.33,214.20) --
	(160.53,215.56) --
	(160.71,216.92) --
	(160.90,218.28) --
	(161.09,219.64) --
	(161.27,221.00) --
	(161.45,222.36) --
	(161.61,223.61) --
	(161.62,223.71) --
	(161.79,225.07) --
	(161.96,226.43) --
	(162.13,227.79) --
	(162.30,229.15) --
	(162.46,230.51) --
	(162.62,231.87) --
	(162.78,233.23) --
	(162.94,234.59) --
	(163.10,235.95) --
	(163.25,237.31) --
	(163.40,238.67) --
	(163.55,240.03) --
	(163.70,241.39) --
	(163.81,242.37) --
	(163.85,242.75) --
	(163.99,244.11) --
	(164.13,245.46) --
	(164.27,246.82) --
	(164.41,248.18) --
	(164.54,249.54) --
	(164.68,250.90) --
	(164.81,252.26) --
	(164.94,253.62) --
	(165.07,254.98) --
	(165.20,256.34) --
	(165.33,257.70) --
	(165.46,259.06) --
	(165.58,260.42) --
	(165.70,261.78) --
	(165.83,263.14) --
	(165.95,264.50) --
	(166.00,265.15) --
	(166.06,265.86) --
	(166.18,267.21) --
	(166.30,268.57) --
	(166.41,269.93) --
	(166.52,271.29) --
	(166.63,272.65) --
	(166.74,274.01) --
	(166.85,275.37) --
	(166.96,276.73) --
	(167.07,278.09) --
	(167.17,279.45) --
	(167.28,280.81) --
	(167.38,282.17) --
	(167.48,283.53) --
	(167.59,284.89) --
	(167.69,286.25) --
	(167.79,287.60) --
	(167.88,288.96) --
	(167.98,290.32) --
	(168.08,291.68) --
	(168.17,293.04) --
	(168.20,293.43) --
	(168.27,294.40) --
	(168.36,295.76) --
	(168.45,297.12) --
	(168.54,298.48) --
	(168.63,299.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41, 87.12) --
	(335.33, 87.78) --
	(335.21, 87.82) --
	(333.01, 88.53) --
	(331.22, 89.14) --
	(330.81, 89.28) --
	(328.62, 90.04) --
	(327.34, 90.50) --
	(326.42, 90.83) --
	(324.22, 91.65) --
	(323.68, 91.86) --
	(322.02, 92.50) --
	(320.22, 93.22) --
	(319.83, 93.38) --
	(317.63, 94.28) --
	(316.94, 94.58) --
	(315.43, 95.23) --
	(313.83, 95.94) --
	(313.23, 96.20) --
	(311.04, 97.22) --
	(310.87, 97.29) --
	(308.84, 98.27) --
	(308.05, 98.65) --
	(306.64, 99.36) --
	(305.37,100.01) --
	(304.44,100.49) --
	(302.80,101.37) --
	(302.25,101.67) --
	(300.35,102.73) --
	(300.05,102.90) --
	(298.01,104.09) --
	(297.85,104.18) --
	(295.76,105.45) --
	(295.65,105.52) --
	(293.61,106.81) --
	(293.46,106.91) --
	(291.54,108.17) --
	(291.26,108.36) --
	(289.55,109.53) --
	(289.06,109.87) --
	(287.64,110.89) --
	(286.86,111.46) --
	(285.81,112.25) --
	(284.67,113.12) --
	(284.04,113.61) --
	(282.47,114.85) --
	(282.33,114.97) --
	(280.68,116.33) --
	(280.27,116.67) --
	(279.10,117.68) --
	(278.07,118.58) --
	(277.56,119.04) --
	(276.08,120.40) --
	(275.88,120.59) --
	(274.64,121.76) --
	(273.68,122.70) --
	(273.26,123.12) --
	(271.91,124.48) --
	(271.48,124.93) --
	(270.61,125.84) --
	(269.35,127.20) --
	(269.28,127.27) --
	(268.13,128.56) --
	(267.09,129.75) --
	(266.94,129.92) --
	(265.79,131.28) --
	(264.89,132.37) --
	(264.67,132.64) --
	(263.58,134.00) --
	(262.69,135.14) --
	(262.52,135.36) --
	(261.50,136.72) --
	(260.50,138.08) --
	(260.49,138.08) --
	(259.52,139.43) --
	(258.58,140.79) --
	(258.30,141.20) --
	(257.65,142.15) --
	(256.75,143.51) --
	(256.10,144.53) --
	(255.88,144.87) --
	(255.02,146.23) --
	(254.19,147.59) --
	(253.90,148.07) --
	(253.38,148.95) --
	(252.58,150.31) --
	(251.81,151.67) --
	(251.70,151.86) --
	(251.05,153.03) --
	(250.31,154.39) --
	(249.59,155.75) --
	(249.51,155.91) --
	(248.89,157.11) --
	(248.20,158.47) --
	(247.52,159.83) --
	(247.31,160.26) --
	(246.86,161.18) --
	(246.22,162.54) --
	(245.59,163.90) --
	(245.11,164.94) --
	(244.97,165.26) --
	(244.36,166.62) --
	(243.77,167.98) --
	(243.19,169.34) --
	(242.92,169.99) --
	(242.62,170.70) --
	(242.06,172.06) --
	(241.52,173.42) --
	(240.98,174.78) --
	(240.72,175.46) --
	(240.46,176.14) --
	(239.94,177.50) --
	(239.43,178.86) --
	(238.94,180.22) --
	(238.52,181.39) --
	(238.45,181.57) --
	(237.97,182.93) --
	(237.51,184.29) --
	(237.05,185.65) --
	(236.59,187.01) --
	(236.32,187.84) --
	(236.15,188.37) --
	(235.71,189.73) --
	(235.29,191.09) --
	(234.86,192.45) --
	(234.45,193.81) --
	(234.13,194.90) --
	(234.05,195.17) --
	(233.64,196.53) --
	(233.25,197.89) --
	(232.86,199.25) --
	(232.49,200.61) --
	(232.11,201.97) --
	(231.93,202.65) --
	(231.74,203.32) --
	(231.38,204.68) --
	(231.02,206.04) --
	(230.67,207.40) --
	(230.33,208.76) --
	(229.99,210.12) --
	(229.73,211.18) --
	(229.66,211.48) --
	(229.33,212.84) --
	(229.00,214.20) --
	(228.68,215.56) --
	(228.37,216.92) --
	(228.06,218.28) --
	(227.75,219.64) --
	(227.53,220.64) --
	(227.45,221.00) --
	(227.16,222.36) --
	(226.86,223.71) --
	(226.58,225.07) --
	(226.29,226.43) --
	(226.01,227.79) --
	(225.74,229.15) --
	(225.47,230.51) --
	(225.34,231.17) --
	(225.20,231.87) --
	(224.93,233.23) --
	(224.67,234.59) --
	(224.41,235.95) --
	(224.16,237.31) --
	(223.91,238.67) --
	(223.66,240.03) --
	(223.42,241.39) --
	(223.18,242.75) --
	(223.14,242.97) --
	(222.94,244.11) --
	(222.70,245.46) --
	(222.47,246.82) --
	(222.24,248.18) --
	(222.02,249.54) --
	(221.79,250.90) --
	(221.57,252.26) --
	(221.36,253.62) --
	(221.14,254.98) --
	(220.94,256.29) --
	(220.93,256.34) --
	(220.72,257.70) --
	(220.51,259.06) --
	(220.31,260.42) --
	(220.11,261.78) --
	(219.91,263.14) --
	(219.71,264.50) --
	(219.51,265.86) --
	(219.32,267.21) --
	(219.13,268.57) --
	(218.94,269.93) --
	(218.76,271.29) --
	(218.74,271.42) --
	(218.58,272.65) --
	(218.39,274.01) --
	(218.21,275.37) --
	(218.03,276.73) --
	(217.86,278.09) --
	(217.68,279.45) --
	(217.51,280.81) --
	(217.34,282.17) --
	(217.17,283.53) --
	(217.01,284.89) --
	(216.84,286.25) --
	(216.68,287.60) --
	(216.55,288.77) --
	(216.52,288.96) --
	(216.36,290.32) --
	(216.20,291.68) --
	(216.05,293.04) --
	(215.89,294.40) --
	(215.74,295.76) --
	(215.59,297.12) --
	(215.44,298.48) --
	(215.29,299.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41,152.71) --
	(336.93,153.03) --
	(335.21,154.21) --
	(334.95,154.39) --
	(333.03,155.75) --
	(333.01,155.76) --
	(331.16,157.11) --
	(330.81,157.36) --
	(329.34,158.47) --
	(328.62,159.01) --
	(327.57,159.83) --
	(326.42,160.73) --
	(325.84,161.18) --
	(324.22,162.50) --
	(324.16,162.54) --
	(322.53,163.90) --
	(322.02,164.33) --
	(320.93,165.26) --
	(319.83,166.22) --
	(319.38,166.62) --
	(317.86,167.98) --
	(317.63,168.19) --
	(316.38,169.34) --
	(315.43,170.22) --
	(314.93,170.70) --
	(313.52,172.06) --
	(313.23,172.34) --
	(312.14,173.42) --
	(311.04,174.53) --
	(310.79,174.78) --
	(309.47,176.14) --
	(308.84,176.80) --
	(308.18,177.50) --
	(306.92,178.86) --
	(306.64,179.16) --
	(305.69,180.22) --
	(304.48,181.57) --
	(304.44,181.61) --
	(303.30,182.93) --
	(302.25,184.17) --
	(302.14,184.29) --
	(301.01,185.65) --
	(300.05,186.82) --
	(299.90,187.01) --
	(298.81,188.37) --
	(297.85,189.59) --
	(297.74,189.73) --
	(296.69,191.09) --
	(295.67,192.45) --
	(295.65,192.47) --
	(294.66,193.81) --
	(293.68,195.17) --
	(293.46,195.48) --
	(292.71,196.53) --
	(291.76,197.89) --
	(291.26,198.61) --
	(290.83,199.25) --
	(289.91,200.61) --
	(289.06,201.89) --
	(289.01,201.97) --
	(288.13,203.32) --
	(287.26,204.68) --
	(286.86,205.32) --
	(286.41,206.04) --
	(285.57,207.40) --
	(284.75,208.76) --
	(284.67,208.90) --
	(283.94,210.12) --
	(283.15,211.48) --
	(282.47,212.66) --
	(282.36,212.84) --
	(281.59,214.20) --
	(280.84,215.56) --
	(280.27,216.59) --
	(280.10,216.92) --
	(279.36,218.28) --
	(278.64,219.64) --
	(278.07,220.73) --
	(277.93,221.00) --
	(277.23,222.36) --
	(276.55,223.71) --
	(275.88,225.07) --
	(275.87,225.07) --
	(275.21,226.43) --
	(274.55,227.79) --
	(273.90,229.15) --
	(273.68,229.63) --
	(273.27,230.51) --
	(272.64,231.87) --
	(272.02,233.23) --
	(271.48,234.44) --
	(271.42,234.59) --
	(270.81,235.95) --
	(270.22,237.31) --
	(269.64,238.67) --
	(269.28,239.51) --
	(269.07,240.03) --
	(268.50,241.39) --
	(267.94,242.75) --
	(267.39,244.11) --
	(267.09,244.86) --
	(266.85,245.46) --
	(266.31,246.82) --
	(265.78,248.18) --
	(265.26,249.54) --
	(264.89,250.52) --
	(264.75,250.90) --
	(264.24,252.26) --
	(263.73,253.62) --
	(263.24,254.98) --
	(262.76,256.34) --
	(262.69,256.52) --
	(262.27,257.70) --
	(261.79,259.06) --
	(261.33,260.42) --
	(260.86,261.78) --
	(260.49,262.87) --
	(260.41,263.14) --
	(259.95,264.50) --
	(259.50,265.86) --
	(259.06,267.21) --
	(258.63,268.57) --
	(258.30,269.63) --
	(258.20,269.93) --
	(257.77,271.29) --
	(257.35,272.65) --
	(256.94,274.01) --
	(256.53,275.37) --
	(256.12,276.73) --
	(256.10,276.81) --
	(255.72,278.09) --
	(255.32,279.45) --
	(254.93,280.81) --
	(254.55,282.17) --
	(254.16,283.53) --
	(253.90,284.47) --
	(253.79,284.89) --
	(253.41,286.25) --
	(253.04,287.60) --
	(252.67,288.96) --
	(252.31,290.32) --
	(251.96,291.68) --
	(251.70,292.66) --
	(251.61,293.04) --
	(251.25,294.40) --
	(250.91,295.76) --
	(250.56,297.12) --
	(250.23,298.48) --
	(249.89,299.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41,201.89) --
	(337.33,201.97) --
	(335.91,203.32) --
	(335.21,204.00) --
	(334.51,204.68) --
	(333.14,206.04) --
	(333.01,206.18) --
	(331.80,207.40) --
	(330.81,208.42) --
	(330.49,208.76) --
	(329.20,210.12) --
	(328.62,210.74) --
	(327.93,211.48) --
	(326.69,212.84) --
	(326.42,213.15) --
	(325.48,214.20) --
	(324.28,215.56) --
	(324.22,215.63) --
	(323.11,216.92) --
	(322.02,218.20) --
	(321.96,218.28) --
	(320.83,219.64) --
	(319.83,220.86) --
	(319.72,221.00) --
	(318.62,222.36) --
	(317.63,223.62) --
	(317.55,223.71) --
	(316.50,225.07) --
	(315.46,226.43) --
	(315.43,226.47) --
	(314.44,227.79) --
	(313.44,229.15) --
	(313.23,229.43) --
	(312.45,230.51) --
	(311.48,231.87) --
	(311.04,232.51) --
	(310.53,233.23) --
	(309.59,234.59) --
	(308.84,235.70) --
	(308.67,235.95) --
	(307.76,237.31) --
	(306.86,238.67) --
	(306.64,239.01) --
	(305.98,240.03) --
	(305.11,241.39) --
	(304.44,242.45) --
	(304.26,242.75) --
	(303.42,244.11) --
	(302.59,245.46) --
	(302.25,246.03) --
	(301.77,246.82) --
	(300.97,248.18) --
	(300.18,249.54) --
	(300.05,249.76) --
	(299.39,250.90) --
	(298.62,252.26) --
	(297.86,253.62) --
	(297.85,253.64) --
	(297.11,254.98) --
	(296.37,256.34) --
	(295.65,257.69) --
	(295.65,257.70) --
	(294.93,259.06) --
	(294.22,260.42) --
	(293.52,261.78) --
	(293.46,261.90) --
	(292.83,263.14) --
	(292.15,264.50) --
	(291.48,265.86) --
	(291.26,266.31) --
	(290.82,267.21) --
	(290.16,268.57) --
	(289.52,269.93) --
	(289.06,270.90) --
	(288.88,271.29) --
	(288.25,272.65) --
	(287.63,274.01) --
	(287.02,275.37) --
	(286.86,275.71) --
	(286.41,276.73) --
	(285.81,278.09) --
	(285.22,279.45) --
	(284.67,280.74) --
	(284.64,280.81) --
	(284.06,282.17) --
	(283.49,283.53) --
	(282.93,284.89) --
	(282.47,286.01) --
	(282.37,286.25) --
	(281.82,287.60) --
	(281.28,288.96) --
	(280.74,290.32) --
	(280.27,291.53) --
	(280.21,291.68) --
	(279.69,293.04) --
	(279.17,294.40) --
	(278.66,295.76) --
	(278.15,297.12) --
	(278.07,297.33) --
	(277.65,298.48) --
	(277.15,299.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41,240.15) --
	(336.34,241.39) --
	(335.21,242.73) --
	(335.19,242.75) --
	(334.06,244.11) --
	(333.01,245.39) --
	(332.95,245.46) --
	(331.85,246.82) --
	(330.81,248.14) --
	(330.78,248.18) --
	(329.72,249.54) --
	(328.67,250.90) --
	(328.62,250.98) --
	(327.65,252.26) --
	(326.64,253.62) --
	(326.42,253.92) --
	(325.64,254.98) --
	(324.66,256.34) --
	(324.22,256.95) --
	(323.69,257.70) --
	(322.74,259.06) --
	(322.02,260.10) --
	(321.80,260.42) --
	(320.88,261.78) --
	(319.97,263.14) --
	(319.83,263.35) --
	(319.07,264.50) --
	(318.19,265.86) --
	(317.63,266.73) --
	(317.32,267.21) --
	(316.45,268.57) --
	(315.61,269.93) --
	(315.43,270.22) --
	(314.77,271.29) --
	(313.95,272.65) --
	(313.23,273.85) --
	(313.14,274.01) --
	(312.33,275.37) --
	(311.54,276.73) --
	(311.04,277.60) --
	(310.76,278.09) --
	(309.98,279.45) --
	(309.23,280.81) --
	(308.84,281.51) --
	(308.47,282.17) --
	(307.73,283.53) --
	(307.00,284.89) --
	(306.64,285.56) --
	(306.28,286.25) --
	(305.56,287.60) --
	(304.86,288.96) --
	(304.44,289.77) --
	(304.16,290.32) --
	(303.47,291.68) --
	(302.79,293.04) --
	(302.25,294.16) --
	(302.13,294.40) --
	(301.46,295.76) --
	(300.80,297.12) --
	(300.16,298.48) --
	(300.05,298.71) --
	(299.52,299.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41,270.76) --
	(337.00,271.29) --
	(335.98,272.65) --
	(335.21,273.71) --
	(334.99,274.01) --
	(334.00,275.37) --
	(333.03,276.73) --
	(333.01,276.76) --
	(332.07,278.09) --
	(331.13,279.45) --
	(330.81,279.91) --
	(330.20,280.81) --
	(329.28,282.17) --
	(328.62,283.17) --
	(328.38,283.53) --
	(327.48,284.89) --
	(326.60,286.25) --
	(326.42,286.53) --
	(325.73,287.60) --
	(324.87,288.96) --
	(324.22,290.02) --
	(324.03,290.32) --
	(323.19,291.68) --
	(322.37,293.04) --
	(322.02,293.62) --
	(321.55,294.40) --
	(320.75,295.76) --
	(319.96,297.12) --
	(319.83,297.35) --
	(319.17,298.48) --
	(318.40,299.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41,295.80) --
	(336.50,297.12) --
	(335.59,298.48) --
	(335.21,299.06) --
	(334.69,299.84);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.16, 30.69) rectangle (338.79,302.56);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21, 27.66) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21, 54.84) {0.1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21, 82.03) {0.2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,109.22) {0.3};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,136.40) {0.4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,163.59) {0.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,190.78) {0.6};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,217.97) {0.7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,245.15) {0.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,272.34) {0.9};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,299.53) {1.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41, 30.69) --
	( 34.16, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41, 57.87) --
	( 34.16, 57.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41, 85.06) --
	( 34.16, 85.06);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,112.25) --
	( 34.16,112.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,139.43) --
	( 34.16,139.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,166.62) --
	( 34.16,166.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,193.81) --
	( 34.16,193.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,221.00) --
	( 34.16,221.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,248.18) --
	( 34.16,248.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,275.37) --
	( 34.16,275.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,302.56) --
	( 34.16,302.56);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 27.94) --
	( 34.16, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (186.47, 27.94) --
	(186.47, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (338.79, 27.94) --
	(338.79, 30.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 34.16, 19.68) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (186.47, 19.68) {1.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (338.79, 19.68) {2.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (186.47,  7.64) {Relative mean asymptomatic generation interval, $G_a/G_s$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,166.62) {Intrinsic proportion of asymptomatic transmission, $z$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (349.79, 25.48) rectangle (391.98,307.77);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\node[inner sep=0pt,outer sep=0pt,anchor=south west,rotate=  0.00] at (355.29,  30.98) {
	\pgfimage[width= 14.45pt,height=256.07pt,interpolate=true]{figheatmap_R0_03_ras2}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (375.24, 34.35) {1.5};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (375.24, 88.41) {2.5};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (375.24,142.47) {3.5};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (375.24,196.53) {4.5};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (375.24,250.59) {5.5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (355.29,293.62) {$\mathcal{R}_0$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.2pt,line join=round] (355.29, 37.38) -- (358.18, 37.38);

\path[draw=drawColor,line width= 0.2pt,line join=round] (355.29, 91.44) -- (358.18, 91.44);

\path[draw=drawColor,line width= 0.2pt,line join=round] (355.29,145.50) -- (358.18,145.50);

\path[draw=drawColor,line width= 0.2pt,line join=round] (355.29,199.56) -- (358.18,199.56);

\path[draw=drawColor,line width= 0.2pt,line join=round] (355.29,253.62) -- (358.18,253.62);

\path[draw=drawColor,line width= 0.2pt,line join=round] (366.85, 37.38) -- (369.74, 37.38);

\path[draw=drawColor,line width= 0.2pt,line join=round] (366.85, 91.44) -- (369.74, 91.44);

\path[draw=drawColor,line width= 0.2pt,line join=round] (366.85,145.50) -- (369.74,145.50);

\path[draw=drawColor,line width= 0.2pt,line join=round] (366.85,199.56) -- (369.74,199.56);

\path[draw=drawColor,line width= 0.2pt,line join=round] (366.85,253.62) -- (369.74,253.62);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 34.16,310.62) {B. Basic reproduction number};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-03-09 figheatmap.R

@@ -1,5 +1,5 @@
 library(emdbook)
-library(ggplot2); theme_set(theme_bw(base_family = "Times"))
+library(ggplot2); theme_set(theme_bw())
 
 r <- 1/7
 G_s <- 8
@@ -39,18 +39,20 @@ g0 <- ggplot(figdata) +
   geom_contour(aes(relG, z, z=q), col="white") +
   # geom_hline(yintercept=example_z, col="red", lwd=1) +
   # geom_point(aes(x=1, y=example_z, fill=example_q2), size=5, col="white", shape=1, stroke=1) +
-  scale_x_log10(expression(paste("Relative mean asymptomatic generation interval, ", italic(G[a]/G[s]))), expand=c(0, 0),
+  scale_x_log10("Relative mean asymptomatic generation interval, $G_a/G_s$", expand=c(0, 0),
                      breaks=c(0.5, 1, 2)) +
-  scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),
+  scale_y_continuous("Intrinsic proportion of asymptomatic transmission, $z$", expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +
-  scale_fill_gradientn(colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
+  scale_fill_gradientn("$q$", colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
                        limits=c(0, 1),
                        breaks=0:5*2/10) +
-  ggtitle("A. Relevance of asymptomatic cases") +
+  ggtitle("A. Realized proportion of asymptomatic transmission") +
   theme(
-    legend.title = element_blank(),
     legend.key.height = unit(1.8, "cm")
   )
 
-ggsave("figheatmap.pdf", g0, width=5.3, height=4.3)
+tikz(file = "figheatmap.tex", width = 5.5, height = 4.5, standAlone = T)
+print(g0)
+dev.off()
+tools::texi2dvi('figheatmap.tex', pdf = T, clean = T)

### 2020-03-09 figheatmap_03.R

@@ -1,5 +1,6 @@
 library(emdbook)
-library(ggplot2); theme_set(theme_bw(base_family = "Times"))
+library(ggplot2); theme_set(theme_bw())
+library(tikzDevice)
 
 r <- 1/7
 G_s <- 8
@@ -26,18 +27,20 @@ figdata <- data.frame(
 g0 <- ggplot(figdata) +
   geom_raster(aes(relG, z, fill=q)) +
   geom_contour(aes(relG, z, z=q), col="white") +
-  scale_x_log10(expression(paste("Relative mean asymptomatic generation interval, ", italic(G[a]/G[s]))), expand=c(0, 0),
+  scale_x_log10("Relative mean asymptomatic generation interval, $G_a/G_s$", expand=c(0, 0),
                      breaks=c(0.5, 1, 2)) +
-  scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),
+  scale_y_continuous("Intrinsic proportion of asymptomatic transmission, $z$", expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +
-  scale_fill_gradientn(colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
+  scale_fill_gradientn("$q$", colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
                        limits=c(0, 1),
                        breaks=0:5*2/10) +
-  ggtitle("A. Relevance of asymptomatic cases") +
+  ggtitle("A. Realized proportion of asymptomatic transmission") +
   theme(
-    legend.title = element_blank(),
     legend.key.height = unit(1.8, "cm")
   )
 
-ggsave("figheatmap_03.pdf", g0, width=5.3, height=4.3)
+tikz(file = "figheatmap_03.tex", width = 5.5, height = 4.5, standAlone = T)
+print(g0)
+dev.off()
+tools::texi2dvi('figheatmap_03.tex', pdf = T, clean = T)

### 2020-03-09 figheatmap_08.R

@@ -1,5 +1,6 @@
 library(emdbook)
-library(ggplot2); theme_set(theme_bw(base_family = "Times"))
+library(ggplot2); theme_set(theme_bw())
+library(tikzDevice)
 
 r <- 1/7
 G_s <- 8
@@ -26,18 +27,20 @@ figdata <- data.frame(
 g0 <- ggplot(figdata) +
   geom_raster(aes(relG, z, fill=q)) +
   geom_contour(aes(relG, z, z=q), col="white") +
-  scale_x_log10(expression(paste("Relative mean asymptomatic generation interval, ", italic(G[a]/G[s]))), expand=c(0, 0),
+  scale_x_log10("Relative mean asymptomatic generation interval, $G_a/G_s$", expand=c(0, 0),
                      breaks=c(0.5, 1, 2)) +
-  scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),
+  scale_y_continuous("Intrinsic proportion of asymptomatic transmission, $z$", expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +
-  scale_fill_gradientn(colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
+  scale_fill_gradientn("$q$", colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
                        limits=c(0, 1),
                        breaks=0:5*2/10) +
-  ggtitle("A. Relevance of asymptomatic cases") +
+  ggtitle("A. Realized proportion of asymptomatic transmission") +
   theme(
-    legend.title = element_blank(),
     legend.key.height = unit(1.8, "cm")
   )
 
-ggsave("figheatmap_08.pdf", g0, width=5.3, height=4.3)
+tikz(file = "figheatmap_08.tex", width = 5.5, height = 4.5, standAlone = T)
+print(g0)
+dev.off()
+tools::texi2dvi('figheatmap_08.tex', pdf = T, clean = T)

### 2020-03-09 figheatmap_R0.R

@@ -1,5 +1,6 @@
 library(emdbook)
-library(ggplot2); theme_set(theme_bw(base_family = "Times"))
+library(ggplot2); theme_set(theme_bw())
+library(tikzDevice)
 
 r <- 1/7
 G_s <- 8
@@ -39,19 +40,21 @@ g0 <- ggplot(figdata) +
   # geom_point(aes(x=1, y=example_z, fill=example_R02), size=5, col="white", stroke=1, shape=21) +
   annotate(geom="text", x=1*sqrt(2), y=0.03, label="underestimated", col="white") +
   annotate(geom="text", x=1/sqrt(2), y=0.03, label="overestimated", col="white") +
-  scale_x_log10(expression(paste("Relative mean asymptomatic generation interval, ", italic(G[a]/G[s]))), expand=c(0, 0),
+  scale_x_log10("Relative mean asymptomatic generation interval, $G_a/G_s$", expand=c(0, 0),
                 breaks=c(0.5, 1, 2),
                 limits=c(0.5, 2)) +
-  scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),
+  scale_y_continuous("Intrinsic proportion of asymptomatic transmission, $z$", expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +
-  scale_fill_gradientn(colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
+  scale_fill_gradientn("$\\mathcal{R}_0$", colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
                        limits=c(1.5, 6),
                        breaks=c(1.5, 2.5, 3.5, 4.5, 5.5)) +
   ggtitle("B. Basic reproduction number") +
   theme(
-    legend.title = element_blank(),
     legend.key.height = unit(1.8, "cm")
   )
 
-ggsave("figheatmap_R0.pdf", g0, width=5.3, height=4.3)
+tikz(file = "figheatmap_R0.tex", width = 5.5, height = 4.5, standAlone = T)
+print(g0)
+dev.off()
+tools::texi2dvi('figheatmap_R0.tex', pdf = T, clean = T)

### 2020-03-09 figheatmap_R0_03.R

@@ -1,5 +1,6 @@
 library(emdbook)
-library(ggplot2); theme_set(theme_bw(base_family = "Times"))
+library(ggplot2); theme_set(theme_bw())
+library(tikzDevice)
 
 r <- 1/7
 G_s <- 8
@@ -26,19 +27,21 @@ figdata <- data.frame(
 g0 <- ggplot(figdata) +
   geom_raster(aes(relG, z, fill=R0)) +
   geom_contour(aes(relG, z, z=R0), col="white") +
-  scale_x_log10(expression(paste("Relative mean asymptomatic generation interval, ", italic(G[a]/G[s]))), expand=c(0, 0),
+  scale_x_log10("Relative mean asymptomatic generation interval, $G_a/G_s$", expand=c(0, 0),
                 breaks=c(0.5, 1, 2),
                 limits=c(0.5, 2)) +
-  scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),
+  scale_y_continuous("Intrinsic proportion of asymptomatic transmission, $z$", expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +
-  scale_fill_gradientn(colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
+  scale_fill_gradientn("$\\mathcal{R}_0$", colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
                        limits=c(1.5, 6),
                        breaks=c(1.5, 2.5, 3.5, 4.5, 5.5)) +
   ggtitle("B. Basic reproduction number") +
   theme(
-    legend.title = element_blank(),
     legend.key.height = unit(1.8, "cm")
   )
 
-ggsave("figheatmap_R0_03.pdf", g0, width=5.3, height=4.3)
+tikz(file = "figheatmap_R0_03.tex", width = 5.5, height = 4.5, standAlone = T)
+print(g0)
+dev.off()
+tools::texi2dvi('figheatmap_R0_03.tex', pdf = T, clean = T)

### 2020-03-09 figheatmap_R0_08.R

@@ -1,5 +1,6 @@
 library(emdbook)
-library(ggplot2); theme_set(theme_bw(base_family = "Times"))
+library(ggplot2); theme_set(theme_bw())
+library(tikzDevice)
 
 r <- 1/7
 G_s <- 8
@@ -26,19 +27,23 @@ figdata <- data.frame(
 g0 <- ggplot(figdata) +
   geom_raster(aes(relG, z, fill=R0)) +
   geom_contour(aes(relG, z, z=R0), col="white") +
-  scale_x_log10(expression(paste("Relative mean asymptomatic generation interval, ", italic(G[a]/G[s]))), expand=c(0, 0),
+  scale_x_log10("Relative mean asymptomatic generation interval, $G_a/G_s$", expand=c(0, 0),
                 breaks=c(0.5, 1, 2),
                 limits=c(0.5, 2)) +
-  scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),
+  scale_y_continuous("Intrinsic proportion of asymptomatic transmission, $z$", expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +
-  scale_fill_gradientn(colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
+  scale_fill_gradientn("$\\mathcal{R}_0$", colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
                        limits=c(1.5, 6),
                        breaks=c(1.5, 2.5, 3.5, 4.5, 5.5)) +
   ggtitle("B. Basic reproduction number") +
   theme(
-    legend.title = element_blank(),
     legend.key.height = unit(1.8, "cm")
   )
 
-ggsave("figheatmap_R0_08.pdf", g0, width=5.3, height=4.3)
+tikz(file = "figheatmap_R0_08.tex", width = 5.5, height = 4.5, standAlone = T)
+print(g0)
+dev.off()
+tools::texi2dvi('figheatmap_R0_08.tex', pdf = T, clean = T)
+
+# ggsave("figheatmap_R0_08.pdf", g0, width=5.3, height=4.3)

### 2020-03-09 figheatmap_kappa.R

@@ -1,5 +1,6 @@
 library(emdbook)
-library(ggplot2); theme_set(theme_bw(base_family = "Times"))
+library(ggplot2); theme_set(theme_bw())
+library(tikzDevice)
 
 r <- 1/7
 G_s <- 8
@@ -26,19 +27,21 @@ figdata <- data.frame(
 g0 <- ggplot(figdata) +
   geom_raster(aes(relkappa, z, fill=q)) +
   geom_contour(aes(relkappa, z, z=q), col="white") +
-  scale_x_log10(expression(paste("Relative asymptomatic generation-interval dispersion, ", italic(kappa[a]/kappa[s]))), expand=c(0, 0),
+  scale_x_log10("Relative asymptomatic generation-interval dispersion, $\\kappa_a/\\kappa_s$", expand=c(0, 0),
                 breaks=c(0.5, 1, 2),
                 limits=c(0.5, 2)) +
-  scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),
+  scale_y_continuous("Intrinsic proportion of asymptomatic transmission, $z$", expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +
-  scale_fill_gradientn(colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
+  scale_fill_gradientn("$q$", colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
                        limits=c(0, 1),
                        breaks=0:5*2/10) +
-  ggtitle("A. Relevance of asymptomatic cases") +
+  ggtitle("A. Realized proportion of asymptomatic transmission") +
   theme(
-    legend.title = element_blank(),
     legend.key.height = unit(1.8, "cm")
   )
 
-ggsave("figheatmap_kappa.pdf", g0, width=5.3, height=4.3)
+tikz(file = "figheatmap_kappa.tex", width = 5.5, height = 4.5, standAlone = T)
+print(g0)
+dev.off()
+tools::texi2dvi('figheatmap_kappa.tex', pdf = T, clean = T)

### 2020-03-09 figheatmap_kappa_R0.R

@@ -1,5 +1,6 @@
 library(emdbook)
-library(ggplot2); theme_set(theme_bw(base_family = "Times"))
+library(ggplot2); theme_set(theme_bw())
+library(tikzDevice)
 
 r <- 1/7
 G_s <- 8
@@ -26,19 +27,21 @@ figdata <- data.frame(
 g0 <- ggplot(figdata) +
   geom_raster(aes(relkappa, z, fill=R0)) +
   geom_contour(aes(relkappa, z, z=R0), col="white") +
-  scale_x_log10(expression(paste("Relative asymptomatic generation-interval dispersion, ", italic(kappa[a]/kappa[s]))), expand=c(0, 0),
+  scale_x_log10("Relative asymptomatic generation-interval dispersion, $\\kappa_a/\\kappa_s$", expand=c(0, 0),
                 breaks=c(0.5, 1, 2),
                 limits=c(0.5, 2)) +
-  scale_y_continuous(expression(paste("Intrinsic proportion of asymptomatic transmission, ", italic(z))), expand=c(0, 0),
+  scale_y_continuous("Intrinsic proportion of asymptomatic transmission, $z$", expand=c(0, 0),
                      limits=c(0, 1),
                      breaks=0:10/10) +
-  scale_fill_gradientn(colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
+  scale_fill_gradientn("$\\mathcal{R}_0$", colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
                        limits=c(1.5, 6),
                        breaks=c(1.5, 2.5, 3.5, 4.5, 5.5)) +
   ggtitle("B. Basic reproduction number") +
   theme(
-    legend.title = element_blank(),
     legend.key.height = unit(1.8, "cm")
   )
 
-ggsave("figheatmap_kappa_R0.pdf", g0, width=5.3, height=4.3)
+tikz(file = "figheatmap_kappa_R0.tex", width = 5.5, height = 4.5, standAlone = T)
+print(g0)
+dev.off()
+tools::texi2dvi('figheatmap_kappa_R0.tex', pdf = T, clean = T)

### 2020-03-09 figheatmap_R0.tex
new fig

@@
-% Created by tikzDevice version 0.12.3 on 2020-03-09 11:51:36
+% Created by tikzDevice version 0.12.3 on 2020-03-09 12:40:36
 % !TEX encoding = UTF-8 Unicode
@@
 
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (181.30, 60.59) {$\mathcal{R}_0=2.5$};
+
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (262.63, 35.04) {underestimated};
@@
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (110.31, 35.04) {overestimated};
+
+\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round] ( 55.10,177.16) --
+	( 64.23,161.35) --
+	( 45.97,161.35) --
+	( 55.10,177.16);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.71] at ( 55.10,150.58) {$\mathcal{R}_0=2.0$};
+
+\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round] (315.64,166.62) circle (  6.78);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.71] at (315.64,150.58) {$\mathcal{R}_0=3.1$};
 \definecolor{drawColor}{gray}{0.20}

### 2020-03-09 figheatmap.R

@@ -23,22 +23,22 @@ figdata <- data.frame(
   relG=rep(relG, each=length(z))
 )
 
-example_p <- 0.18
-example_R_a <- 0.5
-example_R_s <- 1
-example_z <- example_p * example_R_a/(1-example_p)
-example_qodds <- example_z/(1-example_z) *  (1 + kappa_s * r * G_s)^(1/kappa_s)/(1 + kappa_a * r * relG * G_s)^(1/kappa_a)
-example_q <- example_qodds/(1+example_qodds)
-range(example_q)
+zexample <- 0.5
+relg1 <- 0.55
+q1 <- (1 + kappa_s * r * G_s)^(1/kappa_s)/(1 + kappa_a * r * relg1 * G_s)^(1/kappa_a)
+q1/(1+q1)
 
-example_qodds2 <- example_z/(1-example_z) *  (1 + kappa_s * r * G_s)^(1/kappa_s)/(1 + kappa_a * r * G_s)^(1/kappa_a)
-example_q2 <- example_qodds2/(1+example_qodds2)
+relg2 <- 1.8
+q2 <- (1 + kappa_s * r * G_s)^(1/kappa_s)/(1 + kappa_a * r * relg2 * G_s)^(1/kappa_a)
+q2/(1+q2)
 
 g0 <- ggplot(figdata) +
   geom_raster(aes(relG, z, fill=q)) +
   geom_contour(aes(relG, z, z=q), col="white") +
-  # geom_hline(yintercept=example_z, col="red", lwd=1) +
-  # geom_point(aes(x=1, y=example_z, fill=example_q2), size=5, col="white", shape=1, stroke=1) +
+  annotate(geom="point", x=0.55, y=0.5, col="white", shape=2, size=5, stroke=2) +
+  annotate(geom="text", x=0.55, y=0.45, label="$q=0.59$", col="white", size=2.5) +
+  annotate(geom="point", x=1.8, y=0.5, col="white", shape=1, size=5, stroke=2) +
+  annotate(geom="text", x=1.8, y=0.45, label="$q=0.38$", col="white", size=2.5) +
   scale_x_log10("Relative mean asymptomatic generation interval, $G_a/G_s$", expand=c(0, 0),
                      breaks=c(0.5, 1, 2)) +
   scale_y_continuous("Intrinsic proportion of asymptomatic transmission, $z$", expand=c(0, 0),

### 2020-03-09 figheatmap_R0.R

@@ -24,22 +24,26 @@ figdata <- data.frame(
   relG=rep(relG, each=length(z))
 )
 
-example_p <- 0.18
-example_R_a <- 0.5
-example_R_s <- 1
-example_z <- example_p * example_R_a/(1-example_p)
-example_R0 <- 1/((1-example_z) * (1 + kappa_s * r * G_s)^(-1/kappa_s) + example_z * (1 + kappa_a * r * relG * G_s)^(-1/kappa_a))
-example_R02 <- 1/((1-example_z) * (1 + kappa_s * r * G_s)^(-1/kappa_s) + example_z * (1 + kappa_a * r * G_s)^(-1/kappa_a))
-range(example_R0)
+zexample <- 0.5
+relg1 <- 0.55
+1/((1-zexample) * (1 + kappa_s * r * G_s)^(-1/kappa_s) + zexample * (1 + kappa_a * r * relg1 * G_s)^(-1/kappa_a))
+
+relg2 <- 1.8
+1/((1-zexample) * (1 + kappa_s * r * G_s)^(-1/kappa_s) + zexample * (1 + kappa_a * r * relg2 * G_s)^(-1/kappa_a))
+
 
 g0 <- ggplot(figdata) +
   geom_raster(aes(relG, z, fill=R0)) +
   geom_contour(aes(relG, z, z=R0), col="white", bins=9) +
   geom_vline(xintercept=1, lty=2, col="white", lwd=0.8) +
-  # geom_hline(yintercept=example_z, col="red", lwd=1) +
-  # geom_point(aes(x=1, y=example_z, fill=example_R02), size=5, col="white", stroke=1, shape=21) +
+  # geom_point(aes(x=1, y=0), size=8, col="black", stroke=1, shape=1) +
+  annotate(geom="text", x=0.96, y=0.11, label="$\\mathcal{R}_0=2.5$", col="white", angle=90) +
   annotate(geom="text", x=1*sqrt(2), y=0.03, label="underestimated", col="white") +
   annotate(geom="text", x=1/sqrt(2), y=0.03, label="overestimated", col="white") +
+  annotate(geom="point", x=0.55, y=0.5, col="white", shape=2, size=5, stroke=2) +
+  annotate(geom="text", x=0.55, y=0.45, label="$\\mathcal{R}_0=2.0$", col="white", size=2.5) +
+  annotate(geom="point", x=1.8, y=0.5, col="white", shape=1, size=5, stroke=2) +
[…]

### 2020-03-09 short.body.tex
push all files
k

@@
 \begin{center}
-\includegraphics[width=0.4\textwidth]{figheatmap.pdf}
+\includegraphics[width=0.45\textwidth]{figheatmap.pdf}
 \mbox{\hspace{0.05\textwidth}}
-\includegraphics[width=0.4\textwidth]{figheatmap_R0.pdf}
+\includegraphics[width=0.45\textwidth]{figheatmap_R0.pdf}
 \caption{Effects of intrinsic proportion of asymptomatic transmission on the realized proportion of asymptomatic transmission and basic reproduction number, given variation in
 the mean generation interval of asymptomatic cases. 
-(A) Increasing the speed of asymptomatic transmission (shorter generation intervals) increases the importance of asymptomatic cases in transmission, $q$.
-(B) Increasing generation intervals of asymptomatic cases increases the basic reproduction number ${\cal{R}}_0$; 
-When $\bar G_a$ is smaller (larger) than $\bar G_s$, estimates based on the observed generation distribution for symptomatic cases (dashed line) are expected to over- (under-) estimate the true $\mathcal R_0$.
+(A) Increasing the speed of asymptomatic transmission (shorter generation intervals) increases the realized proportion of asymptomatic transmission, $q$.
+(B) Increasing the speed of asymptomatic transmission (shorter generation intervals) decreases the basic reproduction number ${\cal{R}}_0$.
+When $\bar G_a$ is smaller (larger) than $\bar G_s$, estimates based on the observed generation distribution for symptomatic cases (${\cal{R}}_0=2.5$; dashed line) are expected to over- (under-) estimate the true $\mathcal R_0$.
+Triangle assume $z=0.5$ and $\bar G_a/\bar G_s = 0.55$.
+Circle assume $z=0.5$ and $\bar G_a/\bar G_s = 1.8$.
 Solid lines show contours for \Ro\ values. 

### 2020-03-09 abs.tex
Abstract tweaks

@@
-{\footnotesize We assess the impact of asymptomatic cases on epidemic potential of COVID-19 (and COVID-19 like pathogens) -- as measured both by the basic reproduction 
-number (i.e., the expected number of secondary cases generated by an average primary case in a fully susceptible population) and the fraction of new secondary cases attributable to asymptomatic
-individuals. As we show, the impact of asymptomatic
-cases depends on their generation intervals (i.e., time between when an individual is infected and when that individual infects another person).
-If the generation intervals of asymptomatic cases differs from that 
-of symptomatic cases, then estimates of the basic reproduction number which do not explicitly account for asymptomatic cases may be systematically biased.
-Specifically, if asymptomatic cases have a shorter generation interval,
-${\cal{R}}_0$ will be over-estimated, and if they have a longer generation interval, ${\cal{R}}_0$ will be under-estimated.
-%If infectiousness of asymptomatic cases is relatively short/long in duration compared
-%to symptomatic cases, then
-%estimates of the basic reproduction number may be over/under-estimates
-%compared to estimates only attributing secondary cases to symptomatic cases.
-The analysis provides a rationale for assessing the duration of asymptomatic cases 
-of COVID-19 in addition to their prevalence in the population.
+{\footnotesize We assess the impact of asymptomatic transmission on epidemic potential of novel respiratory pathogens (like COVID-19) --
+as measured both by the basic reproduction number (i.e., the expected number of secondary cases generated by an average primary case in a fully susceptible population) and the fraction of new secondary cases attributable to asymptomatic individuals.
+We show that the impact of asymptomatic transmission depends on generation intervals (i.e., time between when an individual is infected and when that individual infects another person).
+If the generation intervals of asymptomatic cases differs from that of symptomatic cases, then estimates of the basic reproduction number which do not explicitly account for asymptomatic cases may be systematically biased.
+Specifically, if asymptomatic cases have a shorter generation interval than symptomatic cases, ${\cal{R}}_0$ will be over-estimated, and if they have a longer generation interval, ${\cal{R}}_0$ will be under-estimated.
+The analysis provides a rationale for assessing the duration of asymptomatic cases of COVID-19 in addition to their prevalence in the population.
 }

### 2020-03-09 figheatmap_R0.tex
new figures!!!!!!

--- 2020-03-09 figheatmap_R0.tex
@@
-% Created by tikzDevice version 0.12.3 on 2020-03-09 11:51:36
+% Created by tikzDevice version 0.12.3 on 2020-03-09 13:46:06
 % !TEX encoding = UTF-8 Unicode
@@
 \definecolor{fillColor}{RGB}{255,255,255}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (397.48,325.21);
+\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (361.35,289.08);
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (397.48,325.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (361.35,289.08);
 \end{scope}
 \begin{scope}
-\path[clip] ( 34.16, 30.69) rectangle (338.79,302.56);
+\path[clip] ( 34.16, 30.69) rectangle (302.65,266.42);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 34.16, 30.69) rectangle (338.79,302.56);
+\path[fill=fillColor] ( 34.16, 30.69) rectangle (302.65,266.42);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 44.28) --
-	(338.79, 44.28);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 42.47) --
+	(302.65, 42.47);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 71.47) --
-	(338.79, 71.47);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 66.05) --
+	(302.65, 66.05);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 98.65) --
-	(338.79, 98.65);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 89.62) --
+	(302.65, 89.62);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,125.84) --
-	(338.79,125.84);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,113.19) --
+	(302.65,113.19);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,153.03) --
-	(338.79,153.03);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,136.77) --
+	(302.65,136.77);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,180.22) --
-	(338.79,180.22);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,160.34) --
+	(302.65,160.34);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,207.40) --
-	(338.79,207.40);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,183.91) --
+	(302.65,183.91);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,234.59) --
-	(338.79,234.59);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,207.49) --
+	(302.65,207.49);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,261.78) --
-	(338.79,261.78);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,231.06) --
+	(302.65,231.06);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,288.96) --
-	(338.79,288.96);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,254.64) --
+	(302.65,254.64);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (110.31, 30.69) --
-	(110.31,302.56);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (101.28, 30.69) --
+	(101.28,266.42);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (262.63, 30.69) --
-	(262.63,302.56);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (235.53, 30.69) --
+	(235.53,266.42);
 
 \path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 30.69) --
-	(338.79, 30.69);
+	(302.65, 30.69);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 57.87) --
-	(338.79, 57.87);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 54.26) --
+	(302.65, 54.26);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 85.06) --
-	(338.79, 85.06);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 77.83) --
+	(302.65, 77.83);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,112.25) --
-	(338.79,112.25);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,101.41) --
+	(302.65,101.41);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,139.43) --
-	(338.79,139.43);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,124.98) --
+	(302.65,124.98);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,166.62) --
-	(338.79,166.62);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,148.55) --
+	(302.65,148.55);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,193.81) --
-	(338.79,193.81);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,172.13) --
+	(302.65,172.13);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,221.00) --
-	(338.79,221.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,195.70) --
+	(302.65,195.70);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,248.18) --
-	(338.79,248.18);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,219.28) --
+	(302.65,219.28);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,275.37) --
-	(338.79,275.37);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,242.85) --
+	(302.65,242.85);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,302.56) --
-	(338.79,302.56);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,266.42) --
+	(302.65,266.42);
 
 \path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 30.69) --
-	( 34.16,302.56);
+	( 34.16,266.42);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (186.47, 30.69) --
-	(186.47,302.56);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (168.41, 30.69) --
+	(168.41,266.42);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (338.79, 30.69) --
-	(338.79,302.56);
-\node[inner sep=0pt,outer sep=0pt,anchor=south west,rotate=  0.00] at ( 35.25,  32.05) {
-	\pgfimage[width=303.25pt,height=269.15pt,interpolate=false]{figheatmap_R0_ras1}};
+\path[draw=drawColor,line width= 0.6pt,line join=round] (302.65, 30.69) --
+	(302.65,266.42);
+\node[inner sep=0pt,outer sep=0pt,anchor=south west,rotate=  0.00] at ( 35.12,  31.86) {
+	\pgfimage[width=267.28pt,height=233.38pt,interpolate=false]{figheatmap_R0_ras1}};
 \definecolor{drawColor}{RGB}{255,255,255}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,192.10) --
-	( 35.87,193.81) --
-	( 36.35,194.30) --
-	( 38.51,196.53) --
-	( 38.55,196.57) --
-	( 40.75,198.92) --
-	( 41.05,199.25) --
-	( 42.95,201.34) --
-	( 43.50,201.97) --
-	( 45.14,203.83) --
-	( 45.87,204.68) --
-	( 47.34,206.41) --
-	( 48.16,207.40) --
-	( 49.54,209.08) --
-	( 50.38,210.12) --
-	( 51.74,211.84) --
-	( 52.52,212.84) --
-	( 53.93,214.69) --
-	( 54.59,215.56) --
-	( 56.13,217.64) --
-	( 56.60,218.28) --
-	( 58.33,220.69) --
-	( 58.54,221.00) --
-	( 60.43,223.71) --
-	( 60.53,223.85) --
-	( 62.26,226.43) --
-	( 62.72,227.14) --
-	( 64.03,229.15) --
-	( 64.92,230.54) --
-	( 65.76,231.87) --
-	( 67.12,234.07) --
-	( 67.43,234.59) --
-	( 69.06,237.31) --
-	( 69.32,237.74) --
-	( 70.64,240.03) --
-	( 71.51,241.56) --
-	( 72.18,242.75) --
-	( 73.68,245.46) --
-	( 73.71,245.53) --
-	( 75.13,248.18) --
-	( 75.91,249.66) --
-	( 76.55,250.90) --
-	( 77.94,253.62) --
-	( 78.11,253.96) --
-	( 79.28,256.34) --
-	( 80.30,258.44) --
-	( 80.60,259.06) --
-	( 81.88,261.78) --
-	( 82.50,263.12) --
-	( 83.13,264.50) --
-	( 84.35,267.21) --
-	( 84.70,268.01) --
-	( 85.54,269.93) --
-	( 86.70,272.65) --
-	( 86.90,273.11) --
-	( 87.83,275.37) --
-	( 88.95,278.09) --
-	( 89.09,278.45) --
-	( 90.03,280.81) --
-	( 91.09,283.53) --
-	( 91.29,284.04) --
-	( 92.12,286.25) --
-	( 93.14,288.96) --
-	( 93.49,289.91) --
-	( 94.13,291.68) --
-	( 95.10,294.40) --
-	( 95.69,296.06) --
-	( 96.05,297.12) --
-	( 96.98,299.84);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,170.65) --
+	( 35.66,172.13) --
+	( 36.09,172.56) --
+	( 37.99,174.49) --
+	( 38.03,174.53) --
+	( 39.97,176.56) --
+	( 40.23,176.84) --
+	( 41.90,178.66) --
+	( 42.40,179.20) --
+	( 43.84,180.82) --
+	( 44.48,181.56) --
+	( 45.78,183.06) --
+	( 46.50,183.91) --
+	( 47.71,185.37) --
+	( 48.45,186.27) --
+	( 49.65,187.76) --
+	( 50.34,188.63) --
+	( 51.59,190.23) --
+	( 52.17,190.99) --
+	( 53.52,192.79) --
+	( 53.94,193.34) --
+	( 55.46,195.44) --
+	( 55.65,195.70) --
+	( 57.31,198.06) --
+	( 57.40,198.18) --
+	( 58.92,200.42) --
+	( 59.33,201.03) --
+	( 60.49,202.77) --
+	( 61.27,203.98) --
+	( 62.01,205.13) --
+	( 63.21,207.04) --
+	( 63.48,207.49) --
+	( 64.92,209.85) --
+	( 65.14,210.22) --
+	( 66.31,212.20) --
+	( 67.08,213.53) --
+	( 67.67,214.56) --
+	( 68.99,216.92) --
+	( 69.02,216.97) --
+	( 70.27,219.28) --
+	( 70.96,220.55) --
+	( 71.52,221.63) --
+	( 72.74,223.99) --
+	( 72.89,224.28) --
+	( 73.93,226.35) --
+	( 74.83,228.17) --
+	( 75.09,228.70) --
+	( 76.22,231.06) --
+	( 76.77,232.23) --
+	( 77.32,233.42) --
+	( 78.39,235.78) --
+	( 78.70,236.46) --
+	( 79.44,238.13) --
+	( 80.47,240.49) --
+	( 80.64,240.89) --
+	( 81.47,242.85) --
+	( 82.45,245.21) --
+	( 82.58,245.52) --
+	( 83.40,247.56) --
+	( 84.34,249.92) --
+	( 84.51,250.37) --
+	( 85.25,252.28) --
+	( 86.14,254.64) --
+	( 86.45,255.45) --
+	( 87.02,256.99) --
+	( 87.87,259.35) --
+	( 88.39,260.79) --
+	( 88.71,261.71) --
+	( 89.53,264.07);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 90.39) --
-	( 34.45, 90.50) --
-	( 36.35, 91.21) --
-	( 38.55, 92.05) --
-	( 40.75, 92.91) --
-	( 41.50, 93.22) --
-	( 42.95, 93.81) --
-	( 45.14, 94.73) --
-	( 47.34, 95.69) --
-	( 47.90, 95.94) --
-	( 49.54, 96.67) --
-	( 51.74, 97.69) --
-	( 53.75, 98.65) --
-	( 53.93, 98.75) --
-	( 56.13, 99.84) --
-	( 58.33,100.97) --
-	( 59.10,101.37) --
-	( 60.53,102.14) --
-	( 62.72,103.35) --
-	( 64.02,104.09) --
-	( 64.92,104.61) --
-	( 67.12,105.92) --
-	( 68.57,106.81) --
-	( 69.32,107.28) --
-	( 71.51,108.69) --
-	( 72.78,109.53) --
-	( 73.71,110.15) --
-	( 75.91,111.68) --
-	( 76.70,112.25) --
-	( 78.11,113.27) --
-	( 80.30,114.93) --
-	( 80.35,114.97) --
-	( 82.50,116.66) --
-	( 83.76,117.68) --
-	( 84.70,118.47) --
-	( 86.90,120.36) --
-	( 86.95,120.40) --
-	( 89.09,122.33) --
-	( 89.94,123.12) --
-	( 91.29,124.40) --
-	( 92.76,125.84) --
-	( 93.49,126.57) --
-	( 95.42,128.56) --
-	( 95.69,128.84) --
-	( 97.88,131.23) --
-	( 97.92,131.28) --
-	(100.08,133.75) --
-	(100.29,134.00) --
-	(102.28,136.40) --
-	(102.53,136.72) --
-	(104.47,139.19) --
-	(104.66,139.43) --
-	(106.67,142.14) --
-	(106.69,142.15) --
-	(108.61,144.87) --
-	(108.87,145.25) --
-	(110.44,147.59) --
-	(111.07,148.56) --
-	(112.18,150.31) --
-	(113.26,152.06) --
-	(113.85,153.03) --
-	(115.44,155.75) --
-	(115.46,155.78) --
-	(116.97,158.47) --
-	(117.66,159.74) --
-	(118.43,161.18) --
-	(119.83,163.90) --
-	(119.86,163.97) --
-	(121.17,166.62) --
-	(122.05,168.48) --
-	(122.45,169.34) --
-	(123.69,172.06) --
-	(124.25,173.32) --
-	(124.88,174.78) --
-	(126.03,177.50) --
-	(126.45,178.52) --
-	(127.13,180.22) --
-	(128.20,182.93) --
-	(128.65,184.12) --
-	(129.22,185.65) --
-	(130.21,188.37) --
-	(130.84,190.16) --
-	(131.17,191.09) --
-	(132.09,193.81) --
-	(132.99,196.53) --
-	(133.04,196.70) --
-	(133.85,199.25) --
-	(134.69,201.97) --
-	(135.24,203.80) --
-	(135.50,204.68) --
-	(136.28,207.40) --
-	(137.04,210.12) --
-	(137.44,211.55) --
-	(137.78,212.84) --
-	(138.50,215.56) --
-	(139.20,218.28) --
-	(139.63,220.03) --
-	(139.87,221.00) --
-	(140.53,223.71) --
-	(141.17,226.43) --
-	(141.79,229.15) --
-	(141.83,229.35) --
-	(142.39,231.87) --
-	(142.98,234.59) --
-	(143.55,237.31) --
-	(144.03,239.63) --
-	(144.11,240.03) --
-	(144.65,242.75) --
-	(145.18,245.46) --
-	(145.69,248.18) --
-	(146.20,250.90) --
-	(146.23,251.05) --
-	(146.69,253.62) --
-	(147.17,256.34) --
-	(147.63,259.06) --
-	(148.09,261.78) --
-	(148.42,263.79) --
-	(148.54,264.50) --
-	(148.97,267.21) --
-	(149.40,269.93) --
-	(149.81,272.65) --
-	(150.22,275.37) --
-	(150.62,278.09) --
-	(150.62,278.09) --
-	(151.01,280.81) --
-	(151.39,283.53) --
-	(151.76,286.25) --
-	(152.13,288.96) --
-	(152.48,291.68) --
-	(152.82,294.27) --
-	(152.84,294.40) --
-	(153.18,297.12) --
-	(153.51,299.84);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 82.46) --
+	( 34.41, 82.55) --
+	( 36.09, 83.16) --
+	( 38.03, 83.89) --
+	( 39.97, 84.64) --
+	( 40.63, 84.91) --
+	( 41.90, 85.42) --
+	( 43.84, 86.22) --
+	( 45.78, 87.05) --
+	( 46.27, 87.26) --
+	( 47.71, 87.90) --
+	( 49.65, 88.79) --
+	( 51.42, 89.62) --
+	( 51.59, 89.70) --
+	( 53.52, 90.65) --
+	( 55.46, 91.63) --
+	( 56.14, 91.98) --
+	( 57.40, 92.64) --
+	( 59.33, 93.69) --
+	( 60.48, 94.33) --
+	( 61.27, 94.79) --
+	( 63.21, 95.92) --
+	( 64.49, 96.69) --
+	( 65.14, 97.10) --
+	( 67.08, 98.32) --
+	( 68.20, 99.05) --
+	( 69.02, 99.59) --
+	( 70.96,100.92) --
+	( 71.65,101.41) --
+	( 72.89,102.30) --
+	( 74.83,103.73) --
+	( 74.87,103.76) --
+	( 76.77,105.24) --
+	( 77.87,106.12) --
+	( 78.70,106.80) --
+	( 80.64,108.44) --
+	( 80.69,108.48) --
+	( 82.58,110.15) --
+	( 83.33,110.84) --
+	( 84.51,111.95) --
+	( 85.81,113.19) --
+	( 86.45,113.83) --
+	( 88.15,115.55) --
+	( 88.39,115.80) --
+	( 90.32,117.87) --
+	( 90.36,117.91) --
+	( 92.26,120.05) --
+	( 92.45,120.27) --
+	( 94.20,122.35) --
+	( 94.42,122.62) --
+	( 96.13,124.77) --
+	( 96.30,124.98) --
+	( 98.07,127.32) --
+	( 98.08,127.34) --
+	( 99.78,129.70) --
+	(100.01,130.03) --
+	(101.39,132.05) --
+	(101.94,132.89) --
+	(102.93,134.41) --
+	(103.88,135.93) --
+	(104.40,136.77) --
+	(105.80,139.12) --
+	(105.82,139.15) --
+	(107.14,141.48) --
+	(107.75,142.59) --
+	(108.43,143.84) --
+	(109.66,146.20) --
+	(109.69,146.25) --
+	(110.84,148.55) --
+	(111.63,150.17) --
+	(111.98,150.91) --
+	(113.07,153.27) --
+	(113.57,154.37) --
+	(114.12,155.63) --
+	(115.13,157.98) --
+	(115.50,158.87) --
+	(116.10,160.34) --
+	(117.04,162.70) --
+	(117.44,163.72) --
+	(117.94,165.06) --
+	(118.82,167.41) --
+	(119.38,168.96) --
+	(119.66,169.77) --
+	(120.47,172.13) --
+	(121.26,174.49) --
+	(121.31,174.63) --
+	(122.02,176.84) --
+	(122.76,179.20) --
+	(123.25,180.79) --
+	(123.48,181.56) --
+	(124.17,183.91) --
+	(124.84,186.27) --
+	(125.19,187.51) --
+	(125.49,188.63) --
+	(126.12,190.99) --
+	(126.74,193.34) --
+	(127.12,194.86) --
+	(127.33,195.70) --
+	(127.91,198.06) --
+	(128.47,200.42) --
+	(129.02,202.77) --
+	(129.06,202.94) --
+	(129.55,205.13) --
+	(130.07,207.49) --
+	(130.57,209.85) --
+	(131.00,211.86) --
+	(131.07,212.20) --
+	(131.54,214.56) --
+	(132.01,216.92) --
+	(132.46,219.28) --
+	(132.91,221.63) --
+	(132.93,221.76) --
+	(133.34,223.99) --
+	(133.76,226.35) --
+	(134.17,228.70) --
+	(134.58,231.06) --
+	(134.87,232.80) --
+	(134.97,233.42) --
+	(135.35,235.78) --
+	(135.73,238.13) --
+	(136.09,240.49) --
+	(136.45,242.85) --
+	(136.81,245.21) --
+	(136.81,245.21) --
+	(137.15,247.56) --
+	(137.48,249.92) --
+	(137.81,252.28) --
+	(138.13,254.64) --
+	(138.45,256.99) --
+	(138.74,259.24) --
+	(138.76,259.35) --
+	(139.06,261.71) --
+	(139.35,264.07);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41, 48.53) --
-	(335.21, 48.76) --
-	(333.01, 48.99) --
-	(330.81, 49.24) --
-	(328.62, 49.49) --
-	(326.69, 49.72) --
-	(326.42, 49.75) --
-	(324.22, 50.02) --
-	(322.02, 50.29) --
-	(319.83, 50.58) --
-	(317.63, 50.87) --
-	(315.43, 51.18) --
-	(313.23, 51.50) --
-	(311.04, 51.83) --
-	(308.84, 52.17) --
-	(307.21, 52.44) --
-	(306.64, 52.53) --
-	(304.44, 52.90) --
-	(302.25, 53.28) --
-	(300.05, 53.68) --
-	(297.85, 54.09) --
-	(295.65, 54.53) --
-	(293.46, 54.98) --
-	(292.63, 55.15) --
-	(291.26, 55.45) --
-	(289.06, 55.94) --
-	(286.86, 56.45) --
-	(284.67, 56.99) --
-	(282.47, 57.55) --
-	(281.27, 57.87) --
-	(280.27, 58.14) --
-	(278.07, 58.76) --
-	(275.88, 59.41) --
-	(273.68, 60.09) --
-	(272.15, 60.59) --
-	(271.48, 60.81) --
-	(269.28, 61.57) --
-	(267.09, 62.37) --
-	(264.89, 63.22) --
-	(264.66, 63.31) --
-	(262.69, 64.11) --
-	(260.49, 65.06) --
-	(258.39, 66.03) --
-	(258.30, 66.07) --
-	(256.10, 67.14) --
-	(253.90, 68.29) --
-	(253.06, 68.75) --
-	(251.70, 69.51) --
-	(249.51, 70.82) --
-	(248.47, 71.47) --
-	(247.31, 72.22) --
-	(245.11, 73.73) --
-	(244.48, 74.19) --
-	(242.92, 75.36) --
-	(240.98, 76.90) --
-	(240.72, 77.12) --
-	(238.52, 79.03) --
-	(237.88, 79.62) --
-	(236.32, 81.11) --
-	(235.11, 82.34) --
-	(234.13, 83.39) --
-	(232.63, 85.06) --
-	(231.93, 85.88) --
-	(230.39, 87.78) --
-	(229.73, 88.63) --
-	(228.36, 90.50) --
-	(227.53, 91.68) --
-	(226.51, 93.22) --
-	(225.34, 95.07) --
-	(224.81, 95.94) --
-	(223.26, 98.65) --
-	(223.14, 98.87) --
-	(221.82,101.37) --
-	(220.94,103.16) --
-	(220.50,104.09) --
-	(219.27,106.81) --
-	(218.74,108.03) --
-	(218.12,109.53) --
-	(217.06,112.25) --
-	(216.55,113.62) --
-	(216.06,114.97) --
-	(215.13,117.68) --
-	(214.35,120.09) --
-	(214.25,120.40) --
-	(213.42,123.12) --
-	(212.65,125.84) --
-	(212.15,127.67) --
-	(211.91,128.56) --
-	(211.22,131.28) --
-	(210.56,134.00) --
-	(209.95,136.67) --
-	(209.94,136.72) --
-	(209.35,139.43) --
-	(208.79,142.15) --
-	(208.25,144.87) --
-	(207.76,147.53) --
-	(207.75,147.59) --
-	(207.26,150.31) --
-	(206.79,153.03) --
-	(206.35,155.75) --
-	(205.92,158.47) --
-	(205.56,160.90) --
-	(205.52,161.18) --
-	(205.12,163.90) --
-	(204.75,166.62) --
-	(204.39,169.34) --
-	(204.04,172.06) --
-	(203.71,174.78) --
-	(203.39,177.50) --
-	(203.36,177.75) --
-	(203.08,180.22) --
-	(202.78,182.93) --
-	(202.49,185.65) --
-	(202.22,188.37) --
-	(201.95,191.09) --
-	(201.69,193.81) --
-	(201.44,196.53) --
-	(201.20,199.25) --
-	(201.16,199.64) --
-	(200.96,201.97) --
-	(200.73,204.68) --
-	(200.51,207.40) --
-	(200.30,210.12) --
-	(200.09,212.84) --
-	(199.89,215.56) --
-	(199.70,218.28) --
-	(199.51,221.00) --
-	(199.32,223.71) --
-	(199.14,226.43) --
-	(198.97,229.15) --
-	(198.97,229.24) --
-	(198.80,231.87) --
-	(198.64,234.59) --
-	(198.47,237.31) --
-	(198.32,240.03) --
-	(198.17,242.75) --
-	(198.02,245.46) --
-	(197.87,248.18) --
-	(197.73,250.90) --
-	(197.59,253.62) --
-	(197.46,256.34) --
-	(197.33,259.06) --
-	(197.20,261.78) --
-	(197.08,264.50) --
-	(196.95,267.21) --
-	(196.83,269.93) --
-	(196.77,271.48) --
-	(196.72,272.65) --
-	(196.60,275.37) --
-	(196.49,278.09) --
-	(196.38,280.81) --
-	(196.27,283.53) --
-	(196.17,286.25) --
-	(196.07,288.96) --
-	(195.97,291.68) --
-	(195.87,294.40) --
-	(195.77,297.12) --
-	(195.68,299.84);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (301.44, 46.16) --
+	(299.50, 46.36) --
+	(297.56, 46.56) --
+	(295.62, 46.77) --
+	(293.69, 46.99) --
+	(291.99, 47.19) --
+	(291.75, 47.22) --
+	(289.81, 47.45) --
+	(287.88, 47.69) --
+	(285.94, 47.93) --
+	(284.00, 48.19) --
+	(282.07, 48.46) --
+	(280.13, 48.73) --
+	(278.19, 49.02) --
+	(276.26, 49.32) --
+	(274.82, 49.54) --
+	(274.32, 49.63) --
+	(272.38, 49.94) --
+	(270.45, 50.28) --
+	(268.51, 50.62) --
+	(266.57, 50.98) --
+	(264.64, 51.36) --
+	(262.70, 51.75) --
+	(261.97, 51.90) --
+	(260.76, 52.16) --
+	(258.83, 52.58) --
+	(256.89, 53.03) --
+	(254.95, 53.49) --
+	(253.02, 53.98) --
+	(251.96, 54.26) --
+	(251.08, 54.49) --
+	(249.14, 55.03) --
+	(247.20, 55.59) --
+	(245.27, 56.19) --
+	(243.92, 56.62) --
+	(243.33, 56.81) --
+	(241.39, 57.47) --
+	(239.46, 58.16) --
+	(237.52, 58.89) --
+	(237.32, 58.97) --
+	(235.58, 59.67) --
+	(233.65, 60.49) --
+	(231.79, 61.33) --
+	(231.71, 61.37) --
+	(229.77, 62.30) --
+	(227.84, 63.29) --
+	(227.09, 63.69) --
+	(225.90, 64.35) --
+	(223.96, 65.48) --
+	(223.05, 66.05) --
+	(222.03, 66.70) --
+	(220.09, 68.01) --
+	(219.54, 68.40) --
+	(218.15, 69.42) --
+	(216.45, 70.76) --
+	(216.22, 70.95) --
+	(214.28, 72.61) --
+	(213.71, 73.12) --
+	(212.34, 74.41) --
+	(211.28, 75.48) --
+	(210.41, 76.38) --
+	(209.09, 77.83) --
+	(208.47, 78.55) --
+	(207.11, 80.19) --
+	(206.53, 80.93) --
+	(205.32, 82.55) --
+	(204.59, 83.57) --
+	(203.69, 84.91) --
+	(202.66, 86.52) --
+	(202.20, 87.26) --
+	(200.83, 89.62) --
+	(200.72, 89.81) --
+	(199.56, 91.98) --
+	(198.78, 93.53) --
+	(198.39, 94.33) --
+	(197.31, 96.69) --
+	(196.85, 97.75) --
+	(196.30, 99.05) --
+	(195.36,101.41) --
+	(194.91,102.60) --
+	(194.48,103.76) --
+	(193.66,106.12) --
+	(192.97,108.21) --
+	(192.89,108.48) --
+	(192.16,110.84) --
+	(191.48,113.19) --
+	(191.04,114.78) --
+	(190.83,115.55) --
+	(190.22,117.91) --
+	(189.64,120.27) --
+	(189.10,122.58) --
+	(189.09,122.62) --
+	(188.57,124.98) --
+	(188.07,127.34) --
+	(187.60,129.70) --
+	(187.16,132.00) --
+	(187.15,132.05) --
+	(186.72,134.41) --
+	(186.31,136.77) --
+	(185.92,139.12) --
+	(185.55,141.48) --
+	(185.23,143.59) --
+	(185.19,143.84) --
+	(184.84,146.20) --
+	(184.51,148.55) --
+	(184.20,150.91) --
+	(183.89,153.27) --
+	(183.60,155.63) --
+	(183.32,157.98) --
+	(183.29,158.20) --
+	(183.04,160.34) --
+	(182.78,162.70) --
+	(182.53,165.06) --
+	(182.28,167.41) --
+	(182.04,169.77) --
+	(181.82,172.13) --
+	(181.60,174.49) --
+	(181.38,176.84) --
+	(181.35,177.19) --
+	(181.18,179.20) --
+	(180.98,181.56) --
+	(180.78,183.91) --
+	(180.59,186.27) --
+	(180.41,188.63) --
+	(180.23,190.99) --
+	(180.06,193.34) --
+	(179.89,195.70) --
+	(179.73,198.06) --
+	(179.57,200.42) --
+	(179.42,202.77) --
+	(179.42,202.85) --
+	(179.27,205.13) --
+	(179.13,207.49) --
+	(178.98,209.85) --
+	(178.85,212.20) --
+	(178.71,214.56) --
+	(178.58,216.92) --
+	(178.45,219.28) --
+	(178.33,221.63) --
+	(178.21,223.99) --
+	(178.09,226.35) --
+	(177.97,228.70) --
+	(177.86,231.06) --
+	(177.75,233.42) --
+	(177.64,235.78) --
+	(177.54,238.13) --
+	(177.48,239.48) --
+	(177.44,240.49) --
+	(177.33,242.85) --
+	(177.24,245.21) --
+	(177.14,247.56) --
+	(177.04,249.92) --
+	(176.95,252.28) --
+	(176.86,254.64) --
+	(176.77,256.99) --
+	(176.69,259.35) --
+	(176.60,261.71) --
+	(176.52,264.07);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41,112.42) --
-	(335.21,113.46) --
-	(333.01,114.54) --
-	(332.16,114.97) --
-	(330.81,115.65) --
-	(328.62,116.79) --
-	(326.96,117.68) --
-	(326.42,117.98) --
-	(324.22,119.20) --
-	(322.14,120.40) --
-	(322.02,120.47) --
-	(319.83,121.78) --
-	(317.66,123.12) --
-	(317.63,123.14) --
-	(315.43,124.54) --
-	(313.48,125.84) --
-	(313.23,126.00) --
-	(311.04,127.51) --
-	(309.56,128.56) --
-	(308.84,129.08) --
-	(306.64,130.71) --
-	(305.89,131.28) --
-	(304.44,132.40) --
-	(302.44,134.00) --
-	(302.25,134.16) --
-	(300.05,135.98) --
-	(299.19,136.72) --
-	(297.85,137.88) --
-	(296.13,139.43) --
-	(295.65,139.87) --
-	(293.46,141.93) --
-	(293.23,142.15) --
-	(291.26,144.09) --
-	(290.48,144.87) --
-	(289.06,146.34) --
-	(287.88,147.59) --
-	(286.86,148.69) --
-	(285.41,150.31) --
-	(284.67,151.15) --
-	(283.06,153.03) --
-	(282.47,153.73) --
-	(280.82,155.75) --
-	(280.27,156.43) --
-	(278.68,158.47) --
-	(278.07,159.26) --
-	(276.64,161.18) --
-	(275.88,162.23) --
-	(274.69,163.90) --
-	(273.68,165.36) --
-	(272.83,166.62) --
-	(271.48,168.66) --
-	(271.04,169.34) --
-	(269.33,172.06) --
-	(269.28,172.13) --
-	(267.68,174.78) --
-	(267.09,175.79) --
-	(266.10,177.50) --
-	(264.89,179.67) --
-	(264.59,180.22) --
-	(263.13,182.93) --
-	(262.69,183.77) --
-	(261.72,185.65) --
-	(260.49,188.11) --
-	(260.37,188.37) --
-	(259.06,191.09) --
-	(258.30,192.73) --
-	(257.80,193.81) --
-	(256.59,196.53) --
-	(256.10,197.64) --
-	(255.41,199.25) --
-	(254.28,201.97) --
-	(253.90,202.88) --
-	(253.18,204.68) --
-	(252.12,207.40) --
-	(251.70,208.48) --
-	(251.09,210.12) --
-	(250.09,212.84) --
-	(249.51,214.47) --
-	(249.12,215.56) --
-	(248.18,218.28) --
-	(247.31,220.90) --
-	(247.28,221.00) --
-	(246.39,223.71) --
-	(245.54,226.43) --
-	(245.11,227.81) --
-	(244.70,229.15) --
-	(243.89,231.87) --
-	(243.11,234.59) --
-	(242.92,235.26) --
-	(242.34,237.31) --
-	(241.59,240.03) --
-	(240.87,242.75) --
-	(240.72,243.33) --
-	(240.16,245.46) --
-	(239.47,248.18) --
-	(238.81,250.90) --
-	(238.52,252.08) --
-	(238.15,253.62) --
-	(237.51,256.34) --
-	(236.89,259.06) --
-	(236.32,261.61) --
-	(236.29,261.78) --
-	(235.69,264.50) --
-	(235.11,267.21) --
-	(234.55,269.93) --
-	(234.13,272.03) --
-	(234.00,272.65) --
-	(233.46,275.37) --
-	(232.93,278.09) --
-	(232.42,280.81) --
-	(231.93,283.46) --
-	(231.92,283.53) --
-	(231.42,286.25) --
-	(230.94,288.96) --
-	(230.46,291.68) --
-	(230.00,294.40) --
-	(229.73,296.05) --
-	(229.55,297.12) --
-	(229.11,299.84);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (301.44,101.56) --
+	(299.50,102.46) --
+	(297.56,103.39) --
+	(296.81,103.76) --
+	(295.62,104.35) --
+	(293.69,105.35) --
+	(292.23,106.12) --
+	(291.75,106.38) --
+	(289.81,107.44) --
+	(287.98,108.48) --
+	(287.88,108.54) --
+	(285.94,109.67) --
+	(284.03,110.84) --
+	(284.00,110.85) --
+	(282.07,112.07) --
+	(280.34,113.19) --
+	(280.13,113.34) --
+	(278.19,114.64) --
+	(276.90,115.55) --
+	(276.26,116.00) --
+	(274.32,117.41) --
+	(273.66,117.91) --
+	(272.38,118.88) --
+	(270.62,120.27) --
+	(270.45,120.40) --
+	(268.51,121.99) --
+	(267.76,122.62) --
+	(266.57,123.64) --
+	(265.05,124.98) --
+	(264.64,125.36) --
+	(262.70,127.15) --
+	(262.50,127.34) --
+	(260.76,129.02) --
+	(260.08,129.70) --
+	(258.83,130.97) --
+	(257.79,132.05) --
+	(256.89,133.01) --
+	(255.61,134.41) --
+	(254.95,135.14) --
+	(253.53,136.77) --
+	(253.02,137.37) --
+	(251.56,139.12) --
+	(251.08,139.71) --
+	(249.68,141.48) --
+	(249.14,142.17) --
+	(247.88,143.84) --
+	(247.20,144.75) --
+	(246.16,146.20) --
+	(245.27,147.46) --
+	(244.52,148.55) --
+	(243.33,150.32) --
+	(242.94,150.91) --
+	(241.43,153.27) --
+	(241.39,153.33) --
+	(239.98,155.63) --
+	(239.46,156.51) --
+	(238.59,157.98) --
+	(237.52,159.86) --
+	(237.25,160.34) --
+	(235.97,162.70) --
+	(235.58,163.42) --
+	(234.73,165.06) --
+	(233.65,167.19) --
+	(233.54,167.41) --
+	(232.38,169.77) --
+	(231.71,171.19) --
+	(231.27,172.13) --
+	(230.20,174.49) --
+	(229.77,175.45) --
+	(229.17,176.84) --
+	(228.17,179.20) --
+	(227.84,180.00) --
+	(227.20,181.56) --
+	(226.26,183.91) --
+	(225.90,184.85) --
+	(225.35,186.27) --
+	(224.47,188.63) --
+	(223.96,190.04) --
+	(223.62,190.99) --
+	(222.80,193.34) --
+	(222.03,195.61) --
+	(222.00,195.70) --
+	(221.22,198.06) --
+	(220.46,200.42) --
+	(220.09,201.61) --
+	(219.73,202.77) --
+	(219.01,205.13) --
+	(218.32,207.49) --
+	(218.15,208.07) --
+	(217.65,209.85) --
+	(216.99,212.20) --
+	(216.35,214.56) --
+	(216.22,215.07) --
+	(215.73,216.92) --
+	(215.12,219.28) --
+	(214.53,221.63) --
+	(214.28,222.66) --
+	(213.95,223.99) --
+	(213.39,226.35) --
+	(212.84,228.70) --
+	(212.34,230.92) --
+	(212.31,231.06) --
+	(211.79,233.42) --
+	(211.28,235.78) --
+	(210.78,238.13) --
+	(210.41,239.95) --
+	(210.29,240.49) --
+	(209.82,242.85) --
+	(209.35,245.21) --
+	(208.90,247.56) --
+	(208.47,249.86) --
+	(208.46,249.92) --
+	(208.02,252.28) --
+	(207.59,254.64) --
+	(207.18,256.99) --
+	(206.77,259.35) --
+	(206.53,260.78) --
+	(206.38,261.71) --
+	(205.98,264.07);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41,163.53) --
-	(336.92,163.90) --
-	(335.21,165.22) --
-	(333.45,166.62) --
-	(333.01,166.97) --
-	(330.81,168.77) --
-	(330.14,169.34) --
-	(328.62,170.64) --
-	(326.99,172.06) --
-	(326.42,172.57) --
-	(324.22,174.56) --
-	(323.98,174.78) --
-	(322.02,176.61) --
-	(321.11,177.50) --
-	(319.83,178.75) --
-	(318.36,180.22) --
-	(317.63,180.95) --
-	(315.72,182.93) --
-	(315.43,183.24) --
-	(313.23,185.61) --
-	(313.19,185.65) --
-	(311.04,188.06) --
-	(310.77,188.37) --
-	(308.84,190.61) --
-	(308.43,191.09) --
-	(306.64,193.25) --
-	(306.19,193.81) --
-	(304.44,196.00) --
-	(304.03,196.53) --
-	(302.25,198.86) --
-	(301.95,199.25) --
-	(300.05,201.83) --
-	(299.95,201.97) --
-	(298.02,204.68) --
-	(297.85,204.92) --
-	(296.15,207.40) --
-	(295.65,208.14) --
-	(294.35,210.12) --
-	(293.46,211.50) --
-	(292.60,212.84) --
-	(291.26,215.00) --
-	(290.92,215.56) --
-	(289.29,218.28) --
-	(289.06,218.66) --
-	(287.71,221.00) --
-	(286.86,222.48) --
-	(286.17,223.71) --
-	(284.69,226.43) --
-	(284.67,226.48) --
-	(283.25,229.15) --
-	(282.47,230.67) --
-	(281.85,231.87) --
-	(280.50,234.59) --
-	(280.27,235.05) --
-	(279.18,237.31) --
-	(278.07,239.66) --
-	(277.90,240.03) --
-	(276.66,242.75) --
-	(275.88,244.49) --
-	(275.45,245.46) --
-	(274.27,248.18) --
-	(273.68,249.58) --
-	(273.12,250.90) --
-	(272.01,253.62) --
-	(271.48,254.93) --
-	(270.92,256.34) --
-	(269.86,259.06) --
-	(269.28,260.57) --
-	(268.83,261.78) --
-	(267.82,264.50) --
-	(267.09,266.53) --
-	(266.84,267.21) --
-	(265.88,269.93) --
-	(264.95,272.65) --
-	(264.89,272.82) --
-	(264.03,275.37) --
-	(263.14,278.09) --
-	(262.69,279.49) --
-	(262.27,280.81) --
-	(261.42,283.53) --
-	(260.59,286.25) --
-	(260.49,286.55) --
-	(259.77,288.96) --
-	(258.98,291.68) --
-	(258.30,294.06) --
-	(258.20,294.40) --
-	(257.44,297.12) --
-	(256.69,299.84);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (301.44,145.87) --
+	(301.00,146.20) --
+	(299.50,147.34) --
+	(297.94,148.55) --
+	(297.56,148.86) --
+	(295.62,150.42) --
+	(295.03,150.91) --
+	(293.69,152.04) --
+	(292.26,153.27) --
+	(291.75,153.71) --
+	(289.81,155.44) --
+	(289.60,155.63) --
+	(287.88,157.22) --
+	(287.07,157.98) --
+	(285.94,159.07) --
+	(284.64,160.34) --
+	(284.00,160.98) --
+	(282.32,162.70) --
+	(282.07,162.96) --
+	(280.13,165.02) --
+	(280.09,165.06) --
+	(278.19,167.14) --
+	(277.95,167.41) --
+	(276.26,169.35) --
+	(275.90,169.77) --
+	(274.32,171.65) --
+	(273.92,172.13) --
+	(272.38,174.03) --
+	(272.02,174.49) --
+	(270.45,176.51) --
+	(270.19,176.84) --
+	(268.51,179.08) --
+	(268.42,179.20) --
+	(266.72,181.56) --
+	(266.57,181.76) --
+	(265.07,183.91) --
+	(264.64,184.55) --
+	(263.48,186.27) --
+	(262.70,187.46) --
+	(261.95,188.63) --
+	(260.76,190.50) --
+	(260.46,190.99) --
+	(259.02,193.34) --
+	(258.83,193.68) --
+	(257.63,195.70) --
+	(256.89,196.99) --
+	(256.28,198.06) --
+	(254.97,200.42) --
+	(254.95,200.46) --
+	(253.70,202.77) --
+	(253.02,204.09) --
+	(252.47,205.13) --
+	(251.28,207.49) --
+	(251.08,207.89) --
+	(250.12,209.85) --
+	(249.14,211.88) --
+	(248.99,212.20) --
+	(247.89,214.56) --
+	(247.20,216.07) --
+	(246.83,216.92) --
+	(245.79,219.28) --
+	(245.27,220.48) --
+	(244.78,221.63) --
+	(243.79,223.99) --
+	(243.33,225.12) --
+	(242.84,226.35) --
+	(241.90,228.70) --
+	(241.39,230.02) --
+	(240.99,231.06) --
+	(240.10,233.42) --
+	(239.46,235.18) --
+	(239.24,235.78) --
+	(238.39,238.13) --
+	(237.57,240.49) --
+	(237.52,240.64) --
+	(236.76,242.85) --
+	(235.98,245.21) --
+	(235.58,246.42) --
+	(235.21,247.56) --
+	(234.46,249.92) --
+	(233.73,252.28) --
+	(233.65,252.55) --
+	(233.01,254.64) --
+	(232.31,256.99) --
+	(231.71,259.05) --
+	(231.62,259.35) --
+	(230.95,261.71) --
+	(230.29,264.07);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41,205.34) --
-	(335.37,207.40) --
-	(335.21,207.57) --
-	(333.01,209.87) --
-	(332.78,210.12) --
-	(330.81,212.24) --
-	(330.27,212.84) --
-	(328.62,214.69) --
-	(327.86,215.56) --
-	(326.42,217.22) --
-	(325.53,218.28) --
-	(324.22,219.84) --
-	(323.28,221.00) --
-	(322.02,222.55) --
-	(321.10,223.71) --
-	(319.83,225.35) --
-	(319.00,226.43) --
-	(317.63,228.25) --
-	(316.96,229.15) --
-	(315.43,231.26) --
-	(314.99,231.87) --
-	(313.23,234.37) --
-	(313.08,234.59) --
-	(311.23,237.31) --
-	(311.04,237.60) --
-	(309.44,240.03) --
-	(308.84,240.95) --
-	(307.69,242.75) --
-	(306.64,244.43) --
-	(306.00,245.46) --
-	(304.44,248.04) --
-	(304.36,248.18) --
-	(302.76,250.90) --
-	(302.25,251.79) --
-	(301.21,253.62) --
-	(300.05,255.70) --
-	(299.70,256.34) --
-	(298.23,259.06) --
-	(297.85,259.76) --
-	(296.79,261.78) --
-	(295.65,264.00) --
-	(295.40,264.50) --
-	(294.04,267.21) --
-	(293.46,268.41) --
-	(292.72,269.93) --
-	(291.43,272.65) --
-	(291.26,273.02) --
-	(290.17,275.37) --
-	(289.06,277.83) --
-	(288.95,278.09) --
-	(287.75,280.81) --
-	(286.86,282.85) --
-	(286.58,283.53) --
-	(285.43,286.25) --
-	(284.67,288.11) --
-	(284.32,288.96) --
-	(283.23,291.68) --
-	(282.47,293.62) --
-	(282.16,294.40) --
-	(281.12,297.12) --
-	(280.27,299.39) --
-	(280.10,299.84);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (301.44,182.13) --
+	(299.64,183.91) --
+	(299.50,184.06) --
+	(297.56,186.05) --
+	(297.35,186.27) --
+	(295.62,188.11) --
+	(295.15,188.63) --
+	(293.69,190.24) --
+	(293.02,190.99) --
+	(291.75,192.43) --
+	(290.97,193.34) --
+	(289.81,194.70) --
+	(288.98,195.70) --
+	(287.88,197.05) --
+	(287.07,198.06) --
+	(285.94,199.48) --
+	(285.21,200.42) --
+	(284.00,201.99) --
+	(283.42,202.77) --
+	(282.07,204.60) --
+	(281.68,205.13) --
+	(280.13,207.30) --
+	(280.00,207.49) --
+	(278.37,209.85) --
+	(278.19,210.10) --
+	(276.78,212.20) --
+	(276.26,213.00) --
+	(275.25,214.56) --
+	(274.32,216.02) --
+	(273.76,216.92) --
+	(272.38,219.15) --
+	(272.31,219.28) --
+	(270.90,221.63) --
+	(270.45,222.41) --
+	(269.53,223.99) --
+	(268.51,225.79) --
+	(268.20,226.35) --
+	(266.90,228.70) --
+	(266.57,229.32) --
+	(265.64,231.06) --
+	(264.64,232.99) --
+	(264.41,233.42) --
+	(263.22,235.78) --
+	(262.70,236.82) --
+	(262.05,238.13) --
+	(260.91,240.49) --
+	(260.76,240.81) --
+	(259.80,242.85) --
+	(258.83,244.98) --
+	(258.72,245.21) --
+	(257.66,247.56) --
+	(256.89,249.34) --
+	(256.64,249.92) --
+	(255.63,252.28) --
+	(254.95,253.90) --
+	(254.65,254.64) --
+	(253.68,256.99) --
+	(253.02,258.67) --
+	(252.75,259.35) --
+	(251.83,261.71) --
+	(251.08,263.67) --
+	(250.93,264.07);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41,240.19) --
-	(335.30,242.75) --
-	(335.21,242.86) --
-	(333.13,245.46) --
-	(333.01,245.62) --
-	(331.03,248.18) --
-	(330.81,248.47) --
-	(328.99,250.90) --
-	(328.62,251.41) --
-	(327.01,253.62) --
-	(326.42,254.44) --
-	(325.08,256.34) --
-	(324.22,257.58) --
-	(323.21,259.06) --
-	(322.02,260.83) --
-	(321.40,261.78) --
-	(319.83,264.19) --
-	(319.63,264.50) --
-	(317.91,267.21) --
-	(317.63,267.67) --
-	(316.24,269.93) --
-	(315.43,271.27) --
-	(314.61,272.65) --
-	(313.23,275.01) --
-	(313.03,275.37) --
-	(311.48,278.09) --
-	(311.04,278.88) --
-	(309.97,280.81) --
-	(308.84,282.90) --
-	(308.50,283.53) --
-	(307.07,286.25) --
-	(306.64,287.07) --
-	(305.67,288.96) --
-	(304.44,291.40) --
-	(304.31,291.68) --
-	(302.97,294.40) --
-	(302.25,295.91) --
-	(301.67,297.12) --
-	(300.40,299.84);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (301.44,212.35) --
+	(299.58,214.56) --
+	(299.50,214.66) --
+	(297.67,216.92) --
+	(297.56,217.05) --
+	(295.82,219.28) --
+	(295.62,219.52) --
+	(294.02,221.63) --
+	(293.69,222.07) --
+	(292.27,223.99) --
+	(291.75,224.70) --
+	(290.57,226.35) --
+	(289.81,227.43) --
+	(288.93,228.70) --
+	(287.88,230.24) --
+	(287.33,231.06) --
+	(285.94,233.16) --
+	(285.77,233.42) --
+	(284.25,235.78) --
+	(284.00,236.17) --
+	(282.78,238.13) --
+	(282.07,239.30) --
+	(281.34,240.49) --
+	(280.13,242.54) --
+	(279.95,242.85) --
+	(278.58,245.21) --
+	(278.19,245.89) --
+	(277.25,247.56) --
+	(276.26,249.38) --
+	(275.96,249.92) --
+	(274.70,252.28) --
+	(274.32,252.99) --
+	(273.46,254.64) --
+	(272.38,256.75) --
+	(272.26,256.99) --
+	(271.08,259.35) --
+	(270.45,260.66) --
+	(269.94,261.71) --
+	(268.81,264.07);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41,269.68) --
-	(337.22,269.93) --
-	(335.26,272.65) --
-	(335.21,272.73) --
-	(333.36,275.37) --
-	(333.01,275.87) --
-	(331.50,278.09) --
-	(330.81,279.11) --
-	(329.69,280.81) --
-	(328.62,282.47) --
-	(327.94,283.53) --
-	(326.42,285.94) --
-	(326.23,286.25) --
-	(324.56,288.96) --
-	(324.22,289.52) --
-	(322.93,291.68) --
-	(322.02,293.22) --
-	(321.34,294.40) --
-	(319.83,297.06) --
-	(319.79,297.12) --
-	(318.28,299.84);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (301.44,237.91) --
+	(301.27,238.13) --
+	(299.54,240.49) --
+	(299.50,240.56) --
+	(297.86,242.85) --
+	(297.56,243.28) --
+	(296.23,245.21) --
+	(295.62,246.10) --
+	(294.64,247.56) --
+	(293.69,249.00) --
+	(293.09,249.92) --
+	(291.75,252.01) --
+	(291.58,252.28) --
+	(290.11,254.64) --
+	(289.81,255.12) --
+	(288.67,256.99) --
+	(287.88,258.33) --
+	(287.27,259.35) --
+	(285.94,261.65) --
+	(285.91,261.71) --
+	(284.57,264.07);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41,294.95) --
-	(335.98,297.12) --
-	(335.21,298.32) --
-	(334.24,299.84);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (301.44,259.83) --
+	(300.18,261.71) --
+	(299.50,262.75) --
+	(298.64,264.07);
 
-\path[draw=drawColor,line width= 0.9pt,dash pattern=on 4pt off 4pt ,line join=round] (186.47, 30.69) -- (186.47,302.56);
+\path[draw=drawColor,line width= 0.9pt,dash pattern=on 4pt off 4pt ,line join=round] (168.41, 30.69) -- (168.41,266.42);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (262.63, 35.04) {underestimated};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (164.30, 56.62) {$\mathcal{R}_0=2.5$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (110.31, 35.04) {overestimated};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (235.53, 33.96) {underestimated};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (101.28, 33.96) {overestimated};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 52.62,148.55) circle (  4.64);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 59.53,135.32) {$\mathcal{R}_0=2.0$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (282.25,155.77) --
+	(288.50,144.95) --
+	(276.00,144.95) --
+	cycle;
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (280.08,135.32) {$\mathcal{R}_0=3.1$};
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.16, 30.69) rectangle (338.79,302.56);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.16, 30.69) rectangle (302.65,266.42);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{drawColor}{gray}{0.30}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21, 54.84) {0.1};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21, 51.23) {0.1};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21, 82.03) {0.2};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21, 74.80) {0.2};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,109.22) {0.3};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21, 98.38) {0.3};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,136.40) {0.4};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,121.95) {0.4};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,163.59) {0.5};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,145.52) {0.5};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,190.78) {0.6};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,169.10) {0.6};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,217.97) {0.7};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,192.67) {0.7};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,245.15) {0.8};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,216.25) {0.8};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,272.34) {0.9};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,239.82) {0.9};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,299.53) {1.0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,263.39) {1.0};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41, 57.87) --
-	( 34.16, 57.87);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41, 54.26) --
+	( 34.16, 54.26);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41, 85.06) --
-	( 34.16, 85.06);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41, 77.83) --
+	( 34.16, 77.83);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,112.25) --
-	( 34.16,112.25);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,101.41) --
+	( 34.16,101.41);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,139.43) --
-	( 34.16,139.43);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,124.98) --
+	( 34.16,124.98);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,166.62) --
-	( 34.16,166.62);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,148.55) --
+	( 34.16,148.55);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,193.81) --
-	( 34.16,193.81);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,172.13) --
+	( 34.16,172.13);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,221.00) --
-	( 34.16,221.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,195.70) --
+	( 34.16,195.70);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,248.18) --
-	( 34.16,248.18);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,219.28) --
+	( 34.16,219.28);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,275.37) --
-	( 34.16,275.37);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,242.85) --
+	( 34.16,242.85);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,302.56) --
-	( 34.16,302.56);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,266.42) --
+	( 34.16,266.42);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (186.47, 27.94) --
-	(186.47, 30.69);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (168.41, 27.94) --
+	(168.41, 30.69);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (338.79, 27.94) --
-	(338.79, 30.69);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (302.65, 27.94) --
+	(302.65, 30.69);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{drawColor}{gray}{0.30}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (186.47, 19.68) {1.0};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (168.41, 19.68) {1.0};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (338.79, 19.68) {2.0};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (302.65, 19.68) {2.0};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (186.47,  7.64) {Relative mean asymptomatic generation interval, $G_a/G_s$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (168.41,  7.64) {Relative mean asymptomatic generation interval, $G_a/G_s$};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,166.62) {Intrinsic proportion of asymptomatic transmission, $z$};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,148.55) {Intrinsic proportion of asymptomatic transmission, $z$};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (349.79, 25.48) rectangle (391.98,307.77);
+\path[fill=fillColor] (313.65, 28.75) rectangle (355.85,268.36);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
-\node[inner sep=0pt,outer sep=0pt,anchor=south west,rotate=  0.00] at (355.29,  30.98) {
-	\pgfimage[width= 14.45pt,height=256.07pt,interpolate=true]{figheatmap_R0_ras2}};
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
+\node[inner sep=0pt,outer sep=0pt,anchor=south west,rotate=  0.00] at (319.15,  34.25) {
+	\pgfimage[width= 14.45pt,height=213.40pt,interpolate=true]{figheatmap_R0_ras2}};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (375.24, 34.35) {1.5};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (339.11, 36.55) {1.5};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (375.24, 88.41) {2.5};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (339.11, 81.60) {2.5};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (375.24,142.47) {3.5};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (339.11,126.65) {3.5};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (375.24,196.53) {4.5};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (339.11,171.70) {4.5};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (375.24,250.59) {5.5};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (339.11,216.75) {5.5};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (355.29,293.62) {$\mathcal{R}_0$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (319.15,254.21) {$\mathcal{R}_0$};
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{drawColor}{RGB}{255,255,255}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] (355.29, 37.38) -- (358.18, 37.38);
+\path[draw=drawColor,line width= 0.2pt,line join=round] (319.15, 39.58) -- (322.05, 39.58);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] (355.29, 91.44) -- (358.18, 91.44);
+\path[draw=drawColor,line width= 0.2pt,line join=round] (319.15, 84.63) -- (322.05, 84.63);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] (355.29,145.50) -- (358.18,145.50);
+\path[draw=drawColor,line width= 0.2pt,line join=round] (319.15,129.68) -- (322.05,129.68);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] (355.29,199.56) -- (358.18,199.56);
+\path[draw=drawColor,line width= 0.2pt,line join=round] (319.15,174.73) -- (322.05,174.73);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] (355.29,253.62) -- (358.18,253.62);
+\path[draw=drawColor,line width= 0.2pt,line join=round] (319.15,219.78) -- (322.05,219.78);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] (366.85, 37.38) -- (369.74, 37.38);
+\path[draw=drawColor,line width= 0.2pt,line join=round] (330.72, 39.58) -- (333.61, 39.58);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] (366.85, 91.44) -- (369.74, 91.44);
+\path[draw=drawColor,line width= 0.2pt,line join=round] (330.72, 84.63) -- (333.61, 84.63);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] (366.85,145.50) -- (369.74,145.50);
+\path[draw=drawColor,line width= 0.2pt,line join=round] (330.72,129.68) -- (333.61,129.68);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] (366.85,199.56) -- (369.74,199.56);
+\path[draw=drawColor,line width= 0.2pt,line join=round] (330.72,174.73) -- (333.61,174.73);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] (366.85,253.62) -- (369.74,253.62);
+\path[draw=drawColor,line width= 0.2pt,line join=round] (330.72,219.78) -- (333.61,219.78);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 34.16,310.62) {B. Basic reproduction number};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 34.16,274.49) {B. Basic reproduction number};
 \end{scope}

### 2020-03-09 figheatmap_R0_03.tex
new figures!!!!!!

@@
-% Created by tikzDevice version 0.12.3 on 2020-03-09 11:51:45
+% Created by tikzDevice version 0.12.3 on 2020-03-09 13:22:38
 % !TEX encoding = UTF-8 Unicode
@@
 \definecolor{fillColor}{RGB}{255,255,255}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (397.48,325.21);
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (361.35,289.08);
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (397.48,325.21);
-\end{scope}
-\begin{scope}
-\path[clip] ( 34.16, 30.69) rectangle (338.79,302.56);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (361.35,289.08);
+\end{scope}
+\begin{scope}
+\path[clip] ( 34.16, 30.69) rectangle (302.65,266.42);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 34.16, 30.69) rectangle (338.79,302.56);
+\path[fill=fillColor] ( 34.16, 30.69) rectangle (302.65,266.42);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 44.28) --
-	(338.79, 44.28);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 71.47) --
-	(338.79, 71.47);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 98.65) --
-	(338.79, 98.65);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,125.84) --
-	(338.79,125.84);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,153.03) --
-	(338.79,153.03);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,180.22) --
-	(338.79,180.22);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,207.40) --
-	(338.79,207.40);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,234.59) --
-	(338.79,234.59);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,261.78) --
-	(338.79,261.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,288.96) --
-	(338.79,288.96);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (110.31, 30.69) --
-	(110.31,302.56);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (262.63, 30.69) --
-	(262.63,302.56);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 42.47) --
+	(302.65, 42.47);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 66.05) --
+	(302.65, 66.05);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 89.62) --
+	(302.65, 89.62);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,113.19) --
+	(302.65,113.19);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,136.77) --
+	(302.65,136.77);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,160.34) --
+	(302.65,160.34);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,183.91) --
+	(302.65,183.91);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,207.49) --
+	(302.65,207.49);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,231.06) --
+	(302.65,231.06);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,254.64) --
+	(302.65,254.64);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (101.28, 30.69) --
+	(101.28,266.42);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (235.53, 30.69) --
+	(235.53,266.42);
 
 \path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 30.69) --
-	(338.79, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 57.87) --
-	(338.79, 57.87);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 85.06) --
-	(338.79, 85.06);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,112.25) --
-	(338.79,112.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,139.43) --
-	(338.79,139.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,166.62) --
-	(338.79,166.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,193.81) --
-	(338.79,193.81);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,221.00) --
-	(338.79,221.00);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,248.18) --
-	(338.79,248.18);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,275.37) --
-	(338.79,275.37);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,302.56) --
-	(338.79,302.56);
+	(302.65, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 54.26) --
+	(302.65, 54.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 77.83) --
+	(302.65, 77.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,101.41) --
+	(302.65,101.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,124.98) --
+	(302.65,124.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,148.55) --
+	(302.65,148.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,172.13) --
+	(302.65,172.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,195.70) --
+	(302.65,195.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,219.28) --
+	(302.65,219.28);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,242.85) --
+	(302.65,242.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,266.42) --
+	(302.65,266.42);
 
 \path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 30.69) --
-	( 34.16,302.56);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (186.47, 30.69) --
-	(186.47,302.56);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (338.79, 30.69) --
-	(338.79,302.56);
-\node[inner sep=0pt,outer sep=0pt,anchor=south west,rotate=  0.00] at ( 35.25,  32.72) {
-	\pgfimage[width=303.25pt,height=267.79pt,interpolate=false]{figheatmap_R0_03_ras1}};
+	( 34.16,266.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (168.41, 30.69) --
+	(168.41,266.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (302.65, 30.69) --
+	(302.65,266.42);
+\node[inner sep=0pt,outer sep=0pt,anchor=south west,rotate=  0.00] at ( 35.12,  32.45) {
+	\pgfimage[width=267.28pt,height=232.20pt,interpolate=false]{figheatmap_R0_03_ras1}};
 \definecolor{drawColor}{RGB}{255,255,255}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,189.02) --
-	( 34.89,189.73) --
-	( 36.28,191.09) --
-	( 36.35,191.16) --
-	( 37.64,192.45) --
-	( 38.55,193.38) --
-	( 38.97,193.81) --
-	( 40.28,195.17) --
-	( 40.75,195.66) --
-	( 41.57,196.53) --
-	( 42.83,197.89) --
-	( 42.95,198.01) --
-	( 44.07,199.25) --
-	( 45.14,200.44) --
-	( 45.29,200.61) --
-	( 46.48,201.97) --
-	( 47.34,202.95) --
-	( 47.66,203.32) --
-	( 48.81,204.68) --
-	( 49.54,205.55) --
-	( 49.95,206.04) --
-	( 51.06,207.40) --
-	( 51.74,208.23) --
-	( 52.16,208.76) --
-	( 53.24,210.12) --
-	( 53.93,211.01) --
-	( 54.30,211.48) --
-	( 55.34,212.84) --
-	( 56.13,213.88) --
-	( 56.37,214.20) --
-	( 57.37,215.56) --
-	( 58.33,216.86) --
-	( 58.37,216.92) --
-	( 59.34,218.28) --
-	( 60.31,219.64) --
-	( 60.53,219.95) --
-	( 61.25,221.00) --
-	( 62.19,222.36) --
-	( 62.72,223.14) --
-	( 63.11,223.71) --
-	( 64.01,225.07) --
-	( 64.90,226.43) --
-	( 64.92,226.46) --
-	( 65.78,227.79) --
-	( 66.64,229.15) --
-	( 67.12,229.91) --
-	( 67.49,230.51) --
-	( 68.33,231.87) --
-	( 69.16,233.23) --
-	( 69.32,233.48) --
-	( 69.98,234.59) --
-	( 70.78,235.95) --
-	( 71.51,237.20) --
-	( 71.57,237.31) --
-	( 72.35,238.67) --
-	( 73.12,240.03) --
-	( 73.71,241.07) --
-	( 73.88,241.39) --
-	( 74.63,242.75) --
-	( 75.37,244.11) --
-	( 75.91,245.10) --
-	( 76.10,245.46) --
-	( 76.82,246.82) --
-	( 77.53,248.18) --
-	( 78.11,249.29) --
-	( 78.23,249.54) --
-	( 78.92,250.90) --
-	( 79.60,252.26) --
-	( 80.28,253.62) --
-	( 80.30,253.67) --
-	( 80.94,254.98) --
-	( 81.60,256.34) --
-	( 82.25,257.70) --
-	( 82.50,258.23) --
-	( 82.89,259.06) --
-	( 83.52,260.42) --
-	( 84.14,261.78) --
-	( 84.70,263.00) --
-	( 84.76,263.14) --
-	( 85.37,264.50) --
-	( 85.97,265.86) --
-	( 86.56,267.21) --
-	( 86.90,267.98) --
-	( 87.15,268.57) --
-	( 87.73,269.93) --
-	( 88.30,271.29) --
-	( 88.87,272.65) --
-	( 89.09,273.19) --
-	( 89.43,274.01) --
-	( 89.98,275.37) --
-	( 90.53,276.73) --
-	( 91.07,278.09) --
-	( 91.29,278.65) --
-	( 91.60,279.45) --
-	( 92.13,280.81) --
-	( 92.65,282.17) --
-	( 93.17,283.53) --
-	( 93.49,284.37) --
-	( 93.68,284.89) --
-	( 94.18,286.25) --
-	( 94.68,287.60) --
-	( 95.18,288.96) --
-	( 95.67,290.32) --
-	( 95.69,290.38) --
-	( 96.15,291.68) --
-	( 96.62,293.04) --
-	( 97.10,294.40) --
-	( 97.57,295.76) --
-	( 97.88,296.69) --
-	( 98.03,297.12) --
-	( 98.48,298.48) --
-	( 98.94,299.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 63.05) --
-	( 35.49, 63.31) --
-	( 36.35, 63.48) --
-	( 38.55, 63.94) --
-	( 40.75, 64.40) --
-	( 41.98, 64.67) --
-	( 42.95, 64.88) --
-	( 45.14, 65.38) --
-	( 47.34, 65.89) --
-	( 47.91, 66.03) --
-	( 49.54, 66.42) --
-	( 51.74, 66.97) --
-	( 53.35, 67.39) --
-	( 53.93, 67.54) --
-	( 56.13, 68.13) --
-	( 58.33, 68.74) --
-	( 58.37, 68.75) --
-	( 60.53, 69.37) --
-	( 62.72, 70.02) --
-	( 63.01, 70.11) --
-	( 64.92, 70.70) --
-	( 67.12, 71.40) --
-	( 67.32, 71.47) --
-	( 69.32, 72.13) --
-	( 71.32, 72.83) --
-	( 71.51, 72.89) --
-	( 73.71, 73.68) --
-	( 75.06, 74.19) --
-	( 75.91, 74.51) --
-	( 78.11, 75.36) --
-	( 78.55, 75.54) --
-	( 80.30, 76.26) --
-	( 81.83, 76.90) --
-	( 82.50, 77.19) --
-	( 84.70, 78.17) --
-	( 84.91, 78.26) --
-	( 86.90, 79.18) --
-	( 87.81, 79.62) --
-	( 89.09, 80.25) --
-	( 90.55, 80.98) --
-	( 91.29, 81.36) --
-	( 93.13, 82.34) --
-	( 93.49, 82.53) --
-	( 95.58, 83.70) --
-	( 95.69, 83.76) --
-	( 97.88, 85.05) --
-	( 97.90, 85.06) --
-	(100.08, 86.41) --
-	(100.10, 86.42) --
-	(102.19, 87.78) --
-	(102.28, 87.83) --
-	(104.19, 89.14) --
-	(104.47, 89.34) --
-	(106.08, 90.50) --
-	(106.67, 90.93) --
-	(107.90, 91.86) --
-	(108.87, 92.61) --
-	(109.63, 93.22) --
-	(111.07, 94.40) --
-	(111.28, 94.58) --
-	(112.87, 95.94) --
-	(113.26, 96.29) --
-	(114.38, 97.29) --
-	(115.46, 98.30) --
-	(115.84, 98.65) --
-	(117.24,100.01) --
-	(117.66,100.43) --
-	(118.58,101.37) --
-	(119.86,102.72) --
-	(119.87,102.73) --
-	(121.11,104.09) --
-	(122.05,105.16) --
-	(122.31,105.45) --
-	(123.46,106.81) --
-	(124.25,107.77) --
-	(124.58,108.17) --
-	(125.65,109.53) --
-	(126.45,110.58) --
-	(126.68,110.89) --
-	(127.68,112.25) --
-	(128.65,113.60) --
-	(128.65,113.61) --
-	(129.59,114.97) --
-	(130.50,116.33) --
-	(130.84,116.86) --
-	(131.37,117.68) --
-	(132.22,119.04) --
-	(133.04,120.39) --
-	(133.05,120.40) --
-	(133.85,121.76) --
-	(134.62,123.12) --
-	(135.24,124.23) --
-	(135.38,124.48) --
-	(136.11,125.84) --
-	(136.82,127.20) --
-	(137.44,128.42) --
-	(137.51,128.56) --
-	(138.18,129.92) --
-	(138.83,131.28) --
-	(139.47,132.64) --
-	(139.63,133.00) --
-	(140.09,134.00) --
-	(140.69,135.36) --
-	(141.28,136.72) --
-	(141.83,138.03) --
-	(141.85,138.08) --
-	(142.41,139.43) --
-	(142.95,140.79) --
-	(143.48,142.15) --
-	(144.00,143.51) --
-	(144.03,143.59) --
-	(144.50,144.87) --
-	(145.00,146.23) --
-	(145.48,147.59) --
-	(145.95,148.95) --
-	(146.23,149.76) --
-	(146.41,150.31) --
-	(146.86,151.67) --
-	(147.30,153.03) --
-	(147.73,154.39) --
-	(148.15,155.75) --
-	(148.42,156.65) --
-	(148.56,157.11) --
-	(148.96,158.47) --
-	(149.36,159.83) --
-	(149.74,161.18) --
-	(150.12,162.54) --
-	(150.49,163.90) --
-	(150.62,164.38) --
-	(150.86,165.26) --
-	(151.21,166.62) --
-	(151.56,167.98) --
-	(151.90,169.34) --
-	(152.24,170.70) --
-	(152.57,172.06) --
-	(152.82,173.12) --
-	(152.89,173.42) --
-	(153.20,174.78) --
-	(153.51,176.14) --
-	(153.82,177.50) --
-	(154.12,178.86) --
-	(154.41,180.22) --
-	(154.70,181.57) --
-	(154.98,182.93) --
-	(155.02,183.09) --
-	(155.26,184.29) --
-	(155.53,185.65) --
-	(155.80,187.01) --
-	(156.06,188.37) --
-	(156.32,189.73) --
-	(156.58,191.09) --
-	(156.83,192.45) --
-	(157.08,193.81) --
-	(157.21,194.57) --
-	(157.32,195.17) --
-	(157.56,196.53) --
-	(157.79,197.89) --
-	(158.02,199.25) --
-	(158.25,200.61) --
-	(158.47,201.97) --
-	(158.69,203.32) --
-	(158.91,204.68) --
-	(159.12,206.04) --
-	(159.33,207.40) --
-	(159.41,207.91) --
-	(159.54,208.76) --
-	(159.74,210.12) --
-	(159.94,211.48) --
-	(160.14,212.84) --
-	(160.33,214.20) --
-	(160.53,215.56) --
-	(160.71,216.92) --
-	(160.90,218.28) --
-	(161.09,219.64) --
-	(161.27,221.00) --
-	(161.45,222.36) --
-	(161.61,223.61) --
-	(161.62,223.71) --
-	(161.79,225.07) --
-	(161.96,226.43) --
-	(162.13,227.79) --
-	(162.30,229.15) --
-	(162.46,230.51) --
-	(162.62,231.87) --
-	(162.78,233.23) --
-	(162.94,234.59) --
-	(163.10,235.95) --
-	(163.25,237.31) --
-	(163.40,238.67) --
-	(163.55,240.03) --
-	(163.70,241.39) --
-	(163.81,242.37) --
-	(163.85,242.75) --
-	(163.99,244.11) --
-	(164.13,245.46) --
-	(164.27,246.82) --
-	(164.41,248.18) --
-	(164.54,249.54) --
-	(164.68,250.90) --
-	(164.81,252.26) --
-	(164.94,253.62) --
-	(165.07,254.98) --
-	(165.20,256.34) --
-	(165.33,257.70) --
-	(165.46,259.06) --
-	(165.58,260.42) --
-	(165.70,261.78) --
-	(165.83,263.14) --
-	(165.95,264.50) --
-	(166.00,265.15) --
-	(166.06,265.86) --
-	(166.18,267.21) --
-	(166.30,268.57) --
-	(166.41,269.93) --
-	(166.52,271.29) --
-	(166.63,272.65) --
-	(166.74,274.01) --
-	(166.85,275.37) --
-	(166.96,276.73) --
-	(167.07,278.09) --
-	(167.17,279.45) --
-	(167.28,280.81) --
-	(167.38,282.17) --
-	(167.48,283.53) --
-	(167.59,284.89) --
-	(167.69,286.25) --
-	(167.79,287.60) --
-	(167.88,288.96) --
-	(167.98,290.32) --
-	(168.08,291.68) --
-	(168.17,293.04) --
-	(168.20,293.43) --
-	(168.27,294.40) --
-	(168.36,295.76) --
-	(168.45,297.12) --
-	(168.54,298.48) --
-	(168.63,299.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41, 87.12) --
-	(335.33, 87.78) --
-	(335.21, 87.82) --
-	(333.01, 88.53) --
-	(331.22, 89.14) --
-	(330.81, 89.28) --
-	(328.62, 90.04) --
-	(327.34, 90.50) --
-	(326.42, 90.83) --
-	(324.22, 91.65) --
-	(323.68, 91.86) --
-	(322.02, 92.50) --
-	(320.22, 93.22) --
-	(319.83, 93.38) --
-	(317.63, 94.28) --
-	(316.94, 94.58) --
-	(315.43, 95.23) --
-	(313.83, 95.94) --
-	(313.23, 96.20) --
-	(311.04, 97.22) --
-	(310.87, 97.29) --
-	(308.84, 98.27) --
-	(308.05, 98.65) --
-	(306.64, 99.36) --
-	(305.37,100.01) --
-	(304.44,100.49) --
-	(302.80,101.37) --
-	(302.25,101.67) --
-	(300.35,102.73) --
-	(300.05,102.90) --
-	(298.01,104.09) --
-	(297.85,104.18) --
-	(295.76,105.45) --
-	(295.65,105.52) --
-	(293.61,106.81) --
-	(293.46,106.91) --
-	(291.54,108.17) --
-	(291.26,108.36) --
-	(289.55,109.53) --
-	(289.06,109.87) --
-	(287.64,110.89) --
-	(286.86,111.46) --
-	(285.81,112.25) --
-	(284.67,113.12) --
-	(284.04,113.61) --
-	(282.47,114.85) --
-	(282.33,114.97) --
-	(280.68,116.33) --
-	(280.27,116.67) --
-	(279.10,117.68) --
-	(278.07,118.58) --
-	(277.56,119.04) --
-	(276.08,120.40) --
-	(275.88,120.59) --
-	(274.64,121.76) --
-	(273.68,122.70) --
-	(273.26,123.12) --
-	(271.91,124.48) --
-	(271.48,124.93) --
-	(270.61,125.84) --
-	(269.35,127.20) --
-	(269.28,127.27) --
-	(268.13,128.56) --
-	(267.09,129.75) --
-	(266.94,129.92) --
-	(265.79,131.28) --
-	(264.89,132.37) --
-	(264.67,132.64) --
-	(263.58,134.00) --
-	(262.69,135.14) --
-	(262.52,135.36) --
-	(261.50,136.72) --
-	(260.50,138.08) --
-	(260.49,138.08) --
-	(259.52,139.43) --
-	(258.58,140.79) --
-	(258.30,141.20) --
-	(257.65,142.15) --
-	(256.75,143.51) --
-	(256.10,144.53) --
-	(255.88,144.87) --
-	(255.02,146.23) --
-	(254.19,147.59) --
-	(253.90,148.07) --
-	(253.38,148.95) --
-	(252.58,150.31) --
-	(251.81,151.67) --
-	(251.70,151.86) --
-	(251.05,153.03) --
-	(250.31,154.39) --
-	(249.59,155.75) --
-	(249.51,155.91) --
-	(248.89,157.11) --
-	(248.20,158.47) --
-	(247.52,159.83) --
-	(247.31,160.26) --
-	(246.86,161.18) --
-	(246.22,162.54) --
-	(245.59,163.90) --
-	(245.11,164.94) --
-	(244.97,165.26) --
-	(244.36,166.62) --
-	(243.77,167.98) --
-	(243.19,169.34) --
-	(242.92,169.99) --
-	(242.62,170.70) --
-	(242.06,172.06) --
-	(241.52,173.42) --
-	(240.98,174.78) --
-	(240.72,175.46) --
-	(240.46,176.14) --
-	(239.94,177.50) --
-	(239.43,178.86) --
-	(238.94,180.22) --
-	(238.52,181.39) --
-	(238.45,181.57) --
-	(237.97,182.93) --
-	(237.51,184.29) --
-	(237.05,185.65) --
-	(236.59,187.01) --
-	(236.32,187.84) --
-	(236.15,188.37) --
-	(235.71,189.73) --
-	(235.29,191.09) --
-	(234.86,192.45) --
-	(234.45,193.81) --
-	(234.13,194.90) --
-	(234.05,195.17) --
-	(233.64,196.53) --
-	(233.25,197.89) --
-	(232.86,199.25) --
-	(232.49,200.61) --
-	(232.11,201.97) --
-	(231.93,202.65) --
-	(231.74,203.32) --
-	(231.38,204.68) --
-	(231.02,206.04) --
-	(230.67,207.40) --
-	(230.33,208.76) --
-	(229.99,210.12) --
-	(229.73,211.18) --
-	(229.66,211.48) --
-	(229.33,212.84) --
-	(229.00,214.20) --
-	(228.68,215.56) --
-	(228.37,216.92) --
-	(228.06,218.28) --
-	(227.75,219.64) --
-	(227.53,220.64) --
-	(227.45,221.00) --
-	(227.16,222.36) --
-	(226.86,223.71) --
-	(226.58,225.07) --
-	(226.29,226.43) --
-	(226.01,227.79) --
-	(225.74,229.15) --
-	(225.47,230.51) --
-	(225.34,231.17) --
-	(225.20,231.87) --
-	(224.93,233.23) --
-	(224.67,234.59) --
-	(224.41,235.95) --
-	(224.16,237.31) --
-	(223.91,238.67) --
-	(223.66,240.03) --
-	(223.42,241.39) --
-	(223.18,242.75) --
-	(223.14,242.97) --
-	(222.94,244.11) --
-	(222.70,245.46) --
-	(222.47,246.82) --
-	(222.24,248.18) --
-	(222.02,249.54) --
-	(221.79,250.90) --
-	(221.57,252.26) --
-	(221.36,253.62) --
-	(221.14,254.98) --
-	(220.94,256.29) --
-	(220.93,256.34) --
-	(220.72,257.70) --
-	(220.51,259.06) --
-	(220.31,260.42) --
-	(220.11,261.78) --
-	(219.91,263.14) --
-	(219.71,264.50) --
-	(219.51,265.86) --
-	(219.32,267.21) --
-	(219.13,268.57) --
-	(218.94,269.93) --
-	(218.76,271.29) --
-	(218.74,271.42) --
-	(218.58,272.65) --
-	(218.39,274.01) --
-	(218.21,275.37) --
-	(218.03,276.73) --
-	(217.86,278.09) --
-	(217.68,279.45) --
-	(217.51,280.81) --
-	(217.34,282.17) --
-	(217.17,283.53) --
-	(217.01,284.89) --
-	(216.84,286.25) --
-	(216.68,287.60) --
-	(216.55,288.77) --
-	(216.52,288.96) --
-	(216.36,290.32) --
-	(216.20,291.68) --
-	(216.05,293.04) --
-	(215.89,294.40) --
-	(215.74,295.76) --
-	(215.59,297.12) --
-	(215.44,298.48) --
-	(215.29,299.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41,152.71) --
-	(336.93,153.03) --
-	(335.21,154.21) --
-	(334.95,154.39) --
-	(333.03,155.75) --
-	(333.01,155.76) --
-	(331.16,157.11) --
-	(330.81,157.36) --
-	(329.34,158.47) --
-	(328.62,159.01) --
-	(327.57,159.83) --
-	(326.42,160.73) --
-	(325.84,161.18) --
-	(324.22,162.50) --
-	(324.16,162.54) --
-	(322.53,163.90) --
-	(322.02,164.33) --
-	(320.93,165.26) --
-	(319.83,166.22) --
-	(319.38,166.62) --
-	(317.86,167.98) --
-	(317.63,168.19) --
-	(316.38,169.34) --
-	(315.43,170.22) --
-	(314.93,170.70) --
-	(313.52,172.06) --
-	(313.23,172.34) --
-	(312.14,173.42) --
-	(311.04,174.53) --
-	(310.79,174.78) --
-	(309.47,176.14) --
-	(308.84,176.80) --
-	(308.18,177.50) --
-	(306.92,178.86) --
-	(306.64,179.16) --
-	(305.69,180.22) --
-	(304.48,181.57) --
-	(304.44,181.61) --
-	(303.30,182.93) --
-	(302.25,184.17) --
-	(302.14,184.29) --
-	(301.01,185.65) --
-	(300.05,186.82) --
-	(299.90,187.01) --
-	(298.81,188.37) --
-	(297.85,189.59) --
-	(297.74,189.73) --
-	(296.69,191.09) --
-	(295.67,192.45) --
-	(295.65,192.47) --
-	(294.66,193.81) --
-	(293.68,195.17) --
-	(293.46,195.48) --
-	(292.71,196.53) --
-	(291.76,197.89) --
-	(291.26,198.61) --
-	(290.83,199.25) --
-	(289.91,200.61) --
-	(289.06,201.89) --
-	(289.01,201.97) --
-	(288.13,203.32) --
-	(287.26,204.68) --
-	(286.86,205.32) --
-	(286.41,206.04) --
-	(285.57,207.40) --
-	(284.75,208.76) --
-	(284.67,208.90) --
-	(283.94,210.12) --
-	(283.15,211.48) --
-	(282.47,212.66) --
-	(282.36,212.84) --
-	(281.59,214.20) --
-	(280.84,215.56) --
-	(280.27,216.59) --
-	(280.10,216.92) --
-	(279.36,218.28) --
-	(278.64,219.64) --
-	(278.07,220.73) --
-	(277.93,221.00) --
-	(277.23,222.36) --
-	(276.55,223.71) --
-	(275.88,225.07) --
-	(275.87,225.07) --
-	(275.21,226.43) --
-	(274.55,227.79) --
-	(273.90,229.15) --
-	(273.68,229.63) --
-	(273.27,230.51) --
-	(272.64,231.87) --
-	(272.02,233.23) --
-	(271.48,234.44) --
-	(271.42,234.59) --
-	(270.81,235.95) --
-	(270.22,237.31) --
-	(269.64,238.67) --
-	(269.28,239.51) --
-	(269.07,240.03) --
-	(268.50,241.39) --
-	(267.94,242.75) --
-	(267.39,244.11) --
-	(267.09,244.86) --
-	(266.85,245.46) --
-	(266.31,246.82) --
-	(265.78,248.18) --
-	(265.26,249.54) --
-	(264.89,250.52) --
-	(264.75,250.90) --
-	(264.24,252.26) --
-	(263.73,253.62) --
-	(263.24,254.98) --
-	(262.76,256.34) --
-	(262.69,256.52) --
-	(262.27,257.70) --
-	(261.79,259.06) --
-	(261.33,260.42) --
-	(260.86,261.78) --
-	(260.49,262.87) --
-	(260.41,263.14) --
-	(259.95,264.50) --
-	(259.50,265.86) --
-	(259.06,267.21) --
-	(258.63,268.57) --
-	(258.30,269.63) --
-	(258.20,269.93) --
-	(257.77,271.29) --
-	(257.35,272.65) --
-	(256.94,274.01) --
-	(256.53,275.37) --
-	(256.12,276.73) --
-	(256.10,276.81) --
-	(255.72,278.09) --
-	(255.32,279.45) --
-	(254.93,280.81) --
-	(254.55,282.17) --
-	(254.16,283.53) --
-	(253.90,284.47) --
-	(253.79,284.89) --
-	(253.41,286.25) --
-	(253.04,287.60) --
-	(252.67,288.96) --
-	(252.31,290.32) --
-	(251.96,291.68) --
-	(251.70,292.66) --
-	(251.61,293.04) --
-	(251.25,294.40) --
-	(250.91,295.76) --
-	(250.56,297.12) --
-	(250.23,298.48) --
-	(249.89,299.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41,201.89) --
-	(337.33,201.97) --
-	(335.91,203.32) --
-	(335.21,204.00) --
-	(334.51,204.68) --
-	(333.14,206.04) --
-	(333.01,206.18) --
-	(331.80,207.40) --
-	(330.81,208.42) --
-	(330.49,208.76) --
-	(329.20,210.12) --
-	(328.62,210.74) --
-	(327.93,211.48) --
-	(326.69,212.84) --
-	(326.42,213.15) --
-	(325.48,214.20) --
-	(324.28,215.56) --
-	(324.22,215.63) --
-	(323.11,216.92) --
-	(322.02,218.20) --
-	(321.96,218.28) --
-	(320.83,219.64) --
-	(319.83,220.86) --
-	(319.72,221.00) --
-	(318.62,222.36) --
-	(317.63,223.62) --
-	(317.55,223.71) --
-	(316.50,225.07) --
-	(315.46,226.43) --
-	(315.43,226.47) --
-	(314.44,227.79) --
-	(313.44,229.15) --
-	(313.23,229.43) --
-	(312.45,230.51) --
-	(311.48,231.87) --
-	(311.04,232.51) --
-	(310.53,233.23) --
-	(309.59,234.59) --
-	(308.84,235.70) --
-	(308.67,235.95) --
-	(307.76,237.31) --
-	(306.86,238.67) --
-	(306.64,239.01) --
-	(305.98,240.03) --
-	(305.11,241.39) --
-	(304.44,242.45) --
-	(304.26,242.75) --
-	(303.42,244.11) --
-	(302.59,245.46) --
-	(302.25,246.03) --
-	(301.77,246.82) --
-	(300.97,248.18) --
-	(300.18,249.54) --
-	(300.05,249.76) --
-	(299.39,250.90) --
-	(298.62,252.26) --
-	(297.86,253.62) --
-	(297.85,253.64) --
-	(297.11,254.98) --
-	(296.37,256.34) --
-	(295.65,257.69) --
-	(295.65,257.70) --
-	(294.93,259.06) --
-	(294.22,260.42) --
-	(293.52,261.78) --
-	(293.46,261.90) --
-	(292.83,263.14) --
-	(292.15,264.50) --
-	(291.48,265.86) --
-	(291.26,266.31) --
-	(290.82,267.21) --
-	(290.16,268.57) --
-	(289.52,269.93) --
-	(289.06,270.90) --
-	(288.88,271.29) --
-	(288.25,272.65) --
-	(287.63,274.01) --
-	(287.02,275.37) --
-	(286.86,275.71) --
-	(286.41,276.73) --
-	(285.81,278.09) --
-	(285.22,279.45) --
-	(284.67,280.74) --
-	(284.64,280.81) --
-	(284.06,282.17) --
-	(283.49,283.53) --
-	(282.93,284.89) --
-	(282.47,286.01) --
-	(282.37,286.25) --
-	(281.82,287.60) --
-	(281.28,288.96) --
-	(280.74,290.32) --
-	(280.27,291.53) --
-	(280.21,291.68) --
-	(279.69,293.04) --
-	(279.17,294.40) --
-	(278.66,295.76) --
-	(278.15,297.12) --
-	(278.07,297.33) --
-	(277.65,298.48) --
-	(277.15,299.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41,240.15) --
-	(336.34,241.39) --
-	(335.21,242.73) --
-	(335.19,242.75) --
-	(334.06,244.11) --
-	(333.01,245.39) --
-	(332.95,245.46) --
-	(331.85,246.82) --
-	(330.81,248.14) --
-	(330.78,248.18) --
-	(329.72,249.54) --
-	(328.67,250.90) --
-	(328.62,250.98) --
-	(327.65,252.26) --
-	(326.64,253.62) --
-	(326.42,253.92) --
-	(325.64,254.98) --
-	(324.66,256.34) --
-	(324.22,256.95) --
-	(323.69,257.70) --
-	(322.74,259.06) --
-	(322.02,260.10) --
-	(321.80,260.42) --
-	(320.88,261.78) --
-	(319.97,263.14) --
-	(319.83,263.35) --
-	(319.07,264.50) --
-	(318.19,265.86) --
-	(317.63,266.73) --
-	(317.32,267.21) --
-	(316.45,268.57) --
-	(315.61,269.93) --
-	(315.43,270.22) --
-	(314.77,271.29) --
-	(313.95,272.65) --
-	(313.23,273.85) --
-	(313.14,274.01) --
-	(312.33,275.37) --
-	(311.54,276.73) --
-	(311.04,277.60) --
-	(310.76,278.09) --
-	(309.98,279.45) --
-	(309.23,280.81) --
-	(308.84,281.51) --
-	(308.47,282.17) --
-	(307.73,283.53) --
-	(307.00,284.89) --
-	(306.64,285.56) --
-	(306.28,286.25) --
-	(305.56,287.60) --
-	(304.86,288.96) --
-	(304.44,289.77) --
-	(304.16,290.32) --
-	(303.47,291.68) --
-	(302.79,293.04) --
-	(302.25,294.16) --
-	(302.13,294.40) --
-	(301.46,295.76) --
-	(300.80,297.12) --
-	(300.16,298.48) --
-	(300.05,298.71) --
-	(299.52,299.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41,270.76) --
-	(337.00,271.29) --
-	(335.98,272.65) --
-	(335.21,273.71) --
-	(334.99,274.01) --
-	(334.00,275.37) --
-	(333.03,276.73) --
-	(333.01,276.76) --
-	(332.07,278.09) --
-	(331.13,279.45) --
-	(330.81,279.91) --
-	(330.20,280.81) --
-	(329.28,282.17) --
-	(328.62,283.17) --
-	(328.38,283.53) --
-	(327.48,284.89) --
-	(326.60,286.25) --
-	(326.42,286.53) --
-	(325.73,287.60) --
-	(324.87,288.96) --
-	(324.22,290.02) --
-	(324.03,290.32) --
-	(323.19,291.68) --
-	(322.37,293.04) --
-	(322.02,293.62) --
-	(321.55,294.40) --
-	(320.75,295.76) --
-	(319.96,297.12) --
-	(319.83,297.35) --
-	(319.17,298.48) --
-	(318.40,299.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41,295.80) --
-	(336.50,297.12) --
-	(335.59,298.48) --
-	(335.21,299.06) --
-	(334.69,299.84);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,167.98) --
+	( 34.80,168.59) --
+	( 36.03,169.77) --
+	( 36.09,169.83) --
+	( 37.22,170.95) --
+	( 38.03,171.75) --
+	( 38.40,172.13) --
+	( 39.56,173.31) --
+	( 39.97,173.73) --
+	( 40.69,174.49) --
+	( 41.80,175.66) --
+	( 41.90,175.77) --
+	( 42.89,176.84) --
+	( 43.84,177.88) --
+	( 43.97,178.02) --
+	( 45.02,179.20) --
+	( 45.78,180.06) --
+	( 46.06,180.38) --
+	( 47.07,181.56) --
+	( 47.71,182.31) --
+	( 48.07,182.74) --
+	( 49.06,183.91) --
+	( 49.65,184.64) --
+	( 50.02,185.09) --
+	( 50.97,186.27) --
+	( 51.59,187.04) --
+	( 51.91,187.45) --
+	( 52.83,188.63) --
+	( 53.52,189.54) --
+	( 53.73,189.81) --
+	( 54.62,190.99) --
+	( 55.46,192.12) --
+	( 55.50,192.17) --
+	( 56.36,193.34) --
+	( 57.21,194.52) --
+	( 57.40,194.79) --
+	( 58.04,195.70) --
+	( 58.86,196.88) --
+	( 59.33,197.56) --
+	( 59.67,198.06) --
+	( 60.47,199.24) --
+	( 61.26,200.42) --
+	( 61.27,200.44) --
+	( 62.03,201.60) --
+	( 62.79,202.77) --
+	( 63.21,203.43) --
+	( 63.54,203.95) --
+	( 64.28,205.13) --
+	( 65.01,206.31) --
+	( 65.14,206.53) --
+	( 65.73,207.49) --
+	( 66.43,208.67) --
+	( 67.08,209.75) --
+	( 67.14,209.85) --
+	( 67.82,211.02) --
+	( 68.50,212.20) --
+	( 69.02,213.11) --
+	( 69.17,213.38) --
+	( 69.83,214.56) --
+	( 70.48,215.74) --
+	( 70.96,216.60) --
+	( 71.13,216.92) --
+	( 71.76,218.10) --
+	( 72.38,219.28) --
+	( 72.89,220.24) --
+	( 73.00,220.45) --
+	( 73.61,221.63) --
+	( 74.21,222.81) --
+	( 74.81,223.99) --
+	( 74.83,224.03) --
+	( 75.39,225.17) --
+	( 75.97,226.35) --
+	( 76.54,227.53) --
+	( 76.77,227.99) --
+	( 77.11,228.70) --
+	( 77.66,229.88) --
+	( 78.21,231.06) --
+	( 78.70,232.12) --
+	( 78.76,232.24) --
+	( 79.29,233.42) --
+	( 79.82,234.60) --
+	( 80.35,235.78) --
+	( 80.64,236.44) --
+	( 80.86,236.96) --
+	( 81.37,238.13) --
+	( 81.88,239.31) --
+	( 82.38,240.49) --
+	( 82.58,240.96) --
+	( 82.87,241.67) --
+	( 83.36,242.85) --
+	( 83.84,244.03) --
+	( 84.32,245.21) --
+	( 84.51,245.69) --
+	( 84.79,246.39) --
+	( 85.25,247.56) --
+	( 85.71,248.74) --
+	( 86.17,249.92) --
+	( 86.45,250.65) --
+	( 86.62,251.10) --
+	( 87.06,252.28) --
+	( 87.50,253.46) --
+	( 87.94,254.64) --
+	( 88.37,255.81) --
+	( 88.39,255.86) --
+	( 88.79,256.99) --
+	( 89.21,258.17) --
+	( 89.63,259.35) --
+	( 90.04,260.53) --
+	( 90.32,261.33) --
+	( 90.45,261.71) --
+	( 90.85,262.89) --
+	( 91.25,264.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 58.75) --
+	( 35.33, 58.97) --
+	( 36.09, 59.12) --
+	( 38.03, 59.52) --
+	( 39.97, 59.92) --
+	( 41.05, 60.15) --
+	( 41.90, 60.34) --
+	( 43.84, 60.77) --
+	( 45.78, 61.21) --
+	( 46.28, 61.33) --
+	( 47.71, 61.67) --
+	( 49.65, 62.15) --
+	( 51.08, 62.51) --
+	( 51.59, 62.64) --
+	( 53.52, 63.15) --
+	( 55.46, 63.68) --
+	( 55.50, 63.69) --
+	( 57.40, 64.23) --
+	( 59.33, 64.79) --
+	( 59.59, 64.87) --
+	( 61.27, 65.38) --
+	( 63.21, 65.99) --
+	( 63.38, 66.05) --
+	( 65.14, 66.63) --
+	( 66.91, 67.23) --
+	( 67.08, 67.28) --
+	( 69.02, 67.97) --
+	( 70.21, 68.40) --
+	( 70.96, 68.68) --
+	( 72.89, 69.43) --
+	( 73.29, 69.58) --
+	( 74.83, 70.20) --
+	( 76.18, 70.76) --
+	( 76.77, 71.01) --
+	( 78.70, 71.85) --
+	( 78.89, 71.94) --
+	( 80.64, 72.74) --
+	( 81.45, 73.12) --
+	( 82.58, 73.66) --
+	( 83.86, 74.30) --
+	( 84.51, 74.63) --
+	( 86.14, 75.48) --
+	( 86.45, 75.64) --
+	( 88.29, 76.65) --
+	( 88.39, 76.71) --
+	( 90.32, 77.82) --
+	( 90.34, 77.83) --
+	( 92.26, 79.00) --
+	( 92.28, 79.01) --
+	( 94.12, 80.19) --
+	( 94.20, 80.24) --
+	( 95.88, 81.37) --
+	( 96.13, 81.55) --
+	( 97.55, 82.55) --
+	( 98.07, 82.92) --
+	( 99.15, 83.73) --
+	(100.01, 84.38) --
+	(100.67, 84.91) --
+	(101.94, 85.93) --
+	(102.13, 86.08) --
+	(103.53, 87.26) --
+	(103.88, 87.57) --
+	(104.87, 88.44) --
+	(105.82, 89.31) --
+	(106.15, 89.62) --
+	(107.38, 90.80) --
+	(107.75, 91.16) --
+	(108.57, 91.98) --
+	(109.69, 93.14) --
+	(109.70, 93.16) --
+	(110.80, 94.33) --
+	(111.63, 95.26) --
+	(111.85, 95.51) --
+	(112.87, 96.69) --
+	(113.57, 97.52) --
+	(113.85, 97.87) --
+	(114.80, 99.05) --
+	(115.50, 99.96) --
+	(115.71,100.23) --
+	(116.59,101.41) --
+	(117.44,102.58) --
+	(117.44,102.59) --
+	(118.27,103.76) --
+	(119.07,104.94) --
+	(119.38,105.41) --
+	(119.84,106.12) --
+	(120.59,107.30) --
+	(121.31,108.47) --
+	(121.32,108.48) --
+	(122.02,109.66) --
+	(122.70,110.84) --
+	(123.25,111.80) --
+	(123.37,112.02) --
+	(124.01,113.19) --
+	(124.64,114.37) --
+	(125.19,115.43) --
+	(125.25,115.55) --
+	(125.84,116.73) --
+	(126.41,117.91) --
+	(126.98,119.09) --
+	(127.12,119.40) --
+	(127.52,120.27) --
+	(128.05,121.44) --
+	(128.57,122.62) --
+	(129.06,123.77) --
+	(129.07,123.80) --
+	(129.57,124.98) --
+	(130.04,126.16) --
+	(130.51,127.34) --
+	(130.97,128.52) --
+	(131.00,128.59) --
+	(131.41,129.70) --
+	(131.85,130.87) --
+	(132.27,132.05) --
+	(132.69,133.23) --
+	(132.93,133.93) --
+	(133.10,134.41) --
+	(133.49,135.59) --
+	(133.88,136.77) --
+	(134.26,137.95) --
+	(134.63,139.12) --
+	(134.87,139.90) --
+	(134.99,140.30) --
+	(135.35,141.48) --
+	(135.69,142.66) --
+	(136.03,143.84) --
+	(136.37,145.02) --
+	(136.69,146.20) --
+	(136.81,146.61) --
+	(137.01,147.38) --
+	(137.33,148.55) --
+	(137.63,149.73) --
+	(137.93,150.91) --
+	(138.23,152.09) --
+	(138.52,153.27) --
+	(138.74,154.19) --
+	(138.80,154.45) --
+	(139.08,155.63) --
+	(139.36,156.81) --
+	(139.62,157.98) --
+	(139.89,159.16) --
+	(140.15,160.34) --
+	(140.40,161.52) --
+	(140.65,162.70) --
+	(140.68,162.84) --
+	(140.90,163.88) --
+	(141.14,165.06) --
+	(141.37,166.23) --
+	(141.60,167.41) --
+	(141.83,168.59) --
+	(142.06,169.77) --
+	(142.28,170.95) --
+	(142.50,172.13) --
+	(142.62,172.78) --
+	(142.71,173.31) --
+	(142.92,174.49) --
+	(143.13,175.66) --
+	(143.33,176.84) --
+	(143.53,178.02) --
+	(143.73,179.20) --
+	(143.92,180.38) --
+	(144.11,181.56) --
+	(144.30,182.74) --
+	(144.49,183.91) --
+	(144.55,184.35) --
+	(144.67,185.09) --
+	(144.85,186.27) --
+	(145.02,187.45) --
+	(145.20,188.63) --
+	(145.37,189.81) --
+	(145.54,190.99) --
+	(145.70,192.17) --
+	(145.87,193.34) --
+	(146.03,194.52) --
+	(146.19,195.70) --
+	(146.35,196.88) --
+	(146.49,197.97) --
+	(146.50,198.06) --
+	(146.65,199.24) --
+	(146.80,200.42) --
+	(146.95,201.60) --
+	(147.10,202.77) --
+	(147.24,203.95) --
+	(147.39,205.13) --
+	(147.53,206.31) --
+	(147.66,207.49) --
+	(147.80,208.67) --
+	(147.94,209.85) --
+	(148.07,211.02) --
+	(148.20,212.20) --
+	(148.33,213.38) --
+	(148.43,214.23) --
+	(148.46,214.56) --
+	(148.59,215.74) --
+	(148.71,216.92) --
+	(148.84,218.10) --
+	(148.96,219.28) --
+	(149.08,220.45) --
+	(149.20,221.63) --
+	(149.31,222.81) --
+	(149.43,223.99) --
+	(149.55,225.17) --
+	(149.66,226.35) --
+	(149.77,227.53) --
+	(149.88,228.70) --
+	(149.99,229.88) --
+	(150.10,231.06) --
+	(150.21,232.24) --
+	(150.31,233.42) --
+	(150.36,233.99) --
+	(150.42,234.60) --
+	(150.52,235.78) --
+	(150.62,236.96) --
+	(150.72,238.13) --
+	(150.82,239.31) --
+	(150.92,240.49) --
+	(151.02,241.67) --
+	(151.11,242.85) --
+	(151.21,244.03) --
+	(151.30,245.21) --
+	(151.39,246.39) --
+	(151.49,247.56) --
+	(151.58,248.74) --
+	(151.67,249.92) --
+	(151.76,251.10) --
+	(151.85,252.28) --
+	(151.93,253.46) --
+	(152.02,254.64) --
+	(152.11,255.81) --
+	(152.19,256.99) --
+	(152.28,258.17) --
+	(152.30,258.51) --
+	(152.36,259.35) --
+	(152.44,260.53) --
+	(152.52,261.71) --
+	(152.60,262.89) --
+	(152.68,264.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (301.44, 79.62) --
+	(299.61, 80.19) --
+	(299.50, 80.22) --
+	(297.56, 80.85) --
+	(295.98, 81.37) --
+	(295.62, 81.49) --
+	(293.69, 82.15) --
+	(292.56, 82.55) --
+	(291.75, 82.84) --
+	(289.81, 83.55) --
+	(289.34, 83.73) --
+	(287.88, 84.28) --
+	(286.29, 84.91) --
+	(285.94, 85.04) --
+	(284.00, 85.83) --
+	(283.40, 86.08) --
+	(282.07, 86.65) --
+	(280.65, 87.26) --
+	(280.13, 87.49) --
+	(278.19, 88.37) --
+	(278.05, 88.44) --
+	(276.26, 89.28) --
+	(275.56, 89.62) --
+	(274.32, 90.23) --
+	(273.20, 90.80) --
+	(272.38, 91.22) --
+	(270.94, 91.98) --
+	(270.45, 92.24) --
+	(268.78, 93.16) --
+	(268.51, 93.30) --
+	(266.71, 94.33) --
+	(266.57, 94.41) --
+	(264.73, 95.51) --
+	(264.64, 95.57) --
+	(262.83, 96.69) --
+	(262.70, 96.78) --
+	(261.01, 97.87) --
+	(260.76, 98.03) --
+	(259.26, 99.05) --
+	(258.83, 99.35) --
+	(257.57,100.23) --
+	(256.89,100.72) --
+	(255.96,101.41) --
+	(254.95,102.16) --
+	(254.40,102.59) --
+	(253.02,103.67) --
+	(252.89,103.76) --
+	(251.44,104.94) --
+	(251.08,105.24) --
+	(250.04,106.12) --
+	(249.14,106.90) --
+	(248.69,107.30) --
+	(247.38,108.48) --
+	(247.20,108.64) --
+	(246.12,109.66) --
+	(245.27,110.47) --
+	(244.90,110.84) --
+	(243.71,112.02) --
+	(243.33,112.40) --
+	(242.56,113.19) --
+	(241.45,114.37) --
+	(241.39,114.44) --
+	(240.37,115.55) --
+	(239.46,116.58) --
+	(239.33,116.73) --
+	(238.31,117.91) --
+	(237.52,118.85) --
+	(237.33,119.09) --
+	(236.37,120.27) --
+	(235.58,121.26) --
+	(235.44,121.44) --
+	(234.53,122.62) --
+	(233.65,123.80) --
+	(233.65,123.80) --
+	(232.79,124.98) --
+	(231.96,126.16) --
+	(231.71,126.51) --
+	(231.14,127.34) --
+	(230.35,128.52) --
+	(229.77,129.39) --
+	(229.58,129.70) --
+	(228.82,130.87) --
+	(228.09,132.05) --
+	(227.84,132.47) --
+	(227.37,133.23) --
+	(226.67,134.41) --
+	(225.99,135.59) --
+	(225.90,135.75) --
+	(225.33,136.77) --
+	(224.67,137.95) --
+	(224.04,139.12) --
+	(223.96,139.27) --
+	(223.42,140.30) --
+	(222.81,141.48) --
+	(222.21,142.66) --
+	(222.03,143.04) --
+	(221.63,143.84) --
+	(221.06,145.02) --
+	(220.51,146.20) --
+	(220.09,147.10) --
+	(219.96,147.38) --
+	(219.43,148.55) --
+	(218.91,149.73) --
+	(218.39,150.91) --
+	(218.15,151.48) --
+	(217.89,152.09) --
+	(217.40,153.27) --
+	(216.92,154.45) --
+	(216.45,155.63) --
+	(216.22,156.22) --
+	(215.98,156.81) --
+	(215.53,157.98) --
+	(215.08,159.16) --
+	(214.65,160.34) --
+	(214.28,161.36) --
+	(214.22,161.52) --
+	(213.80,162.70) --
+	(213.38,163.88) --
+	(212.98,165.06) --
+	(212.58,166.23) --
+	(212.34,166.96) --
+	(212.19,167.41) --
+	(211.81,168.59) --
+	(211.43,169.77) --
+	(211.06,170.95) --
+	(210.69,172.13) --
+	(210.41,173.08) --
+	(210.34,173.31) --
+	(209.98,174.49) --
+	(209.64,175.66) --
+	(209.29,176.84) --
+	(208.96,178.02) --
+	(208.63,179.20) --
+	(208.47,179.79) --
+	(208.31,180.38) --
+	(207.99,181.56) --
+	(207.67,182.74) --
+	(207.36,183.91) --
+	(207.06,185.09) --
+	(206.76,186.27) --
+	(206.53,187.19) --
+	(206.47,187.45) --
+	(206.18,188.63) --
+	(205.89,189.81) --
+	(205.61,190.99) --
+	(205.33,192.17) --
+	(205.06,193.34) --
+	(204.79,194.52) --
+	(204.59,195.39) --
+	(204.53,195.70) --
+	(204.26,196.88) --
+	(204.01,198.06) --
+	(203.75,199.24) --
+	(203.50,200.42) --
+	(203.25,201.60) --
+	(203.01,202.77) --
+	(202.77,203.95) --
+	(202.66,204.53) --
+	(202.54,205.13) --
+	(202.30,206.31) --
+	(202.07,207.49) --
+	(201.84,208.67) --
+	(201.62,209.85) --
+	(201.40,211.02) --
+	(201.18,212.20) --
+	(200.97,213.38) --
+	(200.76,214.56) --
+	(200.72,214.76) --
+	(200.55,215.74) --
+	(200.34,216.92) --
+	(200.13,218.10) --
+	(199.93,219.28) --
+	(199.73,220.45) --
+	(199.54,221.63) --
+	(199.34,222.81) --
+	(199.15,223.99) --
+	(198.96,225.17) --
+	(198.78,226.30) --
+	(198.78,226.35) --
+	(198.59,227.53) --
+	(198.41,228.70) --
+	(198.23,229.88) --
+	(198.05,231.06) --
+	(197.87,232.24) --
+	(197.70,233.42) --
+	(197.53,234.60) --
+	(197.36,235.78) --
+	(197.19,236.96) --
+	(197.03,238.13) --
+	(196.86,239.31) --
+	(196.85,239.42) --
+	(196.70,240.49) --
+	(196.54,241.67) --
+	(196.38,242.85) --
+	(196.22,244.03) --
+	(196.07,245.21) --
+	(195.91,246.39) --
+	(195.76,247.56) --
+	(195.61,248.74) --
+	(195.46,249.92) --
+	(195.32,251.10) --
+	(195.17,252.28) --
+	(195.03,253.46) --
+	(194.91,254.47) --
+	(194.89,254.64) --
+	(194.75,255.81) --
+	(194.61,256.99) --
+	(194.47,258.17) --
+	(194.33,259.35) --
+	(194.20,260.53) --
+	(194.07,261.71) --
+	(193.93,262.89) --
+	(193.80,264.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (301.44,136.49) --
+	(301.02,136.77) --
+	(299.50,137.79) --
+	(299.27,137.95) --
+	(297.58,139.12) --
+	(297.56,139.13) --
+	(295.93,140.30) --
+	(295.62,140.52) --
+	(294.32,141.48) --
+	(293.69,141.96) --
+	(292.76,142.66) --
+	(291.75,143.44) --
+	(291.24,143.84) --
+	(289.81,144.98) --
+	(289.76,145.02) --
+	(288.32,146.20) --
+	(287.88,146.56) --
+	(286.91,147.38) --
+	(285.94,148.21) --
+	(285.54,148.55) --
+	(284.21,149.73) --
+	(284.00,149.91) --
+	(282.90,150.91) --
+	(282.07,151.68) --
+	(281.62,152.09) --
+	(280.38,153.27) --
+	(280.13,153.51) --
+	(279.16,154.45) --
+	(278.19,155.41) --
+	(277.97,155.63) --
+	(276.81,156.81) --
+	(276.26,157.38) --
+	(275.68,157.98) --
+	(274.57,159.16) --
+	(274.32,159.43) --
+	(273.48,160.34) --
+	(272.41,161.52) --
+	(272.38,161.55) --
+	(271.37,162.70) --
+	(270.45,163.77) --
+	(270.35,163.88) --
+	(269.35,165.06) --
+	(268.51,166.07) --
+	(268.37,166.23) --
+	(267.41,167.41) --
+	(266.57,168.47) --
+	(266.47,168.59) --
+	(265.55,169.77) --
+	(264.65,170.95) --
+	(264.64,170.97) --
+	(263.76,172.13) --
+	(262.89,173.31) --
+	(262.70,173.57) --
+	(262.04,174.49) --
+	(261.20,175.66) --
+	(260.76,176.29) --
+	(260.38,176.84) --
+	(259.57,178.02) --
+	(258.83,179.14) --
+	(258.78,179.20) --
+	(258.00,180.38) --
+	(257.24,181.56) --
+	(256.89,182.11) --
+	(256.49,182.74) --
+	(255.75,183.91) --
+	(255.03,185.09) --
+	(254.95,185.22) --
+	(254.31,186.27) --
+	(253.61,187.45) --
+	(253.02,188.47) --
+	(252.92,188.63) --
+	(252.24,189.81) --
+	(251.58,190.99) --
+	(251.08,191.88) --
+	(250.92,192.17) --
+	(250.28,193.34) --
+	(249.64,194.52) --
+	(249.14,195.47) --
+	(249.02,195.70) --
+	(248.40,196.88) --
+	(247.80,198.06) --
+	(247.20,199.23) --
+	(247.20,199.24) --
+	(246.61,200.42) --
+	(246.03,201.60) --
+	(245.47,202.77) --
+	(245.27,203.19) --
+	(244.90,203.95) --
+	(244.35,205.13) --
+	(243.81,206.31) --
+	(243.33,207.36) --
+	(243.27,207.49) --
+	(242.74,208.67) --
+	(242.22,209.85) --
+	(241.71,211.02) --
+	(241.39,211.76) --
+	(241.20,212.20) --
+	(240.70,213.38) --
+	(240.21,214.56) --
+	(239.72,215.74) --
+	(239.46,216.40) --
+	(239.25,216.92) --
+	(238.77,218.10) --
+	(238.31,219.28) --
+	(237.85,220.45) --
+	(237.52,221.30) --
+	(237.39,221.63) --
+	(236.94,222.81) --
+	(236.50,223.99) --
+	(236.07,225.17) --
+	(235.64,226.35) --
+	(235.58,226.50) --
+	(235.21,227.53) --
+	(234.79,228.70) --
+	(234.38,229.88) --
+	(233.97,231.06) --
+	(233.65,232.01) --
+	(233.57,232.24) --
+	(233.17,233.42) --
+	(232.77,234.60) --
+	(232.39,235.78) --
+	(232.00,236.96) --
+	(231.71,237.87) --
+	(231.62,238.13) --
+	(231.25,239.31) --
+	(230.88,240.49) --
+	(230.51,241.67) --
+	(230.15,242.85) --
+	(229.79,244.03) --
+	(229.77,244.10) --
+	(229.44,245.21) --
+	(229.09,246.39) --
+	(228.74,247.56) --
+	(228.40,248.74) --
+	(228.07,249.92) --
+	(227.84,250.74) --
+	(227.74,251.10) --
+	(227.40,252.28) --
+	(227.08,253.46) --
+	(226.75,254.64) --
+	(226.44,255.81) --
+	(226.12,256.99) --
+	(225.90,257.84) --
+	(225.81,258.17) --
+	(225.50,259.35) --
+	(225.20,260.53) --
+	(224.89,261.71) --
+	(224.60,262.89) --
+	(224.30,264.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (301.44,179.14) --
+	(301.37,179.20) --
+	(300.11,180.38) --
+	(299.50,180.96) --
+	(298.88,181.56) --
+	(297.68,182.74) --
+	(297.56,182.85) --
+	(296.50,183.91) --
+	(295.62,184.80) --
+	(295.34,185.09) --
+	(294.20,186.27) --
+	(293.69,186.81) --
+	(293.09,187.45) --
+	(291.99,188.63) --
+	(291.75,188.89) --
+	(290.92,189.81) --
+	(289.87,190.99) --
+	(289.81,191.05) --
+	(288.83,192.17) --
+	(287.88,193.28) --
+	(287.82,193.34) --
+	(286.82,194.52) --
+	(285.94,195.58) --
+	(285.84,195.70) --
+	(284.88,196.88) --
+	(284.00,197.97) --
+	(283.94,198.06) --
+	(283.01,199.24) --
+	(282.09,200.42) --
+	(282.07,200.45) --
+	(281.19,201.60) --
+	(280.31,202.77) --
+	(280.13,203.02) --
+	(279.44,203.95) --
+	(278.59,205.13) --
+	(278.19,205.68) --
+	(277.75,206.31) --
+	(276.92,207.49) --
+	(276.26,208.45) --
+	(276.11,208.67) --
+	(275.30,209.85) --
+	(274.52,211.02) --
+	(274.32,211.32) --
+	(273.74,212.20) --
+	(272.97,213.38) --
+	(272.38,214.31) --
+	(272.22,214.56) --
+	(271.48,215.74) --
+	(270.75,216.92) --
+	(270.45,217.41) --
+	(270.03,218.10) --
+	(269.32,219.28) --
+	(268.62,220.45) --
+	(268.51,220.64) --
+	(267.93,221.63) --
+	(267.25,222.81) --
+	(266.58,223.99) --
+	(266.57,224.01) --
+	(265.92,225.17) --
+	(265.27,226.35) --
+	(264.64,227.52) --
+	(264.63,227.53) --
+	(263.99,228.70) --
+	(263.37,229.88) --
+	(262.76,231.06) --
+	(262.70,231.17) --
+	(262.15,232.24) --
+	(261.55,233.42) --
+	(260.96,234.60) --
+	(260.76,234.99) --
+	(260.37,235.78) --
+	(259.79,236.96) --
+	(259.23,238.13) --
+	(258.83,238.98) --
+	(258.67,239.31) --
+	(258.11,240.49) --
+	(257.56,241.67) --
+	(257.02,242.85) --
+	(256.89,243.14) --
+	(256.49,244.03) --
+	(255.96,245.21) --
+	(255.44,246.39) --
+	(254.95,247.51) --
+	(254.93,247.56) --
+	(254.42,248.74) --
+	(253.91,249.92) --
+	(253.42,251.10) --
+	(253.02,252.08) --
+	(252.93,252.28) --
+	(252.44,253.46) --
+	(251.96,254.64) --
+	(251.49,255.81) --
+	(251.08,256.87) --
+	(251.03,256.99) --
+	(250.56,258.17) --
+	(250.10,259.35) --
+	(249.65,260.53) --
+	(249.21,261.71) --
+	(249.14,261.89) --
+	(248.77,262.89) --
+	(248.33,264.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (301.44,212.31) --
+	(300.50,213.38) --
+	(299.50,214.55) --
+	(299.49,214.56) --
+	(298.49,215.74) --
+	(297.56,216.85) --
+	(297.51,216.92) --
+	(296.54,218.10) --
+	(295.62,219.24) --
+	(295.59,219.28) --
+	(294.66,220.45) --
+	(293.74,221.63) --
+	(293.69,221.70) --
+	(292.83,222.81) --
+	(291.94,223.99) --
+	(291.75,224.25) --
+	(291.06,225.17) --
+	(290.20,226.35) --
+	(289.81,226.88) --
+	(289.35,227.53) --
+	(288.51,228.70) --
+	(287.88,229.61) --
+	(287.68,229.88) --
+	(286.87,231.06) --
+	(286.07,232.24) --
+	(285.94,232.43) --
+	(285.28,233.42) --
+	(284.50,234.60) --
+	(284.00,235.35) --
+	(283.73,235.78) --
+	(282.97,236.96) --
+	(282.22,238.13) --
+	(282.07,238.38) --
+	(281.49,239.31) --
+	(280.76,240.49) --
+	(280.13,241.53) --
+	(280.04,241.67) --
+	(279.33,242.85) --
+	(278.64,244.03) --
+	(278.19,244.79) --
+	(277.95,245.21) --
+	(277.27,246.39) --
+	(276.60,247.56) --
+	(276.26,248.17) --
+	(275.93,248.74) --
+	(275.28,249.92) --
+	(274.64,251.10) --
+	(274.32,251.69) --
+	(274.00,252.28) --
+	(273.37,253.46) --
+	(272.75,254.64) --
+	(272.38,255.34) --
+	(272.13,255.81) --
+	(271.53,256.99) --
+	(270.93,258.17) --
+	(270.45,259.14) --
+	(270.34,259.35) --
+	(269.75,260.53) --
+	(269.17,261.71) --
+	(268.61,262.89) --
+	(268.51,263.09) --
+	(268.04,264.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (301.44,238.85) --
+	(301.08,239.31) --
+	(300.18,240.49) --
+	(299.50,241.41) --
+	(299.30,241.67) --
+	(298.43,242.85) --
+	(297.58,244.03) --
+	(297.56,244.05) --
+	(296.73,245.21) --
+	(295.90,246.39) --
+	(295.62,246.78) --
+	(295.08,247.56) --
+	(294.27,248.74) --
+	(293.69,249.61) --
+	(293.48,249.92) --
+	(292.69,251.10) --
+	(291.91,252.28) --
+	(291.75,252.53) --
+	(291.15,253.46) --
+	(290.39,254.64) --
+	(289.81,255.55) --
+	(289.65,255.81) --
+	(288.91,256.99) --
+	(288.18,258.17) --
+	(287.88,258.67) --
+	(287.46,259.35) --
+	(286.75,260.53) --
+	(286.06,261.71) --
+	(285.94,261.91) --
+	(285.36,262.89) --
+	(284.68,264.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (301.44,260.56) --
+	(300.64,261.71) --
+	(299.84,262.89) --
+	(299.50,263.39) --
+	(299.04,264.07);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.16, 30.69) rectangle (338.79,302.56);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.16, 30.69) rectangle (302.65,266.42);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{drawColor}{gray}{0.30}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21, 54.84) {0.1};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21, 82.03) {0.2};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,109.22) {0.3};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,136.40) {0.4};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,163.59) {0.5};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,190.78) {0.6};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,217.97) {0.7};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,245.15) {0.8};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,272.34) {0.9};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,299.53) {1.0};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21, 51.23) {0.1};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21, 74.80) {0.2};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21, 98.38) {0.3};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,121.95) {0.4};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,145.52) {0.5};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,169.10) {0.6};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,192.67) {0.7};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,216.25) {0.8};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,239.82) {0.9};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 29.21,263.39) {1.0};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41, 57.87) --
-	( 34.16, 57.87);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41, 85.06) --
-	( 34.16, 85.06);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,112.25) --
-	( 34.16,112.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,139.43) --
-	( 34.16,139.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,166.62) --
-	( 34.16,166.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,193.81) --
-	( 34.16,193.81);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,221.00) --
-	( 34.16,221.00);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,248.18) --
-	( 34.16,248.18);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,275.37) --
-	( 34.16,275.37);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,302.56) --
-	( 34.16,302.56);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41, 54.26) --
+	( 34.16, 54.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41, 77.83) --
+	( 34.16, 77.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,101.41) --
+	( 34.16,101.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,124.98) --
+	( 34.16,124.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,148.55) --
+	( 34.16,148.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,172.13) --
+	( 34.16,172.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,195.70) --
+	( 34.16,195.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,219.28) --
+	( 34.16,219.28);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,242.85) --
+	( 34.16,242.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.41,266.42) --
+	( 34.16,266.42);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (186.47, 27.94) --
-	(186.47, 30.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (338.79, 27.94) --
-	(338.79, 30.69);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (168.41, 27.94) --
+	(168.41, 30.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (302.65, 27.94) --
+	(302.65, 30.69);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{drawColor}{gray}{0.30}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (186.47, 19.68) {1.0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (338.79, 19.68) {2.0};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (168.41, 19.68) {1.0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (302.65, 19.68) {2.0};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (186.47,  7.64) {Relative mean asymptomatic generation interval, $G_a/G_s$};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (168.41,  7.64) {Relative mean asymptomatic generation interval, $G_a/G_s$};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,166.62) {Intrinsic proportion of asymptomatic transmission, $z$};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,148.55) {Intrinsic proportion of asymptomatic transmission, $z$};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (349.79, 25.48) rectangle (391.98,307.77);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
-\node[inner sep=0pt,outer sep=0pt,anchor=south west,rotate=  0.00] at (355.29,  30.98) {
-	\pgfimage[width= 14.45pt,height=256.07pt,interpolate=true]{figheatmap_R0_03_ras2}};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\path[fill=fillColor] (313.65, 28.75) rectangle (355.85,268.36);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
+\node[inner sep=0pt,outer sep=0pt,anchor=south west,rotate=  0.00] at (319.15,  34.25) {
+	\pgfimage[width= 14.45pt,height=213.40pt,interpolate=true]{figheatmap_R0_03_ras2}};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (375.24, 34.35) {1.5};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (375.24, 88.41) {2.5};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (375.24,142.47) {3.5};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (375.24,196.53) {4.5};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (375.24,250.59) {5.5};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (339.11, 36.55) {1.5};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (339.11, 81.60) {2.5};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (339.11,126.65) {3.5};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (339.11,171.70) {4.5};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (339.11,216.75) {5.5};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (355.29,293.62) {$\mathcal{R}_0$};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (319.15,254.21) {$\mathcal{R}_0$};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{drawColor}{RGB}{255,255,255}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] (355.29, 37.38) -- (358.18, 37.38);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (355.29, 91.44) -- (358.18, 91.44);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (355.29,145.50) -- (358.18,145.50);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (355.29,199.56) -- (358.18,199.56);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (355.29,253.62) -- (358.18,253.62);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (366.85, 37.38) -- (369.74, 37.38);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (366.85, 91.44) -- (369.74, 91.44);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (366.85,145.50) -- (369.74,145.50);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (366.85,199.56) -- (369.74,199.56);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (366.85,253.62) -- (369.74,253.62);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
+\path[draw=drawColor,line width= 0.2pt,line join=round] (319.15, 39.58) -- (322.05, 39.58);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (319.15, 84.63) -- (322.05, 84.63);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (319.15,129.68) -- (322.05,129.68);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (319.15,174.73) -- (322.05,174.73);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (319.15,219.78) -- (322.05,219.78);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (330.72, 39.58) -- (333.61, 39.58);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (330.72, 84.63) -- (333.61, 84.63);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (330.72,129.68) -- (333.61,129.68);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (330.72,174.73) -- (333.61,174.73);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (330.72,219.78) -- (333.61,219.78);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 34.16,310.62) {B. Basic reproduction number};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 34.16,274.49) {B. Basic reproduction number};
 \end{scope}

### 2020-03-09 figheatmap.R

@@ -35,10 +35,10 @@ q2/(1+q2)
 g0 <- ggplot(figdata) +
   geom_raster(aes(relG, z, fill=q)) +
   geom_contour(aes(relG, z, z=q), col="white") +
-  annotate(geom="point", x=0.55, y=0.5, col="white", shape=2, size=5, stroke=2) +
-  annotate(geom="text", x=0.55, y=0.45, label="$q=0.59$", col="white", size=2.5) +
-  annotate(geom="point", x=1.8, y=0.5, col="white", shape=1, size=5, stroke=2) +
-  annotate(geom="text", x=1.8, y=0.45, label="$q=0.38$", col="white", size=2.5) +
+  annotate(geom="point", x=0.55, y=0.5, col="white", shape=21, size=4, fill="white") +
+  annotate(geom="text", x=0.565, y=0.46, label="$q=0.59$", col="white") +
+  annotate(geom="point", x=1.8, y=0.5, col="white", shape=24, size=4, fill="white") +
+  annotate(geom="text", x=1.775, y=0.46, label="$q=0.38$", col="white") +
   scale_x_log10("Relative mean asymptomatic generation interval, $G_a/G_s$", expand=c(0, 0),
                      breaks=c(0.5, 1, 2)) +
   scale_y_continuous("Intrinsic proportion of asymptomatic transmission, $z$", expand=c(0, 0),
@@ -49,10 +49,10 @@ g0 <- ggplot(figdata) +
                        breaks=0:5*2/10) +
   ggtitle("A. Realized proportion of asymptomatic transmission") +
   theme(
-    legend.key.height = unit(1.8, "cm")
+    legend.key.height = unit(1.5, "cm")
   )
 
-tikz(file = "figheatmap.tex", width = 5.5, height = 4.5, standAlone = T)
+tikz(file = "figheatmap.tex", width = 5, height = 4, standAlone = T)
 print(g0)
 dev.off()
 tools::texi2dvi('figheatmap.tex', pdf = T, clean = T)

### 2020-03-09 figheatmap_03.R

@@ -37,10 +37,10 @@ g0 <- ggplot(figdata) +
                        breaks=0:5*2/10) +
   ggtitle("A. Realized proportion of asymptomatic transmission") +
   theme(
-    legend.key.height = unit(1.8, "cm")
+    legend.key.height = unit(1.5, "cm")
   )
 
-tikz(file = "figheatmap_03.tex", width = 5.5, height = 4.5, standAlone = T)
+tikz(file = "figheatmap_03.tex", width = 5, height = 4, standAlone = T)
 print(g0)
 dev.off()
 tools::texi2dvi('figheatmap_03.tex', pdf = T, clean = T)

### 2020-03-09 figheatmap_08.R

@@ -37,10 +37,10 @@ g0 <- ggplot(figdata) +
                        breaks=0:5*2/10) +
   ggtitle("A. Realized proportion of asymptomatic transmission") +
   theme(
-    legend.key.height = unit(1.8, "cm")
+    legend.key.height = unit(1.5, "cm")
   )
 
-tikz(file = "figheatmap_08.tex", width = 5.5, height = 4.5, standAlone = T)
+tikz(file = "figheatmap_08.tex", width = 5, height = 4, standAlone = T)
 print(g0)
 dev.off()
 tools::texi2dvi('figheatmap_08.tex', pdf = T, clean = T)

### 2020-03-09 figheatmap_R0.R

@@ -31,7 +31,6 @@ relg1 <- 0.55
 relg2 <- 1.8
 1/((1-zexample) * (1 + kappa_s * r * G_s)^(-1/kappa_s) + zexample * (1 + kappa_a * r * relg2 * G_s)^(-1/kappa_a))
 
-
 g0 <- ggplot(figdata) +
   geom_raster(aes(relG, z, fill=R0)) +
   geom_contour(aes(relG, z, z=R0), col="white", bins=9) +
@@ -40,10 +39,10 @@ g0 <- ggplot(figdata) +
   annotate(geom="text", x=0.96, y=0.11, label="$\\mathcal{R}_0=2.5$", col="white", angle=90) +
   annotate(geom="text", x=1*sqrt(2), y=0.03, label="underestimated", col="white") +
   annotate(geom="text", x=1/sqrt(2), y=0.03, label="overestimated", col="white") +
-  annotate(geom="point", x=0.55, y=0.5, col="white", shape=2, size=5, stroke=2) +
-  annotate(geom="text", x=0.55, y=0.45, label="$\\mathcal{R}_0=2.0$", col="white", size=2.5) +
-  annotate(geom="point", x=1.8, y=0.5, col="white", shape=1, size=5, stroke=2) +
-  annotate(geom="text", x=1.8, y=0.45, label="$\\mathcal{R}_0=3.1$", col="white", size=2.5) +
+  annotate(geom="point", x=0.55, y=0.5, col="white", shape=21, size=4, fill="white") +
+  annotate(geom="text", x=0.57, y=0.46, label="$\\mathcal{R}_0=2.0$", col="white") +
+  annotate(geom="point", x=1.8, y=0.5, col="white", shape=24, size=4, fill="white") +
+  annotate(geom="text", x=1.78, y=0.46, label="$\\mathcal{R}_0=3.1$", col="white") +
   scale_x_log10("Relative mean asymptomatic generation interval, $G_a/G_s$", expand=c(0, 0),
                 breaks=c(0.5, 1, 2),
                 limits=c(0.5, 2)) +
@@ -55,10 +54,10 @@ g0 <- ggplot(figdata) +
                        breaks=c(1.5, 2.5, 3.5, 4.5, 5.5)) +
   ggtitle("B. Basic reproduction number") +
   theme(
-    legend.key.height = unit(1.8, "cm")
+    legend.key.height = unit(1.5, "cm")
   )
 
[…]

### 2020-03-09 figheatmap_R0_03.R

@@ -38,10 +38,10 @@ g0 <- ggplot(figdata) +
                        breaks=c(1.5, 2.5, 3.5, 4.5, 5.5)) +
   ggtitle("B. Basic reproduction number") +
   theme(
-    legend.key.height = unit(1.8, "cm")
+    legend.key.height = unit(1.5, "cm")
   )
 
-tikz(file = "figheatmap_R0_03.tex", width = 5.5, height = 4.5, standAlone = T)
+tikz(file = "figheatmap_R0_03.tex", width = 5, height = 4, standAlone = T)
 print(g0)
 dev.off()
 tools::texi2dvi('figheatmap_R0_03.tex', pdf = T, clean = T)

### 2020-03-09 figheatmap_R0_08.R

@@ -38,10 +38,10 @@ g0 <- ggplot(figdata) +
                        breaks=c(1.5, 2.5, 3.5, 4.5, 5.5)) +
   ggtitle("B. Basic reproduction number") +
   theme(
-    legend.key.height = unit(1.8, "cm")
+    legend.key.height = unit(1.5, "cm")
   )
 
-tikz(file = "figheatmap_R0_08.tex", width = 5.5, height = 4.5, standAlone = T)
+tikz(file = "figheatmap_R0_08.tex", width = 5, height = 4, standAlone = T)
 print(g0)
 dev.off()
 tools::texi2dvi('figheatmap_R0_08.tex', pdf = T, clean = T)

### 2020-03-09 figheatmap_kappa.R

@@ -38,10 +38,10 @@ g0 <- ggplot(figdata) +
                        breaks=0:5*2/10) +
   ggtitle("A. Realized proportion of asymptomatic transmission") +
   theme(
-    legend.key.height = unit(1.8, "cm")
+    legend.key.height = unit(1.5, "cm")
   )
 
-tikz(file = "figheatmap_kappa.tex", width = 5.5, height = 4.5, standAlone = T)
+tikz(file = "figheatmap_kappa.tex", width = 5, height = 4, standAlone = T)
 print(g0)
 dev.off()
 tools::texi2dvi('figheatmap_kappa.tex', pdf = T, clean = T)

### 2020-03-09 figheatmap_kappa_R0.R

@@ -38,10 +38,10 @@ g0 <- ggplot(figdata) +
                        breaks=c(1.5, 2.5, 3.5, 4.5, 5.5)) +
   ggtitle("B. Basic reproduction number") +
   theme(
-    legend.key.height = unit(1.8, "cm")
+    legend.key.height = unit(1.5, "cm")
   )
 
-tikz(file = "figheatmap_kappa_R0.tex", width = 5.5, height = 4.5, standAlone = T)
+tikz(file = "figheatmap_kappa_R0.tex", width = 5, height = 4, standAlone = T)
 print(g0)
 dev.off()
 tools::texi2dvi('figheatmap_kappa_R0.tex', pdf = T, clean = T)

### 2020-03-09 short.body.tex
various tweaks
Tweaks to Discussion; nuke commented-out old Discussion for some reason

@@
 Circle assume $z=0.5$ and $\bar G_a/\bar G_s = 1.8$.
-Solid lines show contours for \Ro\ values. 
+Solid lines show contours for $q$ and \Ro\ values. 
 Here, we assume $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.5$.
@@
 
-Much is still unknown about course of asymptomatic infection compared to symptomatic infection in COVID-19. 
-Our current work highlights the need to characterize the duration of asymptomatic infections, relative to that of symptomatic ones, and their consequences not only for contact tracing but for precise estimation of the basic reproduction number of the ongoing COVID-19 outbreak~\citep{park_preprint}.
-The present findings are also consistent with a recent generalization linking speed, strength, and generation intervals, such that for a given observed speed increases in the mean generation interval imply larger reproduction number~\citep{park_2019practical}.
+Much is still unknown about the time scale and effectiveness of asymptomatic transmission in COVID-19. 
+Here we highlight the need to characterize the generation-interval distribution for asymptomatic transmission, and its consequences not only for contact tracing but for estimation of the basic reproduction number of the ongoing COVID-19 outbreak~\citep{park_preprint} and of the effective proportion of asymptomatic transmission during the exponential-growth phase.
+Our reproductive number findings fit into a broader framework linking epidemc speed, strength, and generation intervals -- for a given observed speed increases in the mean generation interval imply larger reproduction number~\citep{park_2019practical}.
+\jd{Add one or two other cites, maybe starting with Wallinga Lipsitch.}
 
-If mild, asymptomatic infections are more persistent than severe, symptomatic ones, the mean generation interval for COVID-19 could be longer than estimated from symptomatic cases alone - possibly increasing ${\cal{R}}_0$ (Figure~\ref{fig.importance}B).
-However, if asymptomatic cases tend to have shorter infection, then current estimates of ${\cal{R}}_0$ may be over-estimates of the underlying strength (Figure~\ref{fig.importance}B), although asymptomatic cases may be driving a larger fraction of secondary cases than we would expect without accounting for their differences (Figure~\ref{fig.importance}A).
-Therefore, current estimates of ${\cal{R}}_0$ that do not account for asymptomatic cases may be systematically biased.
+If asymptomatic infections are more persistent than symptomatic ones, the mean generation interval for COVID-19 could be longer than estimated from symptomatic cases alone -- possibly increasing ${\cal{R}}_0$ (Figure~\ref{fig.importance}B).
+However, if asymptomatic cases tend to resolve quickly, then current estimates of ${\cal{R}}_0$ may be over-estimates of the underlying strength (Figure~\ref{fig.importance}B), and asymptomatic cases may be driving a larger fraction of secondary cases than we would expect without accounting for their differences (Figure~\ref{fig.importance}A).
 
-Finally, it is important to note we focused here on the exponential phase, but that the realized proportion of asymptomatic transmission $q$ is time-dependent, and will vary given the population state structure of infected individuals.
-Such variation in the ratio of asymptomatic to symptomatic cases will also impact estimates of case fatality rates insofar as many asymptomatic cases are not counted, particularly early in an outbreak.
-Future work might also consider the ways in which asymptomatic individuals modulate resurgent epidemics in a networked metapopulation~\citep{watts_pnas2005}.
+We focus here on the exponential phase, so it is worth noting that the realized proportion of asymptomatic transmission $q$ is time-dependent, varying with dynamic changes in incidence and proportion susceptible.
+Future work might also consider the ways in which asymptomatic individuals can modulate resurgent epidemics in a networked metapopulation~\citep{watts_pnas2005}.
 Characterizing the role of asymptomatic individuals in driving the persistence of the epidemic will be critical for assessing the post-pandemic outcome \citep{lipsitch_preprint}.
-
-%We also note that efforts to characterize asymptomatic tranissmion
-%should consider its effect on
-%the basic reproduction number, which for this SEIR coronavirus-like model is ${\cal{R}}_0=p\left(\frac{\beta_a}{\gamma_a}\right)+ (1-p)\left(\frac{\beta_s}{\gamma_s}\right).$
-%%Pooling estimates via a Bayesian approach applied to the early stages of Wuhan case data,
-%%suggests ${\cal{R}}_0\approx 3.0$ 
-%%with a 95\% confidence interval from 2-4.5.  Yet, that information
-%%is not sufficient to disentangle the role of asymptomatic cases, i.e.,
-%%what fraction of secondary cases can be ascribed to transmission
-%%from asymptomatic cases vs.~symptomatic cases?  
-%Strength, ${\cal{R}}_0$ and size $r$
-%can be related via a Gamma approximation to the generation
-%interval distribution as follows:
-%\begin{equation}
-%{\cal{R}}^{gamma}=(1+\kappa r \bar{G})^{1/\kappa}
-%\end{equation}
-%where $\bar{G}$ is the mean generation interval and
-%$\kappa$  is the squared coefficient of variation of
-%the generation interval.  
-%This approximation (explored in Champredon
-%et al.) reveals why for a given observed speed,
-%increases in the mean generation interval imply
-%larger reproduction number. Hence, reports of individuals
-%with mild cases that remain infectious for (relatively)
-%long periods suggest that the mean generation interval
-%could be longer than estimated from symptomatic cases alone - both
-%increasing ${\cal{R}}_0$ and driving a larger fraction of secondary cases.
-%This inference also reinforces 
-%the need to characterize the epidemiological characteristics of asymptomatic transmission.
-
-%Renewal equations provide a route to connect
-%observed increases in case counts, i.e.,
-%\begin{equation}
-%{\cal{R}}_0 = \frac{1}{M(-r)}
-%\end{equation}
-%where $r$ is the speed of the disease spread and $M(r)$ is the
-%moment generating function of the generation interval distribution
-%$g(a)$ (normalized age of transmission) such that 
-%\begin{equation}
-%M(r)=\int_0^{\infty}\mathrm{d} a e^{ra}g(a).
-%\end{equation}
-%For the present model, the moment generating function is
-%\begin{equation}
-%M(r)=qM_E(r)M_{I_a}(r)+(1-q)M_E(r)M_{I_s}(r)
-%\end{equation}
-%where each of the component functions are $M_E(-r)=\frac{\gamma_e}{\gamma_e+r}$,
-%$M_{I_a}(-r)=\frac{\gamma_a}{\gamma_a+r}$, 
-%$M_{I_s}(-r)=\frac{\gamma_s}{\gamma_s+r}$,
-%and $q$ is the fraction of realized new secondary cases caused by
-%asymptomatic individuals. The relevance $q$ is an unknown feature of
-%outbreaks at the population scale, distinct from $p$ the probability of having
-%an asymptomatic cases, conditional upon being infected
-%but not yet infectious. Hence,
-%if one were to observe $r$ (which can vary from country to 
-%country and from region to region) then it should be possible
-%to link the values $p$ and the relative transmission rates,
-%$\beta_a/\beta_s$ to the relevance of asymptomatic transmission
-%at the population scale.
-
-%Renewal equations provide a route to connect
-%observed increases in case counts, i.e.,
-%\begin{equation}
-%{\cal{R}}_0 = \frac{1}{M(-r)}
-%\end{equation}
-%where $r$ is the speed of the disease spread and $M(r)$ is the
-%moment generating function of the generation interval distribution
-%$g(a)$ (normalized age of transmission) such that 
-%\begin{equation}
-%M(r)=\int_0^{\infty}\mathrm{d} a e^{ra}g(a).
-%\end{equation}
-%For the present model, the moment generating function is
-%\begin{equation}
-%M(r)=qM_E(r)M_{I_a}(r)+(1-q)M_E(r)M_{I_s}(r)
-%\end{equation}
-%where each of the component functions are $M_E(-r)=\frac{\gamma_e}{\gamma_e+r}$,
-%$M_{I_a}(-r)=\frac{\gamma_a}{\gamma_a+r}$, 
-%$M_{I_s}(-r)=\frac{\gamma_s}{\gamma_s+r}$,
-%and $q$ is the fraction of realized new secondary cases caused by
-%asymptomatic individuals. The relevance $q$ is an unknown feature of
-%outbreaks at the population scale, distinct from $p$ the probability of having
-%an asymptomatic cases, conditional upon being infected
-%but not yet infectious. Hence,
-%if one were to observe $r$ (which can vary from country to 
-%country and from region to region) then it should be possible
-%to link the values $p$ and the relative transmission rates,
-%$\beta_a/\beta_s$ to the relevance of asymptomatic transmission
-%at the population scale.
-%
-%
-%
-%
-%Hence, recalling the equation for the basic reproduction number
-%\begin{equation}
-%{\cal{R}}_{0,E}= p\left(\frac{\beta_a}{\gamma_a}\right)+ (1-p)\left(\frac{\beta_s}{\gamma_s}\right)
-%\end{equation}
-%suggests that 
-%This gap between intrinsic and realized transmission routes
-%lies at the base of our exploration.
-%
-%\section{Dynamics}
-%We simulate the SEIaIsRD model assuming $N=10^6$ with
-%the following initial conditions: $S_0=10^6-1$, $E_0=1$
-%and all other elements 0.  The following model vary $p$ from
-%0.1 to 0.5 to 0.9.  For various reasons, the parameters are:
-%$\gamma_e=1/4$, $\gamma_a=1/42$, $\gamma_s=1/14$,
-%$\beta_a=1/14$, $\beta_s=3/14$, $f=0.02$.  The resultant
-%value of ${\cal{R}}_0=3$ for all values of $p$, however
-%the realized CFR, fraction of asymptomatic cases, and even
-%the speed of the disease varies significantly. Hence, we 
-%need to adopt a different approach, given that we
-%observe a speed, $r$, and yet are uncertain with
-%respect to the underlying contribution of asymptomatic
-%vs.~symptomatic cases.
-%
-%\begin{figure*}[h!]
-%\begin{center}
-%\includegraphics[width=0.9\textwidth]{figseird_base_noname.pdf}\\
-%\includegraphics[width=0.9\textwidth]{figseird_base2_noname.pdf}\\
-%\includegraphics[width=0.9\textwidth]{figseird_base3_noname.pdf}\\
-%\end{center}
-%\end{figure*}
-%
-%\section{Constrained Dynamics}
-%Here, we simulate the SEIR model developed
-%for coronavirus assuming $N=10^6$ with
-%the following initial conditions: $S_0=10^6-1$, $E_0=1$
-%and all other elements set to 0.  We assume that the speed of
-%the outbreak is $r=1/6$ days$^{-1}$. We further assume that $\gamma_e=1/4$
-%(4 days to onset), $\gamma_a=1/42$, $\gamma_s=1/14$, and $p=0.9$.
-%How do we solve for the unknown transmission rates, $\beta_a$
-%and $\beta_s$?  Alone, it would seem we have a under-determined
-%problem, such that
-%\begin{equation}
-%p\left(\frac{\beta_a}{\gamma_a}\right)+ (1-p)\left(\frac{\beta_s}{\gamma_s}\right)=\frac{1}{M(-r)}.
-%\end{equation}
-%However, if one assumes that a fraction $q$ of secondary infections are caused by
-%asymptomatic individuals, then there is an additional constraint:
-%\begin{equation}
-%p\frac{\beta_a}{\gamma_a}=\frac{q}{M(-r)}
-%\end{equation}
-%such that 
-%\begin{equation}
-%\beta_a = \frac{q\gamma_a}{pM(-r)}.
-%\end{equation}
-%As a result, then 
-%\begin{equation}
-%\beta_s = \frac{(1-q)\gamma_s}{(1-p)M(-r)}
-%\end{equation}
-%In essence, as $q$ varies, then both tranmission rates will have 
-%to covary (indeed in a negative fashion) to reconciled the realized
-%speed of the outbreak. We now put this into practice for three scenarios,
-%all for the case of $p=0.9$ (in which intrinsically most cases
-%are asymptomatic):
-%\begin{description}
-%\item[Short asymptomatic cases] Here we assume
-%$\gamma_s=1/14$ (2 week for severe cases) and $\gamma_a=1/2$ 
-%(2 day resolution, i.e., a 7-fold change). 
-%\item[Long asymptomatic cases] Here we assume
-%$\gamma_s=1/14$ (2 week for severe cases) and $\gamma_a=1/42$ 
-%(6 week for mild cases)
-%\end{description}
-%We also assume as before that $f=0.02$ for severe cases. The following 
-%results show that we can in fact calculate the correct values of
-%$\beta_a$ and $\beta_s$ given variation in $q$.
-%It is also important to point out that
-%${\cal{R}}_0$ can be extended or decreased with $q$ depending
-%on whether $\gamma_a$ is faster or slower relative to $\gamma_s$.
-%The key idea there is the same as that for the impact of post-death
-%transmission of Ebola virus disease.
-%
-%For the short duration asymptomatic cases (see Figure~\ref{constrain}), we find the following trade-offs:
-%\begin{verbatim}
-%         q: [0.0100 0.1000 0.5000 0.9000 0.9900]
-%    beta_a: [0.0258 0.2311 0.7857 1.0714 1.1176]
-%    beta_s: [3.2898 2.6741 1.0102 0.1531 0.0145]
-%        R0: [4.6523 4.1597 2.8286 2.1429 2.0320]
-%\end{verbatim}
-%whereas for the longer duration asymptomatic cases we find
-%\begin{verbatim}
-%         q: [0.0100 0.1000 0.5000 0.9000 0.9900]
-%    beta_a: [0.0013 0.0132 0.0873 0.2311 0.2843]
-%    beta_s: [3.3528 3.2143 2.3571 0.6933 0.0775]
-%        R0: [4.7414 5 6.6000 9.7059 10.8553]
-%\end{verbatim}
-%In the first case, when most illnesses
-%are caused by asymptomatic cases, then shorter generation intervals
-%for the same growth rate means a lower ${\cal{R}}_0$. Whereas,
-%in the second case, when most illnesses are caused by asymptomatic
-%cases, then longer generation intervals for the same growth rate
-%means a higher ${\cal{R}}_0$.
-%\begin{figure*}[b!]
-%\begin{center}
-%\includegraphics[width=0.9\textwidth]{figconstrain_short_noname.pdf}\\
-%\includegraphics[width=0.9\textwidth]{figconstrain_long_noname.pdf}\\
-%\caption{Short, mild asymptomatic cases (top) vs. longer, mild asymptomatic
-%cases (bottom). For both, common parameters are $\gamma_e=0.25$,
-%$\gamma_s=1/14$, $f=0.02$, $p=0.9$, and $r=1/7$.  For the short
-%asymptomatic case scenario, $\gamma_a=1/2$ whereas for the long asymptomatic
-%case scenario $\gamma_a=1/42$.
-%\label{constrain}}
-%\end{center}
-%\end{figure*}
-%
-%Finally, in an effort to try and reconcile this, we point out the following
-%synthetic figure of outbreaks all with a growth rate of $r=1/7$ by construction, yet differ in vastly different ways based on 3 facets, the value of $p$ (the instrinsic fraction of asymptomatic cases),
-%the value of $1/\gamma_a$ (that sets the average duration of asymptomatic cases), and
-%the realized value of $q$ (the fraction of secondary cases caused by asymptomatic cases).  As is
-%apparent, all disease take off at the same speed, but have very different peak strengths,
-%and also, different decomposition of the relative importance of the asymptomatic component.
-%What is notable is that the peak size is more driven by $p$ and $\gamma_a$ than by $q$
-%(see Figure~\ref{constrain2}).
-%\begin{figure*}[bh!]
-%\begin{center}
-%\includegraphics[width=0.9\textwidth]{package_overlay_p_T.pdf}
-%\caption{Synthesis of dynamical results given variation in 
-%the intrinsic generation interval of asymptomatic cases (set by $1/\gamma_a$), frequency ($p$), 
-%and importance ($q$).
-%For all, common parameters are $\gamma_e=0.25$,
-%$\gamma_s=1/14$, $f=0.02$, and $r=1/7$.  For the short
-%asymptomatic case scenario, $\gamma_a=1/2$ whereas for the long asymptomatic
-%case scenario $\gamma_a=1/42$.
-%\label{constrain2}}
-%\end{center}
-%\end{figure*}
-%
-%%
-%%\section{Simulations}
-%%Consider an outbreak whose
-%%symptomatic cases is ${\cal{R}}_0\approx 3$, such that
-%%$\beta_s/\gamma_s=3$.  We further assume that transition from
-%%exposed to either $I_a$ or $I_s$ takes 4 days on average,
-%%such that $\eta=1/4$.  The following is an example
-%%outbreak, in which $\beta_s=\beta_a=3/7$, $\gamma_a=1/45$,
-%%and $f=0.02$ (corresponding to a 2\% case fatality rate
-%%for symptomatic cases). As is apparent, there is an exponential
-%%increase in cases, such that $r\approx 0.30$ days$^{-1}$.
-%%In this case, we expect that in the exponential phase,
-%%then $I_a/I_s\approx 13.8$.  This prediction is borne out
-%%by simulation as in Figure~\ref{fig.ratio}.
-%%\begin{figure*}[h!]
-%%\begin{center}
-%%\includegraphics[width=0.4\textwidth]{figexample1_noname.pdf}
-%%\mbox{\hspace{0.05\textwidth}}
-%%\includegraphics[width=0.4\textwidth]{figexample1_ratio_noname.pdf}
-%%\caption{Asymptomatic to symptomatic case ratio at 
-%%the population scale can exceed the ratio of relative case
-%%production at the individual scale, when $\gamma_a\ll \gamma_s$.\label{fig.ratio}}
-%%\end{center}
-%%\end{figure*}
-%%Similalry, in the case that asymmptomatic cases rapidly
-%%recover, then we expect the population rate to be less then
-%%$z$. In the event that $\gamma_a=1$ (7-fold faster than
-%%the the symptomatic removal rate) then $r\approx 0.17$ and
-%%the ratio is expected to converge to $\approx 2.7$, as shown in Figure~\ref{fig.ratio2}.
-%%\begin{figure*}[h!]
-%%\begin{center}
-%%\includegraphics[width=0.4\textwidth]{figexample2_noname.pdf}
-%%\mbox{\hspace{0.05\textwidth}}
-%%\includegraphics[width=0.4\textwidth]{figexample2_ratio_noname.pdf}
-%%\caption{Asymptomatic to symptomatic case ratio at 
-%%the population scale can exceed the ratio of relative case
-%%production at the individual scale, when $\gamma_a\gg \gamma_s$.
-%%\label{fig.ratio2}
-%%}
-%%\end{center}
-%%\end{figure*}
-%%Finally, in the case that asymptomatic cases and symptomatic
-%%cases have the same exepcted rudation
-%%then we expect the population ratio to be less then
-%%$z$. In the event that $\gamma_a=1$ (7-fold faster than
-%%the the symptomatic removal rate) then $r\approx 0.26$ and
-%%the ratio is expected to converge to $\approx 10$, as shown in Figure~\ref{fig.ratio3}.
-%%\begin{figure*}[h!]
-%%\begin{center}
-%%\includegraphics[width=0.4\textwidth]{figexample3_noname.pdf}
-%%\mbox{\hspace{0.05\textwidth}}
-%%\includegraphics[width=0.4\textwidth]{figexample3_ratio_noname.pdf}
-%%\caption{Asymptomatic to symptomatic case ratio at 
-%%the population scale can exceed the ratio of relative case
-%%production at the individual scale, when $\gamma_s=\gamma_a$.
-%%\label{fig.ratio3}
-%%}
-%%\end{center}
-%%\end{figure*}
-%%
-%%\section{Stability of the infection-free equilibrium}
-%%Consider the following infection subystem, assume $S\approx 1$
-%%\begin{eqnarray}
-%%\dot{E}&=&\beta_a I_a +\beta_s I_s -\eta E\\
-%%\dot{I}_a&=&\frac{z}{z+1}\eta E-\gamma_a I_a\\
-%%\dot{I}_s&=&\frac{1}{z+1}\eta E-\gamma_s I_s
-%%\end{eqnarray}
-%%such that the Jacobian is:
-%%\begin{equation}
-%%J = \left[
-%%\begin{array}{ccc}
-%%-\eta & \beta_a & \beta_s \\
-%%\frac{z}{z+1}E & -\gamma_a & 0 \\
-%%\frac{1}{z+1}E & -\gamma_s & 0 
-%%\end{array}
-%%\right]
-%%\end{equation}

### 2020-03-09 abs.tex
Add one more sentence to abstract

@@
 We show that the impact of asymptomatic transmission depends on generation intervals (i.e., time between when an individual is infected and when that individual infects another person).
-If the generation intervals of asymptomatic cases differs from that of symptomatic cases, then estimates of the basic reproduction number which do not explicitly account for asymptomatic cases may be systematically biased.
+If the generation-interval distribution of asymptomatic transmission differs from that of symptomatic transmission, then estimates of the basic reproduction number which do not explicitly account for asymptomatic cases may be systematically biased.
 Specifically, if asymptomatic cases have a shorter generation interval than symptomatic cases, ${\cal{R}}_0$ will be over-estimated, and if they have a longer generation interval, ${\cal{R}}_0$ will be under-estimated.
-The analysis provides a rationale for assessing the duration of asymptomatic cases of COVID-19 in addition to their prevalence in the population.
+We also show that as the length of asymptomatic generation intervals increase, estimates of the realized proportion of asymptomatic transmission during the exponential phase of the epidemic decrease.
+Our analysis provides a rationale for assessing the duration of asymptomatic cases of COVID-19 in addition to their prevalence in the population.
 }

### 2020-03-10 appendix.tex
push all files
various tweaks
stuff

@@
 \begin{equation}
-\frac{q}{1-q}=\left(\frac{z}{1-z}\right)\left[\frac{(1 + \kappa_s r \bar G_s)^{1/\kappa_s}}{(1 + \kappa_a r \bar G_a)^{1/\kappa_a}}\right],
+\frac{q}{1-q}=\left(\frac{z}{1-z}\right)\left[\frac{(1 + \kappa_a r \bar G_a)^{-1/\kappa_a}}{(1 + \kappa_s r \bar G_s)^{-1/\kappa_s}}\right],
 \end{equation}
 where $\bar G_a$ and $\bar G_s$ are the mean generation intervals for asymptomatic and symptomatic cases, and $\kappa_a$ and $\kappa_s$ are the generation-interval dispersions for asymptomatic and symptomatic cases.
-Finally, the basic reproduction number is calculated by
+Finally, the basic reproduction number is calculated by using the Euler-Lotka equation:
 \begin{equation}
@@
 \end{equation}
-where $z = p {\cal{R}}_a/{\cal{R}}_{0}$ and $1-z=(1-p) {\cal{R}}_s/{\cal{R}}_{0}$.
+where $z = p {\cal{R}}_a/{\cal{R}}_{0}$ and $1-z=(1-p) {\cal{R}}_s/{\cal{R}}_{0}$ -- compare to Eq.~(8) in the main text.
 
@@
 \begin{center}
-\includegraphics[width=0.4\textwidth]{figheatmap_03.pdf}
+\includegraphics[width=0.45\textwidth]{figheatmap_03.pdf}
 \mbox{\hspace{0.05\textwidth}}
-\includegraphics[width=0.4\textwidth]{figheatmap_R0_03.pdf}
+\includegraphics[width=0.45\textwidth]{figheatmap_R0_03.pdf}
 \caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
@@
 \begin{center}
-\includegraphics[width=0.4\textwidth]{figheatmap_08.pdf}
+\includegraphics[width=0.45\textwidth]{figheatmap_08.pdf}
 \mbox{\hspace{0.05\textwidth}}
-\includegraphics[width=0.4\textwidth]{figheatmap_R0_08.pdf}
+\includegraphics[width=0.45\textwidth]{figheatmap_R0_08.pdf}
 \caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
@@
 \begin{center}
-\includegraphics[width=0.4\textwidth]{figheatmap_kappa.pdf}
+\includegraphics[width=0.45\textwidth]{figheatmap_kappa.pdf}
 \mbox{\hspace{0.05\textwidth}}
-\includegraphics[width=0.4\textwidth]{figheatmap_kappa_R0.pdf}
+\includegraphics[width=0.45\textwidth]{figheatmap_kappa_R0.pdf}
 \caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
@@
 (B) Wide/narrow generation intervals of asymptomatic cases decrease/increase the basic reproduction number ${\cal{R}}_0$.
-The white, solid lines represent the contour lines.
+Solid lines show contours for $q$ and \Ro\ values.
 Here, we assume $1/r=7$ days, $\bar G_s=\bar G_a=8$ days, and $\kappa_s=0.5$.

### 2020-03-10 short.body.tex
stuff

@@
 First, the proportion of infections that are asymptomatic (see~\citep{mizumoto_2020}) is critical to attempts to estimate the likely burden of severe outcomes (including mortality \citep{fauci_nejm2020}) when the virus spreads through a population.
-Second, understanding the possible role of \emph{transmission} by asymptomatic individuals is crucial to planning surveillance and control efforts \citep{fraser2004factors}.
+Second, understanding the possible role of \emph{transmission} by asymptomatic individuals is crucial to planning surveillance and control efforts \citep{fraser2004factors, bai2020presumed}.
 
@@
 
-We model viral spread using a renewal-equation framework \citep{heesterbeek1996concept}, which allows us to model the current incidence of infected individuals (i.e., the the rate at which new infections occur in the population) as a function of previous incidence and how infectiousness of an infected individual varies over the course of their infection.
+We model viral spread using a renewal-equation framework \citep{heesterbeek1996concept}, which allows us to model the current incidence of infected individuals (i.e., the rate at which new infections occur in the population) as a function of previous incidence and how infectiousness of an infected individual varies over the course of their infection.
 We divide incidence $i$ into two categories -- $i_a$ and $i_s$ -- corresponding to incidence of asymptomatic and symptomatic cases, respectively.
@@
 \begin{equation}
-\frac{q}{1-q}=\frac{\mathcal R_a S(t) \int_0^\infty i_a(t-\tau) g_a(\tau) \mathrm{d}\tau}{\mathcal R_s S(t) \int_0^\infty i_s(t-\tau) g_s(\tau) \mathrm{d}\tau},
+\frac{q}{1-q}=\frac{\mathcal R_a S(t) \int_0^\infty i_a(t-\tau) g_a(\tau) \mathrm{d}\tau}{\mathcal R_s S(t) \int_0^\infty i_s(t-\tau) g_s(\tau) \mathrm{d}\tau}.
 \end{equation}
@@
 \end{equation}
-In Supplementary Materials, we also use an ordinary differential equation model to give a concrete example of how differences in generation intervals affect both $q$ and estimates of $\mathcal R_0$.
+In Supplementary Materials, we also use an ordinary differential equation model including both asymptomatic and symptomatic cases to give a concrete example of how differences in generation intervals affect both $q$ and estimates of $\mathcal R_0$.
 
@@
 When $\bar G_a$ is smaller (larger) than $\bar G_s$, estimates based on the observed generation distribution for symptomatic cases (${\cal{R}}_0=2.5$; dashed line) are expected to over- (under-) estimate the true $\mathcal R_0$.
-Triangle assume $z=0.5$ and $\bar G_a/\bar G_s = 0.55$.
-Circle assume $z=0.5$ and $\bar G_a/\bar G_s = 1.8$.
+Triangle denotes $z=0.5$ and $\bar G_a/\bar G_s = 0.55$.
+Circle denotes $z=0.5$ and $\bar G_a/\bar G_s = 1.8$.
 Solid lines show contours for $q$ and \Ro\ values. 
@@
 When $\bar G_a$ is long compared to $\bar G_s$, then we are effectively assuming a longer mean for the overall generation interval. 
-This assumption leads to a larger estimate of \Ro\ for a fixed value of $r$. (see~\citep{park_2019practical}).
+This assumption leads to a larger estimate of \Ro\ for a fixed value of $r$ (see~\citep{park_2019practical}).
 Conversely, when $\bar G_a < \bar G_s$, generation intervals are shorter, leading to lower estimates of the epidemic strength \Ro.
@@
 Here we highlight the need to characterize the generation-interval distribution for asymptomatic transmission, and its consequences not only for contact tracing but for estimation of the basic reproduction number of the ongoing COVID-19 outbreak~\citep{park_preprint} and of the effective proportion of asymptomatic transmission during the exponential-growth phase.
-Our reproductive number findings fit into a broader framework linking epidemc speed, strength, and generation intervals -- for a given observed speed increases in the mean generation interval imply larger reproduction number~\citep{park_2019practical}.
-\jd{Add one or two other cites, maybe starting with Wallinga Lipsitch.}
+Our reproductive number findings fit into a broader framework linking epidemc speed, strength, and generation intervals -- for a given observed speed increases in the mean generation interval imply larger reproduction number~\citep{wallinga2007generation, powers2014impact, park_2019practical}.
 
@@
 However, if asymptomatic cases tend to resolve quickly, then current estimates of ${\cal{R}}_0$ may be over-estimates of the underlying strength (Figure~\ref{fig.importance}B), and asymptomatic cases may be driving a larger fraction of secondary cases than we would expect without accounting for their differences (Figure~\ref{fig.importance}A).
+These qualitative results also apply to subclinical and undetected cases, which can depend on mildness of symptoms as well as surveillance efforts.
 
 We focus here on the exponential phase, so it is worth noting that the realized proportion of asymptomatic transmission $q$ is time-dependent, varying with dynamic changes in incidence and proportion susceptible.
-Future work might also consider the ways in which asymptomatic individuals can modulate resurgent epidemics in a networked metapopulation~\citep{watts_pnas2005}.
+Future work might also consider the ways in which asymptomatic individuals can modulate the catalysis of epidemics in a networked metapopulation~\citep{watts_pnas2005, chinazzi2020effect, du2020risk}.
 Characterizing the role of asymptomatic individuals in driving the persistence of the epidemic will be critical for assessing the post-pandemic outcome \citep{lipsitch_preprint}.

### 2020-03-10 short.body.tex
the
archive and fix typo

@@
 Here we highlight the need to characterize the generation-interval distribution for asymptomatic transmission, and its consequences not only for contact tracing but for estimation of the basic reproduction number of the ongoing COVID-19 outbreak~\citep{park_preprint} and of the effective proportion of asymptomatic transmission during the exponential-growth phase.
-Our reproductive number findings fit into a broader framework linking epidemc speed, strength, and generation intervals -- for a given observed speed increases in the mean generation interval imply larger reproduction number~\citep{wallinga2007generation, powers2014impact, park_2019practical}.
+Our reproductive number findings fit into a broader framework linking epidemic speed, strength, and generation intervals -- for a given observed speed increases in the mean generation interval imply larger reproduction number~\citep{wallinga2007generation, powers2014impact, park_2019practical}.
 
@@
 However, if asymptomatic cases tend to resolve quickly, then current estimates of ${\cal{R}}_0$ may be over-estimates of the underlying strength (Figure~\ref{fig.importance}B), and asymptomatic cases may be driving a larger fraction of secondary cases than we would expect without accounting for their differences (Figure~\ref{fig.importance}A).
-These qualitative results also apply to subclinical and undetected cases, which can depend on mildness of symptoms as well as surveillance efforts.
+These qualitative results also apply to subclinical and undetected cases, which can depend on the mildness of symptoms as well as surveillance efforts.
 

### 2020-03-10 short.body.tex
two more citations!

@@
 Here we highlight the need to characterize the generation-interval distribution for asymptomatic transmission, and its consequences not only for contact tracing but for estimation of the basic reproduction number of the ongoing COVID-19 outbreak~\citep{park_preprint} and of the effective proportion of asymptomatic transmission during the exponential-growth phase.
-Our reproductive number findings fit into a broader framework linking epidemic speed, strength, and generation intervals -- for a given observed speed increases in the mean generation interval imply larger reproduction number~\citep{wallinga2007generation, powers2014impact, park_2019practical}.
+Our reproductive number findings fit into a broader framework linking epidemic speed, strength, and generation intervals -- for a given observed speed increases in the mean generation interval imply larger reproduction number~\citep{wearing2005appropriate, roberts2007model, wallinga2007generation, powers2014impact, park_2019practical}.
 

### 2020-03-10 short.body.tex
subclinical fiddling

@@
 However, if asymptomatic cases tend to resolve quickly, then current estimates of ${\cal{R}}_0$ may be over-estimates of the underlying strength (Figure~\ref{fig.importance}B), and asymptomatic cases may be driving a larger fraction of secondary cases than we would expect without accounting for their differences (Figure~\ref{fig.importance}A).
-These qualitative results also apply to subclinical and undetected cases, which can depend on the mildness of symptoms as well as surveillance efforts.
+Note that cases do not have to be completely asymptomatic for our qualitative results to apply.
+People with mild systems unlikely to be characterized as coronavirus in a particular time and place (sometimes referred to as subclinical cases) are expected to have identical effects on transmission patterns.
 

### 2020-03-10 short.body.tex
fiddle some more

@@
 Note that cases do not have to be completely asymptomatic for our qualitative results to apply.
-People with mild systems unlikely to be characterized as coronavirus in a particular time and place (sometimes referred to as subclinical cases) are expected to have identical effects on transmission patterns.
+People with mild systems unlikely to be diagnosed in a particular time and place (sometimes referred to as subclinical cases) are expected to have identical effects on transmission patterns.
 

### 2020-03-10 short.body.tex
mild systems

@@
 Note that cases do not have to be completely asymptomatic for our qualitative results to apply.
-People with mild systems unlikely to be diagnosed in a particular time and place (sometimes referred to as subclinical cases) are expected to have identical effects on transmission patterns.
+People with mild symptoms unlikely to be diagnosed in a particular time and place (sometimes referred to as subclinical cases) are expected to affect transmission patterns in the same way.
 

### 2020-03-11 abs.tex
back

@@
-{\footnotesize We assess the impact of asymptomatic transmission on epidemic potential of novel respiratory pathogens (like COVID-19) --
-as measured both by the basic reproduction number (i.e., the expected number of secondary cases generated by an average primary case in a fully susceptible population) and the fraction of new secondary cases attributable to asymptomatic individuals.
-We show that the impact of asymptomatic transmission depends on generation intervals (i.e., time between when an individual is infected and when that individual infects another person).
+{\footnotesize 
+\section*{Background}
+
+The potential for asymptomatic carriers to transmit the virus poses a challenge for controlling the coronavirus disease 2019 (COVID-19) pandemic but their roles remain unknown.
+We assess the impact of asymptomatic transmission on epidemic potential of novel respiratory pathogens (like COVID-19).
+
+\section*{Methods}
+
+We develope a mathematical model for comparing asymptomatic and symptomatic transmission based on their generation intervals (i.e., time between when an individual is infected and when that individual infects another person).
+We measure the effect of asymptomatic transmission on the basic reproduction number (i.e., the expected number of secondary cases generated by an average primary case in a fully susceptible population) and the fraction of new secondary cases attributable to asymptomatic individuals, across a wide range of assumptions about asymptomatic transmission.
+
+\section*{Findings}
+
 If the generation-interval distribution of asymptomatic transmission differs from that of symptomatic transmission, then estimates of the basic reproduction number which do not explicitly account for asymptomatic cases may be systematically biased.
@@
 We also show that as the length of asymptomatic generation intervals increase, estimates of the realized proportion of asymptomatic transmission during the exponential phase of the epidemic decrease.
+
+\section*{Interpretation}
+
 Our analysis provides a rationale for assessing the duration of asymptomatic cases of COVID-19 in addition to their prevalence in the population.
+
+\section*{Funding}
+
+This work was supported, in part, by support from the Army Research Office to JSW (W911NF1910384).
 }

### 2020-03-15 short.body.tex
git_push

@@
 However, infected individuals who are asymptomatic yet infectious can be a critical factor in the spread of some pathogens \citep{fraser2004factors}.
-Asymptomatic individuals are hard to trace, unlikely to self-isolate, and are likely to retain normal social and travel patterns.
+Asymptomatic individuals are hard to trace, unlikely to self-isolate, and are likely to retain normal social and travel patterns \citep{quilty2020effectiveness}.
 
-There is significant ongoing interest in asymptomatic infections in COVID-19 for two major reasons. 
+There is significant ongoing interest in asymptomatic infections in COVID-19 \citep{chan2020familial, pan2020asymptomatic, tangearly} and their transmission potential \citep{bai2020presumed} for two major reasons.
 First, the proportion of infections that are asymptomatic (see~\citep{mizumoto_2020}) is critical to attempts to estimate the likely burden of severe outcomes (including mortality \citep{fauci_nejm2020}) when the virus spreads through a population.
-Second, understanding the possible role of \emph{transmission} by asymptomatic individuals is crucial to planning surveillance and control efforts \citep{fraser2004factors, bai2020presumed}.
+Second, understanding the possible role of \emph{transmission} by asymptomatic individuals is crucial to planning surveillance and control efforts \citep{fraser2004factors}.
 

### 2020-03-15 research.in.context.tex
ric

\section*{Research in context}

\subsection*{Evidence before this study}

We searched PubMed for articles published up to March 15, 2020 using terms ``2019-nCoV'', ``novel coronavirus'', ``COVID-19'', ``SARS-CoV-2'' AND ``asymptomatic''. We found several studies describing asymptomatic infection and one study suggesting transmission by an asymptomatic carrier. 
However, we found no studies describing the effect of asymptomatic transmission in estimating the basic reproduction number of COVID-19. 
To our knowledge, this is the first study to describe the effects of differences in time scales of asymptomatic and symptomatic transmission on disease dynamics.

\subsection*{Added value of this study}

We use a mathematical model to assess how the time scale of asymptomatic transmission affects the epidemic potential for COVID-like pathogens.
We compare the basic reproduction number and the proportion of secondary cases caused by asymptomatic individuals during the initial exponential growth period across a wide range of assumptions about asymptomatic transmission.
These assumptions broadly fall under two opposite scenarios: asymptomatic individuals can have fast clearance (and therefore, faster transmission) or slow viral replication (and therefore, persistent infection and slower transmission).
If asymptomatic transmission is slower than symptomatic transmission, the basic reproduction number can be underestimated if asymptomatic transmission is not explicitly taken into account.
If asymptomatic transmission is faster than symptomatic transmission, asymptomatic transmission may still account for a large fraction of secondary infection.

\subsection*{Implications of all the available evidence}

The prevalence of asymptomatic carriers of COVID-19 and their transmission potential remain unclear. 
Future research should prioritize characterizing the course of infection for asymptomatic cases and estimating their prevalence.
Current estimates that do not account for asymptomatic transmission may be systematically biased and should be refined accordingly.

### 2020-03-17 abs.tex
First cut at abstract

--- 2020-03-09 abs.tex
@@
-{\footnotesize We assess the impact of asymptomatic transmission on epidemic potential of novel respiratory pathogens (like COVID-19) --
-as measured both by the basic reproduction number (i.e., the expected number of secondary cases generated by an average primary case in a fully susceptible population) and the fraction of new secondary cases attributable to asymptomatic individuals.
-We show that the impact of asymptomatic transmission depends on generation intervals (i.e., time between when an individual is infected and when that individual infects another person).
+{\footnotesize 
+\section*{Background}
+
+The role of asymptomatic carriers to transmit virus poses challenges for control of the COVID-19 pandemic. 
+Study of asymptomatic transmission and implications for surveillance and disease burden is ongoing. 
+There has been little study of the implications of asymptomatic transmission on dynamics of disease.
+
+\section*{Methods}
+
+We use a mathematical framework to evaluate expected effects of asymptomatic transmission on the basic reproduction number (i.e., the expected number of secondary cases generated by an average primary case in a fully susceptible population) and the fraction of new secondary cases attributable to asymptomatic individuals, across a wide range of assumptions about asymptomatic transmission.
+
+\section*{Findings}
+
 If the generation-interval distribution of asymptomatic transmission differs from that of symptomatic transmission, then estimates of the basic reproduction number which do not explicitly account for asymptomatic cases may be systematically biased.
@@
 We also show that as the length of asymptomatic generation intervals increase, estimates of the realized proportion of asymptomatic transmission during the exponential phase of the epidemic decrease.
-Our analysis provides a rationale for assessing the duration of asymptomatic cases of COVID-19 in addition to their prevalence in the population.
+
+\section*{Interpretation}
+
+Our analysis shows that understanding the temporal course of asymptomatic transmission after infection can be important for assessing the importance of this route of transmission, and for disease dynamics as a whole.
+This provides an additional motivation for investigating these time distributions.
+
+\section*{Funding}
+
+This work was supported, in part, by support from the Army Research Office to JSW (W911NF1910384), and support from the Canadian Institutes of Health Research to JD.}
 }

### 2020-03-17 abs.tex
Abstract and push new compiled version

@@
 This work was supported, in part, by support from the Army Research Office to JSW (W911NF1910384), and support from the Canadian Institutes of Health Research to JD.}
-}

### 2020-03-17 research.in.context.tex
need to take a break
ok done?
Comment out last s. of ric

@@
 We found several studies describing asymptomatic infection and one study suggesting transmission by an asymptomatic carrier.
+We found one study, published on March 16, 2020, estimating the transmission rate of asymptomatic carriers of COVID-19, their prevalence, and the proportion of secondary cases caused by them.
 However, we found no studies describing the effect of asymptomatic transmission in estimating the basic reproduction number of COVID-19.
@@
 Future research should prioritize characterizing the course of infection for asymptomatic cases and estimating their prevalence.
-Current estimates that do not account for asymptomatic transmission may be systematically biased and should be refined accordingly.
+%% Current estimates that do not account for asymptomatic transmission may be systematically biased and should be refined accordingly.

### 2020-03-17 abs.tex
Update abs.tex
push

@@
 
-We use a mathematical framework to evaluate expected effects of asymptomatic transmission on the basic reproduction number (i.e., the expected number of secondary cases generated by an average primary case in a fully susceptible population) and the fraction of new secondary cases attributable to asymptomatic individuals, across a wide range of assumptions about asymptomatic transmission.
+We use a mathematical framework to evaluate expected effects of asymptomatic transmission on the basic reproduction number ${\cal{R}}_0$ (i.e., the expected number of secondary cases generated by an average primary case in a fully susceptible population) and the fraction of new secondary cases attributable to asymptomatic individuals, across a wide range of assumptions about asymptomatic transmission.
 
@@
 Our analysis shows that understanding the temporal course of asymptomatic transmission after infection can be important for assessing the importance of this route of transmission, and for disease dynamics as a whole.
-This provides an additional motivation for investigating these time distributions.
+This provides an additional motivation for investigating both the prevalence and relative duration of asymptomatic transmission.
 

### 2020-03-17 research.in.context.tex
push

@@
 We compare the basic reproduction number and the proportion of secondary cases caused by asymptomatic individuals during the initial exponential growth period across a wide range of assumptions about asymptomatic transmission.
-These assumptions broadly fall under two opposite scenarios: asymptomatic individuals can have fast clearance (and therefore, faster transmission) or slow viral replication (and therefore, persistent infection and slower transmission).
+These assumptions broadly fall under two opposite scenarios: asymptomatic individuals can have fast clearance (and therefore, faster transmission) or persistent infection (and therefore, slower transmission).
 If asymptomatic transmission is slower than symptomatic transmission, the basic reproduction number can be underestimated if asymptomatic transmission is not explicitly taken into account.

### 2020-03-17 short.body.tex
need to take a break
ok done?
push

@@
 Second, understanding the possible role of \emph{transmission} by asymptomatic individuals is crucial to planning surveillance and control efforts \citep{fraser2004factors}.
+Given that 86\% of the cases were undocumted in Wuhan prior to travel restriction and may account for 79\% of infection of severe, symptomatic cases \citep{Lieabb3221}, asymptomatic cases are also likely to play important role in the transmission of COVID-19.
 
@@
 Generation intervals, which are defined as the time between when an individual is infected and when that individual infects another person \citep{svensson2007note}, depend on the natural history of infection:
-individuals with subclinical infections may have fast clearance and short generation intervals, or slow viral reproduction and long generation intervals (cf. \citep{roberts2007model}).
+individuals with subclinical infections may have fast clearance and short generation intervals, or persistent infection and long generation intervals (cf. \citep{roberts2007model}).
 The shape of the generation-interval distribution characterizes the relationship between the epidemic growth rate $r$ and the reproduction number \citep{wallinga2007generation}.

### 2020-03-17 short.body.tex
Update short.body.tex

@@
 Second, understanding the possible role of \emph{transmission} by asymptomatic individuals is crucial to planning surveillance and control efforts \citep{fraser2004factors}.
-Given that 86\% of the cases were undocumted in Wuhan prior to travel restriction and may account for 79\% of infection of severe, symptomatic cases \citep{Lieabb3221}, asymptomatic cases are also likely to play important role in the transmission of COVID-19.
+Given that 86\% of the cases were undocumented in Wuhan prior to travel restrictions and may account for 79\% of infection of severe, symptomatic cases \citep{Lieabb3221}, asymptomatic cases are also likely to play an important role in the transmission of COVID-19.
 

### 2020-03-17 short.body.tex
another small push

--- 2020-03-17 short.body.tex
@@
 Second, understanding the possible role of \emph{transmission} by asymptomatic individuals is crucial to planning surveillance and control efforts \citep{fraser2004factors}.
-Given that 86\% of the cases were undocumted in Wuhan prior to travel restriction and may account for 79\% of infection of severe, symptomatic cases \citep{Lieabb3221}, asymptomatic cases are also likely to play important role in the transmission of COVID-19.
+Given that 86\% of the cases were undocumented (i.e., mildly symptomatic or asymptomatic) in Wuhan prior to travel restrictions and may account for 79\% of infection of severe, symptomatic cases \citep{Lieabb3221}, asymptomatic cases are also likely to play an important role in the transmission of COVID-19.
 

### 2020-03-17 appendix.tex
stuff

@@
 \includegraphics[width=0.45\textwidth]{figheatmap_R0_03.pdf}
-\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
+\caption{EEffects of intrinsic proportion of asymptomatic transmission on the realized proportion of asymptomatic transmission and basic reproduction number, given variation in
 the mean generation interval of asymptomatic cases when generation-interval distributions are narrow. 
@@
 \includegraphics[width=0.45\textwidth]{figheatmap_R0_08.pdf}
-\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
+\caption{Effects of intrinsic proportion of asymptomatic transmission on the realized proportion of asymptomatic transmission and basic reproduction number, given variation in
 the mean generation interval of asymptomatic cases when generation-interval distributions are wide. 
@@
 \includegraphics[width=0.45\textwidth]{figheatmap_kappa_R0.pdf}
-\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
+\caption{Effects of intrinsic proportion of asymptomatic transmission on the realized proportion of asymptomatic transmission and basic reproduction number, given variation in
 the generation-interval dispersion of asymptomatic cases.

### 2020-03-17 abs.tex
simplify abstract

@@
 
-We use a mathematical framework to evaluate expected effects of asymptomatic transmission on the basic reproduction number ${\cal{R}}_0$ (i.e., the expected number of secondary cases generated by an average primary case in a fully susceptible population) and the fraction of new secondary cases attributable to asymptomatic individuals, across a wide range of assumptions about asymptomatic transmission.
+We use a mathematical framework to evaluate expected effects of asymptomatic transmission on the basic reproduction number ${\cal{R}}_0$ (i.e., the expected number of secondary cases generated by an average primary case in a fully susceptible population) and the fraction of new secondary cases attributable to asymptomatic individuals.
 
@@
 Specifically, if asymptomatic cases have a shorter generation interval than symptomatic cases, ${\cal{R}}_0$ will be over-estimated, and if they have a longer generation interval, ${\cal{R}}_0$ will be under-estimated.
-We also show that as the length of asymptomatic generation intervals increase, estimates of the realized proportion of asymptomatic transmission during the exponential phase of the epidemic decrease.
+Estimates of the realized proportion of asymptomatic transmission during the exponential phase also depend on asymptomatic generation intervals.
 
@@
 
-Our analysis shows that understanding the temporal course of asymptomatic transmission after infection can be important for assessing the importance of this route of transmission, and for disease dynamics as a whole.
+Our analysis shows that understanding the temporal course of asymptomatic transmission can be important for assessing the importance of this route of transmission, and for disease dynamics.
 This provides an additional motivation for investigating both the prevalence and relative duration of asymptomatic transmission.

### 2020-03-17 appendix.tex
some updates

@@
 \includegraphics[width=0.45\textwidth]{figheatmap_R0_03.pdf}
-\caption{EEffects of intrinsic proportion of asymptomatic transmission on the realized proportion of asymptomatic transmission and basic reproduction number, given variation in
+\caption{Effects of intrinsic proportion of asymptomatic transmission on the realized proportion of asymptomatic transmission and basic reproduction number, given variation in
 the mean generation interval of asymptomatic cases when generation-interval distributions are narrow. 

### 2020-03-17 lancetID/asymp_LID.tex
format

\documentclass[12pt]{article}
\usepackage[top=1in,left=1in, right = 1in, footskip=1in]{geometry}
\usepackage{url}
\usepackage{graphicx}
%\usepackage{adjustbox}

\usepackage{xcolor}
\usepackage{lineno}\renewcommand\thelinenumber{\color{gray}\arabic{linenumber}}
% \linenumbers

\newcommand{\req}[1]{(\ref{#1})}

\newcommand{\eref}[1]{Eq.~\ref{eq:#1}}
\newcommand{\fref}[1]{Fig.~\ref{fig:#1}}
\newcommand{\Fref}[1]{Fig.~\ref{fig:#1}}
\newcommand{\sref}[1]{Sec.~\ref{#1}}
\newcommand{\frange}[2]{Fig.~\ref{fig:#1}--\ref{fig:#2}}
\newcommand{\tref}[1]{Table~\ref{tab:#1}}
\newcommand{\tlab}[1]{\label{tab:#1}}
\newcommand{\seminar}{SE\mbox{$^m$}I\mbox{$^n$}R}

\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}

%\usepackage{lineno}
%\linenumbers

\usepackage[pdfencoding=auto, psdextra]{hyperref}

\usepackage[superscript,biblabel]{cite}

\bibliographystyle{vancouver}
\date{\today}

\usepackage{xspace}
\newcommand*{\ie}{i.e.\@\xspace}

\usepackage{color}

\usepackage{xspace}
\newcommand{\Rx}[1]{\ensuremath{{\mathcal R}_{#1}}\xspace}
% https://tex.stackexchange.com/questions/86565/drawbacks-of-xspace
% avoid double-\xspace
\newcommand{\Ro}{\ensuremath{{\mathcal R}_{0}}\xspace}
\newcommand{\RR}{\ensuremath{{\mathcal R}}}
\newcommand{\Rhat}{\ensuremath{{\hat\RR}}}
\newcommand{\tsub}[2]{#1_{{\textrm{\tiny #2}}}}

\newcommand{\comment}[3]{\textcolor{#1}{\textbf{[#2: }\textsl{#3}\textbf{]}}}

%% \newcommand{\rev}[1]{\comment{red}{REV}{#1}}
\newcommand{\rev}[1]{}

\newcommand{\swp}[1]{\comment{magenta}{SWP}{#1}}
\newcommand{\jd}[1]{\comment{magenta}{JD}{#1}}
\newcommand{\djde}[1]{\comment{magenta}{DJDE}{#1}}
\newcommand{\bmb}[1]{\comment{magenta}{BMB}{#1}}
\newcommand{\dc}[1]{\comment{magenta}{DC}{#1}}
\newcommand{\jsw}[1]{\comment{magenta}{JSW}{#1}}
\newcommand{\mli}[1]{\comment{magenta}{MLi}{#1}}
\newcommand{\new}[1]{\textcolor{blue}{#1}}

\begin{document}

\begin{flushleft}{
	\Large
	\textbf\newline{
		The time scale of asymptomatic transmission affects estimates of epidemic potential in the COVID-19 outbreak
	}
}
\newline
\\
Sang Woo Park B.Sc.\textsuperscript{1}
Daniel M. Cornforth Ph.D.\textsuperscript{2}
Jonathan Dushoff Ph.D.\textsuperscript{3,4,5,*}
Joshua S.\ Weitz Ph.D.\textsuperscript{2,6,*}
\\
\bigskip
\textbf{1} Department of Ecology and Evolutionary Biology, Princeton University, Princeton, NJ, USA
\\
\textbf{2} School of Biological Sciences, Georgia Institute of Technology, Atlanta, GA, USA
\\
\textbf{3} Department of Biology, McMaster University, Hamilton, Ontario, Canada
\\
\textbf{4} Department of Mathematics and Statistics, McMaster University, Hamilton, Ontario, Canada
\\
\textbf{5} M.\,G.\,DeGroote Institute for Infectious Disease Research, McMaster University, Hamilton, Ontario, Canada
\\
\textbf{6} School of Biological Sciences, Georgia Institute of Technology, Atlanta, GA, USA
\\
\textbf{7} School of Physics, Georgia Institute of Technology, Atlanta, GA, USA
\\
\bigskip

*Corresponding authors:\\
Jonathan Dushoff\\
https://mac-theobio.github.io/dushoff.html\\
dushoff@mcmaster.ca
\newline\newline
Joshua S.\ Weitz\\
http://ecotheory.biology.gatech.edu\\
jsweitz@gatech.edu\\

\end{flushleft}

\pagebreak

\section*{Abstract}

\subsection*{Background}

The role of asymptomatic carriers to transmit virus poses challenges for control of the COVID-19 pandemic. 
Study of asymptomatic transmission and implications for surveillance and disease burden is ongoing. 
There has been little study of the implications of asymptomatic transmission on dynamics of disease.

\subsection*{Methods}

We use a mathematical framework to evaluate expected effects of asymptomatic transmission on the basic reproduction number ${\cal{R}}_0$ (i.e., the expected number of secondary cases generated by an average primary case in a fully susceptible population) and the fraction of new secondary cases attributable to asymptomatic individuals.

\subsection*{Findings}

If the generation-interval distribution of asymptomatic transmission differs from that of symptomatic transmission, then estimates of the basic reproduction number which do not explicitly account for asymptomatic cases may be systematically biased. 
Specifically, if asymptomatic cases have a shorter generation interval than symptomatic cases, ${\cal{R}}_0$ will be over-estimated, and if they have a longer generation interval, ${\cal{R}}_0$ will be under-estimated.
Estimates of the realized proportion of asymptomatic transmission during the exponential phase also depend on asymptomatic generation intervals.

\subsection*{Interpretation}

Our analysis shows that understanding the temporal course of asymptomatic transmission can be important for assessing the importance of this route of transmission, and for disease dynamics. This provides an additional motivation for investigating both the prevalence and relative duration of asymptomatic transmission.

\subsection*{Funding}

This work was supported, in part, by support from the Army Research Office to JSW (W911NF1910384), and support from the Canadian Institutes of Health Research to JD.

\pagebreak

\section*{Research in context}

\subsection*{Evidence before this study}

We searched PubMed for articles published up to March 15, 2020 using terms ``2019-nCoV'', ``novel coronavirus'', ``COVID-19'', ``SARS-CoV-2'' AND ``asymptomatic''. We found several studies describing asymptomatic infection and one study suggesting transmission by an asymptomatic carrier. 
We found one study, published on March 16, 2020, estimating the transmission rate of asymptomatic carriers of COVID-19, their prevalence, and the proportion of secondary cases caused by them.
However, we found no studies describing the effect of asymptomatic transmission in estimating the basic reproduction number of COVID-19.
To our knowledge, this is the first study to describe the effects of differences in time scales of asymptomatic and symptomatic transmission on disease dynamics.

\subsection*{Added value of this study}

We use a mathematical model to assess how the time scale of asymptomatic transmission affects the epidemic potential for COVID-like pathogens.
We compare the basic reproduction number and the proportion of secondary cases caused by asymptomatic individuals during the initial exponential growth period across a wide range of assumptions about asymptomatic transmission.
These assumptions broadly fall under two opposite scenarios: asymptomatic individuals can have fast clearance (and therefore, faster transmission) or persistent infection (and therefore, slower transmission).
If asymptomatic transmission is slower than symptomatic transmission, the basic reproduction number can be underestimated if asymptomatic transmission is not explicitly taken into account.
If asymptomatic transmission is faster than symptomatic transmission, asymptomatic transmission may still account for a large fraction of secondary infection.

\subsection*{Implications of all the available evidence}

The prevalence of asymptomatic carriers of COVID-19 and their transmission potential remain unclear. 
Future research should prioritize characterizing the course of infection for asymptomatic cases and estimating their prevalence.
%% Current estimates that do not account for asymptomatic transmission may be systematically biased and should be refined accordingly.

\pagebreak

\section{Introduction}

In an epidemic, symptomatic cases are the predominant focus of treatment and usually represent the bulk of reported cases. 
However, infected individuals who are asymptomatic yet infectious can be a critical factor in the spread of some pathogens \cite{fraser2004factors}.
Asymptomatic individuals are hard to trace, unlikely to self-isolate, and are likely to retain normal social and travel patterns \cite{quilty2020effectiveness}.

There is significant ongoing interest in asymptomatic infections in COVID-19 \cite{chan2020familial, pan2020asymptomatic, tangearly} and their transmission potential \cite{bai2020presumed} for two major reasons.
First, the proportion of infections that are asymptomatic (see~Mizumoto \textit{et al.}\cite{mizumoto_2020}) is critical to attempts to estimate the likely burden of severe outcomes (including mortality \cite{fauci_nejm2020}) when the virus spreads through a population.
Second, understanding the possible role of \emph{transmission} by asymptomatic individuals is crucial to planning surveillance and control efforts \cite{fraser2004factors}.
Given that 86\% of the cases were undocumented (i.e., mildly symptomatic or asymptomatic) in Wuhan prior to travel restrictions and may account for 79\% of infection of severe, symptomatic cases \cite{Lieabb3221}, asymptomatic cases are also likely to play an important role in the transmission of COVID-19.

Here, we focus on a third effect. 
If asymptomatic cases are important for transmission, they also have the potential to affect estimates of key parameters of disease spread such as the basic reproduction number ${\cal{R}}_0$ (i.e., the expected number of secondary cases generated by an average primary case in a fully susceptible population \cite{anderson1992infectious}). 
Thus, we investigate the relationship between individual-level features of asymptomatic cases (e.g., the probability that an infection is asymptomatic, asymptomatic case duration, transmission by asymptomatic individuals) to dynamics at the population scale.

\section{Methods}

We model viral spread using a renewal-equation framework \cite{heesterbeek1996concept}, which allows us to model the current incidence of infected individuals (i.e., the rate at which new infections occur in the population) as a function of previous incidence and how infectiousness of an infected individual varies over the course of their infection.
We divide incidence $i$ into two categories -- $i_a$ and $i_s$ -- corresponding to incidence of asymptomatic and symptomatic cases, respectively.
Newly infected individuals that are either asymptomatically or symptomatically infected can transmit the disease to others, but they differ in their intrinsic reproduction numbers, ${\cal{R}}_a$ and ${\cal{R}}_s$, respectively, as well as intrinsic generation-interval distributions \cite{champredon2015intrinsic}, $g_a(\tau)$ and $g_s(\tau)$.
Generation intervals, which are defined as the time between when an individual is infected and when that individual infects another person \cite{svensson2007note}, depend on the natural history of infection:
individuals with subclinical infections may have fast clearance and short generation intervals, or persistent infection and long generation intervals (cf. Roberts and Heesterbeek\cite{roberts2007model}).
The shape of the generation-interval distribution characterizes the relationship between the epidemic growth rate $r$ and the reproduction number \cite{wallinga2007generation}.

Neglecting births and loss of immunity on the time scale of the outbreak, the dynamics of susceptibles and incidence are:
\begin{eqnarray}
\dot{S}&=&-i(t) \\
i(t)&=&\mathcal R_a S(t) \int_0^\infty i_a(t-\tau) g_a(\tau) \mathrm{d}\tau + \mathcal R_s S(t) \int_0^\infty i_s(t-\tau) g_s(\tau) \mathrm{d}\tau.
\end{eqnarray}
The basic reproduction number of this system is:
\begin{equation}
{\cal{R}}_{0}= p {\cal{R}}_a + (1-p) {\cal{R}}_s,
\end{equation}
where $p$ is the proportion of \emph{incident cases} that are asymptomatic: $i_a(t) = p i(t)$.
The corresponding intrinsic generation-interval distribution of an average infected individual is given by: 
\begin{equation}
g(\tau) = z g_a(\tau) + (1-z) g_s(\tau),
\end{equation}
where we define the ``intrinsic'' proportion of asymptomatic transmission $z$ as the relative contribution of asymptomatic cases to the basic reproduction number:
\begin{equation}
z = p {\cal{R}}_a/{\cal{R}}_{0}.
\end{equation}
Note that the intrinsic proportion of symptomatic transmission satisfies
\begin{equation}
1-z = (1-p) {\cal{R}}_s/{\cal{R}}_{0}.
\end{equation}
Yet, this information is not sufficient to disentangle the role of asymptomatic cases, i.e., what fraction of secondary cases can be ascribed to \emph{realized} transmission from asymptomatic cases vs.~symptomatic cases?

The intrinsic proportion of asymptomatic transmission $z$ is a useful benchmark, but does not necessarily reflect the realized proportion of asymptomatic transmission, unless both types of infection have the same generation-interval distribution.
The \emph{realized} proportion of asymptomatic transmission, $q$ at time $t$ is given by:
\begin{equation}
\frac{q}{1-q}=\frac{\mathcal R_a S(t) \int_0^\infty i_a(t-\tau) g_a(\tau) \mathrm{d}\tau}{\mathcal R_s S(t) \int_0^\infty i_s(t-\tau) g_s(\tau) \mathrm{d}\tau}.
\end{equation}
During the period of exponential growth, we assume $S$ remains nearly constant, and $i(t)$ is proportional to $\exp(r t)$, and simplify by recalling that $i_a(t)= p i(t)$, $i_s(t)=(1-p)i(t)$ such that: 
\begin{equation}
\frac{q}{1-q}=\left(\frac{z}{1-z}\right)\frac{\delta_a}{\delta_s}.
\label{eq.qratio}
\end{equation}
Here, $\delta_c$ for each of the two classes is the average ``discount'' of a new infection -- the average relative contribution of a secondary infection to the epidemic, taking exponential growth into account:
\begin{equation}
	\delta_c = \int_0^\infty \exp(-r\tau) g_c(\tau) \mathrm{d}\tau.
\end{equation}
$\delta_c<1$ and grows smaller as the generation interval grows longer.
Thus, the realized proportion of asymptomatic infections will be increased (resp., decreased) if transmission is relatively faster (slower) along the asymptomatic route.
The discount $\delta$ also depends on the relative variation in the generation-interval distribution, the ``dispersion'': more variation in generation intervals leads to more opportunities for fast spread and thus to higher values of $\delta$ (similar to shorter average generation intervals).

To estimate the effects of assumptions about asymptomatic transmission on the importance of asymptomatic transmission and estimates of the basic reproduction number ${\cal{R}}_0$, we parameterize the generation interval distributions of asymptomatic and symptomatic cases based on their means, $\bar G_a$ and $\bar G_s$, and dispersions, $\kappa_a$ and $\kappa_s$.
We assume that generation intervals are gamma distributed, and we set the dispersion to be equal to the squared coefficient of variation (the reciprocal of the gamma shape parameter, see Supplementary Materials).
We assume that epidemic growth rate $r$ and the generation-interval distribution of symptomatic case are known, using parameter values that are consistent with earlier COVID-19 models \cite{park_preprint}: $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=0.5$.
We infer values of $q$ using Eq.~\req{eq.qratio} and ${\cal{R}}_0$ using the Euler-Lotka equation \cite{lotka1907relation}:
\begin{equation}
\frac{1}{\mathcal R_0} = \int \exp(-r \tau) g(\tau) \mathrm{d} \tau.
\end{equation}
In Supplementary Materials, we also use an ordinary differential equation model including both asymptomatic and symptomatic cases to give a concrete example of how differences in generation intervals affect both $q$ and estimates of $\mathcal R_0$.

\section{Results}

\begin{figure*}[b!]
\begin{center}
\includegraphics[width=0.45\textwidth]{../figheatmap.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.45\textwidth]{../figheatmap_R0.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the realized proportion of asymptomatic transmission and basic reproduction number, given variation in
the mean generation interval of asymptomatic cases. 
(A) Increasing the speed of asymptomatic transmission (shorter generation intervals) increases the realized proportion of asymptomatic transmission, $q$.
(B) Increasing the speed of asymptomatic transmission (shorter generation intervals) decreases the basic reproduction number ${\cal{R}}_0$.
When $\bar G_a$ is smaller (larger) than $\bar G_s$, estimates based on the observed generation distribution for symptomatic cases (${\cal{R}}_0=2.5$; dashed line) are expected to over- (under-) estimate the true $\mathcal R_0$.
Triangle denotes $z=0.5$ and $\bar G_a/\bar G_s = 0.55$.
Circle denotes $z=0.5$ and $\bar G_a/\bar G_s = 1.8$.
Solid lines show contours for $q$ and \Ro\ values. 
Here, we assume $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.5$.
\label{fig.importance}}
\end{center}
\end{figure*}

We explore the effects of different assumptions about speed and effectiveness of asymptomatic transmission on the importance of asymptomatic transmission and estimates of the basic reproduction number ${\cal{R}}_0$, using a gamma assumption (see Methods).
Across the range of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.importance}A).
As the relative mean generation interval of asymptomatic transmission, $\bar G_a/\bar G_s$, increases, $q$ decreases because symptomatic cases are more likely to have short generation intervals (i.e., fast transmission events), which drive the spread during the growth phase (Figure~\ref{fig.importance}A).

Figure~\ref{fig.importance}B shows the effect of different assumptions about the generation interval of asymptomatic cases, $\bar G_a$, on the basic reproduction number ${\cal{R}}_0$.
When $\bar G_a$ is long compared to $\bar G_s$, then we are effectively assuming a longer mean for the overall generation interval. 
This assumption leads to a larger estimate of \Ro\ for a fixed value of $r$ (see~\cite{park_2019practical}).
Conversely, when $\bar G_a < \bar G_s$, generation intervals are shorter, leading to lower estimates of the epidemic strength \Ro. Both of these effects are stronger when the intrinsic proportion of asymptomatic transmission $z$ increases (and disappear as $z\to0$).
Therefore, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread (white, dashed line in Figure~\ref{fig.importance}B), it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
The qualitative effects of $z$ and $\bar G_a/\bar G_s$ on $q$ and ${\cal{R}}_0$ remain robust when we assume narrower ($\kappa_s = \kappa_a = 0.3$; Figure~S1) or wider ($\kappa_s = \kappa_a = 0.8$; Figure~S2) generation intervals.

Relative generation-interval dispersion of asymptomatic cases $\kappa_a/\kappa_s$ have similar, but smaller, effects on $q$ and ${\cal{R}}_0$ (Figure~S3).
Since a wider generation-interval distribution has a higher proportion of early transmission than a narrow one, increasing the generation-interval dispersion has qualitatively similar effects on $q$ and ${\cal{R}}_0$ as decreasing the mean generation interval.

\section{Discussion}

Much is still unknown about the time scale and effectiveness of asymptomatic transmission in COVID-19.
Here we highlight the need to characterize the generation-interval distribution for asymptomatic transmission, and its consequences not only for contact tracing but for estimation of the basic reproduction number of the ongoing COVID-19 outbreak~\cite{park_preprint} and of the effective proportion of asymptomatic transmission during the exponential-growth phase.
Our reproductive number findings fit into a broader framework linking epidemic speed, strength, and generation intervals -- for a given observed speed increases in the mean generation interval imply larger reproduction number~\cite{wearing2005appropriate, roberts2007model, wallinga2007generation, powers2014impact, park_2019practical}.

If asymptomatic infections are more persistent than symptomatic ones, the mean generation interval for COVID-19 could be longer than estimated from symptomatic cases alone -- possibly increasing ${\cal{R}}_0$ (Figure~\ref{fig.importance}B).
However, if asymptomatic cases tend to resolve quickly, then current estimates of ${\cal{R}}_0$ may be over-estimates of the underlying strength (Figure~\ref{fig.importance}B), and asymptomatic cases may be driving a larger fraction of secondary cases than we would expect without accounting for their differences (Figure~\ref{fig.importance}A).
Note that cases do not have to be completely asymptomatic for our qualitative results to apply.
People with mild symptoms unlikely to be diagnosed in a particular time and place (sometimes referred to as subclinical cases) are expected to affect transmission patterns in the same way.

We focus here on the exponential phase, so it is worth noting that the realized proportion of asymptomatic transmission $q$ is time-dependent, varying with dynamic changes in incidence and proportion susceptible. 
Future work might also consider the ways in which asymptomatic individuals can modulate the catalysis of epidemics in a networked metapopulation~\cite{watts_pnas2005, chinazzi2020effect, du2020risk}.
Characterizing the role of asymptomatic individuals in driving the persistence of the epidemic will be critical for assessing the post-pandemic outcome \cite{lipsitch_preprint}.

\mbox{}\\
\noindent
\textbf{Acknowledgments:} The authors thank John Glasser for comments
and discussion on the manuscript, particularly on short notice.

\noindent
\textbf{Data Availabililty:} All code is available at https://github.com/mac-theobio/coronavirus\_asymptomatic.

\noindent
\textbf{Competing interests:} We declare no competing interests.

\pagebreak

\section*{Supplementary Materials}
\renewcommand\thefigure{S\arabic{figure}}
\renewcommand\theequation{S\arabic{equation}}
\setcounter{figure}{0}
\setcounter{equation}{0}

\subsection*{A gamma approximation to generation-interval distributions}

Assuming that the intrinsic generation-interval distribution for each class (asymptomatic and symptomatic) follows a gamma distribution with mean $\bar G_c$ and dispersion $\kappa_c$, the average discount of a new infection can be written as:
\begin{equation}
\delta_c = (1 + \kappa_c r \bar G_c)^{-1/\kappa_c},
\end{equation}
which shows that the average discount increases with smaller $\bar G_c$ and with larger $\kappa_c$.
Then, the odds of the realized proportion of asymptomatic transmission can be written as:
\begin{equation}
\frac{q}{1-q}=\left(\frac{z}{1-z}\right)\left[\frac{(1 + \kappa_a r \bar G_a)^{-1/\kappa_a}}{(1 + \kappa_s r \bar G_s)^{-1/\kappa_s}}\right],
\end{equation}
where $\bar G_a$ and $\bar G_s$ are the mean generation intervals for asymptomatic and symptomatic cases, and $\kappa_a$ and $\kappa_s$ are the generation-interval dispersions for asymptomatic and symptomatic cases.
Finally, the basic reproduction number is calculated by using the Euler-Lotka equation:
\begin{equation}
\mathcal R_0 = \left(z (1 + \kappa_a r \bar G_a)^{-1/\kappa_a} + (1-z) (1 + \kappa_s r \bar G_s)^{-1/\kappa_s}\right)^{-1}.
\end{equation}

\subsection*{A compartmental model for asymptomatic/symptomatic cases}

Consider an SEIR model variant in which an infected individual can be either asymptomatic, $I_a$, or symptomatic, $I_s$.
We note that $I_a$ and $I_s$ represent prevalence (i.e., the total number of currently infectious individuals) of asymptomatic and symptomatic individuals; these quantities are different from $i_s$ and $i_s$ that we present in the main text, which represent incidence (i.e., the rate at which new cases are generated)  of asymptomatic and symptomatic individuals.
While both cases can recover, we assume that only symptomatic cases can lead to fatalities, denoted
by the $D$ category.
In total, the dynamics of susceptibles, exposed, infectious, recovered, and dead are:
\begin{eqnarray}
\dot{S}&=&-\beta_a S I_a -\beta_s S I_s \\
\dot{E}&=&\beta_a S I_a +\beta_s S I_s -\gamma_e E\\
\dot{I}_a&=&p\gamma_e E-\gamma_a I_a\\
\dot{I}_s&=&(1-p)\gamma_e E-\gamma_s I_s\\
\dot{R}&=&\gamma_a I_a + (1-f)\gamma_s I_s \\
\dot{D}&=&f\gamma_s I_s.
\end{eqnarray}
Here, $\beta_a$ and $\beta_s$ denote transmission rates,
$\gamma_e$ denotes the transition from exposed to infectious,
$p$ is the fraction of asymptomatic cases that
are generated for each exposed individual,
$1-p$ is the fraction of symptomatic cases that
are generated for each exposed individual,
$\gamma_a$ and $\gamma_s$ denote recovery rates,
and $f$ denotes the case fatality ratio for symptomatic cases.

Given that the number of infected individuals increase exponentially at rate $r$ initially, the equations
for the infectious cases can be rewritten given the ansatz
$E(t)=c_e e^{rt}$,
$I_a(t)=c_a e^{rt}$,
$I_s(t)=c_s e^{rt}$.
Then, it follows that 
\begin{eqnarray}
r c_a&=&p\gamma_e c_e-\gamma_a c_a,\\
r c_s&=&(1-p)\gamma_e c_e-\gamma_s c_s,
\end{eqnarray} 
which implies that
\begin{equation}
\frac{c_a}{c_s}=\frac{p}{1-p}\left[\frac{r+\gamma_s}{r+\gamma_a}\right].
\end{equation}
This shows that the prevalence of asymptomatic and symptomatic individuals is different from $p$ and $1-p$ because prevalence measures the individuals that are currently infectious and does not account for individuals that have already recovered.
Finally, the ratio of secondary case production caused by asymptomatic vs.~symptomatic
individuals during the exponential phase should be
\begin{equation}
\frac{q}{1-q} = \left(\frac{\beta_a}{\beta_s}\right)\frac{p}{1-p}\left[\frac{r+\gamma_s}{r+\gamma_a}\right],
\end{equation}
where $q$ is the fraction of new secondary cases caused by
asymptomatic individuals.

The basic reproduction number of this system is:
\begin{equation}
{\cal{R}}_{0}= p {\cal{R}}_a + (1-p) {\cal{R}}_s,
\end{equation}
where 
\begin{eqnarray}
{\cal{R}}_a &=& \frac{\beta_a}{\gamma_a},\\
{\cal{R}}_s &=& \frac{\beta_s}{\gamma_s}.
\end{eqnarray}
The generation-interval distributions for asymptomatic and symptomatic individuals follow the same functional form as the corresponding generation-interval distribution for a single-type SEIR model since both asymptomatic and symptomatic individuals have exponentially distributed latent and infectious periods \cite{svensson2015influence}:
\begin{eqnarray}
g_a(\tau) &=& \frac{\gamma_e \gamma_a}{\gamma_e - \gamma_a} \left(\exp(-\gamma_a \tau) - \exp(-\gamma_e \tau)\right),\\
g_s(\tau) &=& \frac{\gamma_e \gamma_s}{\gamma_e - \gamma_s} \left(\exp(-\gamma_s \tau) - \exp(-\gamma_e \tau)\right).
\end{eqnarray}
It immediately follows that 
\begin{equation}
\left(\frac{z}{1-z}\right)\left[\frac{\int_0^\infty \exp(-r\tau) g_a(\tau) \mathrm{d}\tau}{\int_0^\infty \exp(-r\tau) g_s(\tau) \mathrm{d}\tau}\right] = \left(\frac{\beta_a}{\beta_s}\right)\frac{p}{1-p}\left[\frac{r+\gamma_s}{r+\gamma_a}\right],
\end{equation}
where $z = p {\cal{R}}_a/{\cal{R}}_{0}$ and $1-z=(1-p) {\cal{R}}_s/{\cal{R}}_{0}$ -- compare to Eq.~(8) in the main text.

\pagebreak

\subsection*{Supplementary figures}

\begin{figure*}[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{../figheatmap_03.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.45\textwidth]{../figheatmap_R0_03.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the realized proportion of asymptomatic transmission and basic reproduction number, given variation in
the mean generation interval of asymptomatic cases when generation-interval distributions are narrow. 
Here, we assume $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.3$.
See Figure 1 in the main text for figure caption.
}
\end{center}
\end{figure*}

\pagebreak

\begin{figure*}[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{../figheatmap_08.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.45\textwidth]{../figheatmap_R0_08.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the realized proportion of asymptomatic transmission and basic reproduction number, given variation in
the mean generation interval of asymptomatic cases when generation-interval distributions are wide. 
Here, we assume $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.8$.
See Figure 1 in the main text for figure caption.
}
\end{center}
\end{figure*}

\pagebreak

\begin{figure*}[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{../figheatmap_kappa.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.45\textwidth]{../figheatmap_kappa_R0.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the realized proportion of asymptomatic transmission and basic reproduction number, given variation in
the generation-interval dispersion of asymptomatic cases.
(A) Wide/narrow generation intervals of asymptomatic cases increase/decrease the relevance of asymptomatic cases, $q$.
(B) Wide/narrow generation intervals of asymptomatic cases decrease/increase the basic reproduction number ${\cal{R}}_0$.
Solid lines show contours for $q$ and \Ro\ values.
Here, we assume $1/r=7$ days, $\bar G_s=\bar G_a=8$ days, and $\kappa_s=0.5$.
}
\end{center}
\end{figure*}

\pagebreak

\bibliography{coronavirus_abbv.bib}

\end{document}

### 2020-03-17 lancetID/asymp_LID.tex
k
fine

@@
 When $\bar G_a$ is long compared to $\bar G_s$, then we are effectively assuming a longer mean for the overall generation interval. 
-This assumption leads to a larger estimate of \Ro\ for a fixed value of $r$ (see~\cite{park_2019practical}).
+This assumption leads to a larger estimate of \Ro\ for a fixed value of $r$ (see~Park \textit{et al.}\cite{park_2019practical}).
 Conversely, when $\bar G_a < \bar G_s$, generation intervals are shorter, leading to lower estimates of the epidemic strength \Ro.
@@
 and discussion on the manuscript, particularly on short notice. 
-
+\newline\newline
 \noindent
-\textbf{Data Availabililty:} All code is available at https://github.com/mac-theobio/coronavirus\_asymptomatic.
-
+\textbf{Data Availabililty:} All code is available at\\
+https://github.com/mac-theobio/coronavirus\_asymptomatic.
+\newline\newline
 \noindent

### 2020-03-23 abs.tex
some updates
git_push
Light edits to abstract

@@
 {\footnotesize
-\section*{Background}
 
-The role of asymptomatic carriers to transmit virus poses challenges for control of the COVID-19 pandemic. 
-Study of asymptomatic transmission and implications for surveillance and disease burden is ongoing. 
-There has been little study of the implications of asymptomatic transmission on dynamics of disease.
-
-\section*{Methods}
-
+The role of asymptomatic carriers in transmission poses challenges for control of the COVID-19 pandemic. 
+Study of asymptomatic transmission and implications for surveillance and disease burden are ongoing,  
+but there has been little study of the implications of asymptomatic transmission on dynamics of disease.
 We use a mathematical framework to evaluate expected effects of asymptomatic transmission on the basic reproduction number ${\cal{R}}_0$ (i.e., the expected number of secondary cases generated by an average primary case in a fully susceptible population) and the fraction of new secondary cases attributable to asymptomatic individuals.
-
-\section*{Findings}
-
 If the generation-interval distribution of asymptomatic transmission differs from that of symptomatic transmission, then estimates of the basic reproduction number which do not explicitly account for asymptomatic cases may be systematically biased.
@@
 Estimates of the realized proportion of asymptomatic transmission during the exponential phase also depend on asymptomatic generation intervals.
+Our analysis shows that understanding the temporal course of asymptomatic transmission can be important for assessing the importance of this route of transmission, and for disease dynamics.
+This provides an additional motivation for investigating both the importance and relative duration of asymptomatic transmission.
 
-\section*{Interpretation}
+\subsection*{Keywords}
 
-Our analysis shows that understanding the temporal course of asymptomatic transmission can be important for assessing the importance of this route of transmission, and for disease dynamics.
-This provides an additional motivation for investigating both the prevalence and relative duration of asymptomatic transmission.
+SARS-CoV-2, COVID-19, coronavirus disease, asymptomatic transmission, basic reproduction number
 
-\section*{Funding}
+\subsection*{Funding}
 

### 2020-04-04 rev/response.tex
done?

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}

\usepackage{color}

\usepackage{lmodern}
\usepackage{amssymb,amsmath}

\newcommand{\rR}{\mbox{$r$--$\cal R$}}
\newcommand{\RR}{\ensuremath{{\cal R}}}
\newcommand{\RRhat}{\ensuremath{{\hat \cal R}}}
\newcommand{\Rx}[1]{\ensuremath{{\cal R}_{#1}}} 
\newcommand{\Ro}{\Rx{0}}
\newcommand{\Reff}{\Rx{\mathit{eff}}}
\newcommand{\Tc}{\ensuremath{C}}

\newcommand{\rev}{\subsection*}
\newcommand{\revtext}{\textsf}
\setlength{\parskip}{\baselineskip}
\setlength{\parindent}{0em}

\newcommand{\comment}[3]{\textcolor{#1}{\textbf{[#2: }\textsl{#3}\textbf{]}}}
\newcommand{\jd}[1]{\comment{cyan}{JD}{#1}}
\newcommand{\swp}[1]{\comment{magenta}{SWP}{#1}}
\newcommand{\dc}[1]{\comment{blue}{DC}{#1}}
\newcommand{\jsw}[1]{\comment{green}{JSW}{#1}}
\newcommand{\hotcomment}[1]{\comment{red}{HOT}{#1}}

\begin{document}

\noindent Dear Editor:

Thank you for the chance to revise and resubmit our manuscript. 
Below please find our responses to reviewers.

\rev{Reviewer \#1}

\revtext{Summary: This article describes the implications of asymptomatic transmission of COVID-19 for estimating the overall growth of the outbreak during the exponential phase and frames these results in terms of the generation time of asymptomatic cases relative to symptomatic cases.  The central result is intuitive and, as a modeler, I have frequently found myself trying to explain this tendency to colleagues over the past few weeks.  It is useful to see a rigorously developed example here for helping to frame the conversation and guide adjustments to ongoing modeling work.  However, some of the methods require additional clarification and additional discussion is needed to help increase the accessibility of the findings to a broader audience. Specific comments follow.}

Thank you very much!

\revtext{It might be useful to clarify explicitly in the main text that differences in generation time can occur irrespective of differences in transmissibility (as is shown in equations S17 and S18).  For example, asymptomatic cases may be equally infectious to symptomatic cases in the early stages of their infection, but simply recover more quickly, which would lower the generation time for symptomatic vs. asymptomatic cases.  It might be useful to also note in the discussion how differences in infectiousness might layer on top of differences in duration to change estimates of R0.}

We have clarified this point in the following sentence:

``The differences in the generation-interval distributions between asymptomatic and symptomatic cases can be caused by the differences in the natural history of infection irrespective of their transmissibility:
Individuals with asymptomatic infections may recover faster and have short generation intervals, or have persistent infection and long generation intervals.''

\revtext{At present, I think your method implicitly assumes that transmissibility is the same for symptomatic and asymptomatic cases as their r value is the same.}

We do not assume that their transmissibility is the same; the differences in their transmissilibity is modeled by the differences in their intrinsic reproduction numbers $\mathcal R_a$ and $\mathcal R_s$ as well as their generation-interval distributions $g_a(\tau)$ nad $g_s(\tau)$. The exponential growth rate $r$ is the resuling growth rate due to combination of asymptomatic and symptomatic transmission. This growth rate is different from what we would get if we only have asymptomatic or symptomatic individuals. We added the following sentence to clarify this point:

``During the period of exponential growth, we assume $S$ remains nearly constant, and $i(t)$ is proportional to $\exp(r t)$;
here, the observed exponential growth rate $r$ is an ``average'' of the exponential growth rates we would observe if there were only asymptomatic ($p=1$) or symptomatic ($p=0$) cases.''

\revtext{Please be explicit in the methods section about how the naïve estimation of R0 is done (presumably using equation 10) and also provide an expanded equation for the 'corrected' estimation using the stratified generation times. Right now, the clearest description is in the caption of figure 1.  I think you mean to say that the naïve estimate of R0 is based on the generation time of symptomatic cases using the Lotka-Voltera estimation method (equation 10) and assumes that this interval is similar for symptomatic and asymptomatic cases.}

We have added the following sentences:

``We infer values of $q$ using Eq.~(8) and ${\cal{R}}_0$ using the Euler-Lotka equation:
\begin{equation}
1/\mathcal R_0 = \int \exp(-r \tau) \left(z g_a(\tau) + (1-z) g_s(\tau)\right) \mathrm{d} \tau.
\end{equation}
We compare this with the naive estimate of the basic reproduction number that assumes that the generation-interval distributions of the asymptomatic and symptomatic cases are identical:
\begin{equation}
1/\mathcal R_{\tiny \textrm{naive}} = \int \exp(-r \tau) g_s(\tau) \mathrm{d} \tau.
\end{equation}''

\revtext{Top of page 5: provide an example about how we might expect the distribution of generation-intervals to vary between symptomatic vs. asymptomatic infections}

We explain the potential differences earlier as suggested:

``The differences in the generation-interval distributions between asymptomatic and symptomatic cases can be caused by the differences in the natural history of infection irrespective of their transmissilibility:
Individuals with subclinical infections may recover faster and have short generation intervals, or have persistent infection and long generation intervals.''

\revtext{Figure 1:
-In the caption, please state 'For both panels, the triangle…'
-Panel B) Please rename the dashed line something like 'naïve R0' so that it is clear that the contours reflect the corrected reproduction number and we understand why the regions on the left side of the dashed line says underestimated and the right side says overestimated.  It took me a while to realize that the dashed line was the naïve estimate so I thought that the colors were reversed.}

Done. We also added the following sentence in the figure caption:

``Dashed line represents the naive estimate that assumes $\bar G_a = \bar G_s$. ''

\revtext{In the discussion, the authors could note that inaccurate estimation of R0 could impact estimates of control efforts needed to interrupt (or appreciably reduce) transmission.}

We have added the following sentence:

``The biases in the estimates of ${\cal{R}}_0$ will necessarily bias the estimates of the amount of intervention required to control the epidemic.''

\revtext{Although not strictly necessary, it might be useful for the authors to provide a table defining the parameters used in the equations somewhere, as at times I had to go back and forth through the article to remind myself of how things were defined.  This could be a supplementary table.}

Done. We introduce the table when we introduce the model:

``Neglecting births and loss of immunity on the time scale of the outbreak, the dynamics of susceptibles and incidence are (see Table~S1 for parameter definitions)''

\rev{Reviewer \#2}

\revtext{This is a clearly-written, insightful manuscript that shows mathematically and through simulation how R0 estimates for SARS-CoV-2 can be biased if asymptomatic individuals are not taken into consideration. Specifically, if asymptomatic individuals differ from symptomatic individuals in their generation interval distribution, then R0 could be considerably over- or under-estimated. This is fundamentally because estimation of R0 values from observed intrinsic growth rates of an epidemic relies on specification of the generation interval (the time between infection and onward transmission). If these differ between symptomatic and asymptomatically infected individuals (which they very much may), then R0 estimates that assume the generation interval is that of symptomatic individuals could be severely biased.
I have only a couple of very minor suggestions. This manuscript, overall, is excellent and very clearly presented.}

Thank you very much!

\revtext{1. This may be overkill, but near equation (1), explicitly state that i(t) = i_a(t) + i_s(t)?}

Done.

``Neglecting births and loss of immunity on the time scale of the outbreak, the dynamics of susceptibles and incidence are:
\begin{eqnarray}
\dot{S}&=&-i(t), \\
i(t)&=&\mathcal R_a S(t) \int_0^\infty i_a(t-\tau) g_a(\tau) \mathrm{d}\tau + \mathcal R_s S(t) \int_0^\infty i_s(t-\tau) g_s(\tau) \mathrm{d}\tau,
\end{eqnarray}
where $i(t) = i_a(t) + i_s(t)$.''

\revtext{2. Indicate below equation 10 that the ode model in the supplement is an SEIR model}

Done.

``In Supplementary Materials, we also use an ordinary differential equation model (SEIR model) including both asymptomatic and symptomatic cases to give a concrete example of how differences in generation intervals affect both $q$ and estimates of $\mathcal R_0$.''

\revtext{3. Figure 1A: it may be more helpful to see the difference between realized proportion and intrinsic proportion as the heatmap color, rather than the realized proportion}

We have added the figure to the supplementary file with the following sentence in the main text:

``In Figure~S1, we present the same figure but showing differences between the realized and the intrinsic proportion of asymptomatic transmission, $q-z$.''

\end{document}

### 2020-04-04 appendix.tex
done?

@@
 \renewcommand\theequation{S\arabic{equation}}
+\renewcommand\thetable{S\arabic{table}}
 \setcounter{figure}{0}
 \setcounter{equation}{0}
+\setcounter{table}{0}
 
@@
 
+\subsection*{Supplementary table}
+
+\begin{table}[!ht]
+\begin{center}
+\begin{tabular}{|l|l|}
+\hline
+Parameter & Definition\\
+\hline
+$S(t)$ & proportion of susceptible individuals\\
+$i(t)$ & total incidence\\
+$i_a(t)$ & incidence of asymptomatic cases\\
+$i_s(t)$ & incidence of symptomatic cases\\
+$\mathcal R_0$ & basic reproduction number\\
+$\mathcal R_a$ & asymptomatic intrinsic reproduction number\\
+$\mathcal R_s$ & symptomatic intrinsic reproduction number\\
+$g(\tau)$ & intrinsic generation-interval distribution\\
+$g_a(\tau)$ & asymptomatic intrinsic generation-interval distribution\\
+$g_s(\tau)$ & symptomatic intrinsic generation-interval distribution\\
+$\bar G_a$ & mean asymptomatic generation interval\\
+$\bar G_s$ & mean symptomatic generation interval\\
+$\kappa_a$ & asymptomatic generation-interval dispersion\\
+$\kappa_s$ & symptomatic generation-interval dispersion\\
+$p$ & proportion of incident cases that are asymptomatic\\
+$z$ & intrinsic proportion of asymptomatic transmission\\
+$q$ & realized proportion of asymptomatic transmission\\
+$r$ & exponential growth rate\\
+\hline
+\end{tabular}
+\caption{
+Model parameters and definitions
+}
+\end{center}
+\end{table}
+
+\pagebreak
+
 \subsection*{Supplementary figures}
+
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics[width=0.8\textwidth]{figheatmap_diff.pdf}
+\caption{Differences in the realized and the intrinsic proportions of asymptomatic transmission.
+See Figure 1 in the main text for figure caption.
+}
+\end{center}
+\end{figure*}
+
+\pagebreak
 

### 2020-04-04 figheatmap_R0.R

@@ -36,7 +36,7 @@ g0 <- ggplot(figdata) +
   geom_contour(aes(relG, z, z=R0), col="white", bins=9) +
   geom_vline(xintercept=1, lty=2, col="white", lwd=0.8) +
   # geom_point(aes(x=1, y=0), size=8, col="black", stroke=1, shape=1) +
-  annotate(geom="text", x=0.96, y=0.11, label="$\\mathcal{R}_0=2.5$", col="white", angle=90) +
+  annotate(geom="text", x=0.96, y=0.27, label="$\\textrm{Naive estimate},\\,\\mathcal{R}_0=2.5$", col="white", angle=90) +
   annotate(geom="text", x=1*sqrt(2), y=0.03, label="underestimated", col="white") +
   annotate(geom="text", x=1/sqrt(2), y=0.03, label="overestimated", col="white") +
   annotate(geom="point", x=0.55, y=0.5, col="white", shape=21, size=4, fill="white") +

### 2020-04-04 figheatmap_diff.R

@@ -1,0 +1,54 @@
+library(emdbook)
+library(ggplot2); theme_set(theme_bw())
+
+r <- 1/7
+G_s <- 8
+kappa_s <- 0.5
+kappa_a <- 0.5
+
+z <- seq(0.01, 0.99, by=0.01)
+relG <- exp(seq(log(0.5), log(2), by=0.005))
+
+qodds <- apply2d(
+  "*", 
+  z/(1-z),
+  (1 + kappa_s * r * G_s)^(1/kappa_s)/(1 + kappa_a * r * relG * G_s)^(1/kappa_a)
+)
+
+qvals <- qodds/(1+qodds)
+
+figdata <- data.frame(
+  qdiff=c(qvals)-rep(z, length(relG)),
+  z=rep(z, length(relG)),
+  relG=rep(relG, each=length(z))
+)
+
+zexample <- 0.5
+relg1 <- 0.55
+q1 <- (1 + kappa_s * r * G_s)^(1/kappa_s)/(1 + kappa_a * r * relg1 * G_s)^(1/kappa_a)
+q1/(1+q1)
+
+relg2 <- 1.8
+q2 <- (1 + kappa_s * r * G_s)^(1/kappa_s)/(1 + kappa_a * r * relg2 * G_s)^(1/kappa_a)
+q2/(1+q2)
+
+g0 <- ggplot(figdata) +
+  geom_raster(aes(relG, z, fill=qdiff)) +
+  geom_contour(aes(relG, z, z=qdiff), col="white") +
+  scale_x_log10("Relative mean asymptomatic generation interval, $G_a/G_s$", expand=c(0, 0),
+                     breaks=c(0.5, 1, 2)) +
+  scale_y_continuous("Intrinsic proportion of asymptomatic transmission, $z$", expand=c(0, 0),
+                     limits=c(0, 1),
+                     breaks=0:10/10) +
+  scale_fill_gradientn("$q-z$", colors=c("black", "#8a0072", "#cf2661", "#f66d4e", "#ffb34a", "#f9f871", "#f5f3b5"),
+                       limits=c(-0.2, 0.2),
+                       breaks=c(-0.2, -0.1, 0, 0.1, 0.2) ) +
+  ggtitle("Differences in the realized and the intrinsic\nproportions of asymptomatic transmission") +
+  theme(
+    legend.key.height = unit(1.5, "cm")
+  )
+
[…]

### 2020-04-04 rev/response.tex
done??

@@
 For example, asymptomatic cases may be equally infectious to symptomatic cases in the early stages of their infection, but simply recover more quickly, which would lower the generation time for symptomatic vs.
-asymptomatic cases.
-It might be useful to also note in the discussion how differences in infectiousness might layer on top of differences in duration to change estimates of R0.}
+asymptomatic cases.}
 
@@
 Individuals with asymptomatic infections may recover faster and have short generation intervals, or have persistent infection and long generation intervals.''
+
+\revtext{It might be useful to also note in the discussion how differences in infectiousness might layer on top of differences in duration to change estimates of R0.}
+
+Differences in infectiousness is captured by the differences in their intrinsic reproduction numbers $\mathcal R_a$ and $\mathcal R_s$, and therefore their intrinsic proportion of transmission $z$ and $1-z$; this is already explained in the paper.
 
@@
 
-\revtext{1. This may be overkill, but near equation (1), explicitly state that i(t) = i_a(t) + i_s(t)?}
+\revtext{1. This may be overkill, but near equation (1), explicitly state that $i(t) = i_a(t) + i_s(t)$?}
 

### 2020-04-04 rev/response.tex
typo

@@
 
-We do not assume that their transmissibility is the same; the differences in their transmissilibity is modeled by the differences in their intrinsic reproduction numbers $\mathcal R_a$ and $\mathcal R_s$ as well as their generation-interval distributions $g_a(\tau)$ nad $g_s(\tau)$.
-The exponential growth rate $r$ is the resuling growth rate due to combination of asymptomatic and symptomatic transmission.
+We do not assume that their transmissibility is the same; the differences in their transmissibility is modeled by the differences in their intrinsic reproduction numbers $\mathcal R_a$ and $\mathcal R_s$ as well as their generation-interval distributions $g_a(\tau)$ and $g_s(\tau)$.
+The exponential growth rate $r$ is the resulting growth rate due to combination of asymptomatic and symptomatic transmission.
 This growth rate is different from what we would get if we only have asymptomatic or symptomatic individuals.
@@
 
-\revtext{Please be explicit in the methods section about how the naïve estimation of R0 is done (presumably using equation 10) and also provide an expanded equation for the 'corrected' estimation using the stratified generation times.
+\revtext{Please be explicit in the methods section about how the naive estimation of R0 is done (presumably using equation 10) and also provide an expanded equation for the 'corrected' estimation using the stratified generation times.
 Right now, the clearest description is in the caption of figure 1.
-I think you mean to say that the naïve estimate of R0 is based on the generation time of symptomatic cases using the Lotka-Voltera estimation method (equation 10) and assumes that this interval is similar for symptomatic and asymptomatic cases.}
+I think you mean to say that the naive estimate of R0 is based on the generation time of symptomatic cases using the Lotka-Voltera estimation method (equation 10) and assumes that this interval is similar for symptomatic and asymptomatic cases.}
 
@@
 
-``The differences in the generation-interval distributions between asymptomatic and symptomatic cases can be caused by the differences in the natural history of infection irrespective of their transmissilibility:
-Individuals with subclinical infections may recover faster and have short generation intervals, or have persistent infection and long generation intervals.''
+``The differences in the generation-interval distributions between asymptomatic and symptomatic cases can be caused by the differences in the natural history of infection irrespective of their transmissibility:
+Individuals with asymptomatic infections may recover faster and have short generation intervals, or have persistent infection and long generation intervals.''
 
@@
 -In the caption, please state 'For both panels, the triangle…'
--Panel B) Please rename the dashed line something like 'naïve R0' so that it is clear that the contours reflect the corrected reproduction number and we understand why the regions on the left side of the dashed line says underestimated and the right side says overestimated.
-It took me a while to realize that the dashed line was the naïve estimate so I thought that the colors were reversed.}
+-Panel B) Please rename the dashed line something like 'naive R0' so that it is clear that the contours reflect the corrected reproduction number and we understand why the regions on the left side of the dashed line says underestimated and the right side says overestimated.
+It took me a while to realize that the dashed line was the naive estimate so I thought that the colors were reversed.}
 

### 2020-04-05 rev/response.tex
done?

@@
 ``During the period of exponential growth, we assume $S$ remains nearly constant, and $i(t)$ is proportional to $\exp(r t)$;
-here, the observed exponential growth rate $r$ is an ``average'' of the exponential growth rates we would observe if there were only asymptomatic ($p=1$) or symptomatic ($p=0$) cases.''
+here, the observed exponential growth rate $r$ is an average of the exponential growth rates we would observe if there were only asymptomatic ($p=1$) or symptomatic ($p=0$) cases.''
 
@@
 \begin{equation}
-1/\mathcal R_0 = \int \exp(-r \tau) \left(z g_a(\tau) + (1-z) g_s(\tau)\right) \mathrm{d} \tau.
+\frac{1}{\mathcal R_0} = \int \exp(-r \tau) \left(z g_a(\tau) + (1-z) g_s(\tau)\right) \mathrm{d} \tau.
 \end{equation}
@@
 \begin{equation}
-1/\mathcal R_{\tiny \textrm{naive}} = \int \exp(-r \tau) g_s(\tau) \mathrm{d} \tau.
+\frac{1}{\mathcal R_{\tiny \textrm{naive}}} = \int \exp(-r \tau) g_s(\tau) \mathrm{d} \tau.
 \end{equation}''

### 2020-04-05 abs.tex
done?

@@
 SARS-CoV-2, COVID-19, coronavirus disease, asymptomatic transmission, basic reproduction number
-
-\subsection*{Funding}
-
-This work was supported, in part, by support from the Army Research Office to JSW (W911NF1910384), and support from the Canadian Institutes of Health Research to JD.}
+}

### 2020-04-05 acknowledge.tex
back
done?

--- 2020-03-05 acknowledge.tex
@@
 and discussion on the manuscript, particularly on short notice. 
-This work was supported, in part,
-by support from the Army Research Office (W911NF1910384).
+The authors thank multiple reviewers for their feedback.
+Research effort by JSW was enabled
+by support from grants from the Simons Foundation (SCOPE Award ID 329108), the Army Research
+Office (W911NF1910384), National Institutes of Health (1R01AI46592-01),
+and National Science Foundation (1806606 and 1829636). JD was supported, in part, by
+grants from the Canadian Institutes of Health Research.
 
 \noindent
-\textbf{Data Availabililty:} All code is available at weitzgroup.github.io.
+\textbf{Data Availabililty:} All code is available at \url{https://github.com/mac-theobio/coronavirus_asymptomatic}.

### 2020-04-05 figheatmap_R0.tex
done?

@@
-% Created by tikzDevice version 0.12.3 on 2020-03-09 13:46:06
+% Created by tikzDevice version 0.12.3 on 2020-04-05 15:12:58
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (164.30, 56.62) {$\mathcal{R}_0=2.5$};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (164.30, 99.05) {$\textrm{Naive estimate},\,\mathcal{R}_{\tiny\textrm{naive}}=2.5$};
 

### 2020-04-05 short.body.tex
done?

--- 2020-03-17 short.body.tex
@@
 Second, understanding the possible role of \emph{transmission} by asymptomatic individuals is crucial to planning surveillance and control efforts \citep{fraser2004factors}.
-Given that 86\% of the cases were undocumted in Wuhan prior to travel restriction and may account for 79\% of infection of severe, symptomatic cases \citep{Lieabb3221}, asymptomatic cases are also likely to play important role in the transmission of COVID-19.
+Given that 86\% of the cases were undocumented (i.e., mildly symptomatic or asymptomatic) in Wuhan prior to travel restrictions and may account for 79\% of infection in severe, symptomatic cases \citep{Lieabb3221}, asymptomatic cases are also likely to play an important role in the transmission of COVID-19.
 
@@
 We divide incidence $i$ into two categories -- $i_a$ and $i_s$ -- corresponding to incidence of asymptomatic and symptomatic cases, respectively.
-Newly infected individuals that are either asymptomatically or symptomatically infected can transmit the disease to others, but they differ in their intrinsic reproduction numbers, ${\cal{R}}_a$ and ${\cal{R}}_s$, respectively, as well as intrinsic generation-interval distributions \citep{champredon2015intrinsic}, $g_a(\tau)$ and $g_s(\tau)$.
-Generation intervals, which are defined as the time between when an individual is infected and when that individual infects another person \citep{svensson2007note}, depend on the natural history of infection:
-individuals with subclinical infections may have fast clearance and short generation intervals, or persistent infection and long generation intervals (cf. \citep{roberts2007model}).
-The shape of the generation-interval distribution characterizes the relationship between the epidemic growth rate $r$ and the reproduction number \citep{wallinga2007generation}.
+Newly infected individuals that are either asymptomatically or symptomatically infected can transmit the disease to others, but they may differ in their intrinsic reproduction numbers, ${\cal{R}}_a$ and ${\cal{R}}_s$, respectively, as well as intrinsic generation-interval distributions \citep{champredon2015intrinsic}, $g_a(\tau)$ and $g_s(\tau)$.
+Generation intervals, which are defined as the time between when an individual is infected and when that individual infects another person \citep{svensson2007note}, characterize the relationship between the epidemic growth rate $r$ and the reproduction number \citep{wallinga2007generation}.
+The differences in the generation-interval distributions between asymptomatic and symptomatic cases can be caused by the differences in the natural history of infection irrespective of their transmissibility:
+Individuals with asymptomatic infections may recover faster and have short generation intervals, or have persistent infection and long generation intervals (cf. \citep{roberts2007model}).
 
-Neglecting births and loss of immunity on the time scale of the outbreak, the dynamics of susceptibles and incidence are:
+Neglecting births and loss of immunity on the time scale of the outbreak, the dynamics of susceptibles and incidence are (see Table~S1 for parameter definitions):
 \begin{eqnarray}
-\dot{S}&=&-i(t) \\
-i(t)&=&\mathcal R_a S(t) \int_0^\infty i_a(t-\tau) g_a(\tau) \mathrm{d}\tau + \mathcal R_s S(t) \int_0^\infty i_s(t-\tau) g_s(\tau) \mathrm{d}\tau.
+\dot{S}&=&-i(t), \\
+i(t)&=&\mathcal R_a S(t) \int_0^\infty i_a(t-\tau) g_a(\tau) \mathrm{d}\tau + \mathcal R_s S(t) \int_0^\infty i_s(t-\tau) g_s(\tau) \mathrm{d}\tau,
 \end{eqnarray}
+where $i(t) = i_a(t) + i_s(t)$.
 The basic reproduction number of this system is:
@@
 \end{equation}
-During the period of exponential growth, we assume $S$ remains nearly constant, and $i(t)$ is proportional to $\exp(r t)$, and simplify by recalling that $i_a(t)= p i(t)$, $i_s(t)=(1-p)i(t)$ such that:
+During the period of exponential growth, we assume $S$ remains nearly constant, and $i(t)$ is proportional to $\exp(r t)$;
+here, the observed exponential growth rate $r$ is an average of the exponential growth rates we would observe if there were only asymptomatic ($p=1$) or symptomatic ($p=0$) cases.
+We then simplify by recalling that $i_a(t)= p i(t)$, $i_s(t)=(1-p)i(t)$ such that: 
 \begin{equation}
@@
 Thus, the realized proportion of asymptomatic infections will be increased (resp., decreased) if transmission is relatively faster (slower) along the asymptomatic route.
-The discount $\delta$ also depends on the relative variation in the generation-interval distribution, the ``dispersion'': more variation in generation intervals leads to more opportunities for fast spread and thus to higher values of $\delta$ (similar to shorter average generation intervals).
+The discount $\delta$ also depends on the relative variation in the generation-interval distribution, the ``dispersion'': More variation in generation intervals leads to more opportunities for fast spread and thus to higher values of $\delta$ (similar to shorter average generation intervals).
 
-To estimate the effects of assumptions about asymptomatic transmission on the importance of asymptomatic transmission and estimates of the basic reproduction number ${\cal{R}}_0$, we parameterize the generation interval distributions of asymptomatic and symptomatic cases based on their means, $\bar G_a$ and $\bar G_s$, and dispersions, $\kappa_a$ and $\kappa_s$.
+To estimate the effects of assumptions about asymptomatic transmission on the inferred importance of asymptomatic transmission and estimates of the basic reproduction number ${\cal{R}}_0$, we parameterize the generation interval distributions of asymptomatic and symptomatic cases based on their means, $\bar G_a$ and $\bar G_s$, and dispersions, $\kappa_a$ and $\kappa_s$.
 We assume that generation intervals are gamma distributed, and we set the dispersion to be equal to the squared coefficient of variation (the reciprocal of the gamma shape parameter, see Supplementary Materials).
@@
 \begin{equation}
-\frac{1}{\mathcal R_0} = \int \exp(-r \tau) g(\tau) \mathrm{d} \tau.
+\frac{1}{\mathcal R_0} = \int \exp(-r \tau) \left(z g_a(\tau) + (1-z) g_s(\tau)\right) \mathrm{d} \tau.
 \end{equation}
-In Supplementary Materials, we also use an ordinary differential equation model including both asymptomatic and symptomatic cases to give a concrete example of how differences in generation intervals affect both $q$ and estimates of $\mathcal R_0$.
+We compare this with the naive estimate of the basic reproduction number that assumes that the generation-interval distributions of the asymptomatic and symptomatic cases are identical:
+\begin{equation}
+\frac{1}{\mathcal R_{\tiny \textrm{naive}}} = \int \exp(-r \tau) g_s(\tau) \mathrm{d} \tau.
+\end{equation}
+In Supplementary Materials, we also use an ordinary differential equation model (SEIR model) including both asymptomatic and symptomatic cases to give a concrete example of how differences in generation intervals affect both $q$ and estimates of $\mathcal R_0$.
 
@@
 When $\bar G_a$ is smaller (larger) than $\bar G_s$, estimates based on the observed generation distribution for symptomatic cases (${\cal{R}}_0=2.5$; dashed line) are expected to over- (under-) estimate the true $\mathcal R_0$.
-Triangle denotes $z=0.5$ and $\bar G_a/\bar G_s = 0.55$.
-Circle denotes $z=0.5$ and $\bar G_a/\bar G_s = 1.8$.
+For both panels, the circle denotes $z=0.5$ and $\bar G_a/\bar G_s = 0.55$ whereas the triangle denotes $z=0.5$ and $\bar G_a/\bar G_s = 1.8$.
 Solid lines show contours for $q$ and \Ro\ values. 
+The dashed line represents the naive estimate that assumes $\bar G_a = \bar G_s$.
 Here, we assume $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.5$.
@@
 Across the range of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.importance}A).
-As the relative mean generation interval of asymptomatic transmission, $\bar G_a/\bar G_s$, increases, $q$ decreases because symptomatic cases are more likely to have short generation intervals (i.e., fast transmission events), which drive the spread during the growth phase (Figure~\ref{fig.importance}A).
+As the relative mean generation interval of asymptomatic transmission, $\bar G_a/\bar G_s$, increases, $q$ decreases because symptomatic cases are more likely to have short generation intervals, which drive the spread during the growth phase (Figure~\ref{fig.importance}A).
+In Figure~S1, we present the same figure but showing differences between the realized and the intrinsic proportion of asymptomatic transmission, $q-z$.
 
-Figure~\ref{fig.importance}B shows the effect of different assumptions about the generation interval of asymptomatic cases, $\bar G_a$, on the basic reproduction number ${\cal{R}}_0$.
+Figure~\ref{fig.importance}B shows the effect of different assumptions about the generation interval of asymptomatic cases, $\bar G_a$, on the estimated basic reproduction number ${\cal{R}}_0$.
 When $\bar G_a$ is long compared to $\bar G_s$, then we are effectively assuming a longer mean for the overall generation interval. 
@@
 Therefore, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread (white, dashed line in Figure~\ref{fig.importance}B), it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
-The qualitative effects of $z$ and $\bar G_a/\bar G_s$ on $q$ and ${\cal{R}}_0$ remain robust when we assume narrower ($\kappa_s = \kappa_a = 0.3$; Figure~S1) or wider ($\kappa_s = \kappa_a = 0.8$; Figure~S2) generation intervals.
+The qualitative effects of $z$ and $\bar G_a/\bar G_s$ on $q$ and ${\cal{R}}_0$ remain robust when we assume narrower ($\kappa_s = \kappa_a = 0.3$; Figure~S2) or wider ($\kappa_s = \kappa_a = 0.8$; Figure~S3) generation intervals.
 
-Relative generation-interval dispersion of asymptomatic cases $\kappa_a/\kappa_s$ have similar, but smaller, effects on $q$ and ${\cal{R}}_0$ (Figure~S3).
+Relative generation-interval dispersion of asymptomatic cases $\kappa_a/\kappa_s$ have similar, but smaller, effects on $q$ and ${\cal{R}}_0$ (Figure~S4).
 Since a wider generation-interval distribution has a higher proportion of early transmission than a narrow one, increasing the generation-interval dispersion has qualitatively similar effects on $q$ and ${\cal{R}}_0$ as decreasing the mean generation interval.
@@
 
-If asymptomatic infections are more persistent than symptomatic ones, the mean generation interval for COVID-19 could be longer than estimated from symptomatic cases alone -- possibly increasing ${\cal{R}}_0$ (Figure~\ref{fig.importance}B).
+If asymptomatic infections are more persistent than symptomatic ones, the mean generation interval for COVID-19 could be longer than estimated from symptomatic cases alone -- possibly causing ${\cal{R}}_0$ to be underestimated (Figure~\ref{fig.importance}B).
 However, if asymptomatic cases tend to resolve quickly, then current estimates of ${\cal{R}}_0$ may be over-estimates of the underlying strength (Figure~\ref{fig.importance}B), and asymptomatic cases may be driving a larger fraction of secondary cases than we would expect without accounting for their differences (Figure~\ref{fig.importance}A).
+The biases in the estimates of ${\cal{R}}_0$ will necessarily bias the estimates of the amount of intervention required to control the epidemic.
 Note that cases do not have to be completely asymptomatic for our qualitative results to apply.

### 2020-04-05 figheatmap_R0.R

@@ -36,7 +36,7 @@ g0 <- ggplot(figdata) +
   geom_contour(aes(relG, z, z=R0), col="white", bins=9) +
   geom_vline(xintercept=1, lty=2, col="white", lwd=0.8) +
   # geom_point(aes(x=1, y=0), size=8, col="black", stroke=1, shape=1) +
-  annotate(geom="text", x=0.96, y=0.27, label="$\\textrm{Naive estimate},\\,\\mathcal{R}_0=2.5$", col="white", angle=90) +
+  annotate(geom="text", x=0.96, y=0.29, label="$\\textrm{Naive estimate},\\,\\mathcal{R}_{\\tiny\\textrm{naive}}=2.5$", col="white", angle=90) +
   annotate(geom="text", x=1*sqrt(2), y=0.03, label="underestimated", col="white") +
   annotate(geom="text", x=1/sqrt(2), y=0.03, label="overestimated", col="white") +
   annotate(geom="point", x=0.55, y=0.5, col="white", shape=21, size=4, fill="white") +

### 2020-04-05 figheatmap.R
oops typo in supp fig

@@ -1,5 +1,6 @@
 library(emdbook)
 library(ggplot2); theme_set(theme_bw())
+library(tikzDevice)
 
 r <- 1/7
 G_s <- 8

### 2020-04-05 figheatmap_03.R

@@ -4,8 +4,8 @@ library(tikzDevice)
 
 r <- 1/7
 G_s <- 8
-kappa_s <- 0.2
-kappa_a <- 0.2
+kappa_s <- 0.3
+kappa_a <- 0.3
 
 z <- seq(0.01, 0.99, by=0.005)
 relG <- exp(seq(log(0.5), log(2), by=0.005))

### 2020-04-06 short.body.tex
Minor changes

@@
 Newly infected individuals that are either asymptomatically or symptomatically infected can transmit the disease to others, but they may differ in their intrinsic reproduction numbers, ${\cal{R}}_a$ and ${\cal{R}}_s$, respectively, as well as intrinsic generation-interval distributions \citep{champredon2015intrinsic}, $g_a(\tau)$ and $g_s(\tau)$.
-Generation intervals, which are defined as the time between when an individual is infected and when that individual infects another person \citep{svensson2007note}, characterize the relationship between the epidemic growth rate $r$ and the reproduction number \citep{wallinga2007generation}.
-The differences in the generation-interval distributions between asymptomatic and symptomatic cases can be caused by the differences in the natural history of infection irrespective of their transmissibility:
+Generation intervals, which are defined as the time between when an individual is infected and when that individual infects another person \citep{svensson2007note}, shape the relationship between the epidemic growth rate $r$ and the reproduction number \citep{wallinga2007generation}.
+The differences in the generation-interval distributions between asymptomatic and symptomatic cases can be caused by the differences in the natural history of infection:
 Individuals with asymptomatic infections may recover faster and have short generation intervals, or have persistent infection and long generation intervals (cf. \citep{roberts2007model}).
@@
 However, if asymptomatic cases tend to resolve quickly, then current estimates of ${\cal{R}}_0$ may be over-estimates of the underlying strength (Figure~\ref{fig.importance}B), and asymptomatic cases may be driving a larger fraction of secondary cases than we would expect without accounting for their differences (Figure~\ref{fig.importance}A).
-The biases in the estimates of ${\cal{R}}_0$ will necessarily bias the estimates of the amount of intervention required to control the epidemic.
+The biases in the estimates of ${\cal{R}}_0$ will necessarily bias estimates of the amount of intervention required to control the epidemic.
 Note that cases do not have to be completely asymptomatic for our qualitative results to apply.

### 2020-04-06 rev/response.tex
done

@@
 
-Differences in infectiousness is captured by the differences in their intrinsic reproduction numbers $\mathcal R_a$ and $\mathcal R_s$, and therefore their intrinsic proportion of transmission $z$ and $1-z$; this is already explained in the paper.
+Differences in infectiousness is captured by the differences in their intrinsic reproduction numbers $\mathcal R_a$ and $\mathcal R_s$, and therefore their intrinsic proportion of transmission $z$ and $1-z$.
+We added a sentence in the discussion to clarify this point:
+
+``The importance of these effects depends on the relative infectiousness of asymptomatic transmission as well as the proportion of incident cases that are asymptomatic (and therefore the intrinsic proportion of asymptomatic transmission $z$.''
 
@@
 
-``Neglecting births and loss of immunity on the time scale of the outbreak, the dynamics of susceptibles and incidence are:
-\begin{eqnarray}
-\dot{S}&=&-i(t), \\
-i(t)&=&\mathcal R_a S(t) \int_0^\infty i_a(t-\tau) g_a(\tau) \mathrm{d}\tau + \mathcal R_s S(t) \int_0^\infty i_s(t-\tau) g_s(\tau) \mathrm{d}\tau,
-\end{eqnarray}
-where $i(t) = i_a(t) + i_s(t)$.''
-
 \revtext{2. Indicate below equation 10 that the ode model in the supplement is an SEIR model}
@@
 
-``In Supplementary Materials, we also use an ordinary differential equation model (SEIR model) including both asymptomatic and symptomatic cases to give a concrete example of how differences in generation intervals affect both $q$ and estimates of $\mathcal R_0$.''
-
 \revtext{3. Figure 1A: it may be more helpful to see the difference between realized proportion and intrinsic proportion as the heatmap color, rather than the realized proportion}
 
-We have added the figure to the supplementary file with the following sentence in the main text:
+We have added this as a new figure to the supplement, referred to in the main text:
 

### 2020-04-06 short.body.tex
More discussion
done

@@
 Generation intervals, which are defined as the time between when an individual is infected and when that individual infects another person \citep{svensson2007note}, shape the relationship between the epidemic growth rate $r$ and the reproduction number \citep{wallinga2007generation}.
-The differences in the generation-interval distributions between asymptomatic and symptomatic cases can be caused by the differences in the natural history of infection:
+The differences in the generation-interval distributions between asymptomatic and symptomatic cases can be caused by the differences in the natural history of infection irrespective of their transmissibility:
 Individuals with asymptomatic infections may recover faster and have short generation intervals, or have persistent infection and long generation intervals (cf. \citep{roberts2007model}).
@@
 However, if asymptomatic cases tend to resolve quickly, then current estimates of ${\cal{R}}_0$ may be over-estimates of the underlying strength (Figure~\ref{fig.importance}B), and asymptomatic cases may be driving a larger fraction of secondary cases than we would expect without accounting for their differences (Figure~\ref{fig.importance}A).
+The importance of these effects depends on the relative infectiousness of asymptomatic transmission as well as the proportion of incident cases that are asymptomatic (and therefore the intrinsic proportion of asymptomatic transmission $z$.
 The biases in the estimates of ${\cal{R}}_0$ will necessarily bias estimates of the amount of intervention required to control the epidemic.

### 2020-04-06 rev/response.tex
typo

@@
 
-``The importance of these effects depends on the relative infectiousness of asymptomatic transmission as well as the proportion of incident cases that are asymptomatic (and therefore the intrinsic proportion of asymptomatic transmission $z$.''
+``The importance of these effects depends on the relative infectiousness of asymptomatic transmission as well as the proportion of incident cases that are asymptomatic (and therefore the intrinsic proportion of asymptomatic transmission $z$).''
 

### 2020-04-06 short.body.tex
typo

@@
 However, if asymptomatic cases tend to resolve quickly, then current estimates of ${\cal{R}}_0$ may be over-estimates of the underlying strength (Figure~\ref{fig.importance}B), and asymptomatic cases may be driving a larger fraction of secondary cases than we would expect without accounting for their differences (Figure~\ref{fig.importance}A).
-The importance of these effects depends on the relative infectiousness of asymptomatic transmission as well as the proportion of incident cases that are asymptomatic (and therefore the intrinsic proportion of asymptomatic transmission $z$.
+The importance of these effects depends on the relative infectiousness of asymptomatic transmission as well as the proportion of incident cases that are asymptomatic (and therefore the intrinsic proportion of asymptomatic transmission $z$).
 The biases in the estimates of ${\cal{R}}_0$ will necessarily bias estimates of the amount of intervention required to control the epidemic.
